\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{xurl}
\usepackage{hyperref}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue
}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\theoremstyle{remark}
\newtheorem{remark}{Remark}

\newcommand{\F}{\mathbb F}
\newcommand{\PP}{\mathbb P}
\newcommand{\RS}{\operatorname{RS}}
\newcommand{\LD}{\operatorname{LD}}
\newcommand{\eps}{\varepsilon}
\newcommand{\qline}{q_{\rm line}}

\title{A Finite-Row Threshold Theorem for \texorpdfstring{$\RS[\F_{17^{32}},H,256]$}{RS[F17^32,H,256]}}
\author{RS-MCA experimental note}
\date{2026-06-27}

\begin{document}
\maketitle

\begin{abstract}
This note packages the high-agreement tangent staircase as a clean finite-row
threshold theorem for
\[
  C=\RS[\F_{17^{32}},H,256],
  \qquad |H|=512.
\]
Under the finite-slope support-wise MCA convention used in the experimental
ledger, the target \(\eps_*=2^{-128}\) threshold is pinned exactly on the
integer grid: integer Hamming radius \(5\) is safe and integer Hamming radius
\(6\) is already unsafe.  Equivalently, with closed Hamming balls, the real
safe interval is \([0,6/512)\); the supremal transition radius is
\(6/512=3/256\), but the endpoint is unsafe.
\end{abstract}

\section{Scope and Definition Audit}
\label{sec:scope}

The public Proximity Prize page asks, for smooth-domain Reed--Solomon codes at
rates
\[
  \rho\in\{1/2,1/4,1/8,1/16\},
\]
to determine the largest radius \(\delta_C^*\) for which the MCA error is at
most \(\eps_*=2^{-128}\) \cite{ProximityPrize2026}.  The row treated here is the
rate-\(1/2\) smooth subgroup row
\[
  F=\F_{17^{32}},\qquad H\le F^*,\qquad |H|=512,\qquad k=256.
\]
The divisibility \(512\mid 17^{32}-1\) ensures such a multiplicative subgroup
exists; it is a power-of-two smooth domain.

This note proves a theorem for the finite-slope support-wise MCA normalization
used in the experimental ledger.  The exact object is:
\begin{itemize}
\item slopes are sampled from the finite line field \(F\), so the denominator is
  \(\qline=|F|=17^{32}\);
\item a closed integer Hamming radius \(r\) means agreement threshold
  \(a=n-r\);
\item a real closed radius \(\delta\) means integer radius
  \(r(\delta)=\lfloor \delta n\rfloor\), hence agreement threshold
  \(a(\delta)=n-r(\delta)\);
\item support-wise noncontainment is tested on the same support on which the
  line word is explained by a codeword.
\end{itemize}

The high-agreement note also proves the matching projective-slope and no-loss CA
numerators in the same range.  If the sampler is instead uniform on
\(\PP^1(F)\), the numerator below is unchanged in this row and the denominator is
\(|F|+1\).  The same \(5/6\) integer-radius threshold remains true because
\[
  6\cdot 2^{128}<17^{32}<17^{32}+1<7\cdot2^{128}.
\]

\begin{remark}[audit status]
The public prize page is a high-level challenge statement; companion paper
definitions control the official MCA sampler, finite/projective slope choice,
and endpoint convention.  This note therefore records an exact local theorem
and the definition match that has been checked inside this repository.  It is
not a peer-reviewed prize submission.
\end{remark}

\section{Finite-Slope Threshold}
\label{sec:threshold}

Let \(D\subset F\), \(|D|=n\), and \(C=\RS[F,D,k]\).  For an agreement threshold
\(a\), let
\[
  B_{\rm fin}(C,a)=\LD_{\rm sw}(C,a)
\]
be the largest possible number of finite slopes on a received affine line
\(f+zg\) that admit a codeword explanation on some support of size at least
\(a\), but for which \(f\) and \(g\) are not separately explained on that same
support.  The finite-slope MCA error at grid agreement \(a\) is then
\[
  \eps_{\rm mca}^{\rm fin}(C,a)=\frac{B_{\rm fin}(C,a)}{|F|}.
\]

\begin{lemma}[high-agreement tangent staircase]
\label{lem:tangent-staircase}
For \(C=\RS[F,D,k]\), \(|D|=n\), if
\[
  3a-2n\ge k,
\]
then
\[
  B_{\rm fin}(C,a)=n-a+1.
\]
For every \(k+1\le a\le n\), the lower bound
\[
  B_{\rm fin}(C,a)\ge n-a+1
\]
also holds.
\end{lemma}

\begin{proof}
This is the moving-root tangent floor and the very-high-agreement tangent
staircase from \path{experimental/notes/high_agreement/tangent_staircase.tex}.
The proof is finite and uses the MDS rigidity of Reed--Solomon codes plus a
residual-root budget.
\end{proof}

\begin{theorem}[finite-row MCA threshold]
\label{thm:f17-threshold}
Let \(H\subset\F_{17^{32}}^*\) have order \(512\), and put
\[
  C=\RS[\F_{17^{32}},H,256].
\]
Under the finite-slope support-wise MCA convention,
\[
  \eps_{\rm mca}^{\rm fin}(C,a)\le 2^{-128}
  \quad\text{if and only if}\quad
  a\ge507.
\]
Here \(a\) ranges over integer agreement thresholds \(0\le a\le512\).
Equivalently, on the integer Hamming grid, the largest safe radius is
\[
  r=5,\qquad \delta=5/512,
\]
and the first unsafe radius is
\[
  r=6,\qquad \delta=6/512=3/256.
\]
\end{theorem}

\begin{proof}
Here \(n=512\), \(k=256\), and the high-agreement condition
\[
  3a-2n\ge k
\]
is \(3a-1024\ge256\), namely \(a\ge427\).  Lemma~\ref{lem:tangent-staircase}
therefore gives
\[
  B_{\rm fin}(C,a)=513-a
  \qquad(a\ge427).
\]
In particular,
\[
  B_{\rm fin}(C,506)=7,
  \qquad
  B_{\rm fin}(C,507)=6.
\]
The exact field arithmetic is
\[
  17^{32}
  =2367911594760467245844106297320951247361,
\]
\[
  17^{32}-6\cdot2^{128}
  =326217393234836465063858652730341978625>0,
\]
and
\[
  7\cdot2^{128}-17^{32}
  =14064973686101998399515954701426232831>0.
\]
Thus \(6/17^{32}<2^{-128}<7/17^{32}\).

For every \(a\ge507\), the exact high-agreement formula gives
\(B_{\rm fin}(C,a)\le6\), hence the row is safe.  At \(a=506\), the formula gives
seven bad finite slopes, hence the row is unsafe.  For smaller \(a\), closed
balls only get larger, so the MCA error cannot decrease; those thresholds are
unsafe as well.  This proves the claimed grid transition.
\end{proof}

\begin{corollary}[closed endpoint language]
\label{cor:endpoint}
With real closed Hamming balls normalized by
\[
  r(\delta)=\lfloor512\delta\rfloor,
\]
the finite-slope support-wise MCA safe set is
\[
  0\le\delta<6/512.
\]
The supremal safe radius is
\[
  \sup\{\delta:\eps_{\rm mca}^{\rm fin}(C,\delta)\le2^{-128}\}=6/512=3/256,
\]
but the endpoint \(\delta=3/256\) is unsafe.
\end{corollary}

\begin{remark}[maximum versus supremum]
If a challenge statement asks for a maximum radius satisfying the inequality at
the endpoint, the finite real-radius maximum is not attained under this closed
endpoint convention; the largest safe grid point is \(5/512\).  If the intended
object is a supremal threshold, the transition value is \(3/256\), with the
endpoint on the unsafe side.
\end{remark}

\section{Row-Independent Compiler Target}
\label{sec:compiler}

The preceding row is an instance of a more general finite-grid compiler.  Let
\[
  R=n-k,\qquad r=n-a,\qquad B_Q=\left\lfloor\frac{Q}{2^{128}}\right\rfloor,
\]
where \(Q\) is the denominator used by the sampler or protocol term.

\begin{theorem}[high-agreement threshold compiler]
\label{thm:compiler}
Assume \(C=\RS[F,D,k]\), \(|D|=n\), and that the relevant line/MCA/CA object is
in the high-agreement tangent regime.  If
\[
  1\le B_Q\le \left\lfloor\frac{n-k}{3}\right\rfloor,
\]
then the single line/MCA/CA grid threshold at target \(2^{-128}\) is pinned
exactly:
\[
  r\le B_Q-1 \quad\Longrightarrow\quad \text{safe},
\]
while
\[
  r=B_Q \quad\Longrightarrow\quad \text{unsafe}.
\]
Under the same closed-radius convention as Corollary~\ref{cor:endpoint}, the
safe real interval is \([0,B_Q/n)\), the supremal transition radius is \(B_Q/n\),
and the endpoint is unsafe.
\end{theorem}

\begin{proof}
For \(r\le B_Q-1\), the high-agreement condition is valid because
\[
  r\le B_Q-1< B_Q\le\left\lfloor\frac{n-k}{3}\right\rfloor.
\]
The tangent staircase gives numerator \(r+1\le B_Q\).  By definition of
\(B_Q=\lfloor Q/2^{128}\rfloor\), this gives
\[
  \frac{r+1}{Q}\le 2^{-128}.
\]
At \(r=B_Q\), the same exact formula gives numerator \(B_Q+1\), and
\[
  B_Q+1>\frac{Q}{2^{128}},
\]
so the error is strictly larger than \(2^{-128}\).  Larger radii are unsafe by
monotonicity of closed balls.
\end{proof}

For the row of Theorem~\ref{thm:f17-threshold},
\[
  Q=17^{32},\qquad B_Q=6,\qquad
  \left\lfloor\frac{512-256}{3}\right\rfloor=85,
\]
so the compiler applies with substantial room.

\section{Scanner Attachment}
\label{sec:scanner}

The reproducibility attachment is generated from the repository root by running
\texttt{python3} on
\path{experimental/notes/certificate_scanner/certificate_scanner.py} with input
\path{experimental/notes/certificate_scanner/examples/f17_512_mca_only.json};
the JSON and Markdown outputs are written to
\path{experimental/notes/certificate_scanner/outputs/f17_512_mca_only.report.json}
and
\path{experimental/notes/certificate_scanner/outputs/f17_512_mca_only.report.md}.
The attached report confirms:
\[
  \left\lfloor\frac{17^{32}}{2^{128}}\right\rfloor=6,
\]
and gives the following pure line/MCA verdicts.

\begin{center}
\begin{tabular}{rrrrl}
\toprule
\(a\) & \(\sigma=a-k\) & \(r=n-a\) & exact line numerator & verdict\\
\midrule
506 & 250 & 6 & 7 & unsafe\\
507 & 251 & 5 & 6 & safe\\
508 & 252 & 4 & 5 & safe\\
512 & 256 & 0 & 1 & safe\\
\bottomrule
\end{tabular}
\end{center}

The older combined protocol scanner profile also includes an interleaved-list
term.  That is a different ledger: with one extra list term over the same
denominator, the numerator at \(a=507\) is \(6+1\), so the combined line-plus-list
ledger is unsafe at \(a=507\) and safe at \(a=508\).  The theorem in this note is
the pure finite-slope support-wise MCA threshold.

\begin{thebibliography}{9}
\bibitem{ProximityPrize2026}
The Proximity Prize.
\newblock Public challenge page.
\newblock \url{https://proximityprize.org/}, accessed 2026-06-27.
\end{thebibliography}

\end{document}
