\subsection{BC: an interior subfield split-pencil theorem}
\label{subsec:bc-next}

This subsection records a proved subcase of the base-field-normalized
split-pencil problem.  It does not prove the primitive upper census in
\cref{conj:BC}; instead it proves that the base-field term in that conjecture
is forced already by genuine interior split-pencil instances.  In particular,
the \(q\)-normalized model for split pencils is false over extension rows
unless the \(|\B|\)-scale term below is included.

\begin{theorem}[interior prefix witnesses force the base-field BC floor]
\label{thm:bc-interior-prefix-floor}
Let \(C=\RS[\F,D,K]\), where \(D\subseteq\B\subseteq\F\), \(|D|=n\), and
\(|\B|=b\).  Fix an agreement \(m\ge K\), put
\[
        \omega:=n-m,\qquad w:=m-K,
\]
and let \(d_1\) be an interior profile:
\[
        w+2\le d_1\le \left\lfloor {n-K+1\over2}\right\rfloor .
\]
Set \(m_{d_1}:=K-1+d_1\), and assume
\[
        m\le m_{d_1}\le n,\qquad        m_{d_1}+d_1\le n .
\]
For \(z=(z_1,\ldots,z_{d_1-1})\in\B^{d_1-1}\), define the
\(\B\)-valued prefix word
\[
        U_z(X)=X^{m_{d_1}}+\sum_{h=1}^{d_1-1}z_hX^{m_{d_1}-h}
        \quad\text{on }D .
\]
Then \(M_{U_z}\) has minimal shifted degree exactly \(d_1\).  Moreover, for
some \(z^*\in\B^{d_1-1}\), every shifted weak-Popov basis of \(M_{U_{z^*}}\)
with profile \((d_1,d_2)\), \(d_2=n-K+1-d_1\), has split-pencil count at
least
\[
        \binom{m_{d_1}}m
        \left\lceil \binom n{m_{d_1}} b^{-(d_1-1)}\right\rceil .
\]
Equivalently, the interior profile \(d_1\) contains a genuine
base-field-normalized floor
\[
        M_{\B}(d_1)
        =
        \binom{m_{d_1}}m\binom n{m_{d_1}}b^{-(d_1-1)}
\]
up to the indicated integer ceiling.  Thus the correct BC model at interior
profile \(d_1\) must include this \(|\B|\)-normalized term, not only the
challenge-field-generic term.
\end{theorem}

\begin{proof}
We first compute the minimal shifted degree.  The pair \((1,U_z)\) lies in
the interpolation module \(M_{U_z}\), and its shifted degree is
\[
        \max(0,\deg U_z-(K-1))=m_{d_1}-(K-1)=d_1 .
\]
Suppose conversely that \((W,N)\in M_{U_z}\) has shifted degree \(<d_1\).
Then \(\deg W<d_1\) and \(\deg N<K-1+d_1=m_{d_1}\).  The polynomial
\[
        WU_z-N
\]
vanishes on \(D\).  Its degree is at most \(m_{d_1}+d_1-1<n\), by the
hypothesis \(m_{d_1}+d_1\le n\), hence it is the zero polynomial.  If
\(W\ne0\), then the monicity of \(U_z\) gives
\(\deg(WU_z)\ge m_{d_1}\), contradicting \(\deg N<m_{d_1}\).  Therefore
\(W=0\), and then \(N=0\).  Thus no nonzero module element has shifted degree
below \(d_1\).

Now count forced split locators.  For an \(m_{d_1}\)-subset
\(M'\subseteq D\), write
\[
        \ell_{M'}(X)=\prod_{x\in M'}(X-x).
\]
Since \(D\subseteq\B\), the map taking \(M'\) to the first \(d_1-1\)
high-degree coefficients of \(\ell_{M'}\) has image in
\(\B^{d_1-1}\).  Hence some prefix value \(z^*\) has fiber size at least
\[
        \left\lceil \binom n{m_{d_1}}b^{-(d_1-1)}\right\rceil .
\]
For each \(M'\) in this fiber, the polynomial
\[
        c_{M'}:=U_{z^*}-\ell_{M'}
\]
has degree \(<K\): the leading term and the first \(d_1-1\) high-degree
coefficients cancel, and
\[
        m_{d_1}-d_1=K-1 .
\]
Thus \(c_{M'}\) agrees with \(U_{z^*}\) on all points of \(M'\).

Every \(m\)-subset \(T\subseteq M'\) is therefore an agreement support of
size \(m\).  The resulting support-codeword pairs are distinct as
\((M',T)\) varies.  Indeed, if two such pairs gave the same \(T\) and the
same explaining codeword, then
\(\ell_{M'_1}=\ell_{M'_2}\) and hence \(M'_1=M'_2\).  If the explaining
codewords were different but agreed with \(U_{z^*}\) on the same \(T\), their
difference would be a nonzero polynomial of degree \(<K\) with at least
\(|T|=m\ge K\) roots, impossible.

Therefore the agreement-support census of \(U_{z^*}\) at size \(m\) is at
least the displayed binomial multiple of the heaviest fiber size.  By
\cref{prop:lattice-split}, this census is represented inside the split-pencil
count of any shifted weak-Popov basis of \(M_{U_{z^*}}\), with monic
\(D\)-split locator \(W=\ell_{D\setminus T}\).  Since the minimal shifted
degree is \(d_1\), this is a genuine interior profile rather than the
boundary-Q profile.  The final sentence is just the asymptotic version of the
same lower bound.
\end{proof}

\begin{corollary}[rank-one line floor at the same base-field scale]
\label{cor:bc-rank-one-pole-floor}
Let \(C=\RS[\F,D,K]\), where \(D\subseteq\B\subseteq\F\), \(|D|\ge2\), put
\(b:=|\B|\), and fix \(m\ge K+1\).  Put \(w:=m-K\), and let
\(z^*\in\B^w\) be a heaviest depth \(w\) prefix value among \(m\)-subsets of
\(D\).  For any
\(\alpha\in\F\setminus(D\cup\B)\), define the simple-pole line
\[
        f_\alpha(x)={U_{z^*}(x)\over x-\alpha},\qquad
        g_\alpha(x)={-1\over x-\alpha}\qquad(x\in D).
\]
Then at least
\[
        \left\lceil \binom n{m}b^{-w}\right\rceil
\]
\(m\)-supports are non-common rank-one supports for \((f_\alpha,g_\alpha)\).
Consequently the rank-one support census feeding the BC reduction also has a
base-field floor, and this floor is not contained in the \(\B\)-rational
confinement stratum, even up to common scalar.
\end{corollary}

\begin{proof}
The heaviest-fiber pigeonhole gives at least
\[
        \left\lceil \binom n{m}b^{-w}\right\rceil
\]
members \(S\in\Fib_w(z^*)\).  For each such \(S\), \cref{prop:pole-line}
gives a slope
\[
        \zeta_S:=U_{z^*}(\alpha)-\ell_S(\alpha)
\]
for which \(f_\alpha+\zeta_Sg_\alpha\) is explained on \(S\).  In the
slope-elimination notation this means
\(\alpha(S)+\zeta_S\beta(S)=0\).  If \(g_\alpha\) were explained on \(S\) by
a polynomial \(G\) of degree \(<K\), then \((X-\alpha)G+1\) would have degree
at most \(K\), would vanish on the \(m\ge K+1\) points of \(S\), and would
take value \(1\) at \(X=\alpha\).  This is impossible.  Thus
\(\beta(S)\ne0\), so \(S\) is a non-common rank-one support.

Finally we check the confinement assertion.  If some \(\lambda\ne0\) made
\(\lambda g_\alpha(x)\in\B\) for every \(x\in D\), then for distinct
\(x,y\in D\) the ratio
\[
        {g_\alpha(x)\over g_\alpha(y)}={y-\alpha\over x-\alpha}
\]
would lie in \(\B\).  Writing this ratio as \(r\), we have \(r\ne1\), and
\[
        \alpha={y-rx\over 1-r}\in\B,
\]
contradicting \(\alpha\notin\B\).  Hence the line is genuinely
extension-valued and is outside the \(\B\)-confined rational stratum.
\end{proof}

\paragraph{What remains open.}
\Cref{thm:bc-interior-prefix-floor,cor:bc-rank-one-pole-floor} are lower-floor
and normalization theorems.  They prove that the BC ledger must contain the
base-field term \(M_{\B}(d_1)\), and they identify a genuine interior
split-pencil family attaining it.  They do not prove the needed safe-side
upper bound for primitive interior pencils.  To settle one deployed adjacent
row, a certificate must still enumerate the first-match paid cells at
\(a_0+1\), remove tangent, common-GCD, quotient-pulled-back, extension,
boundary-Q, bounded-chart, and subfield-floor contributions, and prove that
the remaining primitive split-pencil count plus the printed base-field floor
is at most the row budget \(B^*=\lfloor\varepsilon^*Q\rfloor\).  An
asymptotic proof may allow \(e^{o(n)}\) loss above logarithmic reserve, but
the deployed adjacent rows require explicit constants fitting inside their
printed bit margins.
