\section{Finite Adjacent Rung Audit}
\label{sec:finite-next}

\paragraph{Status.}
This section records the finite facts presently available from the
\texttt{frontier-adjacent} packet family and the corresponding verifier
\texttt{experimental/scripts/verify\_frontier\_adjacent\_v13\_rows.py}.
It is an \textup{AUDIT}/\textup{PROVED-BY-EXACT-CERTIFICATE} section for the
unsafe side and for the quotient-rung veto checks.  It is not a safe-side
certificate: every row still has \texttt{safe\_certificates.status = OPEN}.

\subsection{Budgets, Rows, and Endpoints}

All four deployed packets have
\[
        n=2^{21}=2097152,\qquad k=2^{20}=1048576,\qquad \rho=\frac12.
\]
The finite budget is
\[
        B^*=\left\lfloor \varepsilon^* Q\right\rfloor,\qquad Q=q_{\rm line}.
\]
For KoalaBear,
\[
        p_{\rm KB}=2^{31}-2^{24}+1=2130706433,\qquad Q_{\rm KB}=p_{\rm KB}^6,
\]
and the packet budget is
\[
        B^*_{\rm KB}=
        \left\lfloor\frac{p_{\rm KB}^6}{2^{128}}\right\rfloor
        =274980728111395087.
\]
For the Mersenne-31 circle rows,
\[
        p_{\rm M31}=2^{31}-1=2147483647,\qquad Q_{\rm M31}=p_{\rm M31}^4,
\]
and the packet budget is
\[
        B^*_{\rm M31}=
        \left\lfloor\frac{p_{\rm M31}^4}{2^{100}}\right\rfloor
        =16777215.
\]
Thus the Mersenne-31 packet target is \(2^{-100}\), not \(2^{-128}\);
indeed \(\left\lfloor p_{\rm M31}^4/2^{128}\right\rfloor=0\).

The active v13 raw adjacent rows are as follows.  For the two MCA rows, the
active pair is the moved-pair block \texttt{v13\_raw\_moved\_pair}; the
older \texttt{agreement\_interval} fields in the same JSON files are historical
and should not be used as the active v13 raw edge.

\begin{center}\footnotesize
\begin{tabular}{@{}llrrrrr@{}}
\toprule
row & object & \(a_0\) & \(a_0+1\) & \(n-a_0\) & \(w(a_0)\) & budget\\
\midrule
KoalaBear & MCA  & 1116047 & 1116048 & 981105 & 67470 & \(B^*_{\rm KB}\)\\
KoalaBear & list & 1116046 & 1116047 & 981106 & 67470 & \(B^*_{\rm KB}\)\\
Mersenne-31 & MCA  & 1116023 & 1116024 & 981129 & 67446 & \(B^*_{\rm M31}\)\\
Mersenne-31 & list & 1116022 & 1116023 & 981130 & 67446 & \(B^*_{\rm M31}\)\\
\bottomrule
\end{tabular}
\end{center}

Here \(w(a_0)=a_0-k-1\) for MCA rows and \(w(a_0)=a_0-k\) for list rows.
The first proved unsafe closed-grid radius is \((n-a_0)/n\).  If a future
upper ledger proves safety at \(a_0+1\), then the largest attained safe
closed-grid radius is \((n-a_0-1)/n\).  Under the real-radius supremum
convention, the threshold lies at the upper edge of this one-grid interval,
so the endpoint convention must be printed with the final certificate.

\subsection{Exact Lower-Side Packet Theorem}

\begin{proposition}[packet-certified unsafe edges]
\label{prop:finite-packet-unsafe}
For the four active rows in the table above, the packet family certifies the
unsafe inequality at \(a_0\):
\[
        N_{\rm row}(a_0)>B^*,
\]
where \(N_{\rm row}\) is the relevant bad numerator: support-wise MCA-bad
slopes for the MCA rows and list codewords for the list rows.  Consequently
the rows are unsafe at the closed radius \(1-a_0/n\):
\[
\begin{array}{c|c}
\text{row} & \text{proved unsafe radius}\\ \hline
\text{KoalaBear MCA} & 981105/2097152\\
\text{KoalaBear list} & 490553/1048576\\
\text{Mersenne-31 MCA} & 981129/2097152\\
\text{Mersenne-31 list} & 490565/1048576.
\end{array}
\]
For the two MCA rows, the active lower numerators stored in the moved-pair
blocks are
\[
\begin{array}{c|cc}
\text{row} & M(a_0) & M(a_0+1)\\ \hline
\text{KoalaBear MCA} &
138634741058327852652 & 57198030366\\
\text{Mersenne-31 MCA} &
4281388998575706 & 1752700.
\end{array}
\]
Thus the moved MCA lower route fires at \(a_0\) and stops at \(a_0+1\).  The
deficits at \(a_0+1\) are exactly
\[
        274980670913364722
        \quad\text{and}\quad
        15024516,
\]
respectively.
\end{proposition}

\begin{proof}
For the list rows, the certificate is the identity-prefix comparison
\[
        \left\lceil \binom n{a_0}/p^{\,a_0-k}\right\rceil > B^*.
\]
For the MCA rows, the certificate first forms the \(C^+=\RS[\F,D,k+1]\)
identity-prefix list floor
\[
        L(m)=
        \left\lceil \binom n m / p^{\,m-k-1}\right\rceil
\]
and then applies the flexible-budget deep-point conversion
\[
        M(m)=
        \left\lceil
        \frac{L(m)(q-n)}{q-n+k(L(m)-1)}
        \right\rceil .
\]
The moved-pair blocks in
\texttt{kb\_mca\_v1.packet.json} and
\texttt{m31\_mca\_v1.packet.json} store the displayed exact values of
\(M(a_0)\) and \(M(a_0+1)\), and the verifier recomputes them from
\(n,k,p,q\) and checks the fire pattern \(M(a_0)>B^*\), \(M(a_0+1)\le B^*\).
The same verifier checks the two list-row identity-prefix fire patterns.
Since \(Q\varepsilon^*\notin\mathbb Z\) in all four rows, a numerator
\(>B^*=\lfloor Q\varepsilon^*\rfloor\) gives error \(>\varepsilon^*\).
\end{proof}

\begin{remark}[what the lower-route failure does and does not mean]
\label{rem:finite-lower-route-failure}
The inequalities \(M(a_0+1)\le B^*\) in the MCA rows, and the analogous
identity-prefix failure in the list rows, are not safe upper bounds.  They
only say that the present identity-prefix lower construction no longer proves
failure one agreement step later.  A safety theorem still needs a complete
upper ledger \(U(a_0+1)\le B^*\).
\end{remark}

\subsection{Dyadic Rung Audit}

There are two audit layers in the present artifact.  Gate G6 of the verifier
implements an exact scan over all dyadic scales
\[
        c=2^j,\qquad 0\le j\le20,
\]
in the graded-prefix, quotient-remainder, and planted quotient-core profiles,
at both agreements of the original four packet pairs.  Gate G7 then checks the
v13 raw moved-pair addendum for the two MCA rows: it recomputes the moved
\(c=1\) lower route and the named Mersenne-31 \(c=2048\) watch item, and it
checks those fields against the packet.  Thus the active moved-row rung
statements below are packet-backed audit facts, with exact G7 checks for the
displayed lower route and the named watch item; a promotion packet should still
print the moved-row rung table directly.  The current packet-level conclusion
at the active adjacent step is:
\[
\begin{array}{c|l}
\text{row} & \text{rung-audit status at }a_0+1\\ \hline
\text{KoalaBear MCA} &
\text{GREEN; no firing or frontier-tight rung; }c=1\text{ margin }-22.1969\\
\text{KoalaBear list} &
\text{GREEN; no firing or frontier-tight rung; }c=1\text{ margin }-22.0109\\
\text{Mersenne-31 MCA} &
\text{one quiet watch item: }G_{\lceil\cdot\rceil},\,c=2048,\text{ margin }-0.3938\\
\text{Mersenne-31 list} &
\text{GREEN at the frontier; sub-frontier }c=2048\text{ watch item, margin }-0.2106.
\end{array}
\]
For the Mersenne-31 MCA watch item, the packet stores the exact mass
\[
        12769758<16777215=B^*_{\rm M31}.
\]
Thus the watch item is quiet but close: it would need \(4007457\) additional
codewords at the same covered agreement to cross the Mersenne-31 MCA budget.

\begin{proposition}[rung-veto consequence]
\label{prop:finite-rung-veto}
Assuming the packet verifier is replayed successfully and the moved-pair
packet blocks are accepted as the active v13 raw audit, no currently printed
quotient-periodic lower floor refutes any of the four active adjacent safe
candidates \(a_0+1\).  In particular, any new unsafe certificate at \(a_0+1\)
must either sharpen one of the quiet watch items, come from an
unscanned/non-dyadic quotient mechanism, or arise from a genuinely aperiodic,
extension, sparse/CA, or list/interleaving residual branch.
\end{proposition}

\begin{proof}
This is the combined scope of gates G6 and G7 of
\texttt{verify\_frontier\_adjacent\_v13\_rows.py}: the script recomputes the
original dyadic rung tables by exact integer arithmetic and compares the fields
\texttt{fires}, \texttt{TIGHT}, \texttt{covered}, \(m\), \(w\), and the stored
margin brackets against the packet JSON, while G7 recomputes the moved MCA
\(c=1\) values and the named Mersenne-31 \(c=2048\) watch item.  The conclusion
is a veto on this printed family of lower-floor refutations only.  It does not
assert a quotient upper bound, since the packets still list the quotient image
upper ledger as open.
\end{proof}

\subsection{Extension Cell Targets}

The artifact \texttt{extension\_cell\_targets\_v1.json} records exact target
ceilings for the genuinely full-extension branch \(K=F\).  The base and
proper intermediate subfield branches are routed to lower-arity cells; the
remaining \(K=F\) branch must be zero-dimensional with bounded total degree.
The row-wise target ceilings are:
\[
\begin{array}{c|c|c}
\text{row} & a_0+1 & \Delta_{\rm ext}\text{ ceiling}\\ \hline
\text{KoalaBear MCA} & 1116048 & 4807520\\
\text{KoalaBear list} & 1116047 & 4226236\\
\text{Mersenne-31 MCA} & 1116024 & 9\\
\text{Mersenne-31 list} & 1116023 & 8.
\end{array}
\]
These numbers are targets, not payments: they state how small an exact
zero-dimensional full-extension chart certificate must be in order to fit the
finite adjacent ledger.  The toy full-orbit scan
\texttt{f1\_full\_orbit\_scan\_v1.json} is useful falsifier evidence for this
branch, but it is explicitly scoped to toy pencils and is not a deployed-row
certificate.

\subsection{What Is Still Missing for a Safe Adjacent Certificate}

The required finite theorem has the form
\[
        U(a_0+1)\le B^*,
\]
where \(U\) is a first-match, deduplicated sum of all paid and residual cells.
The packet family currently leaves the following cells open.

\begin{enumerate}[label=\textup{(\arabic*)},leftmargin=2.4em]
\item \textbf{Quotient image upper ledger.}
The rung audit is a lower-floor veto, not an image-level upper bound.  A final
packet needs exact quotient-image coalescing across all relevant divisor
scales and slack profiles, or a theorem proving that the scanned dyadic
profiles exhaust the periodic quotient branch.

\item \textbf{Q: prefix maximum-fiber bound.}
At the frontier depths \(w=67470\) for KoalaBear and \(w=67446\) for
Mersenne-31, the head-depth Weil range does not apply.  The finite packet needs
an exact maximum-fiber bound after quotient and planted strata are removed.
A polynomial-loss theorem is insufficient unless all constants fit inside the
listed margins.

\item \textbf{BC: base-field-normalized split-pencil census.}
The interior split-pencil branch must be counted with the base-field floor
included.  The Mersenne-31 rows are the binding tests because their margins
are only \(3.2589\) and \(3.0730\) bits.

\item \textbf{SP: primitive shift-pair control.}
The primitive part of the exact second-moment ledger must be bounded after
constant-shift and quotient-pullback pairs have been charged.  The
Mersenne-31 \(c=2048\) watch items should be treated as stress tests for this
deduplication.

\item \textbf{Tangent, sparse/CA, list, and extension residuals.}
The moving-root tangent construction supplies lower floors in this band but
does not license the high-agreement tangent upper cell.  The sparse/plain-CA
layer, list/interleaving layer, and \(K=F\) extension branch must therefore be
paid by exact row-specific certificates or by named theorems.  Any unresolved
branch must remain explicitly labelled
\[
\texttt{CONDITIONAL\_ON\_NAMED\_INPUT}
\quad\text{or}\quad
\texttt{CONJECTURAL\_WITH\_FALSIFIER},
\]
not hidden in a point estimate.
\end{enumerate}

\begin{theorem}[finite adjacent compiler, packet form]
\label{thm:finite-next-compiler}
Fix one of the four active rows above.  Suppose a future packet supplies a
deduplicated upper ledger \(U(a_0+1)\le B^*\), with every term either
\texttt{PAID\_BY\_THEOREM}, \texttt{PAID\_BY\_EXACT\_CERTIFICATE}, or an
explicitly discharged named input.  Then the first safe integer agreement is
\(a_0+1\): the row is unsafe at agreement \(a_0\), safe at agreement
\(a_0+1\), and its closed-grid threshold is pinned to the interval between
\((n-a_0-1)/n\) and \((n-a_0)/n\).
\end{theorem}

\begin{proof}
The unsafe inequality \(N_{\rm row}(a_0)>B^*\) is
\cref{prop:finite-packet-unsafe}.  If the upper ledger is first-match and
deduplicated, every bad line parameter or list object at agreement at least
\(a_0+1\) appears in exactly one paid cell, so the total number is at most
\(U(a_0+1)\le B^*\).  This is exactly the adjacent certificate condition under
the closed integer-ball convention.
\end{proof}
