% Work packet for experimental/grande_finale.tex.
% This file is not input by the main note.  It is a candidate section for the
% primitive shift-pair part of the final safe-side package.

\section{Primitive Shift-Pair Control}
\label{sec:gf-sp}

\paragraph{Status.}
This section proves the structural part of the primitive shift-pair input:
prefix-collision rigidity, the exact second-moment stratification, the
deduplicated quotient-pullback reduction, and the exact normalization of the
remaining primitive ledger.  It does not prove the primitive census bound needed
for finite adjacent safety.  That bound is isolated below as
\cref{conj:gf-sp-primitive-ledger}.

\subsection{Definitions}

Let \(D\subseteq\B\) be a multiplicative coset of size \(n\).  For a finite
set \(S\subseteq D\), put
\[
        \ell_S(X):=\prod_{x\in S}(X-x).
\]
If \(M\subseteq D\) has size \(m\), write
\[
        \ell_M(X)=X^m+\lambda_1(M)X^{m-1}+\cdots+\lambda_m(M),
        \qquad
        \Phi_w(M):=(\lambda_1(M),\ldots,\lambda_w(M)).
\]
This coefficient-prefix definition is characteristic-free.  When
\(\operatorname{char}\B>w\), Newton identities identify it triangularly with
the first \(w\) power sums.

\begin{definition}[shift pairs and primitive scale]
\label{def:gf-sp-shiftpair}
For \(D'\subseteq D\), define
\[
\mathrm{sp}_w(e;D') :=
\#\Bigl\{(A,B):\begin{array}{l}
A,B \text{ are monic squarefree degree-}e\text{ polynomials split over }D',\\
\gcd(A,B)=1,\ \deg(A-B)\le e-w-1
\end{array}\Bigr\}.
\]
Equivalently, if \(A=\ell_{S}\) and \(B=\ell_T\), then
\(|S|=|T|=e\), \(S,T\subseteq D'\), \(S\cap T=\emptyset\), and
\(\deg(\ell_S-\ell_T)\le e-w-1\).

For a divisor \(c\mid n\), let \(\pi_c:D\to D_c\) be \(x\mapsto x^c\).  A
subset \(S\subseteq D\) is \(c\)-pulled back if it is a union of complete
\(\pi_c\)-fibers.  The common scale of an ordered shift pair
\((\ell_S,\ell_T)\) is
\[
        c(S,T):=\gcd(c(S),c(T)),
\]
where \(c(S)\) is the ambient periodicity scale of \(S\).  The pair is
\emph{primitive} if \(c(S,T)=1\).  If \(c(S,T)>1\), it is charged once, at the
maximal common scale \(c(S,T)\), in the quotient-pullback ledger.
\end{definition}

The maximal-scale convention is the first-match rule needed for finite
certificates: a pair with several quotient symmetries is not counted again in
the primitive cell.

\subsection{What Is Proved}

\begin{proposition}[prefix-collision rigidity]
\label{prop:gf-sp-rigidity}
Let \(1\le w<m\le n\).  If \(M\ne M'\) are \(m\)-subsets of \(D\) with
\(\Phi_w(M)=\Phi_w(M')\), then
\[
        |M\setminus M'|=|M'\setminus M|\ge w+1.
\]
Moreover, if equality holds then
\[
        \ell_{M\setminus M'}-\ell_{M'\setminus M}
\]
is a nonzero constant.
\end{proposition}

\begin{proof}
Put \(R:=M\cap M'\), \(S:=M\setminus M'\), \(T:=M'\setminus M\), and
\(e:=|S|=|T|\).  Then
\[
        \ell_M-\ell_{M'}=\ell_R(\ell_S-\ell_T).
\]
Since \(\ell_M\) and \(\ell_{M'}\) are monic and have the same first \(w\)
coefficients, their difference has degree at most \(m-w-1\).  Hence
\[
        \deg(\ell_S-\ell_T)\le (m-w-1)-|R|=e-w-1.
\]
If \(e\le w\), this forces \(\ell_S=\ell_T\), hence \(S=T\), contradicting
\(M\ne M'\).  Thus \(e\ge w+1\).  If \(e=w+1\), the same inequality gives
\(\deg(\ell_S-\ell_T)\le0\).  The difference is not zero, again because
\(S\ne T\), so it is a nonzero constant.
\end{proof}

\begin{proposition}[exact second-moment ledger]
\label{prop:gf-sp-second-moment}
Let
\[
        N_w(z):=\#\{M\subseteq D:\ |M|=m,\ \Phi_w(M)=z\}.
\]
Then
\[
\sum_{z\in\B^w} N_w(z)^2
 =
\binom{n}{m}
+\sum_{e=w+1}^{\min(m,n-m)} P_e,
\qquad
P_e:=
\sum_{\substack{R\subseteq D\\ |R|=m-e}}
\mathrm{sp}_w(e;D\setminus R).
\]
In particular \(P_e=0\) for \(1\le e\le w\).  At the top stratum,
\[
\mathrm{sp}_w(w+1;D')
=
\#\bigl\{(A,c):\ A \text{ monic squarefree split over }D',\ \deg A=w+1,
c\in\B^\times,\ A-c \text{ squarefree split over }D'\bigr\}.
\]
\end{proposition}

\begin{proof}
The left side counts ordered pairs \((M,M')\) of \(m\)-subsets with equal
prefix.  The diagonal contributes \(\binom nm\).  For an off-diagonal pair,
use the notation of the proof of \cref{prop:gf-sp-rigidity}.  The assignment
\[
        (M,M')\longmapsto (R,\ell_S,\ell_T)
\]
is a bijection from off-diagonal collisions with side-difference \(e\) to
triples in which \(R\) has size \(m-e\) and \((\ell_S,\ell_T)\) is a depth
\(w\) shift pair over \(D\setminus R\).  The degree condition is exactly the
one obtained in the rigidity proof.  Rigidity removes \(e\le w\), and the
obvious support constraints give \(e\le\min(m,n-m)\).  When \(e=w+1\), the
degree condition says \(\ell_S-\ell_T=c\in\B^\times\).  Conversely, if \(A\)
and \(A-c\) are both split over \(D'\) with \(c\ne0\), then they have disjoint
root sets, since a common root would force \(c=0\).
\end{proof}

\begin{proposition}[unconditional packing consequence]
\label{prop:gf-sp-packing}
For every prefix value \(z\in\B^w\),
\[
        N_w(z)\le \binom{n}{m-w}\Big/\binom{m}{w}.
\]
\end{proposition}

\begin{proof}
By \cref{prop:gf-sp-rigidity}, the family
\(\{M:\Phi_w(M)=z\}\) has pairwise \(|M\setminus M'|>w\).  Apply the
anticode packing argument: the \((m-w)\)-subsets contained in distinct members
of this family are disjoint, and there are only \(\binom{n}{m-w}\) such
subsets in total.
\end{proof}

\begin{proposition}[quotient-pullback reduction for shift pairs]
\label{prop:gf-sp-pullback}
Let \(c\mid n\), and suppose \((A,B)=(\ell_S,\ell_T)\) is a depth \(w\)
shift pair of degree \(e\) such that \(S\) and \(T\) are both
\(c\)-pulled back.  Write \(e=ce_0\), \(A(X)=A_0(X^c)\), and
\(B(X)=B_0(X^c)\).  Then
\[
        \deg(A_0-B_0)\le e_0-\left\lceil\frac{w+1}{c}\right\rceil.
\]
Equivalently, \((A_0,B_0)\) is a depth
\[
        w_c:=\left\lceil\frac{w+1}{c}\right\rceil-1
\]
shift pair on the quotient coset.  Conversely, any quotient pair satisfying
this displayed bound pulls back to a depth \(w\) shift pair upstairs.
\end{proposition}

\begin{proof}
Since \(S\) and \(T\) are unions of complete \(\pi_c\)-fibers, their locators
have the displayed forms, with \(A_0,B_0\) monic split over the quotient coset.
The depth \(w\) condition gives
\[
        c\,\deg(A_0-B_0)=\deg(A-B)\le ce_0-w-1.
\]
Dividing by \(c\) and using integrality gives
\[
        \deg(A_0-B_0)\le
        \left\lfloor e_0-\frac{w+1}{c}\right\rfloor
        =
        e_0-\left\lceil\frac{w+1}{c}\right\rceil.
\]
This is exactly the depth \(w_c\) condition.  The converse is the same
inequality read upward.
\end{proof}

\begin{remark}[top-stratum quotient mass]
\label{rem:gf-sp-top-pullback}
If \(e=w+1\) and a top-stratum pair is \(c\)-pulled back, then \(c\mid w+1\)
and the quotient pair is again a top-stratum constant-shift pair.  Thus the
binomial prototypes \(X^{w+1}-\beta\), when available because
\((w+1)\mid n\), are not primitive mass; they belong to the quotient ledger.
Top-stratum primitive pairs, if they exist, are pairs \(A,A-c\) with both
polynomials split over the ambient coset but with no common nontrivial
periodicity in their root sets.
\end{remark}

\subsection{Exact Normalization of the Remaining Input}

Split the off-diagonal ledger by the maximal common scale from
\cref{def:gf-sp-shiftpair}:
\[
        P_e=P_e^{\mathrm{quot}}+P_e^{\mathrm{prim}},
\]
where \(P_e^{\mathrm{quot}}\) is assigned to quotient-pullback scales
\(c\ge2\), with no double-counting, and \(P_e^{\mathrm{prim}}\) is the
common-scale-one remainder.  Put
\[
        \bar F:=\binom{n}{m}|\B|^{-w},
        \qquad
        \Gamma_2(m,w):=|\B|^w\sum_{z\in\B^w}
        \left(\frac{N_w(z)}{\binom nm}\right)^2 .
\]

\begin{proposition}[exact \(L^2\) gap identity]
\label{prop:gf-sp-gamma2}
With the above notation,
\[
        \Gamma_2(m,w)
        =
        \frac1{\bar F}
        +\frac{\sum_e P_e^{\mathrm{quot}}}{\binom nm\,\bar F}
        +\frac{\sum_e P_e^{\mathrm{prim}}}{\binom nm\,\bar F}.
\]
Consequently, after quotient-pullback pairs are paid by their quotient ledger,
primitive shift-pair control is exactly the problem of bounding
\[
        \Gamma_{2,\mathrm{prim}}(m,w):=
        \frac{\sum_e P_e^{\mathrm{prim}}}{\binom nm\,\bar F}.
\]
\end{proposition}

\begin{proof}
Divide \cref{prop:gf-sp-second-moment} by \(\binom nm^2|\B|^{-w}\).  The
diagonal term becomes \(1/\bar F\), and the off-diagonal terms split according
to the first-match quotient/primitive decomposition.
\end{proof}

\begin{conjecture}[SP: primitive shift-pair ledger]
\label{conj:gf-sp-primitive-ledger}
For the multiplicative deployed rows and for the smooth multiplicative reserve
regime, the primitive ledger satisfies
\[
        \sum_e P_e^{\mathrm{prim}}
        \le
        R_{SP}(n)\,\binom nm\,\bar F
\]
after tangent, quotient, common-GCD, extension, planted/sunflower, and bounded
chart strata have been removed by the existing first-match ledger.  The
asymptotic target is \(R_{SP}(n)=e^{o(n)}\), or a printed polynomial loss used
only with agreement reserve \(R\gg\log n\).  The finite adjacent target is the
same inequality with row-specific explicit constants small enough to fit inside
the printed margins of the four adjacent rows.
\end{conjecture}

\begin{remark}[why this is not already a finite certificate]
\label{rem:gf-sp-moment-barrier}
Even a polynomial bound on \(\Gamma_{2,\mathrm{prim}}\) is only an \(L^2\)
statement.  For the max-to-mean prefix-fiber ratio
\[
        R_{\max}:=|\B|^w\max_z \frac{N_w(z)}{\binom nm},
\]
the general moment inequality gives
\[
        R_{\max}\le (\Gamma_r(m,w)|\B|^w)^{1/r}.
\]
At the deployed frontier depths, \(w\log_2|\B|\) is of order \(10^6\) bits.
Thus fixed \(r\), and especially \(r=2\), cannot decide a finite adjacent row
with margins of \(22.2,22.0,3.3,3.1\) bits.  The second-moment ledger is a
structural calibration and a route to reserve-form asymptotics; the finite
adjacent theorem still needs either high-moment control, an extremality theorem
such as mode-at-null/exchange-compression, or a direct exact census.
\end{remark}

\subsection{Routes for the Primitive Census}

\begin{enumerate}[label=\textup{SP\arabic*.},leftmargin=*]
\item \textbf{Constant-shift classification.}
The top stratum asks for monic split \(A\) such that \(A-c\) is also split.
After \cref{prop:gf-sp-pullback}, quotient prototypes are removed.  The
primitive problem resembles a finite-field version of classifying polynomials
with two prescribed completely split value fibers over a multiplicative coset.
Possible tools include monodromy of the coefficient space, exceptional
polynomial methods, and finite-field value-set estimates.  A useful finite
certificate would classify or sharply bound primitive \(A,A-c\) at the deployed
depths.

\item \textbf{Low-degree difference incidence.}
For general \(e\), write \(A-B=H\) with \(\deg H\le e-w-1\).  For fixed
\(H\), the condition that both \(A\) and \(A-H\) split over \(D'\) is a
determinantal/incidence problem in the split-locator variety.  The expected
primitive theorem is that a large family of such \(A\)'s forces a paid
structure: common GCD, quotient pullback, tangent containment, extension-pole
containment, or a bounded SPI chart.

\item \textbf{Exchange and anticode rigidity.}
\Cref{prop:gf-sp-rigidity} says collisions are far apart in the Johnson graph.
Long exchange chains between many primitive pairs should either create a
periodic stabilizer or compress to a graded/prefix extremizer.  This is the SP
counterpart of the mode-at-null/exchange-compression route for Q.

\item \textbf{Moment hierarchy.}
The exact pair ledger should be extended to triples and higher tuples of
prefix-colliding split locators.  Fixed-order \(e^{o(n)}\) control feeds the
reserve-form frontier through the moment sandwich.  The finite adjacent rows
require much more than fixed order, so this route should be advertised as
asymptotic unless it is paired with an exact extremality statement.

\item \textbf{References and techniques to mine.}
For the analytic route: Halasz-type inverse Littlewood--Offord theorems over
finite fields, Tao--Vu and Nguyen--Vu inverse theorems, and subgroup
sum-product estimates of Bourgain--Glibichuk--Konyagin and Shkredov.  For the
incidence route: monodromy of split polynomial covers, value-set and exceptional
polynomial classifications, and the Hankel/Padé structure used in
Berlekamp--Massey and Heinig--Rost theory.  These are strategy pointers, not
imported theorems in the present packet.
\end{enumerate}

\paragraph{Conclusion.}
The SP cell is now reduced to a single normalized primitive quantity,
\(\Gamma_{2,\mathrm{prim}}\), after a theorem-level quotient/primitive
decomposition.  The proved lemmas prevent hidden small-side collisions and
show that all visible quotient prototypes are paid by descent.  What remains is
the genuine primitive census in \cref{conj:gf-sp-primitive-ledger}.
