% Promoted from experimental/experiments.tex lines 1451--1715.
% Status: stable high-agreement note.  This is a TeX fragment intended to be
% included from experimental/experiments.tex or another paper-level wrapper.
% Dependencies: theorem environments, standard macros such as \F and \RS,
% and earlier local labels referenced inside the note.

\section{High-Agreement Tangent Staircase}
\label{sec:tangent-staircase}

\textbf{Status: \textsc{New-local} finite MDS theorem.}
This section records a generic moving-root tangent floor and, in the
very-high-agreement range, a matching upper bound.  It is independent of
quotient-periodic structure and does not use smoothness.  It is relevant to the
finite row ledger because the bad slopes are paid with the actual line field
\(\qline\).

For a polynomial \(P\in F[X]\), write
\[
  P=P_{<k}+P_{\ge k},
  \qquad \deg P_{<k}<k,
\]
where \(P_{\ge k}\) is the sum of the terms of degree at least \(k\).  Let
\(\operatorname{LD}_{\rm sw}(C,a)\) denote the largest possible number of finite
slopes on a received line that have a support-wise noncontained explanation on
some support of size at least \(a\).

\begin{theorem}[moving-root tangent floor]
\label{thm:moving-root-tangent-floor}
Let \(D\subset F\) have \(|D|=n\), and let
\(C=\RS[F,D,k]\).  For every integer \(a\) with \(k+1\le a\le n\),
\[
  \operatorname{LD}_{\rm sw}(C,a)\ge n-a+1 .
\]
\end{theorem}

\begin{proof}
Choose a subset \(A\subset D\) of size \(a-1\), and put
\[
  B_A(X)=\prod_{x\in A}(X-x).
\]
Define the received line
\[
  f=(XB_A)_{\ge k},
  \qquad
  g=-(B_A)_{\ge k}.
\]
For every \(t\in D\setminus A\), set
\[
  L_t(X)=(X-t)B_A(X).
\]
Then \(L_t\) is the locator of the support \(A\cup\{t\}\), which has size
\(a\), and linearity of truncation gives
\[
  f+t g=(L_t)_{\ge k}.
\]
On every root of \(L_t\), the word represented by \((L_t)_{\ge k}\) agrees with
\(- (L_t)_{<k}\), a codeword of \(C\).  Thus the slope \(t\) is explained on
\(A\cup\{t\}\).

It remains to check support-wise noncontainment on this same support.  On
\(A\), since \(B_A=0\), we have
\[
  g=-(B_A)_{\ge k}=(B_A)_{<k}.
\]
If \(g\) were explained on \(A\cup\{t\}\) by a degree-\(<k\) polynomial \(q\),
then \(q=(B_A)_{<k}\), because \(|A|=a-1\ge k\).  At the remaining point \(t\),
this would force
\[
  -(B_A)_{\ge k}(t)=(B_A)_{<k}(t),
\]
that is, \(B_A(t)=0\), contrary to \(t\notin A\).  Hence \(g\) is not
separately explained on \(A\cup\{t\}\), so the slope is support-wise
noncontained.  The slopes \(t\in D\setminus A\) are distinct, giving
\(n-a+1\) bad finite slopes.
\end{proof}

\begin{theorem}[very-high-agreement tangent staircase]
\label{thm:very-high-tangent-staircase}
Let \(C=\RS[F,D,k]\) with \(|D|=n\).  If
\[
  3a-2n\ge k,
\]
then
\[
  \operatorname{LD}_{\rm sw}(C,a)=n-a+1 .
\]
\end{theorem}

\begin{proof}
The lower bound is Theorem~\ref{thm:moving-root-tangent-floor}.  For the upper
bound, put \(s=n-a\).  If a received line has at most one support-wise
noncontained finite slope at agreement at least \(a\), then the claimed upper
bound is immediate.  Otherwise pick two such slopes \(z_1\ne z_2\), with
explaining codewords \(p_1,p_2\in C\) on supports \(S_1,S_2\), respectively.
Since \(|S_i|\ge a\),
\[
  |S_1\cap S_2|\ge 2a-n.
\]
On this intersection,
\[
  g=(p_1-p_2)/(z_1-z_2),
  \qquad
  f=p_1-z_1g .
\]
The condition \(3a-2n\ge k\) and the inequality \(a\le n\) imply
\(2a-n\ge k\).  Therefore these two right-hand sides extend uniquely to
codewords \(c_g,c_f\in C\).  Let \(S_0\) be a maximal common support on which
\(f=c_f\) and \(g=c_g\), and put \(b=|S_0|\) and \(d=n-b\).  Then
\[
  b\ge2a-n,\qquad d\le2(n-a)=2s .
\]
By maximality, outside \(S_0\) there is no coordinate at which both residuals
\(f-c_f\) and \(g-c_g\) vanish.

The residual-budget proposition, Proposition~\ref{prop:common-residual}, is
applicable because
\[
  a+b-n\ge a+(2a-n)-n=3a-2n\ge k .
\]
Here its common-zero parameter is \(c_0=0\).  If \(b\ge a\), then every
noncontained slope needs at least one residual zero outside \(S_0\), and there
are only \(d\le s\) such coordinates.  If \(b<a\), then every noncontained
slope needs at least
\[
  h=a-b=d-s
\]
private residual zeros outside \(S_0\).  Since \(s<d\le2s\), the residual
budget gives
\[
  \#\{\text{bad slopes}\}
  \le
  \left\lfloor \frac d{d-s}\right\rfloor
  \le s+1
  =n-a+1 .
\]
This proves the matching upper bound.
\end{proof}

\begin{corollary}[tangent-star extremizers in the exact range]
\label{cor:tangent-star-extremizers}
Let \(C=\RS[F,D,k]\), \(|D|=n\), and suppose that
\[
  k+1\le a\le n,
  \qquad
  3a-2n\ge k.
\]
If a received line \(f+zg\) has exactly \(n-a+1\) support-wise noncontained
finite bad slopes at agreement at least \(a\), and if \(n-a+1\ge2\), then the
line is tangent-star extremal in the following sense.  There are codewords
\(c_f,c_g\in C\) and a common support \(S_0\subseteq D\) of size \(a-1\) such
that, after replacing \(f,g\) by \(f-c_f,g-c_g\), every bad slope is obtained by
choosing exactly one residual coordinate in \(D\setminus S_0\).  More precisely,
writing \(\Omega=D\setminus S_0\), the map
\[
  x\longmapsto
  -\frac{f(x)-c_f(x)}{g(x)-c_g(x)}
\]
is a bijection from \(\Omega\) to the bad-slope set.
\end{corollary}

\begin{proof}
Choose two distinct bad slopes and form the maximal common code-line support
\(S_0\) as in the proof of Theorem~\ref{thm:very-high-tangent-staircase}; write
\(b=|S_0|\), \(s=n-a\), and \(d=n-b\).  Equality in the upper bound from that
proof cannot occur when \(b\ge a\), because then there are at most \(n-a\) bad
slopes.  Hence \(b<a\).  The residual-budget bound is
\[
  \#\{\text{bad slopes}\}
  \le
  \left\lfloor\frac d{d-s}\right\rfloor
  \le s+1=n-a+1.
\]
For equality, the second inequality must be sharp, so \(d-s=1\), equivalently
\(b=a-1\).  The maximality of \(S_0\) gives no common residual zeros outside
\(S_0\).  Since \(|\Omega|=n-a+1\) and each residual coordinate can vanish for
at most one finite slope, equality forces every residual coordinate to be used
exactly once.  This is precisely the displayed residual-root bijection.
\end{proof}

\begin{corollary}[exact high-agreement gate for the \(\F_{17^{32}}\), rate-\(1/2\) row]
\label{cor:f17-32-exact-tangent-gate}
Let \(H\subset \F_{17^{32}}^*\) be any multiplicative subgroup of order
\(512\), and let
\[
  C=\RS[\F_{17^{32}},H,256].
\]
For every \(a\ge427\),
\[
  \operatorname{LD}_{\rm sw}(C,a)=513-a.
\]
In particular,
\[
  \operatorname{LD}_{\rm sw}(C,506)=7,
  \qquad
  \operatorname{LD}_{\rm sw}(C,507)=6.
\]
Since
\[
  6\cdot2^{128}<17^{32}<7\cdot2^{128},
\]
we have
\[
  \frac{\operatorname{LD}_{\rm sw}(C,507)}{17^{32}}<2^{-128}
  \quad\text{but}\quad
  \frac{\operatorname{LD}_{\rm sw}(C,506)}{17^{32}}>2^{-128}.
\]
Thus, under the finite-slope support-wise MCA convention, the \(2^{-128}\)
integer agreement staircase for this row is pinned between \(506\) and \(507\).
The largest safe integer Hamming radius is \(5\), while integer radius \(6\) is
already unsafe.  The corresponding normalized grid radii are
\[
  5/512
  \quad\text{and}\quad
  6/512=3/256.
\]
As a real-radius supremum, the transition is \(3/256\), but the closed endpoint
\(\delta=3/256\) is on the unsafe side.
\end{corollary}

\begin{proof}
Here \(n=512\) and \(k=256\).  The hypothesis
\(3a-2n\ge k\) becomes \(3a-1024\ge256\), hence \(a\ge427\).  The exact formula
is Theorem~\ref{thm:very-high-tangent-staircase}.  The arithmetic inequalities
are
\[
  17^{32}-6\cdot2^{128}
  =326217393234836465063858652730341978625>0
\]
and
\[
  7\cdot2^{128}-17^{32}
  =14064973686101998399515954701426232831>0 .
\]
\end{proof}

\begin{corollary}[no seventh finite-slope branch past agreement \(506\)]
\label{cor:no-seventh-finite-slope-past-506}
For \(C=\RS[\F_{17^{32}},H,256]\) with \(|H|=512\), no finite-slope
support-wise MCA mechanism can add a seventh bad slope at agreement
\(a\ge507\).  At equality, any extremal line is tangent-star in the sense of
Corollary~\ref{cor:tangent-star-extremizers}.
\end{corollary}

\begin{proof}
By Corollary~\ref{cor:f17-32-exact-tangent-gate},
\[
  \operatorname{LD}_{\rm sw}(C,a)=513-a
  \qquad (a\ge427).
\]
For every \(a\ge507\), the right-hand side is at most \(6\).  Thus a seventh
finite support-wise bad slope is impossible in this range.  The extremizer
classification is Corollary~\ref{cor:tangent-star-extremizers}.
\end{proof}

\begin{remark}[effect on the earlier agreement-353 target]
The agreement-353 target is no longer a frontier for the rate-\(1/2\),
\(\F_{17^{32}}\), \(n=512\) row: Theorem~\ref{thm:moving-root-tangent-floor}
already gives
\[
  \operatorname{LD}_{\rm sw}(C,353)\ge512-353+1=160.
\]
The quotient-core strict352 packet remains a useful mechanism record, but the
generic tangent floor gives a stronger lower bound at agreement \(352\) and
beyond.  Corollary~\ref{cor:no-seventh-finite-slope-past-506} rules out a
seventh finite-slope branch past agreement \(506\).  The adjacent-ledger
section below treats the high-agreement projective-slope, CA, curve-MCA, and
interleaved-list coding objects; protocol-facing conversions still require
separate challenge-field, extension-lift, folding, query, and cryptographic
ledgers.
\end{remark}
