
\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{array}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{heuristic}{Heuristic}
\newtheorem{remark}{Remark}
\newtheorem{definition}{Definition}
\newtheorem{conjecture}{Conjecture}

\newcommand{\F}{\mathbb F}
\newcommand{\RS}{\operatorname{RS}}
\newcommand{\Bnum}{B_{\rm num}}
\newcommand{\Deltaone}{\Delta_1}
\newcommand{\Deltazero}{\Delta_0}
\newcommand{\tauone}{\tau_1}
\newcommand{\tautwo}{\tau_2}
\newcommand{\tauthree}{\tau_3}
\newcommand{\Ctwo}{C_2}
\newcommand{\qline}{q_{\rm line}}
\newcommand{\qgen}{q_{\rm gen}}
\newcommand{\qchal}{q_{\rm chal}}
\newcommand{\MCA}{\operatorname{MCA}}
\newcommand{\CA}{\operatorname{CA}}
\newcommand{\List}{\operatorname{List}}
\newcommand{\PG}{\operatorname{PG}}
\newcommand{\BCHKS}{\operatorname{BCHKS}}
\newcommand{\dist}{\Delta}
\newcommand{\efib}{c_{\rm fib}}
\newcommand{\ellpg}{\ell_{\rm pg}}
\newcommand{\epsstar}{\varepsilon_*}
\newcommand{\epsmca}{\varepsilon_{\rm mca}}
\newcommand{\epsca}{\varepsilon_{\rm ca}}
\newcommand{\Fib}{\operatorname{Fib}}
\newcommand{\Lam}{\Lambda}
\newcommand{\Bad}{\operatorname{Bad}}
\newcommand{\LD}{\operatorname{LD}}
\newcommand{\Htwo}{H_2}
\newcommand{\QH}{\mathcal Q_H}

\title{Experiments for Smooth RS-MCA Proximity Thresholds\\
\large Fresh-Eyes Threshold Memo, Missing Theorems, and Retained Locator Ledger}
\author{RS-MCA experimental notes}
\date{June 26, 2026}

\begin{document}
\maketitle

\begin{abstract}
This replacement starts with the current ``fresh eyes'' synthesis for the
smooth Reed--Solomon Proximity Prize problem.  The negative side is now quite
rigid: Paper D v5 gives a prize-facing upper cap on the MCA threshold through a
self-contained deep-point route, while Paper A and the list lower bounds rule
out any no-slack capacity theorem.  The positive side is not yet a theorem; it
should be organized around two local-limit problems, L1 arbitrary-word locator
fibers and M1 all-line residue packing, plus extension-line MCA, Paper D
conversion/radius audits, and exact protocol-ledger rewrites.

The main new additions over the old \texttt{experiments.tex} are two compact
bridge lemmas.  First, for ordinary column-distance interleaving, interleaved
lists inject into common feasible supports, so a uniform base locator-fiber
theorem gives the same polynomial exponent for all protocol arities; there is no
automatic \(n^{\mu B}\) product loss.  Second, a list bound plus an MCA bound
implies a concrete line-decoding bound with loss \(M+nL+1\).  The older BCHKS
provenance notes, quotient-locator dictionaries, normal forms, arithmetic gates,
and finite-threshold infrastructure are retained below whenever they still look
useful.
\end{abstract}

\tableofcontents

\section{Fresh-Eyes Settlement Memo}
\label{sec:fresh-eyes-settlement-memo}

I would frame the current state as follows.  The attached suite substantially
settles the negative side and gives a plausible corrected theorem shape, but it
does not yet settle the Proximity Prize threshold in the sharp ``largest
\(\delta^*\)'' sense.  The clean prize-relevant statement is no longer
``prove smooth RS reaches capacity''.  It is
\[
  \delta=1-\rho-\eta,
  \qquad
  \eta\text{ must clear generated-field entropy, quotient-core, MCA-floor,}
\]
\[
  \text{interleaving, line-field, and challenge-field budgets.}
\]
For
\[
  C=\RS[\F,D,k],\qquad n=|D|,
  \qquad \rho=k/n\in\{1/2,1/4,1/8,1/16\},
\]
the official challenge statements use this MCA/list-threshold form; in this
experimental ledger the concrete prize envelope is~\cite{ProximityPrize26}
\[
  \epsstar=2^{-128},\qquad k\le2^{40},\qquad |\F|<2^{256}.
\]
The protocol-relevant soundness contribution has the schematic form
\[
  \epsmca(C,\delta)
  +\frac{|\Lam(C^{\equiv\mu},\delta)|}{\qline}
  +\text{query error}.
\]
Thus a list theorem alone is not enough unless it is connected to the exact MCA,
correlated-agreement, line-decoding, or curve-MCA quantity used by the protocol,
and unless the denominator is the actual line or challenge field.

\subsection{Bottom line}

For the \textbf{MCA/correlated-agreement threshold}, the strongest attached
result is Paper D v5's universal cap.  Through the self-contained deep-point
route and the stated dyadic-divisor hypotheses,
\[
  \delta^*_{\rm MCA}(2^{-128})
  \le 1-\rho-2^{-9}
  \quad (\rho=1/2,1/4,1/8),
\]
and
\[
  \delta^*_{\rm MCA}(2^{-128})
  \le 1-\rho-2^{-10}
  \quad (\rho=1/16).
\]
Equivalently, throughout the relevant unsafe intervals Paper D gives
\[
  \epsmca(C,\delta)
  >\frac1{2k}\left(1-\frac n{|\F|}\right)
  \ge2^{-86}\gg2^{-128}.
\]
This is a real prize-facing cap, not merely a heuristic obstruction.  It is not
an error-one theorem; it proves failure probability on the order of \(1/k\),
which is already far above \(2^{-128}\), but it does not characterize the full
failure curve.

For the \textbf{interleaved-list threshold}, Paper A's base list lower bound
plus the base-to-interleaved monotonicity gives a clean negative cap.  At quotient
scale \(N\mid n\), with \(\rho N\in\mathbb Z\), there is a received word with at
least
\[
  \binom{N}{\rho N+1}/q,
  \qquad q=|\F|,
\]
base-code codewords at radius \(1-\rho-1/N\).  Therefore the same radius is
unsafe for the interleaved-list budget whenever this exceeds \(2^{-128}q\).  In
the worst case \(q<2^{256}\), the following choices suffice:
\[
\begin{array}{c|c|c|c|c}
\hline
\rho & N & \text{list-failure radius} &
\log_2\binom{N}{\rho N+1}-256 &
\text{margin over }2^{128}\\
\hline
1/2  & 512  & 1/2-2^{-9}    & 251.17 & 123.17\\
1/4  & 512  & 3/4-2^{-9}    & 156.33 & 28.33\\
1/8  & 1024 & 7/8-2^{-10}   & 298.68 & 170.68\\
1/16 & 2048 & 15/16-2^{-11} & 433.89 & 305.89\\
\hline
\end{array}
\]
The fourth column is the exponent of the lower-bound list size after dividing by
the worst-case field size \(2^{256}\); the fifth subtracts the target exponent
\(128\).

\subsection{What is already proved or very close to proved}

The old no-slack smooth-domain capacity claim is dead.  The quotient-locator
construction gives explicit bad slopes for canonical lines and, over deployed
smooth prime fields such as BabyBear, KoalaBear, and \(3\cdot2^{30}+1\), yields
support-wise line-MCA error one on intervals starting at
\(1-\rho-2^{-18}\) for all four prize rates, with the sharper \(2^{-17}\) gap
at rates \(1/2\) and \(1/4\).  These statements rule out any theorem saying
that every radius below \(1-\rho\) has negligible MCA error.

Paper D is the most prize-relevant negative theorem because it converts a deep
point/list phenomenon into MCA at the exact \(2^{-128}\)-style threshold.  In
v5, the headline MCA cap is routed locally through a self-contained deep-point
argument rather than the Crites--Stewart list-to-agreement import.  The remaining
CA/list comparison and fallback statements still need their own radius,
normalization, augmented-code, and import audits.

The list lower-bound side is also stronger than it is currently advertised.  It
should be promoted to an explicit interleaved-list negative corollary: base lists
embed into ordinary interleaved lists, and the binomial numerators above already
exceed the \(2^{-128}|\F|\) budget in the full field envelope for the displayed
quotient divisors.

\subsection{The corrected positive theorem shape}

The positive theorem should use
\[
  a=\lceil(1-\delta)n\rceil=k+\sigma,
  \qquad \delta=1-\rho-\eta,
\]
and require at least
\[
  \sigma\log_2\qgen
  \ge (1+\varepsilon)\log_2\binom n{k+\sigma},
  \qquad
  \sigma\ge C\frac n{\log n},
\]
plus explicit quotient-profile and failure-floor ledgers.  The first inequality
uses the generated field \(\qgen\), not a larger extension or challenge field
that merely appears later in the protocol.  The MCA numerator must be divided by
the actual line field \(\qline\).

The intended list target is an arbitrary-word locator-fiber theorem
\[
  \sup_U |\Fib_U(k+\sigma)|\le n^B.
\]
The intended MCA target is an all-line bound of the form
\[
  \epsmca(C,1-\rho-\eta)
  \le
  \frac{
    n^{1+o(1)}
    +2^{(\beta(\rho)/\Htwo(\rho))\QH(\eta)(1+o(1))}
  }{\qline},
\]
where quotient-periodic classes are removed or charged by \(\QH(\eta)\).  The
current packet contains important special cases and reductions, but not these
full arbitrary-word and all-line theorems.

\subsection{What remains missing}

\begin{enumerate}
\item \textbf{L1: arbitrary-word locator local limit.}  This is the real list
upper-bound theorem.  Characteristic-zero rigidity, monomial-prefix lanes, and
split-prime transfer results are useful but do not yet imply the uniform
polynomial-field theorem needed for arbitrary received words.

\item \textbf{M1: all-line aperiodic residue packing.}  Canonical-line exactness
and quotient floors are lower-bound tools, not all-line upper bounds.  The
positive MCA theorem needs a fixed-field, all-line, all-base residue-packing
bound.

\item \textbf{F1: extension-line MCA.}  The list side has a clean extension-code
identity.  MCA does not.  Base-valued bad lines can deflate when sampled over an
extension field, while Paper D's cap indicates that genuinely extension-valued
bad lines exist in relevant regimes.  Any extension-line lift must therefore be
a corrected-reserve theorem, not a blanket subfield statement.

\item \textbf{Paper D conversion audit.}  Paper D v5's headline MCA cap is no
longer load-bearing on the direct Crites--Stewart conversion.  The self-contained
deep-point step, support-wise monotonicity, integer-radius conventions, and the
remaining CA/list import statements should still be independently checked.

\item \textbf{Protocol-ledger rewrite.}  Deployed FRI/WHIR/IOP analyses must be
rewritten with exact terms
\[
  |\Lam(C^{\equiv\mu},\delta)|/\qline
  \quad\text{and}\quad
  \epsmca\text{ or line-decoding over the actual line field}.
\]
The survey toy protocol already has this shape; deployed analyses still need the
same ledger.
\end{enumerate}

\section{New Bridge I: Common-Support Interleaved Fiber Injection}
\label{sec:common-support-interleaved-fiber-injection}

\textbf{Status: \textsc{New-local} wrapper.}
The older ledger treated interleaving conservatively through a safe product
bound \(L_\mu(\delta)\le L_1(\delta)^\mu\).  For ordinary column-distance RS
interleaving, the following support-level injection gives the sharper upper
bound: once the one-row locator-fiber theorem is proved, interleaving costs no
extra exponent.

For \(S\subseteq D\), let
\[
  L_S(X)=\prod_{x\in S}(X-x).
\]
For a received word \(U\in\F^D\), the condition \(\deg(U\bmod L_S)<k\) means
that the unique polynomial of degree less than \(|S|\) interpolating \(U|_S\)
has degree less than \(k\).

\begin{definition}[one-row and common interleaved fibers]
Let \(C=\RS[\F,D,k]\), let \(a\ge k\), and let
\(\mathbf U=(U_1,\ldots,U_\mu)\in(\F^\mu)^D\).  Define
\[
  \Fib^{(\mu)}_{\mathbf U}(a)
  =
  \{S\subseteq D:
    |S|=a,\ \deg(U_i\bmod L_S)<k
    \text{ for every }i=1,\ldots,\mu\}.
\]
For one row, write \(\Fib_{U_i}(a)\) for the same condition with only \(U_i\).
\end{definition}

\begin{lemma}[common-support interleaved fiber injection]
\label{lem:common-support-interleaved-fiber-injection}
Let \(C=\RS[\F,D,k]\), \(n=|D|\), and let
\(a=\lceil(1-\delta)n\rceil\ge k\).  For every received \(\mu\)-row word
\(\mathbf U\in(\F^\mu)^D\), ordinary column-distance interleaving satisfies
\[
  |\Lam(C^{\equiv\mu},\delta,\mathbf U)|
  \le |\Fib^{(\mu)}_{\mathbf U}(a)|
  \le \min_{1\le i\le\mu}|\Fib_{U_i}(a)|.
\]
Consequently,
\[
  \sup_{\mathbf U}|\Lam(C^{\equiv\mu},\delta,\mathbf U)|
  \le \sup_U |\Fib_U(a)|.
\]
In particular, if L1 proves \(\sup_U|\Fib_U(k+\sigma)|\le n^B\), then
\[
  |\Lam(C^{\equiv\mu},1-\rho-\sigma/n)|\le n^B
\]
for every ordinary column-distance protocol arity \(\mu\).
\end{lemma}

\begin{proof}
Fix a total order on \(D\).  A listed interleaved codeword
\((P_1,\ldots,P_\mu)\in C^{\equiv\mu}\) at column distance at most \(\delta\) from
\(\mathbf U\) agrees with \(\mathbf U\) on at least \(a\) common columns.  Choose
the first \(a\)-subset \(S\) of those agreeing columns.  For this \(S\), every
row \(U_i|_S\) is interpolated by the degree-\(<k\) polynomial \(P_i\), hence
\(S\in\Fib^{(\mu)}_{\mathbf U}(a)\).

For fixed \(S\), the tuple \((P_1,\ldots,P_\mu)\) is uniquely determined,
because each \(P_i\) has degree less than \(k\) and is fixed by its values on
\(|S|\ge k\) points.  Thus the canonical-support map from listed interleaved
codewords to common feasible supports is injective.  The second inequality is
immediate because every common feasible support is feasible for each individual
row.  Taking suprema gives the final claim.
\end{proof}

\begin{remark}[impact]
For ordinary column-distance RS interleaving, L2 should be demoted from a
separate product-exponent problem to a corollary of L1.  The hard list theorem
remains the base arbitrary-word locator local limit.
\end{remark}

\section{New Bridge II: List plus MCA Gives Line Decoding}
\label{sec:list-plus-mca-gives-line-decoding}

\textbf{Status: \textsc{New-local} bridge.}
The next proposition turns a line-decoding proof obligation into a finite-constant
budget once L1 and M1 are available.  It uses finite slopes and the support-wise
MCA normalization used in this packet.

\begin{proposition}[list/MCA bridge to line decoding]
\label{prop:list-mca-to-line-decoding-bridge}
Let \(C=\RS[\F,D,k]\), let \(|D|=n\), and let
\(a=\lceil(1-\delta)n\rceil>k\).  Suppose that every allowed received line
\(f+\gamma g\) has at most \(M\) support-wise MCA-bad finite slopes at radius
\(\delta\), equivalently \(\epsmca(C,\delta)\le M/|\F|\) for the chosen finite
slope sampler.  Suppose also that the two-row interleaved list size satisfies
\[
  |\Lam(C^{\equiv2},\delta,W)|\le L
  \qquad\text{for every }W\in(\F^2)^D.
\]
Then \(C\) is line-decodable with parameters
\[
  (\delta,\ M+nL+1,\ n+1)
\]
in the following sense: if an allowed received line \(f+\gamma g\) has more than
\(M+nL\) finite slopes \(\gamma\) that are \(\delta\)-close to selected codewords
\(U(\gamma)\in C\), then there are codewords \(c_1,c_2\in C\) such that
\[
  U(\gamma)=c_1+\gamma c_2
\]
for at least \(n+1\) of those slopes.
\end{proposition}

\begin{proof}
For each close slope \(\gamma\), choose a support \(S_\gamma\subseteq D\) of size
\(a\) on which \(f+\gamma g\) agrees with the selected codeword \(U(\gamma)\).
Discard the at most \(M\) support-wise MCA-bad slopes.  For every remaining
slope, support-wise containment gives codewords \(c_{1,\gamma},c_{2,\gamma}\in C\)
such that
\[
  c_{1,\gamma}|_{S_\gamma}=f|_{S_\gamma},
  \qquad
  c_{2,\gamma}|_{S_\gamma}=g|_{S_\gamma}.
\]
Thus \((c_{1,\gamma},c_{2,\gamma})\) is a two-row interleaved codeword
\(\delta\)-close to the received two-row word \((f,g)\), using the common support
\(S_\gamma\).  There are at most \(L\) possible pairs.

If the original line has more than \(M+nL\) close slopes, then after discarding
bad slopes more than \(nL\) slopes remain.  By pigeonhole, one pair
\((c_1,c_2)\) occurs for at least \(n+1\) slopes.  For each such slope, the
codewords \(U(\gamma)\) and \(c_1+\gamma c_2\) both agree with \(f+\gamma g\) on
\(S_\gamma\), hence agree with each other on \(a>k\) positions.  Since both have
degree less than \(k\), they are identical codewords.  This proves the stated
line-decoding conclusion.
\end{proof}

\begin{remark}[finite-constant consequence]
If M1 gives \(M=n^{1+o(1)}\) and L1 plus
Lemma~\ref{lem:common-support-interleaved-fiber-injection} gives \(L=n^B\), then
Proposition~\ref{prop:list-mca-to-line-decoding-bridge} gives
\[
  M+nL+1\le n^{B+1+o(1)}.
\]
For \(n\le2^{44}\) and \(|\F|<2^{256}\), a raw list numerator \(n^B\) is
compatible with a \(2^{-128}\) field budget only for about \(B\lesssim2.9\), and
the line-decoding bridge is compatible only for about \(B\lesssim1.9\).  Thus the
bridge is useful, but it leaves a real finite-constant target.
\end{remark}

\section{Updated Positive-Theorem Package}
\label{sec:updated-positive-theorem-package}

The clean theorem to aim for is the following finite-reserve package.  Let
\[
  C=\RS[\F_{\rm line},D,k],\qquad n=|D|,
  \qquad a=k+\sigma,
  \qquad \delta=1-a/n=1-\rho-\eta.
\]
Assume
\[
  \sigma\log_2\qgen
  \ge (1+\varepsilon)\log_2\binom n{k+\sigma},
  \qquad
  \sigma\ge C_{\rho,B,\varepsilon}\frac n{\log n},
\]
the quotient profile \(\QH(\eta)\) is empty or explicitly budgeted, \(\eta\) lies
above all proved failure floors including Paper D's universal-cap floor, and the
MCA or line experiment is proved over \(\qline\), not merely over \(\qchal\).

\begin{conjecture}[corrected finite reserve package]
\label{conj:corrected-finite-reserve-package}
Under the preceding hypotheses, the desired conclusions are
\[
  |\Lam(C^{\equiv\mu},\delta)|\le n^B
\]
for all ordinary column-distance protocol arities \(\mu\), by
Lemma~\ref{lem:common-support-interleaved-fiber-injection}; and
\[
  \epsmca(C,\delta)
  \le
  \frac{
    n^{1+o(1)}
    +2^{(\beta(\rho)/\Htwo(\rho))\QH(\eta)(1+o(1))}
  }{\qline},
\]
or the same bound over \(\qgen\) plus a proved extension-line lift.  If the
consumed primitive is line decoding, then
Proposition~\ref{prop:list-mca-to-line-decoding-bridge} should give
\[
  C\text{ is }(\delta,\ M+nL+1,\ n+1)\text{ line-decodable},
\]
with \(M\) and \(L\) supplied by M1 and L1.
\end{conjecture}

This package would turn the current negative cap into a sharp threshold program:
below the cap one cannot hope for \(2^{-128}\) MCA soundness, while above the
corrected reserve one would have finite numerators that can be checked against
\(\qline\).

\section{Immediate Experimental Additions}
\label{sec:immediate-experimental-additions}

\begin{enumerate}
\item Add \texttt{experimental/interleaved\_fiber\_injection.md}, containing
Lemma~\ref{lem:common-support-interleaved-fiber-injection}.  Update certificate
logic so an L1 locator-fiber theorem gives \(L_\mu=n^B\), not \(n^{\mu B}\), for
ordinary column-distance RS interleaving.

\item Add \texttt{experimental/list\_mca\_to\_linedecoding.md}, containing
Proposition~\ref{prop:list-mca-to-line-decoding-bridge}.  This gives a concrete
M2 bridge and turns line decoding into a finite-constant ledger problem.

\item Build a certificate scanner reporting generated-field entropy margin,
quotient profile after \(k=\rho n-r\), Paper D cap floor, base and interleaved
list numerators, MCA numerator, line-decoding numerator, field separation among
\(\qgen\), \(\qline\), and \(\qchal\), extension status, and exact failure audit.

\item Keep CA/list statements that use Crites--Stewart marked
\textsc{Conditional} until audited.  Paper D v5's MCA cap should instead be
tracked as a draft theorem using the local deep-point conversion, still requiring
human revision and peer review.
\end{enumerate}

\section{Fresh Non-Claims}
\label{sec:fresh-nonclaims}

This revision does not claim an exact settlement of the smooth-case Proximity
Prize threshold.  It claims that the shape is now rigid:
\[
  \boxed{\text{No unslacked capacity theorem; prove a reserve theorem at }
  1-\rho-\eta.}
\]
The theorem-backed negative side gives a draft universal MCA cap at constant gap
\(2^{-9}\) for \(\rho=1/2,1/4,1/8\) and \(2^{-10}\) for \(\rho=1/16\).  The
positive side should be pursued as
\[
  \text{L1 locator local limit}
  +\text{M1 residue-line packing}
  +\text{extension-line theorem}
  +\text{protocol-ledger rewrite}.
\]
The interleaved-list problem is less fundamental than it looked in the old file:
for column-distance interleaving, a uniform locator-fiber theorem immediately
bounds the interleaved list at the same exponent.

\section{Retained Previous Experiments Material}
\label{sec:retained-previous-experiments-material}

The remaining sections are retained from the previous \texttt{experiments.tex}
whenever they still provide useful provenance, notation, normal forms, finite
certificate gates, or non-claims.  The new front matter above should be read as
the current threshold-level guide; the older material below remains a toolbox.

\section{Status, Provenance, and What Counts as New}

This file is the place where we collect new things, but it must separate new
repository contributions from imported constructions.  The status labels used
below are:
\[
\begin{array}{ll}
\textsc{Imported} & \text{an external theorem, proof pattern, or conversion;}\\
\textsc{Wrapper} & \text{a repository repackaging, dictionary, or pigeonhole consequence;}\\
\textsc{New-local} & \text{a restricted algebraic theorem proved in this note;}\\
\textsc{Target} & \text{a precise proof obligation not yet promoted;}\\
\textsc{Heuristic} & \text{evidence or a search direction, not a theorem.}
\end{array}
\]

\paragraph{Hard attribution rule.}
Any locator-polynomial argument derived from the subgroup construction of
Ben-Sasson--Carmon--Hab\"ock--Kopparty--Saraf must cite \cite[Thm.~7.1]{BCHKS25}
where the construction is stated or proved.  Any admissible subgroup
instantiation must also cite \cite[Thm.~1.13]{BCHKS25}.  The citation belongs
at the theorem statement and again at the proof entry point; a bibliography
entry or acknowledgement alone is not enough.

\paragraph{What is new in this note.}
The following items are the repository-side contributions collected here.
\begin{itemize}
\item A smooth-quotient notation dictionary translating BCHKS subgroup
  notation into the RS-MCA notation \(Q=D^{\efib}\) and the dyadic/FFT-domain
  ledgers used in Papers A--D.
\item A list-fiber pigeonhole wrapper: once a locator construction assigns
  many subset certificates to a smaller slope set, one heavy slope has many
  locator certificates, and, after a distinctness check, many nearby
  codewords.
\item A slack-two and subfield-pigeonhole proof target for the older
  Crites--Stewart/CA route: the imported locator construction should be run at
  the augmented-code rung needed by that conversion, and slopes should be
  pigeonholed over the generated/base field when the construction really takes
  values there.
\item A \textsc{New-local} divisibility gate in the restricted Paper B window
  \(B=\F_p\), \(F=\F_{p^2}\), \(D=\F_p\), \(t=\sigma=2\), \(j=3\).  This is
  independent of the BCHKS priority issue and is the main theorem proved in
  Section~\ref{sec:divisibility-gate}.
\end{itemize}

\paragraph{What is not new.}
The polynomial identity behind the item-(d) locator proof is not new here.  In
BCHKS notation it is the expansion of a vanishing polynomial over a complement
of a chosen subset; in smooth-quotient notation it is the same expansion of
\(\prod_{b\in A}(X^{\efib}-b)\), up to choosing a subset or its complement.
The use of \(\ell\) for the chosen subset size also follows the external
presentation closely enough that it should either be cited or renamed to
\(\ellpg\).

\paragraph{Source map.}
The main papers remain the authoritative documents.
\begin{itemize}
\item Paper A, \texttt{tex/RS\_disproof\_v3.tex}, refutes the old no-slack
  smooth-domain support-wise line-MCA statement.  If it uses the locator
  construction, it should cite BCHKS and call the repository contribution a
  smooth-domain/list-fiber corollary, not a new locator proof.
\item Paper B, \texttt{tex/slackMCA\_v3.tex}, is the main target for the local
  resonance material in Sections~\ref{sec:resonance-setup}--\ref{sec:scanner}.
\item Paper C, \texttt{tex/snarks\_v4.tex}, records protocol ledgers.  Nothing
  in this note may be consumed by a protocol without a separate conversion
  theorem.
\item Paper D, \texttt{tex/cs25\_cap\_v4.tex}, gives the universal cap via an
  imported list-to-agreement route.  Its locator-side input should cite BCHKS
  explicitly if it uses the quotient-locator construction.
\end{itemize}

\section{BCHKS Locator Construction in Smooth-Quotient Notation}
\label{sec:bchks}

\textbf{Status: \textsc{Imported} plus \textsc{Wrapper}.}
This section is a provenance-safe restatement and dictionary.  It is included
so later main-paper edits have a clean place to copy from.

\subsection{Imported theorem/proof pattern}

BCHKS prove a general multiplicative-subgroup construction
\cite[Thm.~7.1]{BCHKS25}.  In a compact form, the imported statement is as
follows.

\begin{theorem}[BCHKS quotient-locator construction, imported]
\label{thm:bchks-import}
Let \(G\subseteq H\subseteq \F_q^*\) be multiplicative subgroups and let
\(\Phi:H\to G\) be \(x\mapsto x^c\), where \(c=|H|/|G|\).  Let
\(E\subseteq G\), and let \(\ellpg,a\geq1\) satisfy
\[
  |E^{(+\ellpg)}|
  =\#\{e_1+\cdots+e_{\ellpg}:e_i\in E\text{ distinct}\}\geq a.
\]
Let \(D=\Phi^{-1}(E)\), \(n=|D|\), and
\[
  C=\RS[\F_q,D,n-(\ellpg+2)c].
\]
Then, for \(\gamma=\ellpg c/n\), there are functions
\(f,g:D\to\F_q\) such that
\[
  \#\{z\in\F_q: \dist(f+zg,C)\leq \gamma\}\geq a,
\]
while
\[
  \dist([f,g],C^2)\geq (\ellpg+1)c/n.
\]
\end{theorem}

\begin{proof}[Reference]
This is exactly the imported construction of \cite[Thm.~7.1]{BCHKS25}; the
proof is not reproduced as a repository contribution.  BCHKS define the line
endpoints by the monomials \(x^{n-\ellpg c}\) and
\(x^{n-(\ellpg+1)c}\), then expand a vanishing polynomial over the complement
of a chosen \(\ellpg\)-subset.  The coefficient of
\(X^{n-(\ellpg+1)c}\) is an affine transform of a restricted sum from
\(E^{(+\ellpg)}\), giving the exceptional slope values.
\end{proof}

The BCHKS Theorem~1.13 is the admissible-subgroup specialization of this
construction: take \(E=G\), take \(H=D\), set \(c=|D|/|G|\), and use
\(\ellpg=|G|/2\).  Any RS-MCA statement corresponding to that specialization
should cite \cite[Thm.~1.13]{BCHKS25} directly.

\subsection{Notation dictionary}

\begin{center}
\begin{tabular}{p{0.28\linewidth}p{0.30\linewidth}p{0.32\linewidth}}
\textbf{BCHKS notation} & \textbf{RS-MCA notation} & \textbf{Meaning}\\
\hline
\(H\) & evaluation domain \(D\) & Large multiplicative domain on which codewords are evaluated.\\
\(G\) & quotient \(Q=D^{\efib}\) & Image of the power map; one point in \(Q\) has \(\efib\) preimages in \(D\).\\
\(c=|H|/|G|\) & \(\efib=n/|Q|\) & Fiber size of the quotient map.  Avoid calling this \(a\), because BCHKS also uses \(a\) for the number of exceptional slopes.\\
\(\Phi(x)=x^c\) & \(x\mapsto x^{\efib}\) & Quotient/fiber map.\\
\(E\subseteq G\) & active quotient subset \(E\subseteq Q\) & Quotient-level support used by the locator.\\
\(E^{(+\ellpg)}\) & restricted first-coefficient/slope set & Sums of distinct chosen quotient elements; slopes are affine transforms of these sums.\\
\(\ellpg\) & \(\ellpg\) or renamed subset size & Number of chosen quotient elements.  Use \(\ellpg\) in RS-MCA text to avoid collision with other \(\ell\)'s.\\
\(f=x^{n-\ellpg c}\), \(g=x^{n-(\ellpg+1)c}\) & locator line endpoints & Same monomial line after quotient notation is substituted.\\
\(P_S(X)=\prod_{\alpha\in S'}(X^c-\alpha)\) & \(\prod_{b\in A}(X^{\efib}-b)\), possibly after complementing \(A\) & The locator polynomial.\\
exceptional \(z\)'s & bad slopes / heavy list fibers & Slope parameters for which a line word is close to the RS code.\\
\end{tabular}
\end{center}

\subsection{The shared locator identity}

The following identity is written down because it is the exact place where
priority can be lost.  The identity is the BCHKS identity in RS-MCA notation.

\begin{lemma}[Locator expansion, imported identity]
\label{lem:locator-imported}
Let \(D\) map \(\efib\)-to-one onto a quotient set \(E\) by
\(x\mapsto x^{\efib}\), and let \(A\subseteq E\) have size \(\ellpg\).  Put
\(A^c=E\setminus A\) and define
\[
  P_A(X)=\prod_{\alpha\in A^c}(X^{\efib}-\alpha).
\]
Then
\[
  P_A(X)
  =X^{n-\ellpg\efib}
    -e_1(A^c)X^{n-(\ellpg+1)\efib}
    +\text{terms of degree at most }n-(\ellpg+2)\efib.
\]
Equivalently, since \(e_1(A^c)=e_1(E)-e_1(A)\), the coefficient of the next
monomial is an affine transform of the restricted sum \(e_1(A)\).
\end{lemma}

\begin{proof}[Reference]
This is the elementary expansion used inside \cite[Thm.~7.1]{BCHKS25}.  We
record it only to fix notation.  It should not be cited as a new lemma of the
repository unless the BCHKS provenance is present at the statement.
\end{proof}

\subsection{List-fiber pigeonhole wrapper}

The next proposition is the repository-side wrapper around the imported
identity.  It is intentionally stated in certificate form, because distinctness
of the nearby codewords is a separate check in concrete instantiations.

\begin{proposition}[List-fiber pigeonhole wrapper]
\label{prop:list-fiber-wrapper}
Let \(\mathcal A\) be a family of \(\ellpg\)-subsets of a quotient set \(E\).
Suppose the BCHKS locator construction assigns to each \(A\in\mathcal A\) a
slope \(z(A)\) lying in a finite set \(S\), and a locator certificate showing
that the corresponding word \(f+z(A)g\) is within radius \(\gamma\) of a
locator codeword \(P_A\in C\).  Then some slope \(z_0\in S\) has at least
\[
  \frac{|\mathcal A|}{|S|}
\]
locator certificates above it.  If the codewords \(P_A\) attached to the
certificates over \(z_0\) are distinct, then the Hamming ball of radius
\(\gamma\) around \(f+z_0g\) contains at least \(|\mathcal A|/|S|\) codewords
of \(C\).
\end{proposition}

\begin{proof}
The first assertion is the pigeonhole principle applied to the map
\(A\mapsto z(A)\).  The second assertion is only the definition of list size,
after the distinctness check removes possible duplicate locator codewords.
The construction that supplies the certificates is imported from
Theorem~\ref{thm:bchks-import}.
\end{proof}

\begin{remark}[What the wrapper adds]
The new part here is not the locator polynomial.  The wrapper isolates the
extra bookkeeping needed by RS-MCA: which slope set pays the pigeonhole bill,
whether the slope set is the ambient field \(\F\) or a generated/base subfield
\(B\), and whether locator certificates remain distinct after specialization.
Those are the checks needed before using the construction in Papers A, B, or D.
\end{remark}

\subsection{Slack-two and subfield target for the older CS25 route}

\textbf{Status: \textsc{Target}.}
The older CS25/CA route needs a locator-heavy list fiber in the augmented code
rung \(C^+=\RS[\F,D,k+1]\), because that is the object fed into the
Crites--Stewart list-to-agreement conversion.  Paper D v5 no longer uses this
as the load-bearing MCA-cap route, but the target remains useful for CA/list
comparison audits.  The proof obligation should be stated as follows.

\begin{proposition}[Slack-two/subfield locator target]
\label{prop:slack-two-target}
Let \(D\subseteq B\subseteq\F\), and suppose a BCHKS-type quotient locator
construction over \(D\) produces slopes in \(B\), not merely in \(\F\).  If the
one-rung/augmented-code version produces distinct locator codewords in
\(C^+=\RS[\F,D,k+1]\) for a family \(\mathcal A\) of certificates, then there
exists a slope \(z_0\in B\) with list size at least
\[
  \frac{|\mathcal A|}{|B|}
\]
inside the appropriate Hamming ball for \(C^+\).
\end{proposition}

\begin{proof}[Bookkeeping only]
This is Proposition~\ref{prop:list-fiber-wrapper} with \(S=B\).  The nontrivial
work is external or elsewhere: one must verify the BCHKS locator hypotheses at
the augmented-code rung, verify that the slope coefficients lie in \(B\), and
verify distinctness of the produced codewords.  Until those checks are present,
this proposition is a target, not a promoted Paper D theorem.
\end{proof}

\subsection{Pasteable main-paper wording}

\paragraph{Paper A wording.}
The polynomial locator identity used here is the quotient-fiber form of the
construction of Ben-Sasson--Carmon--Hab\"ock--Kopparty--Saraf
\cite[Thm.~7.1]{BCHKS25}; their Theorem~1.13 is the admissible subgroup
instantiation.  Thus the locator proof itself is not a new contribution of
this manuscript.  The present use is the smooth-domain specialization, the
field/divisor bookkeeping, and the list-fiber pigeonhole packaging.

\paragraph{Paper D wording.}
The locator-side input is the BCHKS quotient-locator construction
\cite[Thm.~7.1; cf.~Thm.~1.13]{BCHKS25}, written in the smooth-domain quotient
notation \(Q=D^{\efib}\).  The additional bookkeeping needed here is the
slack-two augmented-code rung and, when available, subfield pigeonholing over
\(B\) rather than over the ambient extension field \(\F\).

\section{Triage of the AI-Generated Four-Item Packet}
\label{sec:packet-triage}

\textbf{Status: \textsc{Audit}.}
The four advertised items should be positioned as follows before any promotion
into a main paper.  The original AI packet used the labels (a)--(d) without
making them self-contained in this note, so we decode them here.

\begin{center}
\begin{tabular}{p{0.10\linewidth}p{0.28\linewidth}p{0.50\linewidth}}
\textbf{Item} & \textbf{Short name} & \textbf{Meaning in this ledger}\\
\hline
(a) & Weak-slack positive regime & A positive-looking proximity/list or
MCA-adjacent statement that only reaches slack on the order of
\(1/\sqrt n\).  It is useful as a comparison theorem, but it is far from the
constant/reserve bookkeeping needed for the corrected RS-MCA target.\\
(b) & Finite Fermat-prime packet & A special finite-domain instantiation over
only three Fermat-prime cases, in the current experimental ledger represented
by the \(p\in\{17,257,65537\}\) style checks.  It is evidence or a worked
computation, not a uniform theorem.\\
(c) & Exponential-field construction & A large-field variant whose proof
requires the ambient field to be exponential in the domain/parameter size.
This can clarify the mechanism but does not match the polynomial-field or
challenge-field regimes needed by the Proximity Prize ledger.\\
(d) & BCHKS quotient-locator packet & The interesting locator/proximity-gap
construction: choose a quotient of a multiplicative subgroup, use
\(\ellpg\)-subsets and restricted sums to create many exceptional slopes or
nearby locator certificates.  This is the BCHKS construction of
\cite[Thm.~7.1]{BCHKS25}, with the admissible subgroup instance in
\cite[Thm.~1.13]{BCHKS25}; the repository contribution is only the
smooth-domain dictionary, list-fiber wrapper, and later slack-two/subfield
bookkeeping.\\
\end{tabular}
\end{center}

Item (d) should not be confused with the \textsc{New-local} divisibility-gate
theorem in Section~\ref{sec:divisibility-gate}.  The former is an imported
locator/proximity construction; the latter is an independent restricted Paper
B resonance calculation.

\begin{center}
\begin{tabular}{p{0.10\linewidth}p{0.34\linewidth}p{0.44\linewidth}}
\textbf{Item} & \textbf{Limitation} & \textbf{Repository handling}\\
\hline
(a) & Works only at slack on the order of \(1/\sqrt n\). & Use as a weak-slack comparison point only.  It does not clear the corrected-reserve MCA objective.\\
(b) & Applies only to three Fermat-prime cases. & Treat as finite-prime evidence or a worked computation, not as a uniform smooth-domain theorem.\\
(c) & Requires exponential field size. & Treat as a large-field sanity check.  It is not directly usable for polynomial-field or prize-ledger parameters.\\
(d) & Most relevant, but the locator proof is essentially BCHKS. & Import, cite, and adapt from \cite[Thm.~7.1 and Thm.~1.13]{BCHKS25}.  The repository contribution is only the smooth-domain/list-fiber/slack-two packaging after exact hypotheses are checked.\\
\end{tabular}
\end{center}

\paragraph{Promotion checklist.}
Before any statement using item (d) moves to Papers A--D, check the following.
\begin{itemize}
\item Does the statement cite BCHKS at the theorem and proof entry point?
\item Is the object a proximity-gap statement, a list statement, CA, MCA,
  line-decoding, or a protocol-facing theorem?
\item Which field pays the slope/list pigeonhole bill: \(B\), \(\F\), or
  another generated field?
\item Are the locator codewords distinct after specialization?
\item Is the claimed slack in the same normalization as the consumed theorem?
\item Are items (a), (b), and (c) kept out of asymptotic/protocol claims unless
  their limitations are explicitly part of the theorem statement?
\end{itemize}

\section{Restricted Resonance Setup for Paper B}
\label{sec:resonance-setup}

\textbf{Status: \textsc{New-local} for the divisibility gate; otherwise local
normal-form bookkeeping.}
The remaining sections preserve and reorganize the Cycle 14--18 algebraic
material.  This branch is independent of the BCHKS priority correction.

The common restricted setting is
\[
  B=\F_p,\qquad F=\F_{p^2},\qquad D=\F_p,\qquad
  t=\sigma=2,\qquad j=3,
\]
and we work off the tangent/global endpoint
\[
  R_0=\{\, [W]_E\wedge [\Bnum]_E=0\,\}.
\]
The field ledgers remain distinct:
\[
  \qgen=p,\qquad \qline=p^2.
\]
The regime is sub-reserve, since \(\eta=\sigma/n=2/n\).  Thus none of the
following proves a corrected-reserve list, CA, MCA, line-decoding, SNARK, or
protocol theorem.

The base/generated field is \(B=\F_p\).  The line field is the quadratic
extension \(F=\F_{p^2}=B(\alpha)\), with basis \(\{1,\alpha\}\) over \(B\) and
\(\alpha^2=\nu\in B\).  The domain is \(D=\F_p\), so \(n=|D|=p\).

A degree-two residue-line datum consists of
\[
  E\in F[X],\qquad \deg E=2,
  \qquad E(x)\ne0\ \text{for all }x\in D,
\]
and a numerator
\[
  \Bnum\in F[X],\qquad \deg \Bnum<2.
\]
We write
\[
  A=F[X]/E,
  \qquad [P]_E\in A,
  \qquad b=[\Bnum]_E.
\]
The anchor word on \(D\) is interpolated by a polynomial \(W\).  The operation
\(u\wedge v\) means the determinant of the coordinate vectors of \(u,v\in A\)
in a chosen \(F\)-basis of the two-dimensional \(F\)-space \(A\).  Off \(R_0\),
the pair \(\{[W]_E,b\}\) is such a basis.

The co-support has size \(j=3\).  If \(T\subset D\) is the three-point
co-support, define
\[
  \tau_1=e_1(T),\qquad \tau_2=e_2(T),\qquad \tau_3=e_3(T).
\]
All valid co-supports have \(\tau_i\in B\).  The quantity \(\Ctwo\) denotes the
number of distinct slopes produced by the relevant landing branch after
restricting to valid split triples \(T\subset\F_p\).  Bounding landing points
therefore bounds \(\Ctwo\), but a sharp slope theorem may require more because
many landing points can share a slope.

\section{Cycle 14 Normal Form}
\label{sec:cycle14}

The Cycle 14 audit reduces the \(t=2,j=3\) landing equation to two affine forms
in the elementary co-support parameters
\[
  \tau=(\tauone,\tautwo,\tauthree).
\]

\begin{lemma}[Affine wedge normal form]
\label{lem:affine-wedge}
Assume \(\{[W]_E,b\}\) is an \(F\)-basis of \(A\).  Then the landing equation can
be written in the form
\[
  \iota(\tau)=A_0(\tauone,\tautwo)-\tauthree [W]_E,
  \qquad
  \mu(\tau)=B_0(\tauone,\tautwo)-\tauthree b,
\]
where
\[
  A_0=p_1[W]_E+p_2 b,
  \qquad
  B_0=q_1[W]_E+q_2 b,
\]
and \(p_i,q_i\in F\) are affine-linear functions of
\((\tauone,\tautwo)\).  If the basis is normalized so \([W]_E\wedge b=1\), then
\[
  \Delta=\iota\wedge\mu
    =(p_1-\tauthree)(q_2-\tauthree)-p_2q_1.
\]
\end{lemma}

\begin{proof}
The Cycle 14 quotient calculation, which is a concrete instance of Paper B's
residue-line normal form, gives the displayed affine forms.  Expanding in the
ordered basis \(\{[W]_E,b\}\), the coordinate vector of \(\iota\) is
\((p_1-\tauthree,p_2)\), while the coordinate vector of \(\mu\) is
\((q_1,q_2-\tauthree)\).  Their wedge determinant is therefore
\[
  (p_1-\tauthree)(q_2-\tauthree)-p_2q_1.
\]
\end{proof}

\section{Cycle 18 Component Split}
\label{sec:cycle18}

Choose a basis \(F=B+\alpha B\) with \(\alpha^2=\nu\in B\), and write
\[
  p_1=p_{10}+\alpha p_{11},\quad
  p_2=p_{20}+\alpha p_{21},\quad
  q_1=q_{10}+\alpha q_{11},\quad
  q_2=q_{20}+\alpha q_{21}.
\]
Split
\[
  \Delta=\Deltazero+\alpha\Deltaone,
  \qquad
  \Deltazero,\Deltaone\in B[\tauone,\tautwo,\tauthree].
\]

\begin{theorem}[Monic quadratic and linear alpha component]
\label{thm:component-split}
In the setting above,
\[
\begin{aligned}
\Deltazero={}&
  \tauthree^2-(p_{10}+q_{20})\tauthree
  +p_{10}q_{20}+\nu p_{11}q_{21}
  -p_{20}q_{10}-\nu p_{21}q_{11},\\
\Deltaone={}&
  -(p_{11}+q_{21})\tauthree
  +p_{10}q_{21}+p_{11}q_{20}-p_{20}q_{11}-p_{21}q_{10}.
\end{aligned}
\]
Consequently \(\Deltazero\) is monic quadratic in \(\tauthree\), while
\(\Deltaone\) has degree at most one in \(\tauthree\).
\end{theorem}

\begin{proof}
Substitute the coordinate expressions for \(p_i,q_i\) into the identity of
Lemma~\ref{lem:affine-wedge} and use \(\alpha^2=\nu\).  Collecting the
coefficient of \(1\) gives the displayed formula for \(\Deltazero\), and
collecting the coefficient of \(\alpha\) gives the displayed formula for
\(\Deltaone\).  The coefficient of \(\tauthree^2\) in \(\Deltazero\) is \(1\),
and the \(\alpha\)-component has no \(\tauthree^2\)-term.
\end{proof}

\begin{corollary}[Graph reduction outside the zero-alpha branch]
\label{cor:graph}
If \(\Deltaone\) is not the zero polynomial, write
\[
  \Deltaone=s(\tauone,\tautwo)\tauthree+h(\tauone,\tautwo).
\]
On the open locus \(s\ne0\), the common-zero condition
\(\Deltazero=\Deltaone=0\) is supported on the graph
\[
  \tauthree=-h/s.
\]
\end{corollary}

\begin{proof}
This is immediate from solving the linear equation \(\Deltaone=0\) for
\(\tauthree\) on \(s\ne0\).
\end{proof}

\section{New Divisibility-Gate Theorem}
\label{sec:divisibility-gate}

The next theorem is the main \textsc{New-local} theorem extracted from the
Cycle 18 reduction.  It is stronger than merely saying that the branch is a
graph: it shows that any two-dimensional family must satisfy an explicit
divisibility identity.

\begin{theorem}[Divisibility gate for the graph branch]
\label{thm:divisibility-gate}
Assume the restricted setting above and assume \(\Deltaone\ne0\).  Write
\[
  \Deltaone=s(\tauone,\tautwo)\tauthree+h(\tauone,\tautwo),
\]
and define the denominator-cleared graph polynomial
\[
  G(\tauone,\tautwo)
  =s(\tauone,\tautwo)^2
    \Deltazero\bigl(\tauone,\tautwo,-h(\tauone,\tautwo)/s(\tauone,\tautwo)\bigr).
\]
Then \(\deg G\le 4\).  If \(G\) is not the zero polynomial, then
\[
  \#\{\,\tau\in B^3:\Deltazero(\tau)=\Deltaone(\tau)=0\,\}=O(p).
\]
Consequently the corresponding number of distinct slopes satisfies
\[
  \Ctwo=O(p)=O(n).
\]
Therefore a growing-prime family with
\[
  \Ctwo=\Theta(p^2)=\Theta(\qline)
\]
in the nonzero-\(\Deltaone\) branch can occur only if \(G\equiv0\).
\end{theorem}

\begin{proof}
Because the \(p_i,q_i\) are affine-linear in \((\tauone,\tautwo)\), the
coefficient \(s\) has degree at most \(1\), and \(h\) has degree at most \(2\).
Since \(\Deltazero\) is monic quadratic in \(\tauthree\), clearing the
denominators after substituting \(\tauthree=-h/s\) gives a polynomial \(G\) of
degree at most \(4\).

On \(s\ne0\), the equation \(\Deltaone=0\) forces \(\tauthree=-h/s\).  Hence
every common zero on this open locus gives a base pair
\((\tauone,\tautwo)\) with \(G(\tauone,\tautwo)=0\).  If \(G\) is nonzero,
Schwartz--Zippel gives at most \(4p\) such base pairs, and each base pair gives
at most one value of \(\tauthree\).

It remains to count the exceptional locus \(s=0\).  There \(\Deltaone=0\) also
forces \(h=0\).  If \(s\) is a nonzero affine form, this is contained in an
affine line; if \(s\equiv0\), then \(h\) is a nonzero polynomial of degree at
most \(2\).  In either case there are \(O(p)\) base pairs.  For each such pair,
\(\Deltazero\) is a monic quadratic in \(\tauthree\), so it gives at most two
values of \(\tauthree\).  The total common-zero count is \(O(p)\).

Finally, the number of distinct slopes is bounded by the number of landing
points \(\tau\).  Thus \(\Ctwo=O(p)\) whenever \(G\not\equiv0\), and any
\(\Theta(p^2)\) family in this branch must satisfy \(G\equiv0\).
\end{proof}

\begin{remark}
The identity \(G\equiv0\) says that, after clearing the \(s\)-denominator,
\(\Deltazero\) is divisible by the linear equation \(\Deltaone\) on the graph
branch.  This is the first exact algebraic gate that a large slope family in
this restricted window must pass.
\end{remark}

\section{Nearby Proven Gates}
\label{sec:nearby-gates}

The same restricted lane contains two other useful gates.  They are included
here because they explain where Theorem~\ref{thm:divisibility-gate} fits.

\begin{proposition}[Base-component complete-intersection gate]
\label{prop:complete-intersection}
Suppose \(\Deltazero,\Deltaone\in B[\tauone,\tautwo,\tauthree]\) have no common
surface component.  Then
\[
  \#V(\Deltazero,\Deltaone)(B)=O(p),
\]
and hence this branch contributes \(\Ctwo=O(p)\) slopes.
\end{proposition}

\begin{proof}
The two components have bounded degree.  If they share no surface component,
their common zero set in \(\mathbb A^3_B\) is a curve of bounded degree.  A
bounded-degree affine curve over \(\F_p\) has \(O(p)\) rational points, and
slopes are bounded by landing points.
\end{proof}

\begin{proposition}[Cycle 16 determinant gate]
\label{prop:det-gate}
Let \(Q(z_0,z_1)\) be the Cycle 15--16 determinant consistency polynomial for
the affine system
\[
  L_z(\tau)=\iota(\tau)-z\mu(\tau)=0,
  \qquad z=z_0+\alpha z_1.
\]
If \(Q\) is not identically zero, then in the restricted \(D=\F_p\),
\(t=\sigma=2\), \(j=3\), off-\(R_0\) window,
\[
  \Ctwo\le 4p=O(p)=O(n).
\]
\end{proposition}

\begin{proof}
Cycle 16 gives \(\deg Q\le4\) and shows that every landing slope must satisfy
\(Q(z_0,z_1)=0\).  If \(Q\ne0\), Schwartz--Zippel over \(B=\F_p\) gives at most
\(4p\) possible pairs \((z_0,z_1)\), hence at most \(4p\) slopes.
\end{proof}

\section{Slope Map and Remaining Heuristics}
\label{sec:slope-map}

On the graph branch, the landing equation \(\iota=z\mu\) gives
\[
  p_1-\tauthree=zq_1,
  \qquad
  p_2=z(q_2-\tauthree).
\]
Where \(q_1\ne0\), substituting \(\tauthree=-h/s\) yields
\[
  z(\tauone,\tautwo)=\frac{p_1+h/s}{q_1}.
\]
Equivalently, eliminating \(\tauthree\) recovers the Cycle 14 quadratic
\[
  q_1z^2-(p_1-q_2)z-p_2=0,
\]
so the residual map is controlled by
\[
  (\tauone,\tautwo)
  \longmapsto [\,q_1:(p_1-q_2):p_2\,]\in\mathbb P^2(F).
\]

\begin{heuristic}[Exceptional identity should be rare]
For generic source data, the polynomial \(G\) should not vanish identically.
Thus the graph branch should usually be curve-sized, and the first possible
large-slope families should come from algebraically special data satisfying
the divisibility identity \(G\equiv0\) or from the zero-alpha branch
\(\Deltaone\equiv0\).
\end{heuristic}

\begin{heuristic}[What remains after the gate]
If \(G\equiv0\), the problem is no longer to show that the common-zero set is
small.  It may be surface-sized.  The remaining question is whether the
projective coefficient map has one-dimensional image on every source-valid
surface, giving \(\Ctwo=O(p)\), or whether some growing-prime source-valid
family has two-dimensional image and \(\Ctwo=\Theta(p^2)\).
\end{heuristic}

\section{Next Experimental Checks}
\label{sec:scanner}

A useful scanner should compute, for each source-valid candidate,
\[
  \Deltaone=s\tauthree+h,
  \qquad
  G=s^2\Deltazero(\tauone,\tautwo,-h/s),
\]
then record whether \(G\equiv0\), whether \(\Deltaone\equiv0\), the exceptional
locus \(s=h=0\), the image size of
\[
  [\,q_1:(p_1-q_2):p_2\,],
\]
and the direct slope count over distinct split triples \(T\subset\F_p\).

The certificate should keep at least
\[
\begin{gathered}
  p,\ \qgen,\ \qline,\ E,\ \Bnum,\ \text{seed},\ \text{stratum},\
  R_0\text{-status},\\
  \Deltaone\equiv0,
  \quad G\equiv0,
  \quad \#\{s=h=0\},
  \quad \#\operatorname{image},
  \quad \Ctwo,
  \quad \#\{T\text{ split distinct}\}.
\end{gathered}
\]

\section{June 26 Normal-Form and Dependency Results}
\label{sec:june26}

\textbf{Status: mixed.}
This section records the parts of the June 26 PR batch that survived a
statement-level validity check.  The statements below are useful proof
infrastructure, not prize claims.  In particular, they do not improve the
current Cycle116/119 numerator \(52{,}747{,}567{,}092\) over
\(\F_{17^{32}}\), and they do not prove the corrected Paper B MCA conjecture.

\subsection{Syndrome-pencil normal form for support-wise line incidence}

\textbf{Status: \textsc{New-local}.}
This is the cleanest reusable F1 contribution from the batch.  It turns
support-wise line incidence into a Hankel-pencil locator equation over the
actual line field.

Let \(D=\{x_1,\ldots,x_n\}\subset F\) have distinct points and let
\(C=\RS[F,D,k]\) with redundancy \(r=n-k\).  For each \(x_i\), put
\[
  \lambda_i=\left(\prod_{h\ne i}(x_i-x_h)\right)^{-1}.
\]
For a word \(y:D\to F\), define
\[
  \operatorname{Syn}(y)_m
  =\sum_i \lambda_i x_i^m y(x_i),
  \qquad 0\le m<r.
\]
Then \(\operatorname{Syn}(y)=0\) if and only if \(y\in C\).  Fix
\(T\subset D\) with \(|T|=j\), assume \(0\le j\le r\), and set \(t=r-j\).
Write
\[
  L_T(X)=\prod_{x\in T}(X-x)=\ell_0+\ell_1X+\cdots+\ell_jX^j,
  \qquad
  \boldsymbol\ell_T=(\ell_0,\ldots,\ell_j)^T .
\]
For \(w\in F^r\), define the \(t\times(j+1)\) Hankel window
\[
  H_{t,j}(w)_{a,b}=w_{a+b},
  \qquad 0\le a<t,\quad 0\le b\le j.
\]

\begin{theorem}[Hankel-pencil test]
\label{thm:syndrome-pencil}
Let \(f,g:D\to F\), put \(u=\operatorname{Syn}(f)\) and
\(v=\operatorname{Syn}(g)\), and let \(S=D\setminus T\).  For a finite slope
\(z\in F\), the word \(f+zg\) is explained by a codeword of \(C\) on \(S\) if
and only if
\[
  \bigl(H_{t,j}(u)+zH_{t,j}(v)\bigr)\boldsymbol\ell_T=0.
\]
Moreover, this explanation is support-wise noncontained for the line
\(f+zg\) on \(S\) if and only if, in addition,
\[
  H_{t,j}(v)\boldsymbol\ell_T\ne0.
\]
Consequently the support-wise MCA bad slopes at agreement \(k+t\) are exactly
the slopes for which there is a squarefree \(D\)-split locator \(L_T\) of
degree \(j=r-t\) satisfying the displayed incidence and noncontainment tests.
\end{theorem}

\begin{proof}
Let \(W_T\subset F^r\) be the span of the parity-check columns indexed by
\(T\):
\[
  W_T=\operatorname{span}_F\{\lambda_x(1,x,\ldots,x^{r-1}):x\in T\}.
\]
Equivalently, \(w\in W_T\) means that \(w\) is the syndrome of a word supported
on \(T\).  For every \(w\in W_T\), write
\[
  w_m=\sum_{x\in T}c_xx^m.
\]
Then, for \(0\le a<t\),
\[
  \bigl(H_{t,j}(w)\boldsymbol\ell_T\bigr)_a
  =\sum_{b=0}^j\ell_b w_{a+b}
  =\sum_{x\in T}c_xx^aL_T(x)=0.
\]
Conversely, since \(L_T\) is monic, the recurrence
\(\sum_{b=0}^j\ell_b w_{a+b}=0\) for \(0\le a<r-j\) determines all remaining
coordinates from the first \(j\) coordinates, so its solution space has
dimension at most \(j\).  The \(j\) columns indexed by the distinct points of
\(T\) form a Vandermonde system of rank \(j\), hence the recurrence space is
exactly \(W_T\).

The word \(f+zg\) is explained on \(S\) if and only if there is \(c\in C\) such
that \(f+zg-c\) is supported on \(T\).  Taking syndromes, this is equivalent to
\(u+zv\in W_T\), which is the first displayed equation by the recurrence
criterion.  Under that equation, simultaneous explanation of \(f\) and \(g\) on
the same \(S\) is equivalent to \(u,v\in W_T\).  Since
\(u=(u+zv)-zv\), this is equivalent to \(v\in W_T\), hence to
\(H_{t,j}(v)\boldsymbol\ell_T=0\).  Noncontainment is therefore exactly the
negation of that condition.
\end{proof}

\subsection{Interleaved codegree reduction}

\textbf{Status: \textsc{New-local} reduction; saving remains conditional.}
This result is useful for the L2 interleaved-list ledger because it replaces
the naive Cartesian product by a recursion through higher-agreement tails.

Let \(C=\RS[F,D,k]\).  For a word \(V:D\to F\) and codeword \(c\in C\), write
\[
  A_V(c)=\{x\in D:c(x)=V(x)\},
  \qquad
  \operatorname{Fib}_V(s)=\{c\in C:|A_V(c)|\ge s\},
\]
and \(M_V(s)=|\operatorname{Fib}_V(s)|\).  For a \(\mu\)-row word
\(U=(U_1,\ldots,U_\mu)\), define
\[
  \Lambda_\mu^{(s)}(U)
  =
  \#\{(c_1,\ldots,c_\mu)\in C^\mu:
  |\cap_i A_{U_i}(c_i)|\ge s\}.
\]

\begin{theorem}[two-regime codegree bound]
\label{thm:l2-codegree}
For every agreement threshold \(a\),
\[
  \Lambda_2^{(a)}(U_1,U_2)
  \le
  M_{U_2}(a)+M_{U_2}(2a-k)\,M_{U_1}(a).
\]
More generally,
\[
  \Lambda_\mu^{(a)}(U_1,\ldots,U_\mu)
  \le
  \Lambda_{\mu-1}^{(a)}(U_2,\ldots,U_\mu)
  +
  \Lambda_{\mu-1}^{(2a-k)}(U_2,\ldots,U_\mu)\,M_{U_1}(a).
\]
\end{theorem}

\begin{proof}
For the two-row case, sum over \(c_2\in\operatorname{Fib}_{U_2}(a)\), and put
\(N_2=|A_{U_2}(c_2)|\).  The possible \(c_1\)'s are codewords agreeing with
\(U_1\) on at least \(a\) points of \(A_{U_2}(c_2)\).  If
\(N_2<2a-k\), then two such \(c_1\)'s would agree with each other on more than
\(k\) points, forcing equality.  Thus this punctured list has size at most
one.  If \(N_2\ge2a-k\), use the trivial bound \(M_{U_1}(a)\).  Summing these
two regimes gives the displayed two-row inequality.

For the \(\mu\)-row case, fix \((c_2,\ldots,c_\mu)\) and put
\[
  S=\bigcap_{i=2}^\mu A_{U_i}(c_i).
\]
The listed \(c_1\)'s must agree with \(U_1\) on at least \(a\) points of \(S\).
If \(|S|<2a-k\), the same unique-decoding argument gives at most one such
\(c_1\).  If \(|S|\ge2a-k\), use the bound \(M_{U_1}(a)\).  Counting the two
classes of \((c_2,\ldots,c_\mu)\) gives the recursion.
\end{proof}

\begin{remark}
The reduction is unconditional.  The desired L2 saving still requires an
L1-family input saying that the tail lists at agreement \(2a-k\) are small
after quotient-periodic contributions are budgeted.
\end{remark}

\subsection{Deep-point cap dependency split}

\textbf{Status: \textsc{Wrapper} / \textsc{Audit}.}
This result does not edit Paper D, but it explains why the headline MCA cap can
be routed locally without using the imported Crites--Stewart conversion.

\begin{proposition}[CS25-free route to the Paper D MCA cap]
\label{prop:deep-point-cap}
Assume the finite-field, coset, divisibility, and binomial hypotheses used in
Paper D's universal cap theorem.  Let \(C=\RS[F,D,k]\), \(C^+=\RS[F,D,k+1]\),
\(q=|F|\), and suppose the elementary quotient-locator fiber construction gives
a \(C^+\)-list of size
\[
  L\ge \binom{N}{\rho N+2}/|B|\ge q/k+1
\]
at the endpoint \(\delta_N=1-\rho-2/N\).  Then there is a support-wise MCA-bad
line for \(C\) with bad-slope density strictly larger than
\[
  \frac1{2k}\left(1-\frac nq\right).
\]
By support-wise MCA monotonicity, the same lower bound holds for all
\(\delta_N\le\delta<1-\rho\).
\end{proposition}

\begin{proof}
Let \(U:D\to F\) be the received word with a \(C^+\)-list
\(\{P_1,\ldots,P_L\}\) at agreement \(m=k+2n/N\).  For
\(\alpha\in F\setminus D\), form
\[
  f_\alpha(x)=\frac{U(x)}{x-\alpha},
  \qquad
  g_\alpha(x)=-\frac1{x-\alpha}.
\]
For every listed \(P_i\), the slope \(z=P_i(\alpha)\) gives the codeword
\[
  Q_i(X)=\frac{P_i(X)-P_i(\alpha)}{X-\alpha}\in F[X]_{<k}
\]
on the same agreement support.  Conversely every such slope comes from a
listed \(P_i\).  Since \(m>k\), the direction \(g_\alpha\) cannot be explained
by a degree-\(<k\) polynomial on the same support, so these slopes are
support-wise MCA-bad.

Averaging over \(\Omega=F\setminus D\), two distinct degree-\(<k+1\)
polynomials collide at at most \(k\) points of \(\Omega\).  Therefore some
\(\alpha\) has at least
\[
  M\ge \frac{L}{1+k(L-1)/(q-n)}
\]
distinct values among \(P_1(\alpha),\ldots,P_L(\alpha)\).  Its bad-slope
density is at least
\[
  \frac{L(q-n)}{q(q-n+k(L-1))}.
\]
This is strictly greater than \((q-n)/(2kq)\) exactly when
\[
  2kL>q-n+k(L-1).
\]
The lower bound \(L\ge q/k+1\) gives \(kL\ge q+k\), so the left-minus-right
quantity is at least \(n+2k>0\).  This proves the endpoint bound, and
monotonicity in \(\delta\) extends it to the stated interval.
\end{proof}

\subsection{Common code-line residual budget}

\textbf{Status: \textsc{New-local} finite MDS theorem.}
This M2 lemma is a guardrail for line-decoding imports: a close common
code-line exception still pays for residual coordinates outside the common
support.

\begin{proposition}[common code-line residual budget]
\label{prop:common-residual}
Let \(C\subseteq F^D\) be an MDS linear code of dimension \(k\), so every
nonzero codeword has fewer than \(k\) zeros on \(D\).  Let
\(\ell_z=f+zg\) be a received line and suppose that for some codewords
\(c_f,c_g\in C\) there is a common support \(S_0\subseteq D\) of size \(b\)
such that \(f=c_f\) and \(g=c_g\) on \(S_0\).  Fix an agreement threshold
\(a\) with \(a+b-n\ge k\).  Put \(\Omega=D\setminus S_0\),
\[
  f'=f-c_f,\qquad g'=g-c_g,\qquad
  h=\max(1,a-b),
\]
and
\[
  c_0=\#\{x\in\Omega:f'(x)=g'(x)=0\}.
\]
Every support-wise noncontained slope at agreement \(a\) satisfies
\[
  \#\{x\in\Omega:f'(x)+zg'(x)=0\}\ge h.
\]
Consequently, if \(h>c_0\), then the number of such slopes is at most
\[
  \left\lfloor\frac{|\Omega|-c_0}{h-c_0}\right\rfloor.
\]
\end{proposition}

\begin{proof}
If \(\ell_z\) is explained on a support \(S\) of size at least \(a\), then
\[
  |S\cap S_0|\ge a-|\Omega|=a+b-n\ge k.
\]
On \(S\cap S_0\), the explaining codeword agrees with \(c_f+zc_g\).  By the
MDS zero-rigidity condition, the two codewords are equal.  Thus, outside
\(S_0\), the line can only be explained where \(f'+zg'=0\), and at least
\(h=\max(1,a-b)\) such outside zeros are needed for a noncontained support.

Each non-common residual coordinate \(x\in\Omega\) with \((f'(x),g'(x))\ne
(0,0)\) can vanish for at most one finite slope \(z\).  A bad slope needs at
least \(h-c_0\) private non-common residual zeros after the \(c_0\) common zeros
are counted.  Charging these private coordinates to slopes gives the stated
packing bound.
\end{proof}

\section{Recent PR Triage: L1, F1, M1, and Challenge-Map Ledgers}
\label{sec:recent-pr-triage}

\textbf{Status: \textsc{Audit} / \textsc{Experimental} / bounded
\textsc{Proved} notes.}
The open PR batch of June 27, 2026, adds useful proof infrastructure but no new
unconditional prize-scale threshold beyond the tangent-floor consequences already
in the high-agreement ledger.  The promotion rule used here is conservative:
bounded toy theorems and exact normal forms may enter the experimental notes,
while computation-dependent numerators and generated proof programs remain
labelled as such.

\subsection{L1: proper-subgroup and monomial-prefix lanes}

Scott Hughes' \(d=3\) proper-subgroup note records the actual \(H^{2k}\)
collision object for the odd moments \(1,3,5\).  For \(p>5\), \(H\le\F_p^*\)
of order \(n\), and
\[
  S_H(a_1,a_3,a_5)
  =
  \sum_{h\in H}\psi(a_1h+a_3h^3+a_5h^5),
\]
the exact Fourier identity is
\[
  V_{H,k}^{(3)}
  =
  p^{-3}\sum_{a_1,a_3,a_5\in\F_p}
  |S_H(a_1,a_3,a_5)|^{2k}.
\]
After splitting frequencies into the linear, cubic, and quintic strata, and
using the stated one-variable Gauss/Katz inputs, the note gives
\[
0\le
V_{H,k}^{(3)}-\frac{n^{2k}}{p^3}
\le
\frac{p-1}{p^3}p^k
+\frac{p(p-1)}{p^3}(3\sqrt p)^{2k}
+\frac{p^2(p-1)}{p^3}(5\sqrt p)^{2k}.
\]
This is useful L1 infrastructure, not a reserve-scale arbitrary-word locator
local limit.

Vadim Avdeev's monomial-prefix note settles one bounded toy lane over
\[
  F=\F_{17}[z]/(z^{32}-3),\qquad H=\langle z\rangle,\qquad |H|=512,
\]
with degree convention \(\deg P\le256\).  In the range \(258\le A\le512\),
the admissible monomial agreement sizes are
\[
\begin{gathered}
258,259,260,262,264,268,272,280,\\
288,304,320,352,384,512.
\end{gathered}
\]
The proof combines a local length-\(16\) imbalance check over \(\F_{17}\), a
dyadic power-sum descent gate, and quotient-complement survivor families.  This
should be cited only as a monomial-prefix benchmark, not as an arbitrary-word
list theorem.

\subsection{F1: arbitrary-anchor residue clouds}

The F1 arbitrary-anchor update splits the balanced residue-cloud problem from
the residual-list problem.  If \(t<\sigma\), residue-line bad slopes inject into
an ordinary list for \(\RS[F,D,k+t]\) at residual slack \(\sigma-t\).  In the
balanced case \(t=\sigma\), arbitrary anchors have a real free-packing floor:
\[
  \Lambda_{\rm NC}
  \ge
  \left\lfloor\frac{|D|-k}{\sigma}\right\rfloor.
\]
Moreover this is the exact ceiling for ordered \(k\)-degenerate support
families, so any larger arbitrary-anchor packet must use dense overlaps.  The
dense-overlap gate is explicit: for two supports \(S,T\) with overlap \(J\),
compatibility of distinct slopes is controlled by whether the residue direction
\(N/E\) is degree-\(<k\) on \(J\).  This is a useful F1 warning and search
normal form, not an extension-line lift theorem.

\subsection{M1: all-line Hankel aperiodic packet}

The large M1 PR is not promoted wholesale.  The useful distillation is the exact
Hankel-pencil object.  For a line \((f,g)\), syndromes \(u=\operatorname{Syn}(f)\)
and \(v=\operatorname{Syn}(g)\), and a split complement \(T\) with locator vector
\(\ell_T\), finite bad slopes are governed by
\[
  \bigl(H_{t,j}(u)+zH_{t,j}(v)\bigr)\ell_T=0,
  \qquad
  H_{t,j}(v)\ell_T\ne0.
\]
In the \(t=2\) window this becomes
\[
  b_T\ne0,\qquad \det[a_T\ b_T]=0,
  \qquad
  a_T=H_{2,j}(u)\ell_T,\quad b_T=H_{2,j}(v)\ell_T.
\]
Same-slope one-exchange collisions lie in fixed-slope root slices, and the
residual one-exchange graph can be further organized into quadratic companion
slices and top packets.  These reductions define a promising M1 proof program,
but they do not yet prove the desired uniform polynomial bound on residual
aperiodic slope images.

\subsection{Challenge-map pullbacks and public status corrections}

The adjacent-ledger update adds the missing pullback rule from slope ledgers to
protocol challenge maps.  For a challenge-to-slope map \(\phi:K\to Z\), a bad
set \(B\subseteq Z\) pulls back with probability
\[
  \frac{|\phi^{-1}(B)|}{|K|}.
\]
If the nonempty fibers have sizes \(s_1\ge s_2\ge\cdots\), the adversarial
envelope for \(|B|=L\) is \((s_1+\cdots+s_L)/|K|\).  For an \(\F_q\)-linear map
of rank \(r\), the effective denominator is \(q^r\), not the ambient challenge
space size.  This prevents accidental multiplication of denominators in protocol
ledgers.

The public-board status corrections are:
\[
\begin{array}{c|c|c|c}
\text{row} & a & \text{tangent floor} & \text{status}\\
\hline
\text{Cycle116 gate} & 262 & 251 & \text{gate unconditional; exact count conditional}\\
\text{Cycle119 gate} & 263 & 250 & \text{gate unconditional; exact count conditional}\\
\text{reserve272} & 272 & 241 & \text{proved but subsumed}\\
\text{reserve288} & 288 & 225 & \text{proved but subsumed}\\
\text{reserve313} & 313 & 200 & \text{proved but subsumed}
\end{array}
\]
The exact Cycle84 numerator \(52{,}747{,}567{,}092\) remains a
computation-dependent record; only the weaker \(>2^{-128}\) gate follows from
the generic tangent floor without that finite census.

% High-agreement material promoted to clean notes.
\input{notes/high_agreement/tangent_staircase}
\input{notes/high_agreement/line_ca_projective}
\input{notes/high_agreement/curve_mca_ca}
\input{notes/high_agreement/interleaved_uniqueness}
\input{notes/high_agreement/current_row_protocol_ledger}
\input{notes/high_agreement/general_threshold_compiler}
\section{Towards-Prize Finite-Threshold Theorems}
\label{sec:towards-prize-thresholds}

\textbf{Status: \textsc{New-local} finite theorem infrastructure plus
subsumed strict264 proof record.}
The results in this section are deliberately finite and certificate-facing.  They
are meant to move the experimental ledger from lower-bound numerators toward the
integer agreement staircase needed by the Proximity Prize.  They do not prove the
corrected Paper B local-limit conjecture.  The later
high-agreement tangent staircase supersedes the old strict264/265 search target
as a threshold-pinning route for the \(\F_{17^{32}}\), \(n=512\), \(k=256\)
row; the strict264 material below remains useful as certificate language and
as a record of quotient-core mechanisms.

For a received line \(\ell_z=f+zg\), write
\[
  \operatorname{Bad}_{f,g}(C,a)
\]
for the set of finite slopes \(z\in F\) for which there is a support
\(S\subseteq D\), \(|S|\ge a\), and a codeword \(c\in C\) satisfying
\(c|_S=(f+zg)|_S\), but there is no pair of codewords
\(c_f,c_g\in C\) with \(c_f|_S=f|_S\) and \(c_g|_S=g|_S\).  Put
\[
  \operatorname{LD}_{\rm sw}^{f,g}(C,a)
  =|\operatorname{Bad}_{f,g}(C,a)|,
  \qquad
  \operatorname{LD}_{\rm sw}(C,a)
  =\max_{f,g}\operatorname{LD}_{\rm sw}^{f,g}(C,a),
\]
where the maximum is over the line family allowed by the sampler under
consideration.  The field paying the denominator is always \(\qline\), not
silently \(\qgen\) or \(\qchal\).

\begin{proposition}[certificate-to-\(\operatorname{LD}_{\rm sw}\) gate]
\label{prop:certificate-to-ldsw}
Let \(C=\RS[F,D,k]\), let \(a\ge k\), and fix a received line \(f+zg\).  Suppose
there is a finite set \(\mathcal C\) of tuples
\[
  (z_i,S_i,P_i),
  \qquad z_i\in F,
  \quad S_i\subseteq D,
  \quad |S_i|\ge a,
  \quad P_i\in F[X]_{<k},
\]
with the following properties:
\begin{enumerate}
\item the slopes \(z_i\) are pairwise distinct;
\item \(P_i(x)=f(x)+z_i g(x)\) for every \(x\in S_i\);
\item there are no \(P_{i,f},P_{i,g}\in F[X]_{<k}\) satisfying
  \(P_{i,f}|_{S_i}=f|_{S_i}\) and \(P_{i,g}|_{S_i}=g|_{S_i}\).
\end{enumerate}
Then
\[
  \operatorname{LD}_{\rm sw}^{f,g}(C,a)\ge |\mathcal C|,
  \qquad
  \operatorname{LD}_{\rm sw}(C,a)\ge |\mathcal C|.
\]
\end{proposition}

\begin{proof}
Each tuple certifies that the slope \(z_i\) is explained on a support of size at
least \(a\), and the third condition is exactly support-wise noncontainment on
that support.  Pairwise distinctness of the slopes prevents multiple tuples from
paying for the same bad slope.  Thus all \(z_i\)'s lie in
\(\operatorname{Bad}_{f,g}(C,a)\), giving the first inequality.  The second
follows from the definition of \(\operatorname{LD}_{\rm sw}(C,a)\) as a maximum
over lines.
\end{proof}

\begin{corollary}[strict264 certificate target]
\label{cor:strict264-certificate-target}
For the row
\[
  C=\RS[\F_{17^{32}},H,256],
  \qquad |H|=512,
\]
a strict264 certificate consists of seven tuples in
Proposition~\ref{prop:certificate-to-ldsw} with \(a=264\).  Such a certificate
proves
\[
  \operatorname{LD}_{\rm sw}(C,264)\ge 7.
\]
\end{corollary}

\begin{proof}
Apply Proposition~\ref{prop:certificate-to-ldsw} with
\(|\mathcal C|=7\) and \(a=264\).
\end{proof}

\begin{proposition}[fixed-locator unique-slope principle]
\label{prop:fixed-locator-unique-slope}
Use the notation of Theorem~\ref{thm:syndrome-pencil}.  Fix
\(a\ge k\), put \(t=a-k\), \(j=n-a=r-t\), and fix a squarefree
\(D\)-split locator \(L_T\) of degree \(j\).  Let
\[
  A_T=H_{t,j}(u)\boldsymbol\ell_T,
  \qquad
  B_T=H_{t,j}(v)\boldsymbol\ell_T.
\]
If \(B_T\ne0\), then this locator contributes at most one finite
support-wise noncontained slope.  More precisely, a slope exists exactly when
\(A_T\) is a scalar multiple of \(B_T\), in which case the unique slope is
\[
  z_T=-A_{T,m}/B_{T,m}
\]
for any coordinate \(m\) with \(B_{T,m}\ne0\), and the same value must be
obtained from every nonzero coordinate of \(B_T\).
Consequently
\[
  \operatorname{LD}_{\rm sw}^{f,g}(C,a)
  \le
  \#\{T\subset D:
        |T|=n-a,
        L_T\text{ squarefree and }D\text{-split},
        B_T\ne0,
        A_T\in F B_T\}.
\]
\end{proposition}

\begin{proof}
For the fixed locator, Theorem~\ref{thm:syndrome-pencil} gives the incidence
equation
\[
  A_T+zB_T=0
\]
and the noncontainment condition \(B_T\ne0\).  If \(B_T\ne0\), any solution
\(z\) is forced by any coordinate where \(B_T\) is nonzero.  Existence is exactly
the consistency condition that all coordinates give the same scalar, equivalently
\(A_T\in F B_T\).  Counting possible locators gives the final bound; different
locators may still collide to the same slope, so the displayed quantity is an
upper bound on distinct slopes.
\end{proof}

\begin{remark}[why this helps the 265 upper bound]
For the current \(n=512,k=256\) row, this proposition remains useful for
duplicate-aware locator searches.  The old proposed upper bound
\(\operatorname{LD}_{\rm sw}(C,265)\le6\) is now known to be false by
Theorem~\ref{thm:moving-root-tangent-floor}, which already gives
\(\operatorname{LD}_{\rm sw}(C,265)\ge248\).  Future upper-bound searches should
therefore start beyond the exact tangent gate, at agreement \(507\) and higher,
or explicitly isolate non-tangent mechanisms.
\end{remark}

\begin{theorem}[subfield confinement for base-valued lines]
\label{thm:subfield-confinement-base-lines}
Let \(K\subseteq F\) be a subfield, let \(D\subset K\), and let
\(C_F=\RS[F,D,k]\).  Suppose \(f,g:D\to K\), and let
\(S\subseteq D\) have \(|S|\ge k\).  If \(z\in F\setminus K\) and there is a
polynomial \(P\in F[X]_{<k}\) with
\[
  P(x)=f(x)+zg(x)
  \qquad (x\in S),
\]
then there are polynomials \(P_f,P_g\in K[X]_{<k}\) such that
\[
  P_f|_S=f|_S,
  \qquad
  P_g|_S=g|_S.
\]
Consequently, for \(K\)-valued received lines and agreement \(a\ge k\), every
support-wise noncontained finite slope lies in \(K\).
\end{theorem}

\begin{proof}
Choose a subset \(S_0\subseteq S\) of size \(k\).  Interpolate the values of
\(f\) and \(g\) on \(S_0\) to obtain unique polynomials
\(P_f,P_g\in K[X]_{<k}\).  On \(S_0\), the polynomial
\(P_f+zP_g\) agrees with \(P\).  Since both have degree less than \(k\) and agree
on \(k\) points, they are equal as polynomials over \(F\).  For every
\(x\in S\), therefore,
\[
  0=f(x)+zg(x)-P(x)
   =(f(x)-P_f(x))+z(g(x)-P_g(x)).
\]
Both coefficients in the final expression lie in \(K\).  Since
\(z\notin K\), the elements \(1,z\) are linearly independent over \(K\).  Hence
both coefficients vanish for every \(x\in S\), proving the separate explanations
of \(f\) and \(g\).  Thus any explained slope outside \(K\) is support-wise
contained, so a noncontained slope must lie in \(K\).
\end{proof}

\begin{remark}[extension-field warning]
Theorem~\ref{thm:subfield-confinement-base-lines} is intentionally one-sided.
It only treats \(K\)-valued received lines.  It does not rule out genuinely
\(F\)-valued residue-line witnesses, and therefore must not be used as an
extension-field MCA theorem without an additional hypothesis forcing the line to
be \(K\)-valued.
\end{remark}

\begin{theorem}[seven-slope arithmetic gate over \(\F_{17^{32}}\)]
\label{thm:seven-slope-arithmetic-gate}
Let \(\qline=17^{32}\).  If a row over \(\F_{17^{32}}\) has
\(\operatorname{LD}_{\rm sw}(C,264)\ge7\), then at radius
\[
  \delta=1-\frac{264}{512}=\frac{31}{64}
\]
its support-wise MCA error is strictly larger than \(2^{-128}\).  In particular,
for the \(n=512,k=256\) row, any strict264 seven-slope certificate proves
\[
  \varepsilon_{\rm mca}(C,31/64)>2^{-128}.
\]
\end{theorem}

\begin{proof}
The MCA sampler over finite slopes has denominator \(\qline=17^{32}\).  Seven
bad slopes therefore give error at least \(7/17^{32}\).  The exact integer
comparison is
\[
  7\cdot 2^{128}-17^{32}
  =14064973686101998399515954701426232831>0.
\]
Thus \(7/17^{32}>2^{-128}\).  Agreement \(264\) on a domain of size \(512\)
corresponds to relative radius \(1-264/512=31/64\), giving the claim.
\end{proof}

\begin{theorem}[one-step staircase pinning criterion]
\label{thm:one-step-staircase}
Fix a finite-slope sampler of denominator \(\qline\) and a target
\(\varepsilon_*=2^{-128}\).  Let
\[
  B(a)=\operatorname{LD}_{\rm sw}(C,a)
\]
for the allowed line family, and let \(\delta_a=1-a/n\).  If, for some integer
\(a\ge k\),
\[
  B(a)>\varepsilon_*\qline
  \qquad\text{and}\qquad
  B(a+1)\le \varepsilon_*\qline,
\]
then the closed-ball agreement staircase is unsafe at radius \(\delta_a\) and
safe on the next open interval below it, including the grid radius
\(\delta_{a+1}\).  Equivalently, the largest grid radius certified safe is
\(\delta_{a+1}\), while the continuous supremum of certified safe radii is
\(\delta_a\) and is not attained under the closed endpoint convention.

Before the tangent staircase was isolated, the special case
\[
  B(264)\ge7,
  \qquad
  B(265)\le6
\]
would have pinned the finite row to an unsafe/safe transition between
\[
  \delta_{265}=247/512
  \qquad\text{and}\qquad
  \delta_{264}=31/64.
\]
For the \(\F_{17^{32}}\), \(n=512\), \(k=256\) row, the premise
\(B(265)\le6\) is false by the moving-root tangent floor.  The actual
finite-slope staircase gate supplied by Corollary~\ref{cor:f17-32-exact-tangent-gate}
is \(B(506)=7\), \(B(507)=6\).
\end{theorem}

\begin{proof}
The function \(B(a)\) is nonincreasing in \(a\), because raising the agreement
threshold only removes valid supports.  At radius \(\delta_a\), the closed-ball
predicate allows agreement at least \(a\), so the error is \(B(a)/\qline\), which
is larger than \(\varepsilon_*\) by assumption.  At radius \(\delta_{a+1}\), the
predicate requires agreement at least \(a+1\), so the error is
\(B(a+1)/\qline\), which is at most \(\varepsilon_*\).

More generally, any radius \(\delta<\delta_a\) sufficiently close to
\(\delta_a\) has integer distance bound at most \(n-a-1\), hence agreement at
least \(a+1\).  Thus the closed endpoint at \(\delta_a\) is the first unsafe
grid step, while the safe side is immediately below that endpoint.  For
\(\qline=17^{32}\), the inequalities
\[
  6\cdot2^{128}<17^{32}<7\cdot2^{128}
\]
convert the printed integer conditions into the two displayed error inequalities,
and \(1-265/512=247/512\), \(1-264/512=31/64\).
\end{proof}

\section{Non-Claims}
\label{sec:nonclaims}

This note does not claim:
\begin{itemize}
\item a proof of the corrected MCA conjecture;
\item a positive theorem above corrected reserve;
\item a \(\qgen\) local-limit theorem;
\item a list, CA, MCA, line-decoding, SNARK, or protocol consequence;
\item a large \(\Theta(p^2)\) counterpacket;
\item a new prize-worthy numerator beyond the current Cycle116/119
  \(52{,}747{,}567{,}092\) finite/source-scoped record;
\item priority for the BCHKS quotient-locator proof pattern.
\end{itemize}

The mathematical value is narrower.  On the imported side, the file gives a
provenance-safe dictionary and wrapper for using BCHKS without claiming it as
new.  On the local Paper B side, the possible large branch in the restricted
quadratic-extension window must satisfy an explicit algebraic identity before
it can even be surface-sized.

\appendix

\section{BibTeX Entry to Copy into Main Papers}

\begin{verbatim}
@misc{BCHKS25,
  author = {Eli Ben-Sasson and Dan Carmon and Ulrich Habock and
            Swastik Kopparty and Shubhangi Saraf},
  title  = {On Proximity Gaps for Reed--Solomon Codes},
  year   = {2025},
  note   = {Manuscript dated November 11, 2025},
  url    = {https://www.math.toronto.edu/swastik/rs-proximity-gaps-2025.pdf}
}
\end{verbatim}

\begin{thebibliography}{99}
\bibitem{ProximityPrize26}
The Proximity Prize.  \emph{The Proximity Prize: Reed--Solomon Challenge}.
Preliminary version, accessed June 26, 2026.
\url{https://proximityprize.org/}.

\bibitem{BCHKS25}
Eli Ben-Sasson, Dan Carmon, Ulrich Hab\"ock, Swastik Kopparty, and Shubhangi
Saraf.  \emph{On Proximity Gaps for Reed--Solomon Codes}.  Manuscript dated
November 11, 2025.
\url{https://www.math.toronto.edu/swastik/rs-proximity-gaps-2025.pdf}.
\end{thebibliography}

\end{document}
