\documentclass[11pt,a4paper]{amsart}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\emergencystretch=3em
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{array}
\usepackage{float}
\usepackage{aliascnt}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage[capitalize,nameinlink]{cleveref}
\numberwithin{equation}{section}

\newtheorem{theorem}{Theorem}[section]
\newaliascnt{proposition}{theorem}\newtheorem{proposition}[proposition]{Proposition}\aliascntresetthe{proposition}
\newaliascnt{lemma}{theorem}\newtheorem{lemma}[lemma]{Lemma}\aliascntresetthe{lemma}
\newaliascnt{corollary}{theorem}\newtheorem{corollary}[corollary]{Corollary}\aliascntresetthe{corollary}
\newaliascnt{definition}{theorem}\newtheorem{definition}[definition]{Definition}\aliascntresetthe{definition}
\newtheorem{hypothesis}[theorem]{Hypothesis}
\newtheorem{problem}[theorem]{Problem}
\theoremstyle{remark}
\newaliascnt{remark}{theorem}\newtheorem{remark}[remark]{Remark}\aliascntresetthe{remark}
\crefname{theorem}{Theorem}{Theorems}\Crefname{theorem}{Theorem}{Theorems}
\crefname{proposition}{Proposition}{Propositions}\Crefname{proposition}{Proposition}{Propositions}
\crefname{lemma}{Lemma}{Lemmas}\Crefname{lemma}{Lemma}{Lemmas}
\crefname{corollary}{Corollary}{Corollaries}\Crefname{corollary}{Corollary}{Corollaries}
\crefname{definition}{Definition}{Definitions}\Crefname{definition}{Definition}{Definitions}
\crefname{remark}{Remark}{Remarks}\Crefname{remark}{Remark}{Remarks}
\crefname{hypothesis}{Hypothesis}{Hypotheses}\Crefname{hypothesis}{Hypothesis}{Hypotheses}
\crefname{problem}{Problem}{Problems}\Crefname{problem}{Problem}{Problems}

\DeclareMathOperator{\RS}{RS}\DeclareMathOperator{\MCA}{MCA}\DeclareMathOperator{\CA}{CA}
\DeclareMathOperator{\rank}{rank}\DeclareMathOperator{\Span}{Span}\DeclareMathOperator{\Spec}{Spec}
\DeclareMathOperator{\Hom}{Hom}\DeclareMathOperator{\im}{im}\DeclareMathOperator{\codim}{codim}
\DeclareMathOperator{\supp}{supp}\DeclareMathOperator{\Fib}{Fib}\DeclareMathOperator{\Sym}{Sym}
\DeclareMathOperator{\Gr}{Gr}\DeclareMathOperator{\Ent}{H}\DeclareMathOperator{\ord}{ord}
\DeclareMathOperator{\Tr}{Tr}\DeclareMathOperator{\Gal}{Gal}\DeclareMathOperator{\Res}{Res}
\DeclareMathOperator{\Aut}{Aut}\DeclareMathOperator{\diag}{diag}\DeclareMathOperator{\wt}{wt}
\DeclareMathOperator{\Q}{Q}\DeclareMathOperator{\poly}{poly}\DeclareMathOperator{\wdeg}{wdeg}
\DeclareMathOperator{\Cen}{Cen}\DeclareMathOperator{\LineRay}{LineRay}\DeclareMathOperator{\dist}{dist}

\newcommand{\F}{\mathbb F}\newcommand{\B}{\mathbb B}\newcommand{\K}{\mathbb K}\newcommand{\Z}{\mathbb Z}
\newcommand{\A}{\mathbb A}\newcommand{\Pj}{\mathbb P}\newcommand{\C}{\mathbb C}\newcommand{\Prob}{\mathbb P}
\newcommand{\E}{\mathbb E}\newcommand{\eps}{\varepsilon}\newcommand{\emca}{\varepsilon_{\mathrm{mca}}}
\newcommand{\eca}{\varepsilon_{\mathrm{ca}}}\newcommand{\Htwo}{H_2}\newcommand{\Omc}{\Omega^{\circ}}
\newcommand{\Ccal}{\mathcal C}\newcommand{\Dcal}{\mathcal D}\newcommand{\Ecal}{\mathcal E}
\newcommand{\Fcal}{\mathcal F}\newcommand{\Gcal}{\mathcal G}\newcommand{\Hcal}{\mathcal H}
\newcommand{\Ical}{\mathcal I}\newcommand{\Jcal}{\mathcal J}\newcommand{\Lcal}{\mathcal L}
\newcommand{\Mcal}{\mathcal M}\newcommand{\Ncal}{\mathcal N}\newcommand{\Pcal}{\mathcal P}
\newcommand{\Qcal}{\mathcal Q}\newcommand{\Rcal}{\mathcal R}\newcommand{\Scal}{\mathcal S}
\newcommand{\Tcal}{\mathcal T}\newcommand{\Ucal}{\mathcal U}\newcommand{\Vcal}{\mathcal V}
\newcommand{\Wcal}{\mathcal W}\newcommand{\Xcal}{\mathcal X}\newcommand{\Ycal}{\mathcal Y}
\newcommand{\Zcal}{\mathcal Z}\newcommand{\Gord}{\Gamma^{\rm ord}}\newcommand{\Gsid}{\Gamma^{\rm sid}}
\newcommand{\Gprim}{\Gamma^{\rm prim}}\newcommand{\barN}{\overline N}\newcommand{\Renyi}{R\'enyi}
\newcommand{\Hb}{H_2}\newcommand{\UU}{\mathbb U}\newcommand{\abs}[1]{\lvert #1\rvert}
\newcommand{\norm}[1]{\lVert #1\rVert}\newcommand{\floor}[1]{\left\lfloor #1\right\rfloor}
\newcommand{\ceil}[1]{\left\lceil #1\right\rceil}\newcommand{\defeq}{\coloneqq}
\newcommand{\one}{\mathbf 1}\newcommand{\Fq}{\mathbb F_q}
\newcommand{\cA}{\mathcal A}\newcommand{\cB}{\mathcal B}\newcommand{\cC}{\mathcal C}
\newcommand{\cE}{\mathcal E}\newcommand{\cH}{\mathcal H}\newcommand{\cK}{\mathcal K}
\newcommand{\cL}{\mathcal L}\newcommand{\cM}{\mathcal M}\newcommand{\cP}{\mathcal P}
\newcommand{\cS}{\mathcal S}\newcommand{\cZ}{\mathcal Z}
\newcommand{\vander}[2]{(1,#1,\ldots,#1^{#2-1})}
\newcommand{\fall}[2]{#1^{\underline{#2}}}\newcommand{\rise}[2]{#1^{\overline{#2}}}
\newcommand{\Bbad}{B_{\mathrm{MCA}}}




\title[Grande Finale v4]{Grande Finale v4:\\
Exact Threshold Compilers, Primitive Q, and Order-$32$ Reed--Solomon MCA}
\author{Przemek Chojecki}
\hypersetup{
pdftitle={Grande Finale v4: Exact Threshold Compilers, Primitive Q, and Order-32 Reed--Solomon MCA},
pdfauthor={Przemek Chojecki},
pdfsubject={A complete companion to CAP25 v13.2 integrating exact threshold refinements, primitive Q, support compilers, order-32 rank, rational atoms, owner localization, and spread-core incidence},
pdfkeywords={Reed--Solomon codes, mutual correlated agreement, primitive Q, Sidon moments, generalized Hamming weights, order-32 rank, rational atoms, spread cores}
}
\subjclass[2020]{94B35, 11T71, 05B40}
\keywords{Reed--Solomon codes, mutual correlated agreement, primitive Q, Sidon moments, generalized Hamming weights, order-$32$ rank, rational atoms, spread cores}
\date{July 2026}

\begin{document}
\begin{abstract}
This paper is a complete companion to CAP25 v13.2 \cite{CAP25v132}.  It imports by citation, and does not reprove, the support-wise MCA conventions, universal cap, four deployed unsafe endpoints, identity-prefix and simple-pole constructions, aperiodic and subfield floors, prefix rigidity and exact second moment, quotient and extension reductions, balanced-core reduction, and normalized finite ledger established there.

The first half develops the full safe-side compiler.  It proves exact support sparsification, syndrome--secant and fixed-union compilers, recursive affine-span and generalized-weight bounds, common-zero and directional Johnson estimates, codimension-one and arbitrary-codimension support-flag recursions, a minimum-distance sharpening using the actual direction-code support, fixed-mismatch puncturing, a quadratic mean-overlap staircase, exact quotient--remainder prefix normal forms, effective-image Fourier normalization, primitive Q after an explicit Sidon payment, saturation, a moving-root theorem for one-parameter split pencils, and the implication that a row-sharp Q theorem pays the primitive shift-pair ledger.

The second half develops a different MCA completion mechanism.  A rank-two reduced intersection matrix gives an exact kernel dictionary and shows that the deployed critical order is $32$.  Exact dyadic descent identifies the quotient branch.  Maximal-support interpolation excludes all primitive slope degrees below $18$, while support-collapsed interpolation extracts every low-complexity explanation into a scalar-locator rational atom.  Rational atoms satisfy collision rigidity and local-to-global coherence.  A finite critical example shows that primitive spread cores can exist, so the remaining theorem is abundance rather than nonexistence.  Canonical owner localization pays every small-owner atom, component-free owner pencils contribute at most seven rich points, core-compatible slopes contribute at most $58$, a complete correction ray contributes at most $2(n-m+1)+963$, and proper or clone-tolerant correction spaces are paid in the explicit deployed ranges.

The manuscript does not assert the adjacent safe rows unconditionally.  For MCA, the remaining inputs are the classification and payment of high-dimensional positive-dimensional correction components, the row-sharp image bound for one coherent large-owner atom---most sharply the Mersenne-31 factor-$9.57219783037$ prefix target---and complete routing of denominator-root, extension, clone, imperfect-quotient, and near-sunflower exceptions.  For the list rows, the remaining inputs are the row-sharp high-nullity prefix and arbitrary-word interior bounds, extension payment, and one exact summed integer certificate.
\end{abstract}
\maketitle
\tableofcontents

\section{Scope and relation to CAP25 v13.2}\label{sec:relation-v132}
Throughout, CAP25 v13.2 \cite{CAP25v132} is the foundational source for the deployed unsafe frontier and the normalized first-match ledger.  Its theorems are invoked by citation rather than re-numbered here.  This paper contains all of the additional threshold, compiler, rank, atom, and spread-incidence results needed for the current completion programme.

\begin{center}
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.39\textwidth}>{\raggedright\arraybackslash}p{0.53\textwidth}@{}}
\toprule
Imported from CAP25 v13.2 & Proved in this paper\\
\midrule
MCA conventions, universal cap, active unsafe endpoints & Exact sparsification, syndrome--secant, fixed-union, affine-span, generalized-weight, support-flag, and minimum-distance compilers\\
Identity-prefix, pole-line, aperiodic, subfield, quotient, and extension packages & Quadratic threshold staircases, exact profile normal forms, effective Fourier normalization, and primitive Q after the stated Sidon payment\\
Prefix rigidity, exact second moment, balanced-core reduction, normalized ledger & Saturation, moving-root BC, Q $\Rightarrow$ SP, order-$32$ rank, rational-atom extraction and coherence, owner localization, and spread-core correction incidence\\
\bottomrule
\end{tabular}
\end{center}

The paper uses the closed integer-ball convention of CAP25 v13.2.  An adjacent certificate consists of the imported unsafe inequality at agreement $a_0$ and a proved upper inequality at $a_0+1$.  Structural reductions, asymptotic estimates, and route-cut boundaries are not called adjacent certificates unless they fit the literal row budget.

\section{Main theorem package}\label{sec:new-contributions}
\begin{theorem}[Integrated theorem package]\label{thm:v4-package}
The following statements hold.
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=*]
\item The exact support, syndrome--secant, fixed-union, affine-span, generalized-weight, common-zero, codimension-one, support-flag, minimum-distance, puncturing, directional-Johnson, paving, mean-overlap, packing, and explicit prime-row results of Part~I are unconditional.
\item The quotient--remainder normal form, partial-occupancy disintegration, effective-image Fourier identities, and profile add-back of Part~II are unconditional.  Primitive Q follows from the Sidon-moment payment of Part~III, and the shallow Fourier theorem proves that payment in its displayed range.
\item Saturation, the one-parameter moving-root theorem, and Q $\Rightarrow$ SP are unconditional.  The finite compilers pay the displayed low-nullity, low-affine-span, common-zero, support-flag, and direction-defect ranges.
\item The rank-two kernel dictionary, critical order $32$, global affine-block bound, dyadic pair descent, rational-profile converse, slope-degree barrier, low-complexity atom extraction, collision rigidity, atom coherence, owner localization, owner-pencil incidence bound, core-compatible abundance bound, complete correction-ray bound, and the stated proper and clone-tolerant correction-space bounds are unconditional.
\item The two deployed MCA adjacent rows follow from the three explicit inputs in \cref{thm:conditional-final}; the two list adjacent rows follow from the exact summed certificate in \cref{thm:exact-completion-certificate}.  Those remaining inputs are not asserted in this paper.
\end{enumerate}
\end{theorem}

\part{Exact threshold refinements beyond CAP25 v13.2}

\section{Exact decomposition of the mutual layer}\label{sec:mutual-decomposition}
Let $C\subseteq\F^D$ be linear, let $a$ be an agreement threshold, and put $t=|D|-a$.  We use the foundation's definitions of support-wise MCA-badness and of the challenge-restricted numerator $B^{\rm MCA}_{C,\Gamma}(a)$ \cite[Secs.~1--2]{CAP25v132}.

A received pair is \emph{column-far at agreement $a$} when no support of size at least $a$ simultaneously explains its two coordinates.  Let $B^{\rm CA}_{C,\Gamma}(a)$ be the maximum number of challenge slopes whose affine combination is explained on some support of size at least $a$, maximized over column-far pairs.  Define the sparse mutual numerator
\[
 \sigma_{C,\Gamma}(a)=\max\#\{\gamma\in\Gamma:\gamma\text{ is MCA-bad for }(e_0,e_1)\},
\]
where the maximum is over pairs with $|\supp(e_0)\cup\supp(e_1)|\le t$.

\begin{theorem}[Exact sparsification of the mutual layer]\label{thm:exact-sparsification}
For every linear code, every nonempty challenge set $\Gamma$, and every $a$,
\begin{equation}
 B^{\rm MCA}_{C,\Gamma}(a)=
 \max\{B^{\rm CA}_{C,\Gamma}(a),\sigma_{C,\Gamma}(a)\}.\label{eq:exact-sparsification}
\end{equation}
\end{theorem}
\begin{proof}
Both terms on the right maximize over subclasses of received pairs, so the left side dominates them.  Conversely fix a pair.  If it is column-far, its MCA-bad and CA-bad challenge slopes coincide.  Otherwise translate it by a codeword pair that explains it on one common support of size at least $a$.  The translated pair is supported on at most $t$ coordinates, and translation preserves, slope by slope and support by support, both affine explanation and simultaneous explanation.  Its bad set is therefore bounded by $\sigma_{C,\Gamma}(a)$.
\end{proof}

The foundation supplies the exact-agreement reduction, support uniqueness, tangent floor, and deep-regime theorem used below \cite[Secs.~13--14]{CAP25v132}.  We invoke those interfaces only by citation.

\section{Syndrome--secant geometry and finite ray compilers}
\label{sec:syndrome-exact}

The \emph{syndrome} of a word is the result of applying a parity-check
matrix; it vanishes exactly on codewords.  Thus syndrome space forgets the
part of a received word already lying in the code and retains only its error
class.  This description separates possible error supports from distinct
line parameters.  Put \(R=n-k\), the redundancy (and syndrome-space
dimension), and choose the generalized Vandermonde parity-check matrix
\(H\) with columns
\begin{equation}
 h_x=\lambda_x(1,x,\ldots,x^{R-1})^{\mathsf T},\qquad
 \lambda_x=\left(\prod_{y\in D\setminus\{x\}}(x-y)\right)^{-1}.\label{eq:parity-columns}
\end{equation}
Lagrange interpolation gives
\(\sum_{x\in D}\lambda_xx^j=0\) for \(0\le j\le n-2\), so this matrix
annihilates every degree-less-than-\(k\) evaluation.  Every set of at most
\(R\) columns is independent.  For \(E\subseteq D\), write
\(V_E=\Span\{h_x:x\in E\}\); it is exactly the set of syndromes of words
supported on \(E\).  We write \(s(u)=Hu^{\mathsf T}\) for the syndrome of
\(u\).

\begin{proposition}[Syndrome-line normal form]
\label{prop:syndrome-line-normal-form}
Let \(S=D\setminus E\).  A word \(u\) is explained on \(S\) if and only if
\(s(u)\in V_E\).  Consequently \(\gamma\) is MCA-bad on \(S\) for a pair
\((u_0,u_1)\) if and only if
\begin{equation}
 s(u_0)+\gamma s(u_1)\in V_E,
 \qquad
 \{s(u_0),s(u_1)\}\not\subseteq V_E.\label{eq:syndrome-line}
\end{equation}
For fixed \(E\), there is at most one such finite slope.
\end{proposition}

\begin{proof}
If \(u=c+e\), where \(c\in C\) and \(e\) is supported on \(E\), then
\(s(u)=s(e)\in V_E\).  Conversely, if
\(s(u)=\sum_{x\in E}e_xh_x\), subtract the word supported on \(E\) with
values \(e_x\); the result has zero syndrome and belongs to \(C\).  Apply
this equivalence to the line point and to both coordinates.  Passing
\eqref{eq:syndrome-line} to \(\F^R/V_E\) shows that two distinct solutions
would put both projected syndromes at zero, contradicting badness.
\end{proof}

Since \(\lambda_x\ne0\), one has
\([h_x]=[1:x:\cdots:x^{R-1}]\); these are the points of the rational
normal curve in projective syndrome space, while the weights
\(\lambda_x\) merely choose vector representatives.  A \emph{secant span} is the linear span
\(V_E\) of a selected set of those points.  We call the meeting of a
syndrome line with \(V_E\) \emph{transverse} when the entire line is not
contained in \(V_E\), equivalently when its two generators are not both in
\(V_E\).  The next result is a \emph{compiler} in the sense that it
translates the bad-slope problem, exactly and in both directions, into this
line--secant incidence problem.  A \emph{ray} means a one-dimensional
direction in syndrome or coefficient space; different raw witnesses may
represent the same ray and hence the same slope.

\begin{theorem}[Exact syndrome--secant compiler]
\label{thm:syndrome-secant-exact}
Put \(t=n-a\), and for a syndrome line
\(\ell_{y_0,y_1}=\{y_0+\gamma y_1:\gamma\in\F\}\) define
\begin{equation}
 \Theta_t(y_0,y_1)=
 \abs{\{\gamma\in\F:\exists E\subseteq D,\ \abs E\le t,
 y_0+\gamma y_1\in V_E,
 \ \{y_0,y_1\}\not\subseteq V_E\}}.\label{eq:transverse-secant-count}
\end{equation}
Then
\begin{equation}
 B_C^{\rm MCA}(a)=\max_{y_0,y_1\in\F^{n-k}}
                    \Theta_t(y_0,y_1).\label{eq:exact-secant-numerator}
\end{equation}
For each fixed \(E\), the affine line has at most one transverse
intersection parameter with \(V_E\).  For a Reed--Solomon code the
spaces \(V_E\) are the spans of at most \(t\) points of the weighted
rational normal curve in \eqref{eq:parity-columns}.  Thus the
higher-dimensional ray problem is exactly a transverse line--secant
incidence problem, with repeated intersection parameters deduplicated.
\end{theorem}

\begin{proof}
Apply \cref{prop:syndrome-line-normal-form} with \(S=D\setminus E\), and
take the union over \(\abs E\le t\).  The syndrome map is surjective, so
maximizing over received pairs is the same as maximizing over
\((y_0,y_1)\).  In the quotient \(\F^{n-k}/V_E\), a transverse
intersection solves
\(\overline y_0+\gamma\overline y_1=0\) with the two projected vectors
not both zero, and therefore has at most one finite solution.  The last
assertion is the Vandermonde description of the parity columns.
\end{proof}

A \emph{parity-column circuit} is a minimally linearly dependent set of
columns of \(H\).  The next lemma says that many distinct transverse rays
cannot all be supported inside an independent union of columns.

\begin{lemma}[Independent-union ray bound]
\label{lem:independent-union-rays}
Let every set of at most \(R\) parity columns be independent, put
\(t<R\), and fix a syndrome line.  For each slope in a transverse set
\(Z\), choose an error set \(E_\gamma\), \(\abs{E_\gamma}\le t\),
witnessing \eqref{eq:transverse-secant-count}.  If
\(U=\bigcup_{\gamma\in Z}E_\gamma\) has size at most \(R\), then
\(\abs Z\le t+1\).  Consequently, more than \(t+1\) transverse slopes
force the witness union to contain a parity-column circuit.
\end{lemma}

\begin{proof}
If \(\abs Z\le1\), there is nothing to prove; assume that \(Z\) contains
two distinct slopes.  Two distinct line points lie in \(V_U\), hence
\(y_0,y_1\in V_U\).
Column independence gives unique coefficient lifts
\(e_0,e_1\in\F^U\), and every chosen lift is
\(e_\gamma=e_0+\gamma e_1\).  Let \(U'\) be the set of \(s\) coordinates
where the pair \((e_0,e_1)\) is nonzero.  If \(s\le t\) and
\(E_\gamma\) contained all of \(U'\), then
\(y_0,y_1\in V_{U'}\subseteq V_{E_\gamma}\), contradicting the
transversality of this particular witness.  Hence some
\(x\in U'\setminus E_\gamma\) exists, and uniqueness of the lift gives
\(e_0(x)+\gamma e_1(x)=0\).  Each nonzero affine coordinate function has
at most one root, so \(\abs Z\le s\le t\).  If \(s>t\), every chosen lift of
weight at most \(t\) has at least \(s-t\) zero coordinates.  Double
counting the pairs \((\gamma,x)\) with
\(e_0(x)+\gamma e_1(x)=0\) gives
\(\abs Z(s-t)\le s\), whence
\(\abs Z\le\floor{s/(s-t)}\le t+1\).  If \(\abs U\le R\), independence
holds; the contrapositive proves the circuit assertion.
\end{proof}

\begin{theorem}[Bounded residual-kernel ray compiler]
\label{thm:bounded-residual-kernel-ray}
Let \(H\) be a parity-check matrix over \(\F\), let \(U\) be a set of
columns, and put
\[
 \kappa(U)=\dim_\F\ker(H_U:\F^U\longrightarrow\F^{n-k}).
\]
Fix a syndrome line \(y_0+\gamma y_1\), an integer \(t\ge0\), and a set
\(Z\) of finite transverse slopes.  Suppose that for every \(\gamma\in Z\)
there is \(E_\gamma\subseteq U\), \(\abs{E_\gamma}\le t\), such that
\[
 y_0+\gamma y_1\in V_{E_\gamma},\qquad
 \{y_0,y_1\}\not\subseteq V_{E_\gamma}.
\]
Then
\[
                  \abs Z\le(t+1)\abs{\F}^{\kappa(U)}. \tag{RC$_{\rm ker}$}
\]
For a Reed--Solomon parity check of redundancy \(R=n-k\),
\(\kappa(U)=\max\{0,\abs U-R\}\).  Hence a certified residual chart with
\((\abs U-R)_+\log\abs\F=o(n)\) has a direct subexponential ray payment
with the displayed exact finite loss.
\end{theorem}

\begin{proof}
The assertion is immediate when \(\abs Z\le1\).  Otherwise two line
points belong to \(V_U\), so \(y_0,y_1\in V_U\).  Choose lifts
\(b_0,b_1\in\F^U\) with \(H_Ub_i=y_i\).  For every \(\gamma\), choose a
lift \(c_\gamma\) supported in \(E_\gamma\) and put
\(z_\gamma=c_\gamma-b_0-\gamma b_1\in\ker H_U\).

Fix \(z\in\ker H_U\), and consider the slopes for which
\(z_\gamma=z\).  Put
\[
 U_z=\{x\in U:(b_0(x)+z(x),b_1(x))\ne(0,0)\},
 \qquad s=\abs{U_z}.
\]
Every active coordinate is a nonzero affine function of \(\gamma\), and
therefore vanishes for at most one slope.  Hence the total number of active
zero incidences in this kernel class is at most \(s\).  If \(s>t\), the
weight bound on \(c_\gamma\) forces at least \(s-t\) active zeros, so
\[
 \abs{Z_z}(s-t)\le s,\qquad
 \abs{Z_z}\le\floor{s/(s-t)}\le t+1.
\]
If \(s\le t\), transversality forces
at least one active zero: without one,
\(U_z=\supp c_\gamma\subseteq E_\gamma\), while both \(b_0+z\) and
\(b_1\) are supported in \(U_z\), putting \(y_0,y_1\) in
\(V_{E_\gamma}\).  Thus this kernel class contains at most \(s\le t\)
slopes.  Summing over the \(\abs{\F}^{\kappa(U)}\) kernel elements proves
the bound.  The MDS column property gives the Reed--Solomon formula for
\(\kappa(U)\).
\end{proof}


\begin{theorem}[Multiplicity-amplified fixed-union ray compiler]
\label{thm:fixed-union-ray}
Let \(H\) be a Reed--Solomon parity check of redundancy \(R\), let
\(U\subseteq D\) have size \(N=R+\nu\) with \(\nu\ge1\), and put
\(C_U=\ker H_U\).  Fix \(t<R\), a syndrome line
\(y_0+\gamma y_1\), and a set \(Z\) of distinct finite transverse slopes.
Suppose that for every \(\gamma\in Z\) there is
\(e_\gamma\in\F^U\) such that
\[
 H_Ue_\gamma=y_0+\gamma y_1,
 \qquad \wt(e_\gamma)\le t,
 \qquad
 \{y_0,y_1\}\not\subseteq V_{\supp e_\gamma}.
\]
Then
\begin{equation}
 |Z|\le
 \left\lfloor
 \frac{\binom{R+\nu}{\nu+1}}{R-t}
 \right\rfloor .
 \label{eq:fixed-union-ray}
\end{equation}
The estimate is independent of \(|\F|\); it replaces the factor
\(|\F|^\nu\) in \cref{thm:bounded-residual-kernel-ray} by an exact
incidence multiplicity.
\end{theorem}

\begin{proof}
There is nothing to prove when \(|Z|\le1\).  Otherwise two line points lie
in \(V_U\), hence \(y_0,y_1\in V_U\).  Choose lifts
\(b_0,b_1\in\F^U\), and choose a basis of the \(\nu\)-dimensional kernel
\(C_U\).  Write its generator matrix as \(K\), with row \(K_x\) at
\(x\in U\).  Every chosen error has a unique expression
\[
 e_\gamma=b_0+\gamma b_1+Kc_\gamma,
 \qquad c_\gamma\in\F^\nu.
\]
Put \(p_\gamma=(\gamma,c_\gamma)\in\F^{\nu+1}\).  A zero coordinate of
\(e_\gamma\) is the affine hyperplane incidence
\begin{equation}
 b_0(x)+\gamma b_1(x)+K_xc_\gamma=0,
 \qquad x\in U,                                     \label{eq:fixed-union-hyperplane}
\end{equation}
whose normal is \(n_x=(b_1(x),K_x)\in\F^{\nu+1}\).  Since
\(\wt(e_\gamma)\le t\), the point \(p_\gamma\) lies on at least
\(h=N-t\) of these hyperplanes.

We claim that the normals incident with \(p_\gamma\) span
\(\F^{\nu+1}\).  Otherwise a nonzero pair \((\delta,v)\) is orthogonal
to all of them.  Then
\[
 q=\delta b_1+Kv
\]
vanishes at every zero coordinate of \(e_\gamma\), so
\(\supp q\subseteq\supp e_\gamma\) and \(\wt(q)\le t\).  If
\(\delta=0\), then \(q=Kv\ne0\) is a kernel word of weight at most
\(t<R+1\), contradicting the MDS distance of
\(C_U=[R+\nu,\nu,R+1]\).  If \(\delta\ne0\), divide by \(\delta\).
The word \(q/\delta\) represents \(y_1\), and
\(e_\gamma-\gamma q/\delta\) represents \(y_0\); both are supported
inside \(\supp e_\gamma\), contradicting transversality.

Every normal \(n_x\) is nonzero.  Indeed, if the coordinate functional of
\(C_U\) vanished at \(x\), then puncturing at \(x\) would leave kernel
dimension \(\nu\), whereas the MDS rank of \(H_{U\setminus\{x\}}\) makes
that dimension \(\nu-1\).  Thus the incident normals form a loopless
rank-\((\nu+1)\) matroid on at least \(h\) elements.  Fix one basis.
Each of the other incident elements enters a basis by a fundamental-circuit
exchange, producing a distinct basis.  Hence \(p_\gamma\) is incident with
at least
\[
 h-(\nu+1)+1=R-t
\]
independent \((\nu+1)\)-subsets of hyperplanes.  An independent subset
has at most one affine intersection point.  Counting pairs consisting of a
slope point and one of its incident bases gives
\[
 |Z|(R-t)\le\binom{R+\nu}{\nu+1},
\]
which is \eqref{eq:fixed-union-ray}.
\end{proof}

\begin{corollary}[Single MDS-circuit ray compiler, multiplicity form]
\label{thm:single-mds-circuit-ray}
Under the hypotheses of the former single-circuit chart, namely
\(|U|=R+1\),
\begin{equation}
 |Z|\le
 \left\lfloor\frac{R(R+1)}{2(R-t)}\right\rfloor .
 \label{eq:single-circuit-multiplicity}
\end{equation}
Thus the pair-charge \(\binom{R+1}{2}\) is divided by the exact number
\(R-t\) of independent zero-coordinate pairs forced by every transverse
slope.
\end{corollary}

\begin{proof}
Apply \cref{thm:fixed-union-ray} with \(\nu=1\).
\end{proof}

\begin{theorem}[Fixed-syndrome GRS--Johnson compiler]
\label{thm:fixed-union-list-johnson}
Let \(H\) be a Reed--Solomon parity check of redundancy \(R\), let
\(U\subseteq D\) have size \(N=R+\nu\), and fix a syndrome \(y\).  Put
\[
 \mathcal L_U(y,t)=
 \{e\in\F^U:H_Ue=y,\ \wt(e)\le t\},
 \qquad h=N-t,
\]
where \(t<R\).  If \(\nu=0\), then \(|\mathcal L_U(y,t)|\le1\).  If
\(\nu\ge1\) and
\begin{equation}
 h^2>N(\nu-1),                                      \label{eq:fixed-union-johnson-condition}
\end{equation}
then
\begin{equation}
 |\mathcal L_U(y,t)|
 \le
 \left\lfloor
 \frac{N(h-\nu+1)}{h^2-N(\nu-1)}
 \right\rfloor .                                  \label{eq:fixed-union-list-johnson}
\end{equation}
Equivalently, the same bound holds for the number of codewords in one
Reed--Solomon list whose error supports are all contained in the fixed
union \(U\).
\end{theorem}

\begin{proof}
For \(\nu=0\), the columns in \(U\) are independent, so a syndrome has at
most one lift.  Assume \(\nu\ge1\), choose one lift \(b\) of \(y\), and
put \(C_U=\ker H_U\).  This is an
\([N,\nu,R+1]\) generalized Reed--Solomon code.  The set
\(\mathcal L_U(y,t)\) is the low-weight part of the affine coset
\(b+C_U\).  Thus its members are in bijection with codewords of \(C_U\)
that agree with the fixed word \(-b\) on at least \(h=N-t\) coordinates.

For each such codeword choose an \(h\)-subset \(A_i\) of its agreement
set.  Distinct codewords of the \([N,\nu]\) GRS code agree on at most
\(\nu-1\) coordinates, so \(|A_i\cap A_j|\le\nu-1\).  If there are \(L\)
sets, and \(d_x\) is the number containing \(x\), then
\[
 \sum_xd_x=Lh,
 \qquad
 \sum_x\binom{d_x}{2}\le\binom L2(\nu-1).
\]
Cauchy--Schwarz gives
\[
 \sum_x\binom{d_x}{2}
 \ge\frac12\left(\frac{L^2h^2}{N}-Lh\right).
\]
Combining the two inequalities and using
\eqref{eq:fixed-union-johnson-condition} yields
\[
 L\bigl(h^2-N(\nu-1)\bigr)
 \le N(h-\nu+1),
\]
which proves \eqref{eq:fixed-union-list-johnson}.
\end{proof}

\begin{theorem}[Recursive affine-span Reed--Solomon list compiler]
\label{thm:affine-span-list}
Let \(C=\RS[\F,D,K]\) have length \(n\), let \(u\in\F^D\), and put
\(m=K+w\le n\).  Let \(\mathcal A=c_0+C'\subseteq C\) be an affine
subspace of codewords whose direction space has dimension \(s\ge0\).  Then
\begin{equation}
 |\mathcal L_{\mathcal A}(u,m)|
 \le
 \left\lfloor
 \frac{(n-K+s)^{\underline s}}
      {(w+1)^{\overline s}}
 \right\rfloor
 =
 \left\lfloor
 \frac{\binom{n-K+s}{s}}
      {\binom{w+s}{s}}
 \right\rfloor .
 \label{eq:affine-span-list}
\end{equation}
The empty products at \(s=0\) are one.  In particular, a one-dimensional
codeword pencil contains at most
\(\lfloor(n-K+1)/(w+1)\rfloor\) members of the list.
\end{theorem}

\begin{proof}
We induct on \(s\).  The case \(s=0\) is immediate.  Assume \(s\ge1\),
and let
\[
 G=\{x\in D:c(x)=0\text{ for every }c\in C'\},
 \qquad z=|G|.
\]
The polynomial space representing \(C'\) has dimension \(s\).  Division
by the locator of \(G\) embeds it into the polynomials of degree less than
\(K-z\), so
\begin{equation}
                         z\le K-s.                 \label{eq:affine-common-zero}
\end{equation}
Let \(g\le z\) be the number of coordinates in \(G\) at which the common
value of the affine flat agrees with \(u\).  Every member of
\(\mathcal L_{\mathcal A}(u,m)\) therefore has at least \(m-g\)
agreements outside \(G\).

For \(x\in D\setminus G\), the evaluation functional on \(C'\) is
nonzero.  Hence
\[
 \mathcal A_x=\{c\in\mathcal A:c(x)=u(x)\}
\]
is either empty or an affine subspace of dimension \(s-1\).  By the
induction hypothesis, the number of listed codewords in \(\mathcal A_x\)
is at most
\[
 B_{s-1}:=
 \frac{\binom{n-K+s-1}{s-1}}
      {\binom{w+s-1}{s-1}}.
\]
Double-counting pairs \((c,x)\) with
\(c\in\mathcal L_{\mathcal A}(u,m)\), \(x\notin G\), and \(c(x)=u(x)\)
gives
\begin{equation}
 |\mathcal L_{\mathcal A}(u,m)|(m-g)
 \le (n-z)B_{s-1}.                                \label{eq:affine-recursion}
\end{equation}

Put \(b=z-g\) and \(q=K-s-z\).  Both are nonnegative by
\eqref{eq:affine-common-zero}, and the exact identity
\begin{equation}
 \begin{split}
 &(m-g)(n-K+s)-(n-z)(w+s)\\
 &\qquad=b(n-K+s)+q(n-m)\ge0
 \end{split}                                      \label{eq:affine-ratio-identity}
\end{equation}
shows that
\[
 \frac{n-z}{m-g}\le\frac{n-K+s}{w+s}.
\]
Combining this with \eqref{eq:affine-recursion} yields
\[
 |\mathcal L_{\mathcal A}(u,m)|
 \le B_{s-1}\frac{n-K+s}{w+s}
 =\frac{\binom{n-K+s}{s}}{\binom{w+s}{s}}.
\]
Taking the integer floor proves \eqref{eq:affine-span-list}.
\end{proof}


\begin{theorem}[Generalized-weight rank-flat list compiler]
\label{thm:rank-flat-list}
Retain the hypotheses of \cref{thm:affine-span-list}, assume \(s\ge1\),
and let
\[
 d_j=d_j(C'):=
 \min_{\substack{V\le C'\\ \dim V=j}}|\supp(V)|,
 \qquad 1\le j\le s,
\]
be the generalized Hamming weights of the direction code.  Put
\[
 R=n-K,\qquad t=n-m,
\]
let \(G\) be the common-zero set of \(C'\), let \(z=|G|=n-d_s\),
let \(g\) be the number of common agreements with \(u\) on \(G\), and
put \(b=z-g\).  Then
\begin{equation}
 |\mathcal L_{\mathcal A}(u,m)|
 \le
 \left\lfloor
 \frac{d_s^{\underline s}}
      {\prod_{j=1}^{s}(d_j-t+b)}
 \right\rfloor .
 \label{eq:rank-flat-list}
\end{equation}
Every factor in the denominator is positive.  More precisely,
\begin{equation}
                    d_j\ge R+j,
 \qquad
                    d_j-t+b\ge w+j+b.
 \label{eq:rank-flat-singleton}
\end{equation}
\end{theorem}

\begin{proof}
Choose a basis of \(C'\) and identify the affine flat with \(\F^s\).
For each active coordinate \(x\in D\setminus G\), agreement with \(u\)
is an affine hyperplane whose nonzero normal is the evaluation functional
\(\ell_x\in(C')^*\).  Every listed point is incident with at least
\[
 h=m-g=d_s-t+b
\]
of these hyperplanes.

Suppose that \(r\) independent incident normals have already been chosen
and span \(W\le(C')^*\).  The coordinates whose normals lie in \(W\) are
common zeros of the \((s-r)\)-dimensional subcode \(W^\perp\).  This
subcode has support at least \(d_{s-r}\); after the common-zero set \(G\)
is removed, at most
\[
 (n-d_{s-r})-z=d_s-d_{s-r}
\]
active normals lie in \(W\).  Hence there are at least
\[
 h-(d_s-d_{s-r})=d_{s-r}-t+b
\]
choices for the next independent incident normal.  Each listed point is
therefore incident with at least
\[
 \prod_{j=1}^{s}(d_j-t+b)
\]
ordered bases of coordinate hyperplanes.  There are at most
\(d_s^{\underline s}\) ordered coordinate bases globally, and an
independent affine-hyperplane basis has at most one common point.  Double
counting proves \eqref{eq:rank-flat-list}.

Finally, if \(V\le C'\) has dimension \(j\) and common-zero set of size
\(z_V\), division by its locator embeds the representing polynomial space
into the polynomials of degree less than \(K-z_V\).  Thus
\(j\le K-z_V\), so \(|\supp(V)|=n-z_V\ge n-K+j=R+j\).  This proves
\eqref{eq:rank-flat-singleton} and positivity.
\end{proof}

\begin{corollary}[Over-budget rank-flat concentration]
\label{cor:rank-flat-concentration}
In \cref{thm:rank-flat-list}, let \(s\ge2\) and let \(B\) be a nonnegative
integer.  Define
\begin{equation}
 \Theta_{s,B}(d_s,b)=
 \max\left\{q\in\mathbb Z_{\ge0}:
 q^{s-1}\le
 \left\lfloor
 \frac{d_s^{\underline s}}
 {(B+1)(d_s-t+b)}
 \right\rfloor
 \right\}.
 \label{eq:rank-flat-theta}
\end{equation}
If \(|\mathcal L_{\mathcal A}(u,m)|>B\), then some proper direction
subcode has dimension \(1\le j<s\) and
\begin{equation}
                     d_j\le t-b+\Theta_{s,B}(d_s,b).
 \label{eq:rank-flat-concentration}
\end{equation}
A row-independent coarse version is obtained by replacing
\(d_s^{\underline s}\) by \(n^{\underline s}\) and
\(d_s-t+b\) by \(w+s\).
\end{corollary}

\begin{proof}
If the list contains at least \(B+1\) points, \eqref{eq:rank-flat-list}
implies
\[
 \prod_{j=1}^{s-1}(d_j-t+b)
 \le
 \left\lfloor
 \frac{d_s^{\underline s}}
 {(B+1)(d_s-t+b)}
 \right\rfloor .
\]
At least one of the \(s-1\) integer factors is at most the integer root in
\eqref{eq:rank-flat-theta}, proving \eqref{eq:rank-flat-concentration}.
The coarse form follows from \(d_s\le n\) and
\eqref{eq:rank-flat-singleton}.
\end{proof}

\begin{theorem}[Common-zero Johnson list compiler]
\label{thm:common-zero-johnson}
In the notation of \cref{thm:rank-flat-list}, put
\[
 N=d_s,
 \qquad h=m-g=d_s-t+b,
 \qquad \alpha=d_s-d_1.
\]
If
\begin{equation}
                         h^2>N\alpha,
 \label{eq:common-zero-johnson-condition}
\end{equation}
then
\begin{equation}
 |\mathcal L_{\mathcal A}(u,m)|
 \le
 \left\lfloor
 \frac{N(h-\alpha)}{h^2-N\alpha}
 \right\rfloor .
 \label{eq:common-zero-johnson}
\end{equation}
Equivalently, write \(z=K-\nu\).  Then \(N=R+\nu\),
\(h=w+\nu+b\), and the generalized Singleton bound gives the universal
specialization
\begin{equation}
 |\mathcal L_{\mathcal A}(u,m)|
 \le
 \left\lfloor
 \frac{(R+\nu)(w+b+1)}
 {(w+\nu+b)^2-(R+\nu)(\nu-1)}
 \right\rfloor
 \label{eq:common-zero-nu}
\end{equation}
whenever the displayed denominator is positive.
\end{theorem}

\begin{proof}
All codewords of the affine flat have the same values on \(G\).  Delete
those coordinates and, for each listed codeword, choose an \(h\)-subset of
its active agreement set.  If two distinct codewords are chosen, their
difference is a nonzero word of \(C'\), has weight at least \(d_1\), and
therefore vanishes on at most \(N-d_1=\alpha\) active coordinates.  The
standard Johnson incidence count now gives
\[
 L(h^2-N\alpha)\le N(h-\alpha),
\]
which proves \eqref{eq:common-zero-johnson}.

If \(z=K-\nu\), then \(N=n-z=R+\nu\) and
\(h=m-(z-b)=w+\nu+b\).  By \eqref{eq:rank-flat-singleton},
\(d_1\ge R+1\), so \(\alpha\le\nu-1\).  The Johnson fraction is
nondecreasing in \(\alpha\) while its denominator is positive.  Replacing
\(\alpha\) by \(\nu-1\) gives \eqref{eq:common-zero-nu}.
\end{proof}

\section{Coset-free codimension-one rank-flat recursion}
\label{sec:codim-one-recursion}
The rank-flat concentration theorem produces a low-support direction
subcode, but a naive partition into its affine cosets introduces the field
size.  The next theorem removes that loss when the support closure has
codimension one.  It counts the whole affine chart at once by two disjoint
resources: bases using an agreement in the new support layer, and bases
whose final coordinate lies in the old support.

\begin{theorem}[Two-resource codimension-one recursion]
\label{thm:codim-one-recursion}
Let
\[
 C=\RS[\F,D,K],\qquad n=|D|,\qquad m=K+w,\qquad t=n-m,
\]
and let \(\mathcal A=c_0+C'\subseteq C\) be an affine codeword flat with
\(\dim C'=j+1\), where \(j\ge1\).  Let \(V<C'\) be a hyperplane, put
\[
 U=\supp(V),\qquad S=\supp(C'),\qquad
 T=S\setminus U,\qquad H=D\setminus S,
\]
and assume \(e:=|T|\ge1\).  Write \(d=|U|\).  Then
\begin{equation}
 V=\{v\in C':\supp(v)\subseteq U\};
 \label{eq:codim-one-saturation}
\end{equation}
in particular every word of \(C'\setminus V\) is nonzero at every
coordinate of \(T\).

Fix a received word \(u\in\F^D\).  Let \(b_0\) be the number of
coordinates in \(H\) on which the common value of \(\mathcal A\)
disagrees with \(u\).  For \(0\le b\le e\), let \(L_b\) count the
members \(c\in\mathcal A\) satisfying
\[
 \operatorname{agr}(u,c)\ge m,
 \qquad
 |\{x\in T:c(x)\ne u(x)\}|=b.
\]
Let \(f_i=d_i(V)\), \(1\le i\le j\), be the generalized Hamming weights
of \(V\), and put
\begin{equation}
 P_b=\prod_{i=1}^{j}(f_i-t+b_0+b),
 \qquad Q=w+1+b_0.
 \label{eq:codim-one-profile}
\end{equation}
Then every factor in \(P_b\) is positive and
\begin{align}
 \sum_{b=0}^{e}L_b(e-b)P_b
 &\le e\,d^{\underline j},
 \label{eq:codim-one-T-resource}\\
 \sum_{b=0}^{e}L_b(Q-e+b)_+P_b
 &\le d^{\underline{j+1}}.
 \label{eq:codim-one-U-resource}
\end{align}
Moreover, with \(L=\sum_bL_b\),
\begin{equation}
 L\le
 \left\lfloor
 \frac{(n-j)d^{\underline j}}{QP_0}
 \right\rfloor .
 \label{eq:codim-one-all-extenders}
\end{equation}
More generally, if \(x,y\ge0\) satisfy
\begin{equation}
 x(e-b)P_b+y(Q-e+b)_+P_b\ge1
 \qquad(0\le b\le e),
 \label{eq:codim-one-dual-feasible}
\end{equation}
then
\begin{equation}
 L\le
 \left\lfloor
 xe\,d^{\underline j}+y\,d^{\underline{j+1}}
 \right\rfloor .
 \label{eq:codim-one-dual-bound}
\end{equation}
Thus the affine cosets of \(V\) are never summed separately.
\end{theorem}

\begin{proof}
For \(x\in T\), every word of \(V\) vanishes at \(x\), whereas some word
of \(C'\) is nonzero there.  Evaluation at \(x\) therefore induces a
nonzero functional on the one-dimensional quotient \(C'/V\).  It is
nonzero on every nonzero quotient class, proving
\eqref{eq:codim-one-saturation}.

Parameterize \(\mathcal A\) by the direction space \(C'\).  Agreement at
a coordinate \(x\) is an affine hyperplane with normal
\(\ell_x\in(C')^*\).  A listed point counted by \(L_b\) has at least
\[
 m-(|H|-b_0)-(e-b)=d-t+b_0+b
\]
agreements in \(U\).  Restrict the corresponding normals to \(V\).
After \(r\) independent restricted normals have been selected, their span
annihilates a \((j-r)\)-dimensional subcode of \(V\), whose support has
size at least \(f_{j-r}\).  Hence at most \(d-f_{j-r}\) normals of
\(U\) lie in the old span, and there are at least
\[
 f_{j-r}-t+b_0+b
\]
choices for the next independent normal.  Every listed point counted by
\(L_b\) is therefore incident with at least \(P_b\) ordered
\(V\)-normal bases.  The generalized Singleton inequalities
\(f_i\ge n-K+i\) show at the same time that all factors in \(P_b\) are
at least \(w+i+b_0+b\).

The span in \((C')^*\) of a lifted \(V\)-normal basis meets the
one-dimensional annihilator \(V^\perp\) trivially.  Every agreeing
coordinate of \(T\) has a nonzero normal in \(V^\perp\), and therefore
extends the basis.  A point in class \(b\) supplies at least
\((e-b)P_b\) ordered bases of this type.  Globally there are at most
\(e\,d^{\underline j}\) ordered choices, and an independent affine
hyperplane basis cuts out at most one point.  This proves
\eqref{eq:codim-one-T-resource}.

Fix now one lifted \(V\)-normal basis and let \(h\in C'\setminus V\)
generate its one-dimensional annihilator.  A coordinate normal extends
the basis exactly when \(h\) is nonzero at that coordinate.  The
nonzero Reed--Solomon word \(h\) has at most \(K-1\) zeros.  All
coordinates of \(H\) are zeros of \(h\), and exactly \(|H|-b_0\) of
them are agreements.  Thus among the at least \(m\) agreement coordinates
of the listed point, at most \(K-1-b_0\) fail to extend the basis.  There
are consequently at least
\[
 m-(K-1-b_0)=Q
\]
extending agreement coordinates.  All \(e-b\) agreeing coordinates of
\(T\) already extend, so at least \((Q-e+b)_+\) extending agreements lie
in \(U\).  Double-counting the resulting ordered \((j+1)\)-tuples inside
\(U\) proves \eqref{eq:codim-one-U-resource}.

The same argument without separating \(U\) from \(T\) gives at least
\(QP_b\ge QP_0\) full bases through every listed point.  There are at
most \((n-j)d^{\underline j}\) ordered choices of a \(V\)-basis and one
additional coordinate, proving \eqref{eq:codim-one-all-extenders}.
Finally multiply \eqref{eq:codim-one-T-resource} by \(x\), multiply
\eqref{eq:codim-one-U-resource} by \(y\), and use
\eqref{eq:codim-one-dual-feasible}; this gives
\eqref{eq:codim-one-dual-bound}.
\end{proof}

\begin{lemma}[Profile interpolation]
\label{lem:codim-one-profile-interpolation}
Let
\[
 P(z)=\prod_{i=1}^{j}(a_i+z),\qquad a_i>0,
\]
and let \(e,Q>0\).  For every integer \(0\le b\le e\),
\begin{equation}
 \frac{(e-b)P(b)}{eP(0)}+
 \frac{(Q-e+b)_+P(b)}{QP(e)}\ge1
 \label{eq:profile-interpolation}
\end{equation}
under either of the following conditions:
\begin{enumerate}[label=\textup{(\alph*)},leftmargin=*]
\item \(e\le Q\);
\item \(e>Q\) and
\begin{equation}
 \left(\frac{P(e)}{P(0)}\right)^{1-Q/e}\ge\frac eQ.
 \label{eq:profile-ratio-condition}
\end{equation}
\end{enumerate}
If \(j\ge2\), \(A=\max_i a_i\), and \((j-1)Q\ge A\), then
\eqref{eq:profile-ratio-condition} holds for every \(e\ge Q\).
\end{lemma}

\begin{proof}
Put \(r=P(e)/P(0)\ge1\).  Since \(\log P\) is concave, with
\(\theta=b/e\) one has
\[
 \frac{P(b)}{P(0)}\ge r^\theta,
 \qquad
 \frac{P(b)}{P(e)}\ge r^{-(1-\theta)}.
\]
If \(e\le Q\), then \((Q-e+b)/Q\ge\theta\), and weighted AM--GM gives
\[
 (1-\theta)r^\theta+\theta r^{-(1-\theta)}\ge1.
\]
This proves \eqref{eq:profile-interpolation} in case \textup{(a)}.

Assume \(e>Q\), put \(c=Q/e\), and first take
\(0\le\theta\le1-c\).  The second summand in
\eqref{eq:profile-interpolation} vanishes, while concavity gives the lower
bound \((1-\theta)r^\theta\).  The logarithm of this expression is
concave in \(\theta\); it is zero at \(0\), and at \(1-c\) it is
nonnegative exactly when \eqref{eq:profile-ratio-condition} holds.

For \(1-c\le\theta\le1\), write \(\alpha=1-\theta\in[0,c]\).  After
multiplication by \(r^\alpha\), the lower bound supplied by log-concavity
is
\[
 \alpha r+1-\frac\alpha c.
\]
Convexity of \(r^\alpha\) on \([0,c]\) gives
\[
 r^\alpha\le1+\frac\alpha c(r^c-1).
\]
The former expression dominates the latter precisely when
\(cr\ge r^c\), which is again
\eqref{eq:profile-ratio-condition}.  This proves case \textup{(b)}.

Finally, if \(A=\max_i a_i\), then
\[
 r\ge(1+e/A)^j.
\]
For \(e\ge Q\), set
\[
 \phi(e)=j(1-Q/e)\log(1+e/A)-\log(e/Q).
\]
One has \(\phi(Q)=0\), and the elementary inequality
\(\log(1+x)\ge x/(1+x)\) gives
\[
 \phi'(e)\ge \frac{j}{A+e}-\frac1e
 =\frac{(j-1)e-A}{e(A+e)}\ge0.
\]
Thus \(\phi(e)\ge0\), which is
\eqref{eq:profile-ratio-condition}.
\end{proof}

\begin{corollary}[MDS-soft codimension-one compiler]
\label{cor:codim-one-mds-soft}
Retain the hypotheses of \cref{thm:codim-one-recursion}, and put
\begin{equation}
 \Pi_b=(d-t+b_0+b)
 \prod_{i=1}^{j-1}(w+i+b_0+b).
 \label{eq:codim-one-mds-profile}
\end{equation}
Suppose the profile interpolation inequality
\eqref{eq:profile-interpolation} holds for \(P=\Pi\), with
\(Q=w+1+b_0\).  Then
\begin{equation}
 L\le
 \left\lfloor
 \frac{d^{\underline j}}{\Pi_0}+
 \frac{d^{\underline{j+1}}}{Q\Pi_e}
 \right\rfloor .
 \label{eq:codim-one-closed}
\end{equation}
Independently of profile interpolation,
\begin{equation}
 L\le
 \left\lfloor
 \frac{(n-j)d^{\underline j}}{Q\Pi_0}
 \right\rfloor .
 \label{eq:codim-one-all-extenders-mds}
\end{equation}
In particular, \eqref{eq:codim-one-closed} is a bound for the whole affine
chart, not a per-coset estimate.
\end{corollary}

\begin{proof}
The generalized Singleton inequalities give \(f_i\ge n-K+i\) for
\(i<j\), while \(f_j=d\).  Hence \(P_b\ge\Pi_b\).  The two resource
inequalities of \cref{thm:codim-one-recursion} remain true after replacing
\(P_b\) by \(\Pi_b\).  Under profile interpolation, the choices
\[
 x=\frac1{e\Pi_0},\qquad y=\frac1{Q\Pi_e}
\]
are feasible in \eqref{eq:codim-one-dual-feasible}, and
\eqref{eq:codim-one-dual-bound} gives
\eqref{eq:codim-one-closed}.  The all-extender estimate follows directly
from \eqref{eq:codim-one-all-extenders}.
\end{proof}



\section{Higher-codimension support-flag recursion}
\label{sec:support-flag-recursion}
The codimension-one theorem removes the field-size loss for a single
support-saturated hyperplane.  The same principle extends to arbitrary
codimension, but one must keep all possible choices of ``new-layer'' and
``old-support'' extenders.  The resulting object is a finite exact linear
program with one resource inequality for each binary flag pattern.  In
particular, no affine coset is ever counted separately.

\begin{definition}[Support saturation]
\label{def:support-saturation}
If $V\le W\le C$, the \emph{support closure of $V$ in $W$} is
\[
 \overline V^{\,W}
 =\{c\in W:\supp(c)\subseteq\supp(V)\}.
\]
We call $V$ \emph{support-saturated in $W$} when
$\overline V^{\,W}=V$.
\end{definition}

\begin{lemma}[Generalized-weight minimizers are support-saturated]
\label{lem:weight-minimizer-saturated}
Let $W$ be a finite-length linear code, and let $V\le W$ have dimension
$j$ and support size $d_j(W)$.  Then $V$ is support-saturated in $W$.
More generally, the generalized Hamming weights satisfy
\[
 d_1(W)<d_2(W)<\cdots<d_{\dim W}(W).
\]
\end{lemma}

\begin{proof}
Let $Y\le W$ have dimension $i+1$ and support size $d_{i+1}(W)$.
Choose a coordinate on which some word of $Y$ is nonzero.  The kernel of
evaluation at that coordinate is an $i$-dimensional subcode whose support
omits that coordinate, so
\[
 d_i(W)\le d_{i+1}(W)-1.
\]
This proves strict increase.  If the support closure of a
$j$-dimensional minimizer $V$ had dimension $k>j$, then
\[
 d_k(W)\le|\supp(V)|=d_j(W),
\]
contradicting strict increase.
\end{proof}

\begin{lemma}[Existence of a support-saturated flag]
\label{lem:support-saturated-flag}
Let $V$ be support-saturated in $W$ and put
$r=\dim W-\dim V$.  There is a flag
\[
 V=V_0<V_1<\cdots<V_r=W,
 \qquad \dim V_\ell=\dim V+\ell,
\]
such that $V_{\ell-1}$ is support-saturated in $V_\ell$ for every
$1\le\ell\le r$.  Consequently, with
\[
 U_\ell=\supp(V_\ell),\qquad
 T_\ell=U_\ell\setminus U_{\ell-1},
\]
every layer $T_\ell$ is nonempty.
\end{lemma}

\begin{proof}
Construct the flag downward.  Suppose $V<X\le W$.  Since $V$ is
support-saturated in $W$, some word of $X\setminus V$ is nonzero at a
coordinate $x\notin\supp(V)$.  Put
\[
 X'=\{c\in X:c(x)=0\}.
\]
Then $V\le X'$, $X'$ is a hyperplane of $X$, and $x\notin\supp(X')$.
If $c\in X$ has support contained in $\supp(X')$, then $c(x)=0$, hence
$c\in X'$.  Thus $X'$ is support-saturated in $X$.  Repeating until the
dimension reaches $\dim V$ gives the claimed flag; the terminal subspace
contains $V$ and has the same dimension, so it is $V$.  A proper
support-saturated inclusion cannot have equal supports, proving
$T_\ell\ne\varnothing$.
\end{proof}

\begin{theorem}[Exact support-flag resource recursion]
\label{thm:support-flag-recursion}
Let
\[
 C=\RS[\F,D,K],\qquad n=|D|,\qquad m=K+w,\qquad t=n-m,
\]
and let $\mathcal A=c_0+C'\subseteq C$ be an affine codeword flat.
Assume that
\[
 V_0<V_1<\cdots<V_r=C'
\]
is a support-saturated flag with
\[
 \dim V_0=j\ge1,
 \qquad \dim V_\ell=j+\ell.
\]
Put
\[
 U_\ell=\supp(V_\ell),\quad d_\ell=|U_\ell|,
 \quad T_\ell=U_\ell\setminus U_{\ell-1},
 \quad e_\ell=|T_\ell|,
\]
and $H=D\setminus U_r$.  Fix a received word $u\in\F^D$, and let
$b_0$ be the number of coordinates of $H$ on which the common value of
$\mathcal A$ disagrees with $u$.

For a profile
$\mathbf b=(b_1,\ldots,b_r)$ with $0\le b_\ell\le e_\ell$, let
$L_{\mathbf b}$ count the words $c\in\mathcal A$ satisfying
\[
 \operatorname{agr}(u,c)\ge m,
 \qquad
 |\{x\in T_\ell:c(x)\ne u(x)\}|=b_\ell
 \quad(1\le\ell\le r).
\]
Let $f_i=d_i(V_0)$, $1\le i\le j$, and define
\begin{align}
 P_{\mathbf b}
 &=\prod_{i=1}^{j}
   \left(f_i-t+b_0+\sum_{q=1}^{r}b_q\right),
 \label{eq:flag-profile-P}\\
 Q_\ell(\mathbf b)
 &=w+1+b_0+\sum_{q>\ell}b_q,
 \label{eq:flag-profile-Q}\\
 A_\ell(\mathbf b)&=e_\ell-b_\ell,
 \qquad
 B_\ell(\mathbf b)
 =\bigl(Q_\ell(\mathbf b)-e_\ell+b_\ell\bigr)_+.
 \label{eq:flag-profile-AB}
\end{align}
For a binary pattern $\sigma\in\{T,U\}^r$, put
\begin{align}
 C_\sigma(\mathbf b)
 &=P_{\mathbf b}
   \prod_{\ell:\sigma_\ell=T}A_\ell(\mathbf b)
   \prod_{\ell:\sigma_\ell=U}B_\ell(\mathbf b),
 \label{eq:flag-profile-resource}\\
 G_\sigma
 &=d_0^{\underline j}
   \prod_{\ell:\sigma_\ell=T}e_\ell
   \prod_{\ell:\sigma_\ell=U}
   \bigl(d_{\ell-1}-(j+\ell-1)\bigr).
 \label{eq:flag-global-resource}
\end{align}
Then every factor in $P_{\mathbf b}$ is positive and, for every
$\sigma\in\{T,U\}^r$,
\begin{equation}
 \boxed{
 \sum_{\mathbf b}L_{\mathbf b}C_\sigma(\mathbf b)
 \le G_\sigma.}
 \label{eq:flag-resource-inequality}
\end{equation}
Consequently, if nonnegative weights $x_\sigma$ satisfy
\begin{equation}
 \sum_{\sigma\in\{T,U\}^r}
 x_\sigma C_\sigma(\mathbf b)\ge1
 \qquad
 \text{for every profile }\mathbf b,
 \label{eq:flag-dual-feasible}
\end{equation}
then, with $L=\sum_{\mathbf b}L_{\mathbf b}$,
\begin{equation}
 \boxed{
 L\le
 \left\lfloor
 \sum_{\sigma\in\{T,U\}^r}x_\sigma G_\sigma
 \right\rfloor.}
 \label{eq:flag-dual-bound}
\end{equation}
The bound is for the whole affine chart and contains no factor depending
on $|\F|$ or on the number of affine cosets of $V_0$.
\end{theorem}

\begin{proof}
Parameterize $\mathcal A$ by $C'$.  Agreement at a coordinate $x$ is an
affine hyperplane with normal $\ell_x\in(C')^*$.  A point of profile
$\mathbf b$ has at least
\[
 d_0-t+b_0+\sum_{q=1}^{r}b_q
\]
agreements in $U_0$.  Applying the ordered-basis argument of
\cref{thm:rank-flat-list} inside $V_0$ shows that it is incident with at
least $P_{\mathbf b}$ ordered coordinate bases whose restrictions form a
basis of $V_0^*$.

Suppose an adapted basis has already been chosen through level
$V_{\ell-1}$.  Its annihilator in $V_\ell$ is one-dimensional; let
$h_\ell\in V_\ell\setminus V_{\ell-1}$ generate it.  At a coordinate
of $T_\ell$, evaluation vanishes on $V_{\ell-1}$ but not on $V_\ell$;
on the one-dimensional quotient $V_\ell/V_{\ell-1}$ it is therefore a
nonzero functional.  Hence $h_\ell$ is nonzero at every coordinate of
$T_\ell$.
Moreover, $h_\ell$ vanishes outside $U_\ell$.  The number of mismatches
outside $U_\ell$ is
\[
 b_0+\sum_{q>\ell}b_q.
\]
Since a nonzero degree-$<K$ word has at most $K-1$ zeros, at most
$K-1-b_0-\sum_{q>\ell}b_q$ agreement coordinates fail to extend the
current basis.  Hence there are at least
$Q_\ell(\mathbf b)$ extending agreement coordinates in total.  The
$A_\ell(\mathbf b)$ agreeing coordinates of $T_\ell$ all extend, so at
least $B_\ell(\mathbf b)$ extending agreement coordinates lie in
$U_{\ell-1}$.

Fix a pattern $\sigma$.  Multiplying the preceding lower bounds over the
flag levels gives at least $C_\sigma(\mathbf b)$ adapted ordered bases
of pattern $\sigma$ through every point of profile $\mathbf b$.  Globally,
the initial ordered basis has at most $d_0^{\underline j}$ choices.  At a
$T$-level there are at most $e_\ell$ coordinate choices.  At a $U$-level,
all $j+\ell-1$ previously selected coordinates lie in $U_{\ell-1}$, and
an extending normal cannot repeat one of them; there are therefore at
most $d_{\ell-1}-(j+\ell-1)$ choices.  An independent affine-hyperplane
basis cuts out at most one parameter point.  Double counting proves
\eqref{eq:flag-resource-inequality}.  Multiplying those inequalities by
$x_\sigma$, summing over $\sigma$, and using
\eqref{eq:flag-dual-feasible} proves \eqref{eq:flag-dual-bound}.
Positivity follows from $f_i\ge n-K+i$.
\end{proof}

\begin{corollary}[All-extender flag bound]
\label{cor:flag-all-extender}
In the notation of \cref{thm:support-flag-recursion}, put
\[
 P_0=\prod_{i=1}^{j}(f_i-t+b_0),
 \qquad Q=w+1+b_0.
\]
Then
\begin{equation}
 \boxed{
 L\le
 \left\lfloor
 \frac{d_0^{\underline j}
       \prod_{\ell=1}^{r}
       \bigl(d_\ell-(j+\ell-1)\bigr)}
      {P_0Q^r}
 \right\rfloor.}
 \label{eq:flag-all-extender}
\end{equation}
In particular, the numerator may be replaced by
$d_0^{\underline j}(n-j)^{\underline r}$.
\end{corollary}

\begin{proof}
Every point has at least $P_0$ initial bases.  At level $\ell$ it has at
least $Q_\ell(\mathbf b)\ge Q$ extending agreement coordinates, without
separating the two resources.  The global number of adapted extensions at
that level is at most $d_\ell-(j+\ell-1)$.  Multiplication and double
counting give the first bound.  Since $d_\ell\le n$, each factor is at most
$n-j-\ell+1$, giving the second statement.
\end{proof}

\begin{lemma}[One-level interpolation defect]
\label{lem:flag-interpolation-defect}
For $e,Q>0$ and $\rho\ge1$, define
\begin{equation}
 \eta(e,Q,\rho)=
 \begin{cases}
 1,&e\le Q,\\
 \displaystyle
 \min\left\{1,\frac Qe\rho^{1-Q/e}\right\},&e>Q.
 \end{cases}
 \label{eq:flag-eta}
\end{equation}
Then, for every real $0\le b\le e$,
\begin{equation}
 \rho^{b/e}
 \left(
  \frac{e-b}{e}
  +\frac{(Q-e+b)_+}{Q\rho}
 \right)
 \ge\eta(e,Q,\rho).
 \label{eq:flag-one-level-interpolation}
\end{equation}
Thus the right side is $1$ precisely in the profile-interpolation range
used in \cref{lem:codim-one-profile-interpolation}.
\end{lemma}

\begin{proof}
If $e\le Q$, the proof is the weighted AM--GM argument of
\cref{lem:codim-one-profile-interpolation}.  Suppose $e>Q$, put
$c=Q/e$ and $\theta=b/e$.  On $0\le\theta\le1-c$, the logarithm of the
left side is
$\log(1-\theta)+\theta\log\rho$, a concave function, so its minimum is
at an endpoint and equals at least
$\min\{1,c\rho^{1-c}\}$.  On $1-c\le\theta\le1$, put
$\alpha=1-\theta\in[0,c]$.  The left side becomes
\[
 \rho^{-\alpha}\left(\alpha\rho+1-\frac\alpha c\right).
\]
Its logarithm is a linear function plus the logarithm of a positive
affine function, hence is concave.  Its endpoint values are again
$1$ and $c\rho^{1-c}$.  This proves the claim.
\end{proof}

\begin{corollary}[Tensorized support-flag certificate]
\label{cor:flag-tensor-certificate}
Retain the notation of \cref{thm:support-flag-recursion}.  Put
\[
 E=\sum_{\ell=1}^{r}e_\ell,
 \qquad
 P(z)=\prod_{i=1}^{j}(f_i-t+b_0+z),
 \qquad
 \rho=\frac{P(E)}{P(0)},
\]
and define
\[
 \rho_\ell=\rho^{e_\ell/E},
 \qquad
 \eta_\ell=\eta(e_\ell,Q,\rho_\ell),
 \qquad Q=w+1+b_0.
\]
Then
\begin{equation}
 \boxed{
 L\le
 \left\lfloor
 \frac{d_0^{\underline j}}
      {P(0)\prod_{\ell=1}^{r}\eta_\ell}
 \prod_{\ell=1}^{r}
 \left(
 1+\frac{d_{\ell-1}-(j+\ell-1)}{Q\rho_\ell}
 \right)
 \right\rfloor.}
 \label{eq:flag-tensor-bound}
\end{equation}
If every $\eta_\ell=1$, this is a closed higher-codimension analogue of
\eqref{eq:codim-one-closed}.  For $r=1$ it specializes to the
codimension-one two-resource certificate, with the explicit defect factor
when profile interpolation fails.
\end{corollary}

\begin{proof}
Let $B=\sum b_\ell$.  Concavity of $\log P$ on $[0,E]$ gives
\[
 \frac{P(B)}{P(0)}
 \ge\rho^{B/E}
 =\prod_{\ell=1}^{r}\rho_\ell^{b_\ell/e_\ell}.
\]
Also $Q_\ell(\mathbf b)\ge Q$, so
$B_\ell(\mathbf b)\ge(Q-e_\ell+b_\ell)_+$.  By
\cref{lem:flag-interpolation-defect},
\[
 \frac{P_{\mathbf b}}{P(0)}
 \prod_{\ell=1}^{r}
 \left(
  \frac{A_\ell(\mathbf b)}{e_\ell}
  +\frac{B_\ell(\mathbf b)}{Q\rho_\ell}
 \right)
 \ge\prod_{\ell=1}^{r}\eta_\ell.
\]
Use the tensor-product dual weights
\[
 x_\sigma=
 \frac1{P(0)\prod_\ell\eta_\ell}
 \prod_{\ell:\sigma_\ell=T}\frac1{e_\ell}
 \prod_{\ell:\sigma_\ell=U}\frac1{Q\rho_\ell}.
\]
They satisfy \eqref{eq:flag-dual-feasible}; substituting them into
\eqref{eq:flag-dual-bound} and factoring the sum over binary patterns
gives \eqref{eq:flag-tensor-bound}.
\end{proof}

\begin{remark}[What the flag theorem closes]
\label{rem:flag-theorem-scope}
The uncontrolled field-size coset sum is now removed in every codimension.
For a concrete finite chart, \eqref{eq:flag-resource-inequality} is an
exact rational linear-program certificate, while
\eqref{eq:flag-tensor-bound} is a closed analytic certificate.  What can
still fail is numerical payment: a low-mismatch flag with several short
layers may have a certified bound above the row budget.  Such a flag is a
specific finite residual atom, not an unproved multiplicity principle.
\end{remark}



\begin{theorem}[Affine-span transverse MCA compiler]
\label{thm:affine-span-mca}
Let \(C=\RS[\F,D,K]\) have length \(n\), let
\(r_\gamma=r_0+\gamma r_1\), and put \(m=K+w\).  Let
\(\mathcal A=c_0+C'\subseteq C\) be an affine codeword subspace with
\(\dim C'=s\ge1\).  Suppose the line direction is separated from the
agreement ball,
\begin{equation}
 \max_{c\in C}\operatorname{agr}(r_1,c)<m.
 \label{eq:direction-list-separated}
\end{equation}
Let \(Z\subseteq\F\) be a set of distinct slopes such that for every
\(\gamma\in Z\) some \(c_\gamma\in\mathcal A\) satisfies
\(\operatorname{agr}(r_\gamma,c_\gamma)\ge m\).  Then
\begin{equation}
 |Z|\le
 \left\lfloor
 \max\left\{
 \frac{n^{\underline{s+1}}}
      {m\,w^{\overline s}},
 \frac{(n-K+s)^{\underline{s+1}}}
      {w^{\overline{s+1}}}
 \right\}
 \right\rfloor .
 \label{eq:affine-span-mca}
\end{equation}
The second term is
\(\binom{n-K+s}{s+1}/\binom{w+s}{s+1}\).  Failure of
\eqref{eq:direction-list-separated} is an explicit direction-list cell:
the direction word itself agrees with a codeword on at least \(m\)
coordinates.
\end{theorem}

\begin{proof}
Choose a basis \(c_1,\ldots,c_s\) of \(C'\), write
\(c_\gamma=c_0+\sum_i\lambda_{\gamma,i}c_i\), and associate the parameter
point
\(p_\gamma=(\gamma,\lambda_{\gamma,1},\ldots,\lambda_{\gamma,s})\in
\F^{s+1}\).  Agreement at coordinate \(x\) is an affine hyperplane with
normal
\[
 v_x=(r_1(x),-c_1(x),\ldots,-c_s(x)).
\]
Let \(z\) be the number of zero normals and let \(g\le z\) of them agree
identically.  Since every \(c_i\) vanishes at those \(z\) coordinates,
the polynomial-space argument of \cref{thm:affine-span-list} gives
\(z\le K-s\).

The normals incident with any \(p_\gamma\) span \(\F^{s+1}\).  Otherwise
a nonzero relation \((\delta,\mu)\) gives a word
\(\delta r_1-\sum_i\mu_i c_i\) vanishing on at least \(m\) agreement
coordinates.  If \(\delta=0\), a nonzero degree-\(<K\) codeword has more
than \(K-1\) roots.  If \(\delta\ne0\), the direction word agrees with a
codeword on at least \(m\) coordinates, contradicting
\eqref{eq:direction-list-separated}.

If \(W\le\F^{s+1}\) has dimension \(r\), with \(1\le r\le s\), then the
coordinates with \(v_x\in W\) are common zeros of the
\((s+1-r)\)-dimensional space indexed by \(W^\perp\).  If the slope
coordinate vanishes on that whole space, these are common zeros of
\((s+1-r)\) independent codewords and number at most
\(K-s-1+r\).  Otherwise the kernel of the slope coordinate supplies
\(s-r\) independent codewords, giving the uniform bound
\(K-s+r\).  Put \(c=z-g\).  After \(r\) independent incident normals
have been chosen, at least
\[
 (m-g)-(K-s+r-z)=w+s-r+c
\]
further incident normals lie outside their span.  Therefore each slope
point is incident with at least
\[
 (m-g)\prod_{r=1}^{s}(w+s-r+c)
\]
ordered bases.
Counting ordered independent coordinate tuples gives
\[
 |Z|\le
 \frac{(n-g-c)^{\underline{s+1}}}
 {(m-g)(w+c)^{\overline s}},
 \qquad g,c\ge0,\quad g+c\le K-s.
\]
For fixed \(c\), the successive ratio in \(g\) has the sign of
\(n-c-(s+1)m+sg\), so again there is no interior maximum.  Both endpoint
families decrease with \(c\).  The endpoints \((g,c)=(0,0)\) and
\((K-s,0)\) give the two terms of \eqref{eq:affine-span-mca}.
\end{proof}

\begin{theorem}[Directional Johnson ray compiler]
\label{thm:directional-johnson-ray}
Retain the hypotheses and notation of \cref{thm:fixed-union-ray}, but allow
\(\nu\ge0\).  Choose a lift \(b_1\in\F^U\) of \(y_1\), put
\(C_U=\ker H_U\), and define the lift-invariant directional agreement
\begin{equation}
 \alpha_U(y_1)=
 \max_{c\in C_U}|\{x\in U:b_1(x)+c(x)=0\}|.
 \label{eq:directional-agreement}
\end{equation}
If \(h=N-t\) and
\begin{equation}
 h^2>N\alpha_U(y_1),                                \label{eq:directional-johnson-condition}
\end{equation}
then
\begin{equation}
 |Z|\le
 \left\lfloor
 \frac{N(h-\alpha_U(y_1))}
 {h^2-N\alpha_U(y_1)}
 \right\rfloor .                                  \label{eq:directional-johnson-ray}
\end{equation}
Moreover, with
\[
 d_U(y_1)=\min\{\wt(e):e\in\F^U,\ H_Ue=y_1\},
\]
one has
\begin{equation}
 \alpha_U(y_1)=N-d_U(y_1)\ge\nu.                  \label{eq:direction-distance}
\end{equation}
Equality holds exactly when the direction syndrome has no representation
on fewer than \(R\) columns of \(U\).
\end{theorem}

\begin{proof}
Changing the lift \(b_1\) by a kernel word merely permutes the maximization
in \eqref{eq:directional-agreement}, so \(\alpha_U(y_1)\) is intrinsic.
Choose a lift \(b_0\) of \(y_0\).  For every slope write
\[
 e_\gamma=b_0+\gamma b_1+k_\gamma,
 \qquad k_\gamma\in C_U,
\]
and choose an \(h\)-set \(A_\gamma\) of zero coordinates of
\(e_\gamma\).  On \(A_\gamma\), the codeword \(-k_\gamma\) agrees with
\(b_0+\gamma b_1\).  If \(\gamma\ne\delta\), then on
\(A_\gamma\cap A_\delta\),
\[
 b_1=\frac{-k_\gamma+k_\delta}{\gamma-\delta},
\]
which is a codeword of \(C_U\).  Hence
\(|A_\gamma\cap A_\delta|\le\alpha_U(y_1)\).  The same Johnson
incidence count as in \cref{thm:fixed-union-list-johnson}, with
\(\alpha_U(y_1)\) in place of \(\nu-1\), gives
\eqref{eq:directional-johnson-ray}.

Finally, the words \(b_1+c\), \(c\in C_U\), are exactly all lifts of
\(y_1\) supported in \(U\).  Maximizing their number of zero coordinates
is therefore equivalent to minimizing their weight, proving the equality
in \eqref{eq:direction-distance}.  Any \(R\) columns of \(H_U\) span
syndrome space, so \(d_U(y_1)\le R\) and \(\alpha_U(y_1)\ge N-R=\nu\).
The equality criterion is immediate.
\end{proof}

\begin{corollary}[Rank-regular fixed-union ray bound]
\label{cor:rank-regular-fixed-union-ray}
In \cref{thm:directional-johnson-ray}, suppose the direction syndrome is
rank-regular on \(U\), meaning \(d_U(y_1)=R\).  If
\((R+\nu-t)^2>(R+\nu)\nu\), then
\begin{equation}
 |Z|\le
 \left\lfloor
 \frac{(R+\nu)(R-t)}
 {(R+\nu-t)^2-(R+\nu)\nu}
 \right\rfloor .                                  \label{eq:rank-regular-fixed-union-ray}
\end{equation}
Thus every failure of this stronger low-nullity payment is either a
high-nullity chart or an explicit direction-rank-defect cell
\(d_U(y_1)<R\).
\end{corollary}

\begin{proof}
By \eqref{eq:direction-distance}, rank regularity is exactly
\(\alpha_U(y_1)=\nu\).  Substitute this value into
\eqref{eq:directional-johnson-ray}.
\end{proof}

\begin{corollary}[Quantitative direction-rank-defect payment]
\label{cor:quantitative-direction-defect}
Retain the notation of \cref{thm:directional-johnson-ray}, and write
\[
 d=R-t,\qquad
 j=R-d_U(y_1),\qquad
 N=R+\nu,\qquad
 D_0=(d+\nu)^2-N\nu.
\]
Thus \(j\ge0\) measures the direction-rank defect and
\(\alpha_U(y_1)=\nu+j\).  Whenever \(D_0-Nj>0\),
\begin{equation}
 |Z|\le
 \left\lfloor\frac{N(d-j)}{D_0-Nj}\right\rfloor .
 \label{eq:direction-defect-ray}
\end{equation}
For an integer budget \(B>1\), define
\begin{equation}
 J_B(\nu)=\min\left\{
 d-1,
 \left\lfloor\frac{D_0-1}{N}\right\rfloor,
 \left\lfloor\frac{BD_0-Nd}{N(B-1)}\right\rfloor
 \right\}.
 \label{eq:direction-defect-threshold}
\end{equation}
If \(0\le j\le J_B(\nu)\), then the whole fixed-union ray chart costs at
most \(B\) slopes.  Hence the residual direction cell at a fixed nullity
can be stated quantitatively as \(j>J_B(\nu)\), rather than merely as
\(j>0\).
\end{corollary}

\begin{proof}
By \eqref{eq:direction-distance},
\(\alpha_U(y_1)=N-d_U(y_1)=\nu+j\).  Substitution into
\eqref{eq:directional-johnson-ray} gives
\eqref{eq:direction-defect-ray}.  The second term in
\eqref{eq:direction-defect-threshold} makes its denominator positive,
and the first makes its numerator positive.  The final term is exactly the
rearrangement
\[
 N(d-j)\le B(D_0-Nj).
\]
Thus the real fraction in \eqref{eq:direction-defect-ray} is at most
\(B\), and so is its floor.
\end{proof}


\begin{theorem}[Paving-basis direction-defect ray compiler]
\label{thm:paving-ray}
Retain the fixed-union MCA notation of
\cref{thm:fixed-union-ray,thm:directional-johnson-ray}.  Write
\[
 N=R+\nu,
 \qquad h=N-t,
 \qquad d=R-t,
 \qquad j=R-d_U(y_1).
\]
Assume \(0\le j<d\), equivalently that the direction word is outside the
agreement ball on this chart.  Then
\begin{equation}
 |Z|\le
 \left\lfloor
 \frac{(\nu+1)\binom{R+\nu}{\nu+1}}
 {(R-t-j)\binom{R+\nu-t}{\nu}}
 \right\rfloor .
 \label{eq:paving-ray}
\end{equation}
This estimate is independent of the Johnson denominator and is strongest
for small nullity, including large direction defect.
\end{theorem}

\begin{proof}
Choose a minimum-weight lift \(q\in\F^U\) of the direction syndrome, so
\(\wt(q)=R-j\), and choose a basis \(k_1,\ldots,k_\nu\) of the MDS kernel
\(C_U=\ker H_U\).  In the parameter space with coordinates
\((\gamma,\lambda_1,\ldots,\lambda_\nu)\), agreement at coordinate \(x\)
has normal
\[
                       v_x=(q_x,k_1(x),\ldots,k_\nu(x)).
\]
Every set of at most \(\nu\) such normals is independent, because its
projection to the last \(\nu\) coordinates is a set of columns of a
generator matrix of the \([R+\nu,\nu,R+1]\) MDS code \(C_U\).

Every rank-\(\nu\) flat of these normals contains at most \(\nu+j\)
coordinates.  Indeed, such a flat is annihilated by a nonzero functional
\((\delta,a)\).  If \(\delta\ne0\), the vanishing coordinates are zeros of
a lift \(\delta q+c\) of \(\delta y_1\), which has weight at least
\(R-j\).  If \(\delta=0\), they are zeros of a nonzero MDS kernel word and
number at most \(\nu-1\).

Fix a slope point and choose \(h\) incident coordinate hyperplanes.  Put
\(r=\nu+1\) and \(\alpha=\nu+j\).  Every \((r-1)\)-subset of their normals
is independent.  A dependent \(r\)-subset is counted by each of its \(r\)
subsets of size \(r-1\), while the closure of any such subset contains at
most \(\alpha\) coordinate normals.  Hence the number of independent
\(r\)-subsets among the \(h\) incident normals is at least
\[
 \binom hr-\frac{\alpha-r+1}{r}\binom h{r-1}
 =\frac{h-\alpha}{r}\binom h{r-1}
 =\frac{d-j}{\nu+1}\binom{R+\nu-t}{\nu}.
\]
Globally there are at most \(\binom{R+\nu}{\nu+1}\) independent coordinate
bases, and each basis cuts out at most one parameter point.  Double
counting proves \eqref{eq:paving-ray}.
\end{proof}

\begin{corollary}[Exact paving defect threshold]
\label{cor:paving-threshold}
For an integer budget \(B\ge0\), define
\begin{equation}
 J_B^{\rm pav}(\nu)=
 \max\left\{-1,
 d-1-
 \left\lfloor
 \frac{(\nu+1)\binom{R+\nu}{\nu+1}}
 {(B+1)\binom{R+\nu-t}{\nu}}
 \right\rfloor
 \right\}.
 \label{eq:paving-threshold}
\end{equation}
Every separated fixed-union MCA chart with
\(0\le j\le J_B^{\rm pav}(\nu)\) costs at most \(B\) slopes.  Combining
this with \cref{cor:quantitative-direction-defect}, the exact certified
defect range is
\[
                0\le j\le
                \max\{J_B(\nu),J_B^{\rm pav}(\nu)\}.
\]
\end{corollary}

\begin{proof}
The floor in \eqref{eq:paving-ray} is at most \(B\) exactly when its
numerator is strictly smaller than \(B+1\) times its denominator.  Solving
this integer inequality for \(j\) gives \eqref{eq:paving-threshold}.
\end{proof}




\section{Minimum-distance sharpening and the exact primitive wedge}
\label{sec:min-distance-sharpening}
Retain the notation of \cref{thm:support-flag-recursion}.  Let
\[
 \mu=d_1(C')=\min_{0\ne c\in C'}|\supp(c)|.
\]
The generalized Singleton bound gives
\[
 \mu\ge n-K+1=R+1,
 \qquad R=n-K.
\]
The general flag theorem uses only the ambient MDS lower bound for each flag-annihilator direction.  Every such direction actually belongs to $C'$, so the true minimum support gives a sharper resource count.

\begin{theorem}[Minimum-distance enhanced flag resources]
\label{thm:min-distance-flag-resources}
Retain the hypotheses and notation of \cref{thm:support-flag-recursion}.  For a profile $\mathbf b=(b_1,\ldots,b_r)$ define
\begin{align}
 P_{\mathbf b}^{\sharp}
 &=\prod_{i=1}^{j}
 \left(f_i-t+b_0+\sum_{q=1}^{r}b_q\right),\label{eq:min-flag-P}\\
 Q_{\ell}^{\sharp}(\mathbf b)
 &=\mu-t+b_0+\sum_{q>\ell}b_q,\label{eq:min-flag-Q}\\
 A_\ell(\mathbf b)&=e_\ell-b_\ell,
 \qquad
 B_{\ell}^{\sharp}(\mathbf b)
 =\bigl(Q_{\ell}^{\sharp}(\mathbf b)-e_\ell+b_\ell\bigr)_+ .\label{eq:min-flag-AB}
\end{align}
For $\sigma\in\{T,U\}^r$, put
\begin{align}
 C_{\sigma}^{\sharp}(\mathbf b)
 &=P_{\mathbf b}^{\sharp}
 \prod_{\ell:\sigma_\ell=T}A_\ell(\mathbf b)
 \prod_{\ell:\sigma_\ell=U}B_{\ell}^{\sharp}(\mathbf b),\label{eq:min-flag-C}\\
 G_\sigma
 &=d_0^{\underline j}
 \prod_{\ell:\sigma_\ell=T}e_\ell
 \prod_{\ell:\sigma_\ell=U}
 \bigl(d_{\ell-1}-(j+\ell-1)\bigr).\label{eq:min-flag-G}
\end{align}
Then
\begin{equation}
 \boxed{
 \sum_{\mathbf b}L_{\mathbf b}C_{\sigma}^{\sharp}(\mathbf b)
 \le G_\sigma
 }
 \label{eq:min-flag-resource}
\end{equation}
for every binary resource pattern.  Consequently every nonnegative family $x_\sigma$ satisfying
\[
 \sum_\sigma x_\sigma C_{\sigma}^{\sharp}(\mathbf b)\ge1
 \quad\text{for every profile }\mathbf b
\]
gives the whole-chart bound
\begin{equation}
 \boxed{
 L\le\left\lfloor\sum_\sigma x_\sigma G_\sigma\right\rfloor .
 }
 \label{eq:min-flag-dual}
\end{equation}
The tensor and all-extender corollaries remain valid after replacing $w+1+b_0$ by $\mu-t+b_0$ and replacing every old-support factor by \eqref{eq:min-flag-AB}.
\end{theorem}

\begin{proof}
Fix a flag level $\ell$ and an adapted coordinate basis through $V_{\ell-1}$.  Its annihilator in $V_\ell$ is generated by a nonzero word
\[
 h_\ell\in V_\ell\setminus V_{\ell-1}\subseteq C'.
\]
Therefore $\wt(h_\ell)\ge\mu$.  The word vanishes outside $U_\ell$.  The number of mismatches outside $U_\ell$ is
\[
 b_{\rm out}=b_0+\sum_{q>\ell}b_q,
\]
and all of those coordinates are zeros of $h_\ell$.  Among the zero coordinates of $h_\ell$, at most
\[
 (n-\mu)-b_{\rm out}
\]
are agreements.  Since every listed point has at least $m$ agreements, at least
\[
 m-\bigl((n-\mu)-b_{\rm out}\bigr)
 =\mu-t+b_{\rm out}
 =Q_\ell^{\sharp}(\mathbf b)
\]
agreement coordinates are nonzeros of $h_\ell$ and hence extend the adapted basis.  The $A_\ell=e_\ell-b_\ell$ agreeing coordinates in the new layer all extend, so at least $B_\ell^{\sharp}$ extending agreements lie in the old support.  The global basis capacities are unchanged.  The double count and finite dual are therefore identical to the proof of \cref{thm:support-flag-recursion} with the sharpened factors.
\end{proof}

\begin{corollary}[Minimum-word all-extender bound]
\label{cor:min-word-all-extender}
Choose $V_0=\langle h\rangle$, where $h$ is a minimum-weight word of $C'$.  If $s=\dim C'$, then
\begin{equation}
 \boxed{
 L\le
 \left\lfloor
 \frac{\mu\prod_{\ell=1}^{s-1}(d_\ell-\ell)}
      {(\mu-t+b_0)^s}
 \right\rfloor
 \le
 \left\lfloor
 \frac{\mu(n-s+1)^{s-1}}
      {(\mu-t+b_0)^s}
 \right\rfloor .
 }
 \label{eq:min-word-bound}
\end{equation}
Writing $\mu=R+a$, $a\ge1$, the soft form is
\begin{equation}
 L\le
 \left\lfloor
 \frac{(R+a)(n-s+1)^{s-1}}
      {(w+a+b_0)^s}
 \right\rfloor .
 \label{eq:min-word-soft}
\end{equation}
\end{corollary}

\begin{proof}
A generalized-weight minimizer is support-saturated by \cref{lem:weight-minimizer-saturated}, so the minimum-weight line admits a support-saturated flag.  Apply the all-extender form of \cref{thm:min-distance-flag-resources}.  The initial basis count is $\mu$, and $\mu-t+b_0$ is a lower bound at every extension level.  Since every remaining support layer is nonempty and $d_{s-1}\le n$, one has $d_\ell-\ell\le n-s+1$.
\end{proof}

\begin{proposition}[Exact active minimum-support transitions]
\label{prop:min-support-transitions}
At $b_0=0$, \eqref{eq:min-word-soft} pays every first-unpaid affine chart at and above the following support excesses:
\[
\begin{array}{c|r|r|r|r}
\toprule
\text{row}&s&a_{\rm paid}&\text{bound at }a_{\rm paid}&\text{bound at }a_{\rm paid}-1\\
\midrule
\text{KoalaBear MCA}&15&70832&274974324324469113&275003903412638889\\
\text{KoalaBear list}&15&70832&274974569967317804&275004149082130935\\
\text{Mersenne-31 MCA}&7&111529&16776653&16777295\\
\text{Mersenne-31 list}&7&111529&16776668&16777309\\
\bottomrule
\end{array}
\]
Thus a surviving zero-mismatch chart has $a\le70831$ on KoalaBear or $a\le111528$ on Mersenne-31.  Positive $b_0$ only shrinks this residual.
\end{proposition}

\begin{proposition}[Exact mismatch curve]
\label{prop:min-mismatch-curve}
For selected support excesses, the least outside mismatch paid by \eqref{eq:min-word-soft} is
\[
\begin{array}{c|rrrrr}
\toprule
& a=1&a=1000&a=10000&a=50000&a=70000\\
\midrule
\text{KoalaBear MCA/list}&70230&69240&60318&20659&825\\
\text{Mersenne-31 MCA/list}&108962&107987&99202&60141&40599\\
\bottomrule
\end{array}
\]
The curve is strictly decreasing in the actual direction-code support excess.
\end{proposition}

\begin{remark}[Combination with the actual first generalized weight]
Let the full support have size $d_s=R+\nu$.  Replacing the ambient lower bound in the common-zero Johnson compiler by $d_1(C')=R+a$ gives
\begin{equation}
 L\le
 \left\lfloor
 \frac{(R+\nu)(w+a+b_0)}
 {(w+\nu+b_0)^2-(R+\nu)(\nu-a)}
 \right\rfloor
 \label{eq:actual-d1-johnson}
\end{equation}
when the denominator is positive.  Combining \eqref{eq:actual-d1-johnson} with the nonuniform form of \eqref{eq:min-word-bound} gives the exact residual wedge in $(a,\nu,b_0)$.
\end{remark}

\begin{theorem}[Fixed-mismatch puncturing compiler]
\label{thm:fixed-mismatch-puncturing}
Let $\mathcal L\subseteq\mathcal A$ be a family of codewords, each agreeing with a received word $u$ on at least $m$ coordinates.  Suppose a fixed set $Z\subseteq D$, $|Z|=z$, is a mismatch set for every member of $\mathcal L$.  Then $z\le t$, and if the affine span of $\mathcal L$ has direction dimension at most $s$, then
\begin{equation}
 \boxed{
 |\mathcal L|
 \le
 \left\lfloor
 \frac{\binom{R-z+s}{s}}
      {\binom{w+s}{s}}
 \right\rfloor .
 }
 \label{eq:fixed-mismatch-puncturing}
\end{equation}
\end{theorem}

\begin{proof}
Every listed word has at most $t$ mismatches, so $z\le t$.  Puncture the coordinates in $Z$.  Since $z<t<R=n-K$, evaluation of degree-$<K$ polynomials remains injective on $D\setminus Z$, no agreement is deleted, and the affine direction dimension does not increase.  Apply the recursive affine-span compiler to the punctured code of length $n-z$.
\end{proof}

\begin{corollary}[Active puncture thresholds]
\label{cor:active-puncture-thresholds}
At the first unpaid affine dimensions, a subfamily with a common fixed mismatch set is paid at the following first integers:
\[
\begin{array}{c|r|r|r}
\toprule
\text{row}&z_{\rm paid}&\text{bound at }z_{\rm paid}&\text{bound at }z_{\rm paid}-1\\
\midrule
\text{KoalaBear MCA}&67313&274978201175970494&274982404608707323\\
\text{KoalaBear list}&67314&274978201175970494&274982404608707323\\
\text{Mersenne-31 MCA}&322321&16777133&16777295\\
\text{Mersenne-31 list}&322322&16777133&16777295\\
\bottomrule
\end{array}
\]
\end{corollary}

\begin{proposition}[Exchange defect dominates support excess]
\label{prop:exchange-defect}
In one boundary prefix fiber, let the associated codeword direction space have minimum support $R+a$.  For distinct supports $M,M'$ of size $m$, write
\[
 e=|M\setminus M'|=|M'\setminus M|=w+r.
\]
Then
\begin{equation}
 \boxed{r\ge a.}
 \label{eq:exchange-defect}
\end{equation}
\end{proposition}

\begin{proof}
The prefix-rigidity identity of CAP25 v13.2 gives
\[
 \Lambda_M-\Lambda_{M'}=G(A-B),
 \qquad \deg(A-B)\le r-1,
\]
where $G$ is the locator of $M\cap M'$ and has degree $m-e$.  The corresponding nonzero codeword difference vanishes on the $m-e$ common support coordinates, so its weight is at most
\[
 n-(m-e)=t+e=R+r.
\]
By the definition of $a$, its weight is at least $R+a$.  Hence $r\ge a$.
\end{proof}

\begin{corollary}[Top-seam localization]
\label{cor:top-seam-localization}
The top seam $e=w+1$ can occur only in the exact-minimum-distance branch $a=1$.  Every chart with $a\ge2$ has first possible exchange defect at least $a$.
\end{corollary}

\begin{theorem}[Exact primitive residual after minimum-distance payment]
\label{thm:min-distance-residual}
After all unconditional first-match payments in Parts~I--IV, an over-budget first-unpaid Q or list chart must lie in the following simultaneous wedge:
\begin{enumerate}[label=\textup{(R\arabic*)}]
\item its support excess $a$ lies below the exact curve \eqref{eq:min-word-soft};
\item its full-support nullity lies beyond both \eqref{eq:actual-d1-johnson} and the minimum-word flag bound;
\item it contains no fixed mismatch block meeting \cref{thm:fixed-mismatch-puncturing};
\item every boundary neighbour has exchange defect at least $a$, and the top seam is restricted to $a=1$;
\item it is not in an earlier quotient, occupancy, extension, common-zero, saturation, or rank-defect cell.
\end{enumerate}
\end{theorem}


\section{The quadratic mean-overlap staircase}\label{sec:mean-overlap-v3}
\begin{lemma}[Large-overlap collapse]
\label{lem:large-overlap-collapse}
Fix a received pair and an exact agreement \(a=n-r\ge k+1\).  Choose one
noncommon exact witness support \(S_z\) and explaining polynomial \(p_z\)
for every slope \(z\) in its bad set \(Z\).  If two distinct chosen
supports satisfy
\[
                    \abs{S_z\cap S_w}\ge k+r,       \tag{MO1}
\label{eq:large-overlap-collapse}
\]
then \(\abs Z\le r+1\).
\end{lemma}

\begin{proof}
Put
\[
 c_1=\frac{p_z-p_w}{z-w},\qquad c_0=p_z-zc_1.
\]
On \(S_z\cap S_w\), the two line equations imply that the received pair
equals \((c_0,c_1)\).  Let \(C_0\) be the full common support of this
codeword pair and write \(c=\abs{C_0}\ge k+r\).  For every \(u\in Z\),
\(\abs{S_u\cap C_0}\ge a+c-n\ge k\), so the explaining polynomial
\(p_u\) equals \(c_0+uc_1\).

Subtract this codeword pair from the received pair.  At every coordinate
outside \(C_0\) at least one of the two residual values is nonzero, and a
coordinate can cancel at at most one finite slope.  A noncommon witness
for \(u\) must contain at least \(\max\{1,a-c\}\) such cancellations:
the support-size condition gives \(a-c\), and one is still necessary when
\(a\le c\).  Double counting therefore gives
\[
 \abs Z\le
 \floor{\frac{n-c}{\max\{1,a-c\}}}\le r+1.        \tag{MO2}
\label{eq:large-overlap-count}
\]
Indeed, for \(c\ge a\) the numerator is at most \(r\); for \(c=a-1\)
it is \(r+1\); and, with \(x=a-c\ge2\), the quotient is
\((r+x)/x\le r+1\).
\end{proof}

\begin{theorem}[Quadratic mean-overlap theorem]
\label{thm:quadratic-mean-overlap}
Let \(C=\RS_\F(D,k)\), put \(R=n-k\), let
\(0\le r\le R-1\), and let \(\varnothing\ne\Gamma\subseteq\F\).  If
\[
 (n-r)^2\ge n(k+r),
 \qquad\text{equivalently}\qquad
 r^2\ge n(3r-R),                                  \tag{MO3}
\label{eq:quadratic-overlap-condition}
\]
then
\[
 B_{C,\Gamma}^{\rm MCA}(n-r)=\min\{\abs\Gamma,r+1\}. \tag{MO4}
\label{eq:quadratic-overlap-exact}
\]
The same upper bound holds for every linear \([n,k]\) MDS code.
\end{theorem}

\begin{proof}
The universal tangent construction imported from \cite[Sec.~13]{CAP25v132} gives the lower bound.  For the upper
bound, fix a received pair and its challenge-restricted bad set \(Z\).
If \(\abs Z\le r+1\) there is nothing to prove.  Otherwise choose
\(r+2\) slopes and distinct exact witness supports
\(S_1,\ldots,S_{r+2}\), each of size \(a=n-r\).  Suppose every pair had
intersection at most \(k+r-1\), and put
\(d_x=\#\{i:x\in S_i\}\).  Then
\[
 \sum_x\binom{d_x}{2}\le\binom{r+2}{2}(k+r-1),    \tag{MO5}
\]
whereas Cauchy--Schwarz and \(a^2/n\ge k+r\) give
\[
 \sum_x\binom{d_x}{2}
 \ge\frac{(r+2)^2a^2/n-(r+2)a}{2}
 \ge\frac{(r+2)^2(k+r)-(r+2)a}{2}.                \tag{MO6}
\]
The last lower bound exceeds the upper bound in \textup{(MO5)} by
\[
 \frac{r+2}{2}\bigl(k+3r-n+1\bigr).
\]
When \(3r>R\) this is positive.  When \(3r\le R\), the exact deep theorem
already gives the desired upper bound.  Thus in the remaining case some
pair satisfies \eqref{eq:large-overlap-collapse}, and
\cref{lem:large-overlap-collapse} contradicts \(\abs Z\ge r+2\).
The exact-support reduction and large-overlap lemma use only the MDS
information-set property, proving the stated extension.
\end{proof}

\begin{corollary}[Exact quadratic staircase]
\label{cor:mean-overlap-exact}
Put
\[
 r_{\rm quad}(n,k)=
 \floor{\frac{3n-\sqrt{n(5n+4k)}}2}.
 \tag{MO7}\label{eq:quadratic-radius}
\]
For every \(0\le r\le r_{\rm quad}(n,k)\) and every nonempty challenge
set \(\Gamma\),
\[
 B_{C,\Gamma}^{\rm MCA}(n-r)=\min\{\abs\Gamma,r+1\}.
\]
If \(k/n\to\rho\), then
\(r_{\rm quad}(n,k)/n\to
\alpha_\rho=(3-\sqrt{5+4\rho})/2\).
\end{corollary}

\begin{proof}
The smaller root of \(r^2-3nr+n(n-k)=0\) is the real number inside the
floor in \eqref{eq:quadratic-radius}.  Apply
\cref{thm:quadratic-mean-overlap}; the limiting formula follows by
division by \(n\).
\end{proof}

\begin{proposition}[Limit of pairwise-overlap information]
\label{prop:pairwise-overlap-limit}
Let \(k/n\to\rho\in(0,1)\), \(r/n\to\alpha\in(0,1)\), and suppose
\[
 \alpha^2<3\alpha-(1-\rho).
 \tag{MO8}\label{eq:pairwise-overlap-limit}
\]
For all sufficiently large \(n\), there are \(r+2\) distinct
\(r\)-subsets \(T_i\) such that, whenever
\(j=3r-(n-k)\le r\),
\(\abs{T_i\cap T_\ell}\le j-1\) for every \(i\ne\ell\).  If \(j>r\),
that intersection condition is automatic.  Hence pairwise support overlap
alone cannot extend the exact theorem past the quadratic boundary; further
progress must use the syndrome, determinant, or fiber incidence.  This is
a limitation of the method, not a construction of an MCA-bad line.
\end{proposition}

\begin{proof}
When \(j\le r\), choose \(r+2\) independent uniform \(r\)-subsets.
The intersection of a fixed pair is hypergeometric with mean
\(r^2/n=(\alpha^2+o(1))n\), whereas
\(j=(3\alpha-(1-\rho)+o(1))n\).  More explicitly,
\[
 \Pr(\abs{T_1\cap T_2}=s)
 =\frac{\binom rs\binom{n-r}{r-s}}{\binom nr}.
\]
After writing \(s=xn\), Stirling's formula gives the exponent
\[
 \alpha h(x/\alpha)+(1-\alpha)
 h((\alpha-x)/(1-\alpha))-h(\alpha),
\]
which is strictly concave and has its unique maximum zero at
\(x=\alpha^2\).  The strict gap in
\eqref{eq:pairwise-overlap-limit}, followed by summing at most \(n+1\)
terms, therefore gives probability \(e^{-\Omega(n)}\) that one fixed
intersection reaches \(j\).  A union bound over \(O(n^2)\) pairs is
smaller than one.  A
successful family is automatically distinct, because equal members have
intersection \(r\ge j\).  When \(j>r\), choose any \(r+2\) distinct
\(r\)-sets.
\end{proof}

The following complementary theorem can be stronger when the overlap
defect \(j=3r-R\) is small.  Its only new input is a packing inequality;
in particular it uses no smoothness or Fourier estimate.

\begin{theorem}[Exact overlap--packing criterion]
\label{thm:overlap-packing-exact}
Let \(C=\RS_\F(D,k)\), put \(R=n-k\), and fix an integer
\(0\le r\le R-1\).  Set \(a=n-r\) and \(j=3r-R\).  If either
\[
 j\le0,
 \tag{OP0}\label{eq:op-deep}
\]
or
\[
 1\le j\le r,
 \qquad
 \binom nj\le(r+1)\binom rj,
 \tag{OP}\label{eq:op-packing}
\]
then
\[
                    B_C^{\rm MCA}(n-r)=r+1.       \tag{OP$'$}
\label{eq:op-exact}
\]
The same upper bound holds for every linear \([n,k]\) MDS code; the
matching lower bound holds whenever the field contains at least \(r+1\)
distinct slope parameters.
\end{theorem}

\begin{proof}
Condition \eqref{eq:op-deep} is the imported deep-regime case \cite[Sec.~13]{CAP25v132}, so assume
\eqref{eq:op-packing}.  Fix an arbitrary received pair \((f,g)\), let
\(Z\) be its bad-slope set, and use the exact-agreement reduction imported from \cite[Sec.~13]{CAP25v132} to choose, for every \(z\in Z\), an
exact witness support \(S_z\), \(\abs{S_z}=a\), and an explaining
polynomial \(p_z\in\F[X]_{<k}\).  A single noncommon support cannot carry
two distinct slopes, so the supports chosen for distinct elements of
\(Z\) are distinct.

For the stated MDS extension, the same exact-support reduction is
available: interpolate the unexplained component on any \(k\)-subset of
the original witness support; because every \(k\)-subset is an information
set, nonexplanation is detected at one further coordinate, and that
\((k+1)\)-set can be enlarged to size \(a\).

First suppose that two of them have a large intersection:
\[
 \abs{S_z\cap S_w}\ge n+k-a=k+r
 \qquad(z\ne w).
 \tag{OP1}\label{eq:op-large-overlap}
\]
Then \cref{lem:large-overlap-collapse} gives \(\abs Z\le r+1\).

It remains to consider the complementary case, in which every pair of
chosen supports satisfies
\(\abs{S_z\cap S_w}\le n+k-a-1\).  Put
\(T_z=D\setminus S_z\), so \(\abs{T_z}=r\).  For distinct slopes,
\[
 \abs{T_z\cap T_w}
 =n-2a+\abs{S_z\cap S_w}
 \le3r-R-1=j-1.                                  \tag{OP3}
\label{eq:op-small-overlap}
\]
No \(j\)-subset of \(D\) can therefore lie in two different \(T_z\)'s.
Counting pairs \((z,J)\) with \(J\in\binom{T_z}{j}\) yields
\[
                 \abs Z\binom rj\le\binom nj\le
                 (r+1)\binom rj,
\]
and hence \(\abs Z\le r+1\).  The universal tangent construction gives
the reverse inequality.  The proof used only linearity, the fact that
agreement of two codewords on \(k\) coordinates forces equality, and the
exact-support reduction; these are MDS properties.  The coordinate
tangent construction gives the stated MDS lower bound.
\end{proof}

\begin{proposition}[General overlap--packing upper bound]
\label{prop:general-overlap-packing-upper}
For \(1\le j=3r-(n-k)\le r\), let \(A(n,r,j)\) be the largest size of a
family of \(r\)-subsets of an \(n\)-set whose distinct members intersect
in at most \(j-1\) points.  Then
\[
 B_{C,\Gamma}^{\rm MCA}(n-r)
 \le\min\left\{\abs\Gamma,
     \max\left(r+1,A(n,r,j)\right)\right\}          \tag{OP5}
\label{eq:general-overlap-packing-upper}
\]
and
\[
 A(n,r,j)\le
 \floor{\frac{\binom nj}{\binom rj}}.              \tag{OP6}
\label{eq:packing-number-bound}
\]
\end{proposition}

\begin{proof}
For a fixed received pair, either two chosen exact witness supports have
intersection at least \(k+r\), in which case
\cref{lem:large-overlap-collapse} gives at most \(r+1\) slopes, or every
pair of complementary \(r\)-sets intersects in at most \(j-1\) points.
The latter family has size at most \(A(n,r,j)\).  Finally, no \(j\)-subset
can lie in two members of such a packing, so counting contained
\(j\)-subsets proves \eqref{eq:packing-number-bound}.
\end{proof}


\section{Exact thresholds for explicit prize rows}\label{sec:prize-rows}

\begin{table}[H]
\centering
\caption{Explicit maximal-dimension prize-admissible rows.  In each row
\(k=2^{40}\), \(B=\floor{p/2^{128}}=r_\rho(n)+1\), and \((s,a_0)\) is part of
the Proth certificate in \cref{prop:proth-row-check}.}
\label{tab:prize-proth-rows}
\small
\begin{tabular}{@{}ccrrc@{}}
\hline
rate & length & \(B\) & bits of \(p\) & \((s,a_0)\)\\
\hline
\(1/2\)  & \(2^{41}\) & \(389500552609\)  & 167 & \((92,3)\)\\
\(1/4\)  & \(2^{42}\) & \(1210584858040\) & 169 & \((93,13)\)\\
\(1/8\)  & \(2^{43}\) & \(2879806199253\) & 170 & \((95,5)\)\\
\(1/16\) & \(2^{44}\) & \(6233898019554\) & 171 & \((97,5)\)\\
\hline
\end{tabular}
\end{table}

For completeness, the four field orders are
\begin{align*}
p_{1/2}&=132540169958804033333249306710494641010898987122689,\\
p_{1/4}&=411940680852499481698306614369841346700408394874881,\\
p_{1/8}&=979947269755402568812854322316630667196565607677953,\\
p_{1/16}&=2121285573237585848299875619011192262679065433997313.
\end{align*}
Their odd Proth coefficients \(u\), in the same order, are
\begin{align*}
u_{1/2}&=26766274163673319604503,
&u_{1/4}&=41595378994516821279015,\\
u_{1/8}&=24737346889219389259839,
&u_{1/16}&=13387194060291799253121.
\end{align*}
For \(F_{n,k}(r)=r^2-n(3r-(n-k))\), the exact boundary checks are
\[
\begin{array}{c|r|r}
 \rho&F_{n,k}(B-1)&F_{n,k}(B)\\ \hline
 1/2&5154112775168&-663955886271\\
 1/4&7590647904465&-3182321912768\\
 1/8&13908181940112&-6720484728007\\
 1/16&19335616403905&-20973145690236.
\end{array}                                                    \tag{PC0}
\label{eq:quadratic-row-certificates}
\]

\begin{proposition}[Exact arithmetic and primality certificates]
\label{prop:proth-row-check}
For the four rows in \cref{tab:prize-proth-rows}, the displayed integer
\(p\) satisfies
\[
 p=u\,2^s+1,\qquad u\text{ odd},\qquad u<2^s,\qquad
 a_0^{(p-1)/2}\equiv-1\pmod p.                  \tag{PC1}
\label{eq:proth-certificates}
\]
Consequently every \(p\) is prime.  Moreover
\[
 n\mid p-1,\qquad p<2^{256},\qquad
 B\,2^{128}\le p<(B+1)2^{128},                  \tag{PC2}
\label{eq:prize-row-arithmetic}
\]
where \(n\) and \(B\) are the corresponding entries of the table.
They also satisfy \(F_{n,k}(B-1)\ge0>F_{n,k}(B)\).  Since
\(F_{n,k}'(r)=2r-3n<0\) on \([0,n]\), these two signs locate its smaller
root and give \(B-1=r_\rho(n)=r_{\rm quad}(n,k)\).
Thus \(\F_p^*\) contains a subgroup of order \(n\), and each displayed code exists with the asserted slope budget.
\end{proposition}

\begin{proof}
All identities and inequalities in
\eqref{eq:quadratic-row-certificates}--\eqref{eq:prize-row-arithmetic}
are direct
integer calculations; the values of \((s,a_0)\), \(u\), \(p\), \(n\),
and \(B\) have all been printed above so that the calculation is
independently reproducible.  We recall why the certificate proves
primality.  If a prime \(\ell\) divides \(p\), then
\(a_0^{u2^{s-1}}\equiv-1\pmod\ell\), whereas
\(a_0^{u2^s}\equiv1\pmod\ell\).  The multiplicative order of \(a_0\)
modulo \(\ell\) therefore has exact \(2\)-part \(2^s\), so
\(2^s\mid\ell-1\).  Since \(u<2^s\), one has \(2^s>\sqrt p\); hence a
composite \(p\) would have a prime divisor both at most \(\sqrt p\) and
at least \(2^s+1\), a contradiction.  This is Proth's theorem in the
special form used here.  Finally \(s\ge\log_2 n\) gives \(n\mid p-1\),
and cyclicity of \(\F_p^*\) gives the required subgroup.
\end{proof}

\begin{theorem}[Exact first adjacent row over a separating field]
\label{thm:exact-first-adjacent-row}
Let \(C=\RS_\F(D,k)\), put \(R=n-k\) and
\(M=\binom n{R-1}=\binom n{k+1}\), and define
\[
                    Q_{\rm sep}(M)=\max\left\{M,\binom M2\right\}.
\]
If \(\abs\F>Q_{\rm sep}(M)\), then for the full-field challenge
\[
                         B_C^{\rm MCA}(k+1)=M.      \tag{AD1}
\]
If \(R\ge2\) and \(b=\floor{\eps\abs\F}\), the exact target threshold
therefore satisfies
\[
 \begin{array}{ll}
 b\ge M &\Longrightarrow\quad a^*=k+1,\\
 \displaystyle\binom n{R-2}\le b<M
   &\Longrightarrow\quad a^*=k+2.
 \end{array}                                       \tag{AD2}
\]
Thus the first finite adjacent comparison has literal binomial constants;
no \(e^{o(n)}\) or unspecified polynomial factor occurs.
\end{theorem}

\begin{proof}
The upper bound in \textup{(AD1)} is the exact support-atlas bound imported from \cite[Sec.~13]{CAP25v132}.  For the reverse inequality use the
Reed--Solomon parity check of redundancy \(R\).  For every
\((R-1)\)-set \(E\subseteq D\), its column span \(V_E\) is a hyperplane
in \(\F^R\), and distinct sets give distinct hyperplanes: otherwise the
union of two distinct \((R-1)\)-sets would contain at least \(R\) columns
in one \((R-1)\)-space, contradicting the MDS column property.

Every proper linear hyperplane in \(\F^R\) has
\(\abs{\F}^{R-1}\) points.  Since \(M<\abs\F\), the union of the \(M\)
spaces \(V_E\) has fewer than \(\abs{\F}^{R}\) points; choose \(y_1\)
outside it.  For each \(E\),
choose a nonzero linear functional \(\ell_E\) with kernel \(V_E\).
The line \(y_0+\gamma y_1\) meets \(V_E\) at
\[
                 \gamma_E=-\ell_E(y_0)/\ell_E(y_1).
\]
For \(E\ne E'\), equality \(\gamma_E=\gamma_{E'}\) cuts out a proper
hyperplane in the variable \(y_0\), because the normalized functionals
\(\ell_E/\ell_E(y_1)\) and
\(\ell_{E'}/\ell_{E'}(y_1)\) are distinct.  There are at most
\(\binom M2<\abs\F\) collision hyperplanes; their union also has fewer
than \(\abs{\F}^{R}\) points, so choose \(y_0\) outside it.  Since
\(y_1\notin V_E\), the line is not contained in \(V_E\), and every
intersection is transverse.  The \(M\) parameters \(\gamma_E\) are then
finite and pairwise distinct.  Syndrome surjectivity and
\cref{thm:syndrome-secant-exact} realize them as \(M\) bad slopes at
agreement \(k+1\), proving \textup{(AD1)}.

If \(b\ge M\), the support upper bound makes the first allowed agreement
safe.  If \(\binom n{R-2}\le b<M\), equality \textup{(AD1)} makes
\(k+1\) unsafe, whereas
the exact support-atlas bound imported from \cite[Sec.~13]{CAP25v132} makes \(k+2\) safe.  Monotonicity proves
\textup{(AD2)}.
\end{proof}


\section{Asymptotic consequences of the imported prefix floor}\label{sec:shallow-prefix-exponent}
\begin{theorem}[Unconditional shallow-prefix RS--MCA exponent]
\label{thm:unconditional-asymptotic-rs-mca}
Let \(C_n=\RS_{\F_n}(D_n,k_n)\), where
\(D_n\subseteq\B_n\subseteq\F_n\), \(\abs{D_n}=n\), and
\(k_n/n\to\rho\in(0,1)\).  Let \(a_n\ge k_n+1\), put
\(w_n=a_n-k_n-1\), and assume
\[
 \frac{a_n}{n}\to\alpha\in(0,1),\qquad
 w_n\log\abs{\B_n}=o(n),                           \tag{AS1}
\]
\(\abs{\F_n}>n\), and, for some finite \(\phi\ge0\),
\[
 \frac1n\log\abs{\F_n}\to\phi,
 \qquad
 \frac1n\log(\abs{\F_n}-n)\to\phi.               \tag{AS2}
\]
For the full-field challenge,
\[
 \frac1n\log B_{C_n}^{\rm MCA}(a_n)
   =\min\{h(\alpha),\phi\}+o(1),                   \tag{AS3}
\]
and therefore
\[
 \frac1n\log e_{\rm MCA}
   \left(C_n,1-\frac{a_n}{n}\right)
   =-\bigl(\phi-h(\alpha)\bigr)_++o(1).            \tag{AS4}
\]
Because \(\abs{\B_n}\ge n\), condition \textup{(AS1)} forces
\(\alpha=\rho\).  No smoothness, Fourier estimate, or auxiliary ray
hypothesis is assumed.
\end{theorem}

\begin{proof}
Put \(M_n=\binom n{a_n}\) and
\(L_n=\ceil{M_n\abs{\B_n}^{-w_n}}\).  Exact-agreement reduction and
fixed-support slope uniqueness give the unconditional upper bound
\[
 B_{C_n}^{\rm MCA}(a_n)\le\min\{\abs{\F_n},M_n\}.  \tag{AS5}
\]
The exact locator-prefix list and collision-aware pole compiler imported from \cite[Secs.~14--18]{CAP25v132} give
\[
 B_{C_n}^{\rm MCA}(a_n)\ge
 \left\lceil
 \frac{L_n(\abs{\F_n}-n)}
 {\abs{\F_n}-n+k_n(L_n-1)}
 \right\rceil.                                     \tag{AS6}
\]
By Stirling's formula and \textup{(AS1)},
\(\log L_n=h(\alpha)n+o(n)\).  For positive \(x,y\),
\(xy/(x+k_ny)\ge\frac12\min\{y,x/k_n\}\); hence
\textup{(AS2)}, \(\log k_n=o(n)\), and the ceiling show that the
right side of \textup{(AS6)} has logarithm
\(n\min\{h(\alpha),\phi\}+o(n)\).  The upper bound
\textup{(AS5)} has the same exponent, proving \textup{(AS3)}; subtracting
\(\log\abs{\F_n}\) proves \textup{(AS4)}.  Finally
\(w_n\log n=o(n)\), so \((a_n-k_n)/n\to0\) and
\(\alpha=\rho\).
\end{proof}

\begin{corollary}[Unconditional large-challenge RS--MCA threshold]
\label{cor:unconditional-rs-mca-capacity}
Under the row hypotheses of
\cref{thm:unconditional-asymptotic-rs-mca}, let the full-field target
satisfy \(\eps_n=\exp(-\lambda n+o(n))\) for a finite
\(\lambda\ge0\).  If
\[
                         \lambda<\phi-h(\rho),      \tag{AS7}
\]
then, for every sufficiently large \(n\),
\[
 a_n^*=k_n+1,\qquad
 \delta_n^*=1-\frac{k_n+1}{n}=1-\rho+o(1).         \tag{AS8}
\]
Conversely, if \(\lambda>(\phi-h(\rho))_+\), every agreement sequence
satisfying \((a_n-k_n-1)\log\abs{\B_n}=o(n)\) is unsafe.  The critical
boundary \(\lambda=(\phi-h(\rho))_+\) is governed by the
exact finite constants and is not decided by exponent asymptotics.  This
is a large scalar-extension regime.  If \(\abs{\F_n}\) is polynomial in
\(n\), then \(\phi=0\) and \textup{(AS7)} cannot hold; the corollary does
not settle that Proximity-Prize parameter regime.
\end{corollary}

\begin{proof}
At \(a=k_n+1\), \textup{(AS5)} is
\(B_{C_n}^{\rm MCA}(a)\le\binom n{k_n+1}
=\exp(h(\rho)n+o(n))\).  Under \textup{(AS7)},
\(\eps_n\abs{\F_n}=\exp((\phi-\lambda)n+o(n))\) has strictly larger
exponent, and taking the integer floor does not change the comparison.
Thus the first permitted agreement is safe
and \textup{(AS8)} follows.  The converse follows from \textup{(AS4)}
and the strict reverse exponential inequality.
\end{proof}


\part{Exact profile refinements and the profile envelope}
\section{Profile envelope and the sequel compiler}\label{sec:profile-envelope-compiler}
A realized first-match profile $\lambda$ has a full support slice $\Omega^0_\lambda$, a coefficient field $\B_\lambda$, a proved boundary map
$\Phi_\lambda:\Omega^0_\lambda\to\B_\lambda^{R_\lambda}$, realized image size
$L_\lambda=|\Phi_\lambda(\Omega^0_\lambda)|$, and image-normalized average
\[
 \bar N_\lambda=\frac{|\Omega^0_\lambda|}{L_\lambda}.
\]
For a received line and agreement $a$, let $\Lambda(a)$ be the realized first-match profile set and define
\begin{equation}
 \mathfrak E_n(a)=1+(n-a+1)+
 \sup_{\text{received lines}}\sum_{\lambda\in\Lambda(a)}(1+\bar N_\lambda).\label{eq:profile-envelope}
\end{equation}
The formal codomain size $|\B_\lambda|^{R_\lambda}$ may replace $L_\lambda$ only after a full-image certificate
$L_\lambda\ge e^{-o(n)}|\B_\lambda|^{R_\lambda}$ has been proved.  Otherwise the leaf stays at realized-image scale or is routed to an earlier effective-image-collapse cell.

\begin{definition}[Admissible sequel compiler]\label{def:admissible-sequence}
A row sequence is \emph{admissible} when: (i) every bad witness belongs to an ordered first-match atlas with $e^{o(n)}$ realized profiles; (ii) all quotient, planted, field-drop, tangent, rank, extension, and directly counted ray cells have proved distinct-slope payments; (iii) every remaining primitive profile has a fixed-density Boolean support slice, an exact boundary map, and image normalization; (iv) its nontrivial effective Fourier characters satisfy the certified minor/major payment of \cref{def:effective-major-minor,def:aggregate-minor-payment,def:major-arc-aggregate}, or an equivalent direct Sidon payment; and (v) every residual ray chart has either a direct slope bound or the ray compiler of \cref{hyp:ray-compiler}.  All profile fields and quotient scales are included in \eqref{eq:profile-envelope}.
\end{definition}

\begin{theorem}[Conditional profile-envelope compiler]\label{thm:main-smooth-circle}
Every admissible row sequence satisfies
\begin{equation}
 B_{C_n}^{\rm MCA}(a_n)\le e^{o(n)}\mathfrak E_n(a_n).\label{eq:conditional-numerator}
\end{equation}
For a finite row the same proof is literal after every $e^{o(n)}$ term is replaced by its exact integer constant and all first-match cells are summed once.
\end{theorem}
\begin{proof}
The first-match atlas pays the algebraic cells.  The effective Fourier/Sidon step and \cref{thm:primitive-q} pay primitive Q, while the ray compiler and \cref{prop:q-implies-sp} convert the support bounds to distinct slopes.  Summation over the realized profile set gives \eqref{eq:conditional-numerator}.  The finite statement is the same disjoint first-match count with integer constants.
\end{proof}

\begin{definition}[Complete-fiber folding map]\label{def:structured-folding}
Let $D\subseteq\B$ be finite.  A polynomial map $\phi:D\to Q=\phi(D)$ is a $c$-fold complete-fiber folding map when every fiber has exactly $c$ points.  A support is complete at this scale when it is a union of full fibers.  Multiplicative power maps and the Chebyshev twin-coset foldings of the foundation \cite[Secs.~7 and 11]{CAP25v132} are the motivating examples.
\end{definition}

\section{Quotient--remainder prefix normal form}\label{sec:quotient-remainder-profiles}
The quotient-prefix floors and descent mechanisms of CAP25 v13.2 are imported from \cite[Secs.~3, 8, and 14]{CAP25v132}.  The normal forms and obstruction theorems below refine that package for the sequel's Q compiler.

The quotient and remainder variables can be separated exactly at the
locator-prefix level.  This removes a spurious factor coming from summing
over marked remainder sets, but it also exposes a genuine scaled quotient-
coefficient-field term which prevents an unrestricted comparison with the
identity profile.

\begin{definition}[Quotient/remainder profile and field drop]
\label{def:quotient-remainder-profile}
Let \(\phi:D\to Q\) be a \(c\)-fold complete-fiber folding map in the
sense of \cref{def:structured-folding}.  A
\emph{complete-fiber-plus-remainder support} is
\[
                  S=\phi^{-1}(E)\sqcup R,
\]
where \(E\subseteq Q\) and
\(R\subseteq D\setminus\phi^{-1}(E)\).  The set \(R\) is the
\emph{support remainder}: it records the selected points in fibers that
are not declared complete.  A \emph{quotient/remainder profile} fixes
\(\phi\), its degree \(c\), the size \(r=\abs R\), the relevant
coefficient field, and any planted remainder data, while \(E\) and the
unfixed part of \(R\) range subject to the displayed disjointness.
A fixed-\(R\) profile is the subprofile in which the remainder support
itself is part of the label.  The adjective \emph{Euclidean} used below
refers to separating the locator factor of degree \(r<c\) from the
composed quotient locator; it does not mean that an arbitrary support
remainder has size less than \(c\).

We call \(\B_\phi\subseteq\B\) a \emph{scaled quotient coefficient
field} when, for some \(\eta\in\B^\times\),
\[
                         Q=\phi(D)\subseteq\eta\B_\phi .
\]
When this field is recorded in a profile, it is taken minimal among the
subfields with this property.
Then the \(j\)-th elementary quotient coefficient lies in
\(\eta^j\B_\phi\).  A \emph{field drop} is the use of a proper such
subfield.  It is a \emph{positive-rate field drop} along a sequence when
\[
       1-\frac{\log\abs{\B_\phi}}{\log\abs\B}
\]
stays bounded away from zero and a positive-density number on the
entropy scale of quotient-prefix slots is live.  The payment saved in
each live slot is the factor \(\abs\B/\abs{\B_\phi}\); this is the term
quantified in \cref{prop:identity-quotient-comparison}.
\end{definition}

\begin{definition}[Balanced quotient core]
\label{def:balanced-quotient-core}
A \emph{split locator} is a monic squarefree polynomial all of whose roots
lie in the evaluation domain \(D\).
After common locator factors, fixed quotient data, and planted remainder
points have been removed, let \(A\) and \(B\) be two monic split
locators of the same degree \(e\).  They form a
\emph{depth-\(w\) balanced core} if they have the same first \(w\)
nonleading coefficients, equivalently
\[
                         \deg(A-B)\le e-w-1.
\]
It is a \emph{balanced quotient core} when the remaining locator factors
are pullbacks through the same folding map \(\phi\).  The word
\emph{balanced} records equality of degree and leading normalization;
the \emph{core} consists of the roots still allowed to move after common
and planted factors are removed.  If the resulting projective locator
family is one-dimensional it is a split pencil
\(Q_0+\lambda Q_1\); in higher dimension this definition supplies no
distinct-ray bound, and the separate ray compiler is required.
\end{definition}

For a monic polynomial
\[
 A(X)=X^d+a_1X^{d-1}+\cdots+a_d
\]
and an integer $0\le u\le d$, write
\(\operatorname{pref}_u(A)=(a_1,\ldots,a_u)\).  Equivalently, if
\(A^\vee(Z):=Z^dA(Z^{-1})\), then
\(\operatorname{pref}_u(A)\) is the coefficient vector of
\(A^\vee(Z)\bmod Z^{u+1}\), with its constant coefficient omitted.

\begin{theorem}[Exact quotient--remainder prefix normal form]
\label{thm:exact-quotient-remainder-normal-form}
Let $\B\subseteq\F$ be finite fields, let $D\subseteq\B$ have $n$
distinct elements, and let $\phi\in\B[X]$ be monic of degree $c\ge2$.
Assume that the restriction
\[
             \phi:D\longrightarrow Q:=\phi(D)
\]
has complete fibers of size $c$; in particular, $N:=|Q|=n/c$.
Fix integers $m,r$ with $0\le r<c$ and $cm+r\le n$.  For
\[
 E\in\binom Qm,
 \qquad
 R\in\binom{D\setminus\phi^{-1}(E)}r,
\]
put
\[
 \begin{split}
 V_E(Y)&:=\prod_{y\in E}(Y-y)
       =Y^m+\sum_{j=1}^m v_j(E)Y^{m-j},\\
 P_R(X)&:=\prod_{x\in R}(X-x)
       =X^r+\sum_{i=1}^r p_i(R)X^{r-i},\\
 L_{E,R}(X)&:=P_R(X)V_E(\phi(X)).
 \end{split}                                      \tag{QR1}\label{eq:qr-locators}
\]
Then $L_{E,R}$ is the monic locator of the support
\(\phi^{-1}(E)\sqcup R\), of degree $A=cm+r$.

Let $0\le w\le A$ and put $d=\lfloor w/c\rfloor$.

\begin{enumerate}[label=\textup{(\roman*)},leftmargin=*]
\item If $w\ge r$, every nonempty fiber of
      \((E,R)\mapsto\operatorname{pref}_w(L_{E,R})\) determines $R$
      uniquely and, after $R$ is recovered, is exactly one quotient-prefix
      fiber.  More precisely, for every prefix value $z$ there are unique
      data $R_z$ and $\eta_z\in\B^d$, whenever the fiber is nonempty, such
      that
      \[
      \begin{split}
       &\{(E,R):\operatorname{pref}_w(L_{E,R})=z\}\\
       &\quad=
       \{(E,R_z): E\in\tbinom{Q\setminus\phi(R_z)}m,
           \ \operatorname{pref}_d(V_E)=\eta_z\}.
      \end{split}                                  \tag{QR2}\label{eq:qr-fiber-exact}
      \]
      Thus no factor counting possible remainder sets occurs in a fixed
      global prefix fiber.

\item If $w<r$, then necessarily $w<c$, and the quotient set $E$ is
      invisible to the first $w$ coefficients.  There is a fixed
      unitriangular bijection $T_{\phi,m,w}:\B^w\to\B^w$ such that
      \[
          \operatorname{pref}_w(L_{E,R})
          =T_{\phi,m,w}(\operatorname{pref}_w(P_R))                 \tag{QR3}
      \]
      for every admissible $(E,R)$.  Consequently, with the convention
      \(\binom uv=0\) for $v>u$,
      \[
      \begin{split}
       &\#\{(E,R):\operatorname{pref}_w(L_{E,R})=z\}\\
       &\quad=
       \sum_{\substack{R\in\binom Dr\\
          \operatorname{pref}_w(P_R)=T_{\phi,m,w}^{-1}(z)}}
          \binom{N-|\phi(R)|}{m}.
      \end{split}                                  \tag{QR4}\label{eq:qr-shallow-remainder}
      \]
      Thus this case is a remainder-prefix problem, multiplied by the
      number of quotient sets still available after $R$ is fixed.
\end{enumerate}
\end{theorem}

\begin{proof}
For a monic degree-$e$ polynomial $A$, set
\(A^\vee(Z)=Z^eA(Z^{-1})\).  Also set
\[
       \Phi(Z):=Z^c\phi(Z^{-1})
       =1+\phi_1Z+\cdots+\phi_cZ^c.
\]
Taking reciprocal polynomials in \eqref{eq:qr-locators} gives the exact
formal-power-series identity
\[
 L_{E,R}^\vee(Z)=P_R^\vee(Z)
 \left(
   \Phi(Z)^m+
   \sum_{j=1}^m v_j(E)Z^{cj}\Phi(Z)^{m-j}
 \right).                                          \tag{QR5}\label{eq:qr-infinity}
\]
All factors on the right have constant coefficient one except for the
displayed scalar coefficients $v_j(E)$.

Suppose first that $w\ge r$.  Since $r<c$, no term containing a $v_j$
occurs below degree $c$.  For $1\le i\le r$, the coefficient of $Z^i$
on the right of \eqref{eq:qr-infinity} is
\(p_i(R)\) plus an expression depending only on
\(p_1(R),\ldots,p_{i-1}(R)\), on $m$, and on $\Phi$.  The first $r$
coefficients therefore recover $p_1(R),\ldots,p_r(R)$ successively.
They recover the monic polynomial $P_R$, hence its root set $R$, uniquely.

We may now divide \(L_{E,R}^\vee\) by the unit
\(P_R^\vee\) modulo $Z^{w+1}$.  In the remaining factor of
\eqref{eq:qr-infinity}, the coefficient of $Z^{cj}$ is
\(v_j(E)\) plus an expression depending only on
\(v_1(E),\ldots,v_{j-1}(E)\), on $m$, and on $\Phi$.  Hence the
coefficients at degrees $c,2c,\ldots,dc$ recover
\(v_1(E),\ldots,v_d(E)\) successively.  Conversely, $P_R$ and these $d$
coefficients determine the right side of \eqref{eq:qr-infinity} modulo
$Z^{w+1}$, because every term containing $v_j$ with $j>d$ starts in degree
$cj>w$.  This proves \eqref{eq:qr-fiber-exact}; admissibility of $E$ is
exactly the condition $E\cap\phi(R)=\varnothing$.

If $w<r<c$, every term involving a $v_j$ starts in degree at least
$c>w$, so modulo $Z^{w+1}$ the bracket in \eqref{eq:qr-infinity} is the
fixed unit $\Phi(Z)^m$.  Multiplication by this unit sends the first $w$
coefficients of $P_R^\vee$ to the first $w$ coefficients of
$L_{E,R}^\vee$ by a unitriangular transformation.  It is independent of
$E$ and invertible.  For a fixed $R$, the admissible $E$ are precisely the
$m$-subsets of $Q\setminus\phi(R)$, of which there are
\(\binom{N-|\phi(R)|}{m}\).  Summing over the indicated remainder-prefix
fiber proves \eqref{eq:qr-shallow-remainder}.
\end{proof}

\begin{proposition}[Complete support factorization and its limitation]
\label{prop:complete-support-factorization}
Under the complete-fiber hypotheses of
\cref{thm:exact-quotient-remainder-normal-form}, every support
\(S\subseteq D\) has the unique decomposition
\[
 E(S)=\{y\in Q:\phi^{-1}(y)\subseteq S\},\qquad
 R(S)=S\setminus\phi^{-1}(E(S)),
 \tag{QR5a}\label{eq:complete-support-factorization}
\]
and
\(Q_S(X)=P_{R(S)}(X)V_{E(S)}(\phi(X))\).  The remainder meets every
nonfull \(\phi\)-fiber in at most \(c-1\) points, but its total size may
be \(\Theta(n)\).  The reciprocal identity \eqref{eq:qr-infinity} remains
valid for this arbitrary remainder.  When \(\abs{R(S)}\ge c\), however,
the quotient coefficients and the remainder coefficients begin to
interlace at degree \(c\), so the triangular recovery theorem above does
not give a comparison without an additional partial-occupancy atlas.
\end{proposition}

\begin{proof}
A fiber is put into \(E(S)\) exactly when all of its points lie in \(S\);
all other selected points form \(R(S)\).  This proves existence,
disjointness, the occupancy bound, and uniqueness.  Multiplying the
corresponding linear factors gives the locator identity.  The reciprocal
calculation used for \eqref{eq:qr-infinity} is purely multiplicative and
does not require \(\deg P_R<c\).  If \(\deg P_R\ge c\), both
\(p_c(R)\) and \(v_1(E)\) occur in degree \(c\), which proves the stated
limitation of the triangular separation.
\end{proof}

\begin{theorem}[Exact partial-occupancy disintegration]
\label{thm:exact-partial-occupancy}
Let \(D=D_0\sqcup X\), where \(\abs X=b\), and let
\(\phi:D_0\twoheadrightarrow Q\) have exactly \(N=\abs Q\) fibers, each
of cardinality \(c\).  For \(S\subseteq D\), put
\[
 X_S=S\cap X,\qquad
 E(S)=\{y\in Q:\phi^{-1}(y)\subseteq S\},\qquad
 R(S)=(S\cap D_0)\setminus\phi^{-1}(E(S)).
\]
Write
\[
 t=\abs{X_S},\qquad m=\abs{E(S)},\qquad
 p=\abs{\phi(R(S))},\qquad r=\abs{R(S)}.
\]
Then this datum is unique, every fiber meeting \(R(S)\) contains between
one and \(c-1\) points of \(R(S)\), and \(\abs S=t+cm+r\).  If
\(\Omega_{t,m,p,r}\) denotes the family of supports with these four
parameters, then
\[
 \abs{\Omega_{t,m,p,r}}
 =\binom bt\binom Np\binom{N-p}m
   [x^r]\bigl((1+x)^c-1-x^c\bigr)^p.                 \tag{PO1}
\]
Consequently the nonempty families \(\Omega_{t,m,p,r}\) partition
\(\binom Da\), and their exact add-back is
\[
 \sum_{\substack{t,m,p,r\\t+cm+r=a}}\abs{\Omega_{t,m,p,r}}
 =\binom{cN+b}{a}.                                   \tag{PO2}
\]
If \(\phi\) is the restriction of a monic degree-\(c\) polynomial and
every fiber \(\phi^{-1}(y)\) is the complete simple root set in \(D_0\)
of \(\phi(X)-y\), then their locators satisfy
\[
             Q_S=Q_{X_S}P_{R(S)}V_{E(S)}(\phi).
\]
\end{theorem}

\begin{proof}
Full fibers, partial fibers, and empty fibers are mutually exclusive, so
the displayed decomposition is canonical.  Choose the \(t\) exceptional
points, the \(p\) partial fibers, and the \(m\) full fibers in
\(\binom bt\binom Np\binom{N-p}m\) ways.  On one partial fiber the
weight enumerator of the allowed nonempty proper subsets is
\((1+x)^c-1-x^c\); hence the coefficient in \textup{(PO1)} counts the
choices having total partial weight \(r\).  Summing \textup{(PO1)} and
extracting the coefficient of \(x^a\) gives
\[
 [x^a](1+x)^b
 \left(1+x^c+\bigl((1+x)^c-1-x^c\bigr)\right)^N
 =[x^a](1+x)^{b+cN}=\binom{b+cN}{a}.
\]
Multiplying the linear factors belonging to the three disjoint parts of
the support proves the locator identity.
\end{proof}

\begin{proposition}[Partial-occupancy Fourier factorization]
\label{prop:partial-occupancy-fourier}
In the setting of \cref{thm:exact-partial-occupancy}, let \(G\) be a
finite abelian group, let \(g:D\to G\), and put
\(\Phi(S)=\sum_{x\in S}g(x)\).  For a character
\(\chi\in\widehat G\) and a regular fiber \(F_y=\phi^{-1}(y)\), define
\[
 A_y(\chi)=\prod_{x\in F_y}\chi(g(x)),\qquad
 P_y(\chi;z)=
 \prod_{x\in F_y}\bigl(1+z\chi(g(x))\bigr)-1-z^cA_y(\chi).
\]
Then
\[
 \sum_{S\in\Omega_{t,m,p,r}}\chi(\Phi(S))
 =[u^tv^m\zeta^pz^r]
 \prod_{x\in X}\bigl(1+u\chi(g(x))\bigr)
 \prod_{y\in Q}
 \bigl(1+vA_y(\chi)+\zeta P_y(\chi;z)\bigr).          \tag{PO3}
\]
Consequently, for every \(s\in G\),
\[
 \abs{\{S\in\Omega_{t,m,p,r}:\Phi(S)=s\}}
 =\frac1{\abs G}\sum_{\chi\in\widehat G}
   \overline{\chi(s)}
   \sum_{S\in\Omega_{t,m,p,r}}\chi(\Phi(S)).         \tag{PO4}
\]
At the trivial character, \textup{(PO3)} is exactly the support count
\textup{(PO1)}.  Thus support add-back is unconditional, while a finite
flatness theorem is exactly a bound for the nontrivial-character sum in
\textup{(PO4)}.
\end{proposition}

\begin{proof}
For a fixed regular fiber the three terms in the second product encode,
respectively, an empty fiber, a full fiber, and a nonempty proper subset.
The variables \(v,\zeta,z\) record the numbers \(m,p,r\), while \(u\)
records the exceptional weight \(t\).  Multiplicativity of \(\chi\) turns
the character of the support sum into the product of its selected-point
characters, proving \textup{(PO3)} by coefficient extraction.
Formula \textup{(PO4)} is character orthogonality on \(G\).
\end{proof}

\begin{remark}[Effective normalization of a partial-occupancy slice]
Fix a nonempty slice \(\Omega_\lambda=\Omega_{t,m,p,r}\), choose
\(S_0\in\Omega_\lambda\), and let
\[
 G_\lambda=
 \left\langle\Phi(S)-\Phi(S_0):S\in\Omega_\lambda\right\rangle
 \le G.
\]
The attained boundary values lie in the affine coset
\(\Phi(S_0)+G_\lambda\), and the effective inversion is
\[
 \abs{\{S\in\Omega_\lambda:\Phi(S)=s\}}
 =\frac1{\abs{G_\lambda}}
   \sum_{\chi\in\widehat{G_\lambda}}
   \overline{\chi(s-\Phi(S_0))}
   \sum_{S\in\Omega_\lambda}
      \chi(\Phi(S)-\Phi(S_0)).                       \tag{PO5}
\]
Every character of \(G_\lambda\) extends to the ambient finite abelian
group, so the inner sum may be evaluated from \textup{(PO3)} after
multiplication by the fixed factor
\(\overline{\chi(\Phi(S_0))}\).  Different extensions agree on support
differences.  Equivalently, ambient characters group by their restriction
to \(G_\lambda\), and the annihilator multiplicity cancels exactly against
the ambient denominator.  This identifies the correct Fourier denominator;
it does not assert that the realized image fills the affine group.
\end{remark}

\begin{remark}[What partial-occupancy add-back does and does not prove]
The exponentially many local proper-subset choices are already contained
inside the coarse slices \(\Omega_{t,m,p,r}\); they incur no separate
profile-count loss in \textup{(PO2)}.  The theorem does not bound the
nontrivial Fourier terms in \textup{(PO4)}, the size of a realized
boundary image, or the projection of a witness cell to distinct slopes.
Those are separate analytic and ray payments.
\end{remark}

\begin{theorem}[Canonical partial-occupancy atlas and bounded-boundary closure]
\label{thm:canonical-partial-occupancy-atlas}
Fix a received line and exact agreement \(a\).  For every nonempty
canonical slice \(\Omega_\lambda=\Omega_{t,m,p,r}\) of
\cref{thm:exact-partial-occupancy}, let \(\Ccal_\lambda\) be the witnesses
whose support lies in \(\Omega_\lambda\), and order these cells
arbitrarily.  Then they form a witness-exhaustive first-match atlas and,
with \(Z_\lambda^\circ\) its first-match slope projections,
\[
 \abs{Z_\lambda^\circ}\le\abs{\Omega_\lambda},
 \qquad
 \sum_\lambda\abs{Z_\lambda^\circ}
 \le\sum_\lambda\abs{\Omega_\lambda}=\binom na.    \tag{PO6}
\]

More generally, give each slice a boundary map
\(\Phi_\lambda:\Omega_\lambda\to G_\lambda^{\rm amb}\) into a finite
abelian group of order \(A_\lambda\), let \(N_\lambda\) be its
active-coordinate count, let \(L_\lambda\) be its realized image size,
and put
\(\bar N_\lambda=\abs{\Omega_\lambda}/L_\lambda\).  The exact finite ray
multiplier and challenge-set bound are
\[
             \abs{Z_\lambda^\circ}
             \le L_\lambda\bar N_\lambda.          \tag{PO7}
\]
\[
 B_{C,\Gamma}^{\rm MCA}(a)
 \le\min\left\{\abs\Gamma,\
       \sup_r\sum_{\lambda\in\Lambda(r;a)}
              L_\lambda\bar N_\lambda\right\}
 \le\min\left\{\abs\Gamma,\binom na\right\}.        \tag{PO7a}
\]
Define the coarse partial-occupancy envelope
\[
 \mathfrak E_n^{\rm PO}(a)
 =1+\sup_r\sum_{\lambda\in\Lambda(r;a)}(1+\bar N_\lambda).
\]
If, uniformly over received lines and the polynomially many nonempty
canonical slices,
\[
                         \log A_\lambda=o(n),       \tag{PO8}
\]
then this atlas has a closed asymptotic profile-envelope compiler:
\[
 B_{C}^{\rm MCA}(a)\le
 e^{o(n)}\mathfrak E_n^{\rm PO}(a).                \tag{PO9}
\]
Condition \textup{(PO8)} discharges atlas exhaustivity, support add-back,
and the direct alternative in \textup{(RC)}, whose exact multiplier is
\(L_\lambda\le A_\lambda\).  If, in addition,
\[
                         \log A_\lambda=o(N_\lambda) \tag{PO10}
\]
on every slice to which effective Fourier terminology is applied, then
the effective inversion \textup{(PO5)} may designate every nontrivial
effective character major: its minor sum is empty and its exact major
multiplier is at most \(A_\lambda-1\).  Thus \textup{(PO10)} verifies the
slice analogues of MI and MA rather than assuming them.  A concrete
specialization is a polynomial-size coefficient field with uniformly
bounded boundary depth and \(N_\lambda=\Theta(n)\) on every live canonical
folding profile.  This is a coarse support-paid envelope, not an
identity-scale or refined quotient-envelope comparison.  It gives a safe
target whenever the literal right side of \textup{(PO7a)} is at most
\(B^*\); a sharp frontier additionally uses the unsafe inequality in
\textup{(SB2)}.  Condition \textup{(PO8)} alone does not locate a target
frontier.
\end{theorem}

\begin{proof}
The support slices partition \(\binom Da\) by \textup{(PO2)}, hence the
corresponding witness cells partition the exact witness incidence.  For
each first-match slope choose one witness support in its cell.  A fixed
noncommon support carries at most one slope, so this choice is injective
and proves the first inequality in \textup{(PO6)}.  Exact add-back gives
the equality there, and \textup{(PO7)} is the same inequality rewritten
using \(\abs{\Omega_\lambda}=L_\lambda\bar N_\lambda\).

The exact challenge bound follows by summing \textup{(PO7)}, taking the
maximum over received lines, and using \textup{(PO2)}.  Since
\(L_\lambda\le A_\lambda\), condition \textup{(PO8)} turns
\textup{(PO7)} into
\(e^{o(n)}\bar N_\lambda\).  There are only polynomially many quadruples
\((t,m,p,r)\), so their sum proves \textup{(PO9)}.  If
\(A_\lambda\le\abs\B^{R_\lambda}\), a polynomial-size \(\B\) and
bounded \(R_\lambda\) imply \textup{(PO8)}.  Finally, the effective
difference group in \textup{(PO5)} has at most \(A_\lambda\) characters.
Under \textup{(PO10)}, designating all of its nontrivial characters major
makes the minor sum empty and bounds the normalized major aggregate by
\(A_\lambda-1=e^{o(N_\lambda)}\).
\end{proof}

\begin{remark}[Exact dimension rounding]
\label{rem:qr-rounding}
If the global locator degree is $A=cm+r$, the list-code dimension is $K$,
and $w=A-K$, then the quotient depth in
\cref{thm:exact-quotient-remainder-normal-form} is
\[
 d=\left\lfloor\frac{A-K}{c}\right\rfloor
   =m-\left\lceil\frac{K-r}{c}\right\rceil.         \tag{QR5b}\label{eq:qr-rounding}
\]
Thus the descended list dimension is exactly
\(K_c=\lceil(K-r)/c\rceil\).  More explicitly, if \(w=cu+s\) with
\(0\le s<c\), then
\[
 \abs{\B_\phi}^{-\floor{w/c}}
 =\abs{\B_\phi}^{s/c}\abs{\B_\phi}^{-w/c}.          \tag{QR5c}
\]
Thus the exact rounding multiplier is \(\abs{\B_\phi}^{s/c}\), lying
between one and \(\abs{\B_\phi}^{(c-1)/c}\).  Retaining the integer
\(\floor{w/c}\) avoids even this comparison; no polynomial or
\(e^{o(n)}\) placeholder is needed in a finite certificate.
\end{remark}

\begin{remark}[Nonmonic maps and Chebyshev maps]
\label{rem:qr-chebyshev}
If the leading coefficient of $\phi$ is $b\ne0$, replace $\phi$ by
$b^{-1}\phi$ and $Q$ by $b^{-1}Q$.  This changes quotient coefficients by
fixed nonzero scalar factors and leaves every support and every fiber
cardinality unchanged.  The theorem therefore applies to the Chebyshev
folding map $T_c$ after this normalization.  On a circle twin-coset domain
on which $T_c$ has complete fibers of size $c$, it gives the same statement
verbatim.  The fixed or ramified endpoints form an exceptional set \(X\)
of cardinality \(b\) and are included exactly by the factor \(\binom bt\)
in \textup{(PO1)}; the crude total exceptional-point multiplier is at most
\(2^b\), with \(b\le2\) for involution-fixed endpoints.  Coincident twin
cosets are not a bounded planted set: they form the separate dihedral
collapse profile of the circle edge-case audit imported from \cite[Sec.~11]{CAP25v132}.
\end{remark}

For a declared complete-fiber-plus-Euclidean-remainder profile, the exact
normal-form theorem separates algebraic bookkeeping from prefix
equidistribution only when the remainder degree is less than \(c\).  The
exact disintegration of \cref{thm:exact-partial-occupancy} exhausts
arbitrary partial-occupancy supports, but when \(\deg P_R\ge c\) the
quotient and remainder coefficients interlace.  Thus that disintegration
does not by itself prove prefix flatness on the resulting coarse slices.
Let
$\B_\phi\subseteq\B$ be a subfield and suppose
\(Q\subseteq\eta\B_\phi\) for some $\eta\in\B^\times$.  Then
\(v_j(E)\in\eta^j\B_\phi\).  Hence, in case
\textup{(i)}, the natural average scale of the quotient-prefix fiber with
fixed $R$ is
\[
 \overline N_{\phi,R}(w)
 :=\binom{N-|\phi(R)|}{m}
       |\B_\phi|^{-\lfloor w/c\rfloor}.             \tag{QR6}\label{eq:qr-natural-scale}
\]
Pigeonholing proves a fiber of size at least
\(\lceil\overline N_{\phi,R}(w)\rceil\).  An upper bound of the same order
is not a consequence of the normal form: it is precisely the uniform
prefix-flatness, or Sidon/Fourier, input on the quotient row.

\begin{proposition}[Identity--quotient exponent comparison]
\label{prop:identity-quotient-comparison}
Consider a sequence to which
\cref{thm:exact-quotient-remainder-normal-form} applies with fixed
$c\ge2$ and fixed $0\le r<c$.  Suppose
\[
 \frac an\longrightarrow\alpha\in(0,1),\qquad
 \log|\B|=o(n),\qquad
 \log\binom na-w\log|\B|=o(n),                     \tag{QR7}\label{eq:identity-crossing-qr}
\]
where $a=cm+r$, and suppose
\(Q\subseteq\eta\B_c\) for a subfield $\B_c\subseteq\B$.
Write \(\overline N_{c,r}(w)=\overline N_{\phi,R}(w)\) for the natural
scale in \eqref{eq:qr-natural-scale}, with this fixed remainder profile.
Then $w\to\infty$, so $w\ge r$ eventually, and
\[
 \log\overline N_{c,r}(w)
 =\frac1c\log\!\left(\binom na|\B|^{-w}\right)
  +\frac wc\log\frac{|\B|}{|\B_c|}+o(n),           \tag{QR8}\label{eq:qr-comparison-general}
\]
where replacing $N-|\phi(R)|$ by $N$ changes only the $o(n)$ term.
Equivalently, if
\(\lambda_c=\log|\B_c|/\log|\B|\) has a limit, then at the identity
crossing
\[
       \frac1n\log\overline N_{c,r}(w)
       =\frac{h(\alpha)}c(1-\lambda_c)+o(1),         \tag{QR9}\label{eq:qr-comparison-crossing}
\]
using the entropy convention fixed in the Introduction.
Thus the natural average scale of this bounded-degree quotient profile is
comparable with the identity scale at exponential accuracy exactly when
\(\log|\B_c|/\log|\B|=1-o(1)\).  A proper field drop of fixed relative
degree produces a positive exponential quotient term.
\end{proposition}

\begin{proof}
Stirling's formula, $a/n\to\alpha$, and fixed $c,r$ give
\[
 \log\binom{n/c+O(1)}{(a-r)/c}
 =\frac1c\log\binom na+o(n).
\]
Also
\(\lfloor w/c\rfloor\log|\B_c|
=(w/c)\log|\B_c|+o(n)\), because the rounding error is at most
\(\log|\B_c|\le\log|\B|=o(n)\).  This proves
\eqref{eq:qr-comparison-general}.  Since
\(\log\binom na=nh(\alpha)+o(n)\),
\eqref{eq:identity-crossing-qr} gives
\(w\log|\B|=nh(\alpha)+o(n)\).  In particular $w\to\infty$ because
\(\log|\B|=o(n)\).  Substitution in
\eqref{eq:qr-comparison-general} proves
\eqref{eq:qr-comparison-crossing}.
\end{proof}

\begin{remark}[Unbounded quotient degrees]
If $c=c_n\to\infty$, the complete-fiber choice contributes at most
\(2^{n/c}=e^{o(n)}\).  When $w\ge r$, the remainder is recovered exactly
and no further remainder multiplicity occurs.  When $w<r<c$, the exact
formula \eqref{eq:qr-shallow-remainder} reduces the profile to an ordinary
prefix problem for the remainder support, multiplied by $e^{o(n)}$
quotient choices.  Thus only bounded quotient degrees can create a new
positive-rate field-drop term; large degrees either cost $e^{o(n)}$ or
return to an identity/remainder prefix problem.  This does not prove
flatness of the remaining prefix problem.
\end{remark}


\section{Effective-image Fourier normalization}\label{sec:partial-occupancy}
There is, however, an exact normalization that must be performed before
declaring any character major.  Assume \(1\le m\le\abs T-1\), as on every
fixed-density primitive leaf, put \(p=\operatorname{char}\B\), and fix
\(S_0\in\binom Tm\) and \(t_0\in T\).
Then
\[
 \Span_{\F_p}\{\Psi(S)-\Psi(S_0):S\in\tbinom Tm\}
 =\Span_{\F_p}\{g(t)-g(t_0):t\in T\}.               \tag{EF0}
\]
Define the \emph{effective Fourier span}
\[
 V_g=\Span_{\F_p}\{g(t)-g(t_0):t\in T\}\subseteq\B^R,
 \qquad A_{\rm eff}=\abs{V_g}.
 \tag{EF1}\label{eq:effective-fourier-span}
\]
The fixed-weight sum map takes values in the affine space
\(m g(t_0)+V_g\).  Thus Fourier inversion belongs on the additive group
\(V_g\), not automatically on the ambient group \(\B^R\).

\begin{lemma}[Effective-span Fourier inversion]
\label{lem:effective-span-fourier}
For \(z\in V_g\), let
\[
 N_g(z)=\abs{\left\{S\in\binom Tm:
       \sum_{t\in S}g(t)=m g(t_0)+z\right\}}.
\]
Then
\[
 N_g(z)=\frac1{A_{\rm eff}}
 \sum_{\chi\in\widehat{V_g}}\overline{\chi(z)}
 e_m\bigl(\chi(g(t)-g(t_0)):t\in T\bigr).           \tag{EF2}
\]
In particular,
\[
 \max_zN_g(z)\le\frac1{A_{\rm eff}}
 \left(\binom{\abs T}m+
 \sum_{1\ne\chi\in\widehat{V_g}}
 \left|e_m\bigl(\chi(g(t)-g(t_0)):t\in T\bigr)\right|\right). \tag{EF3}
\]
Every character of \(V_g\) extends to a trace character of \(\B^R\),
and a nontrivial effective character is not constant on all the generators
\(g(t)-g(t_0)\).  Ambient characters that are trivial on \(V_g\) occur
with multiplicity \(\abs{\B}^R/A_{\rm eff}\), which cancels exactly
against the ambient Fourier normalization.
\end{lemma}

\begin{proof}
The inclusion from left to right in \textup{(EF0)} follows by expanding a
difference of two support sums.  Conversely, for distinct \(t,u\in T\),
choose an \((m-1)\)-set \(A\subseteq T\setminus\{t,u\}\); such a set
exists because \(1\le m\le\abs T-1\).  Then
\(\Psi(A\cup\{t\})-\Psi(A\cup\{u\})=g(t)-g(u)\), so the two spans agree.
The first formula is character orthogonality on the finite additive group
\(V_g\), applied after translating by \(m g(t_0)\); the second follows by
the triangle inequality.  The trace pairing on the \(\F_p\)-space
\(\B^R\) is nondegenerate, so every character of its subspace \(V_g\)
extends to the ambient space.  A character trivial on each displayed
generator is trivial on their span.  Finally, the annihilator
\(V_g^\perp\) has size \(\abs{\B}^R/A_{\rm eff}\); grouping ambient
characters by their restriction to \(V_g\) proves the cancellation claim.
\end{proof}

\begin{definition}[Certified effective major/minor partition]
\label{def:effective-major-minor}
Let
\(\operatorname{res}:\widehat{\B^R}\twoheadrightarrow\widehat{V_g}\)
be restriction.  A \emph{certified effective Fourier partition} is a
disjoint union
\[
 \widehat{V_g}\setminus\{1\}
 =\mathfrak m_{\rm eff}\sqcup\mathfrak M_{\rm eff}
\]
such that every \(\chi\in\mathfrak m_{\rm eff}\) is supplied with an
ambient lift whose rational phase satisfies the character-sum hypotheses
used to pay it.  Characters without such a certified lift may be placed in
\(\mathfrak M_{\rm eff}\), but their aggregate must then be paid by
\textup{(MA)}.  This designation is data of the chart; it is not a
property of an unspecified ambient lift.
\end{definition}

\begin{definition}[Effective Fourier payment]
\label{def:effective-fourier-payment}
The full slice has an \emph{effective Fourier payment with constant
\(\kappa\ge1\)} if
\[
 \sum_{1\ne\chi\in\widehat{V_g}}
 \left|e_m\bigl(\chi(g(t)-g(t_0)):t\in T\bigr)\right|
 \le (\kappa-1)\binom{\abs T}m.                    \tag{EFP}
\]
By \cref{lem:effective-span-fourier}, this implies the exact max-fiber
bound
\[
               \max_zN_g(z)\le
               \kappa\binom{\abs T}m/A_{\rm eff}. \tag{EF4}
\]
It also implies that the realized image contains at least
\(A_{\rm eff}/\kappa\) points.  The ambient instances of \textup{(PF)}
and \textup{(MA)} are one sufficient way to prove \textup{(EFP)}, but
\textup{(EFP)} is phase-dependent and does not pay an ambient annihilator
twice.
\end{definition}

\begin{proof}[Proof of the image-size assertion]
The fibers sum to \(\binom{\abs T}m\), and each nonempty fiber is at most
\(\kappa\binom{\abs T}m/A_{\rm eff}\) by \textup{(EF4)}.
Hence at least \(A_{\rm eff}/\kappa\) fibers are nonempty.
\end{proof}

\begin{lemma}[Constant and Artin--Schreier modes are annihilator modes]
\label{lem:constant-modes-annihilator}
Suppose an ambient trace character has phase constant on \(T\).  Then its
restriction to \(V_g\) is trivial.  In particular, if an ambient rational
phase is Artin--Schreier of the form \(G^p-G+c\) and \(G\) is defined at
the \(\B\)-rational points of \(T\), then its character is an annihilator
mode and disappears from the nontrivial sum in \textup{(EF2)}.
\end{lemma}

\begin{proof}
The quotient of the character values at \(g(t)\) and \(g(t_0)\) is one
for every \(t\), so the character is trivial on the generators of
\(V_g\).  For an Artin--Schreier phase,
\(\Tr_{\B/\F_p}(G(t)^p-G(t))=0\), hence its additive-character value is
constant on all points where it is defined.
\end{proof}

\begin{remark}[Effective normalization does not prove the remaining aggregate]
The effective-span reduction removes exactly the constant annihilator
multiplicity.  A nonconstant character may still factor through a quotient
map or have a phase-dependent estimate too weak for \textup{(EFP)}.  Such
modes require a recursive quotient estimate, the aggregate
\textup{(MA)}, or a direct full-slice bound.  Thus effective normalization
repairs the Fourier denominator but is not a proof of unrestricted deep-prefix
flatness.
\end{remark}

\begin{definition}[Major-character aggregate]
\label{def:major-arc-aggregate}
Let \(A_*\) be the additive target on which Fourier inversion is being
performed, let \(h:T\to A_*\), and let
\(\mathfrak M_*\subseteq\widehat{A_*}\setminus\{1\}\) be the designated
major characters.  The chart satisfies \textup{(MA)} on \(A_*\) if
\[
 \tag{MA}\label{eq:major-arc-aggregate}
 \sum_{\chi\in\mathfrak M_*}
 \left|e_m\bigl(\chi(h(t)):t\in T\bigr)\right|
 \le e^{o(\abs T)}\binom{\abs T}m .
\]
Unless the ambient target is explicitly named, \(A_*=V_g\) and
\(h(t)=g(t)-g(t_0)\).  For the ambient target \(A_*=\B^R\), the same
condition is equivalently
\[
 \abs\B^{-R}\sum_{\alpha\in\mathfrak M_{\rm amb}}
 \left|e_m\bigl(\psi(\alpha\cdot g(t)):t\in T\bigr)\right|
 \le e^{o(\abs T)}\barN_0.
\]
The condition is vacuous when the designated major set is empty.  It can
be proved by a recursive quotient census or replaced by a direct
full-slice max-fiber bound; first-match terminology alone does not imply
it.
\end{definition}

\begin{lemma}[Sparse effective major set]
\label{lem:sparse-major-payment}
On the effective group \(V_g\), let \(\mathfrak M_{\rm eff}\) be any set
of nontrivial characters designated major.  Its exact normalized Fourier
loss is at most \(\abs{\mathfrak M_{\rm eff}}\).  Consequently
\(\abs{\mathfrak M_{\rm eff}}=e^{o(\abs T)}\) proves the effective form
of \textup{(MA)}; for a finite row, the literal cardinality is a valid
major-character constant.
\end{lemma}

\begin{proof}
Every fixed-weight Fourier coefficient is a sum of \(\binom{\abs T}m\)
complex numbers of modulus one, and hence has absolute value at most that
binomial coefficient.  Sum this bound over the designated set.
\end{proof}

\begin{theorem}[Exact low-boundary-entropy closure]
\label{thm:small-effective-dual-closure}
Let \(\Omega=\binom Tm\), let \(W\) be a finite additive
\(\F_p\)-space, and let \(\Psi:\Omega\to W\) be a fixed-weight additive
boundary map.  Fix \(S_0\in\Omega\), put \(z_0=\Psi(S_0)\), and define
the effective difference span
\[
 V=\Span_{\F_p}\{\Psi(S)-\Psi(S_0):S\in\Omega\}\subseteq W.
\]
Then \(\Psi(\Omega)\subseteq z_0+V\).  Put
\[
       A=\abs V,\qquad L=\abs{\Psi(\Omega)},
       \qquad M=\binom{\abs T}m,\qquad \bar N=M/L.
\]
Designate every nontrivial character of \(V\) as major and no character
as minor.  Then the literal finite-row constants are
\[
 C_{\rm min}=0,\qquad C_{\rm maj}\le A-1,\qquad
 \max_z\abs{\Psi^{-1}(z)}\le L\bar N=M.            \tag{SE1}
\]
For every exact-agreement witness cell whose support projection is
contained in \(\Omega\), its first-match slope set satisfies
\[
                         \abs Z\le L\bar N=M.       \tag{SE2}
\]
Consequently, if \(\log A=o(\abs T)\), effective \textup{(MI)},
effective \textup{(MA)}, image-normalized Q, and the direct alternative
in \textup{(RC)} all hold with subexponential loss.  Taking the
support-restricted incidence over \(\Omega\) as one ordered cell is
exhaustive for that restricted incidence; it is exhaustive for the whole
exact-agreement incidence when \(\Omega=\binom Da\), or after an
exhaustive partition into such slices.  For a locator prefix with
\(\abs T=\Theta(n)\), the concrete condition
\((a-k-1)\log\abs\B=o(n)\) implies this hypothesis because
\(A\le\abs\B^{a-k-1}\).
\end{theorem}

\begin{proof}
Fourier inversion is performed on the effective group \(V\).  The minor
sum is empty.  Every fixed-weight Fourier coefficient has
modulus at most \(M\), so the normalized major loss is at most \(A-1\).
The max-fiber estimate in \textup{(SE1)} is the trivial bound by the whole
support slice, written as the exact image-normalized multiplier \(L\).
By exact-agreement reduction, every bad slope in the cell has a noncommon
\(m\)-support, and a fixed noncommon support carries at most one slope.
Choosing one support for each slope is therefore injective and proves
\textup{(SE2)}.  Since \(L\le A\), all three finite multipliers
\(A-1,L,L\) are \(e^{o(\abs T)}\) when \(\log A=o(\abs T)\).
The one-cell atlas is exhaustive for its support-restricted incidence by
construction; the stated whole-incidence alternatives give global
exhaustivity.  If it is refined by a partial-occupancy partition,
\textup{(PO1)}--\textup{(PO2)} add the same support set back exactly and
do not change the conclusion.
\end{proof}

\begin{definition}[Aggregate minor payment]
\label{def:aggregate-minor-payment}
After effective-span normalization, let \(\mathfrak m_{\rm eff}\) be the
nontrivial characters not designated major.  The chart satisfies
\textup{(MI)} if
\[
 \sum_{\chi\in\mathfrak m_{\rm eff}}
 \left|e_m\bigl(\chi(g(t)-g(t_0)):t\in T\bigr)\right|
 \le e^{o(\abs T)}\binom{\abs T}m.                 \tag{MI}
\]
For a finite row the corresponding exact loss is this sum divided by
\(\binom{\abs T}m\).  The pointwise condition \textup{(PF)} is only one
sufficient way to prove \textup{(MI)}; phase-dependent estimates may be
strictly stronger.
\end{definition}

\begin{proposition}[Effective MI plus MA]
\label{prop:effective-mi-ma-flatness}
Partition the nontrivial effective characters as
\(\widehat{V_g}\setminus\{1\}
=\mathfrak m_{\rm eff}\sqcup\mathfrak M_{\rm eff}\).  Suppose
\textup{(MI)} and the effective form of \textup{(MA)} in
\cref{def:major-arc-aggregate} hold.
Then the full slice and every first-match residual satisfy
\[
 \max_z\abs{\{S:\Psi(S)=z\}}
 \le e^{o(\abs T)}\binom{\abs T}m/A_{\rm eff}.     \tag{EF5}
\]
The realized image has size at least
\(e^{-o(\abs T)}A_{\rm eff}\), so the same assertion holds at image
normalization.  For a finite row the exact multiplier is
\[
 1+\binom{\abs T}m^{-1}
 \sum_{1\ne\chi\in\widehat{V_g}}
 \left|e_m\bigl(\chi(g(t)-g(t_0)):t\in T\bigr)\right|.
 \tag{EF6}
\]
\end{proposition}

\begin{proof}
Add the minor and major sums and apply
\cref{lem:effective-span-fourier,def:effective-fourier-payment}.  A
first-match residual only deletes supports from a full-slice fiber.
\end{proof}

\begin{corollary}[Exact finite minor and major constants]
\label{cor:exact-finite-fourier-constants}
Put \(M=\binom{\abs T}m\) and, for an arbitrary partition of the
nontrivial effective dual, define
\[
 C_{\rm min}=M^{-1}\sum_{\chi\in\mathfrak m_{\rm eff}}\abs{E_m(\chi)},
 \qquad
 C_{\rm maj}=M^{-1}\sum_{\chi\in\mathfrak M_{\rm eff}}\abs{E_m(\chi)},
\]
where
\(E_m(\chi)=e_m(\chi(g(t)-g(t_0)):t\in T)\).  Then
\[
              \max_zN_g(z)\le
              \frac{M}{A_{\rm eff}}
              (1+C_{\rm min}+C_{\rm maj}).          \tag{EF7}
\]
If every minor character has power sums bounded by \(\Lambda\) through
order \(m\), then
\[
 C_{\rm min}\le
 \frac{\abs{\mathfrak m_{\rm eff}}}{M}
 \binom{\ceil\Lambda+m-1}{m}.                      \tag{EF8}
\]
Thus \textup{(EF7)}, with the two actual finite sums, records every finite
Fourier loss in an adjacent-row certificate exactly.
\end{corollary}

\begin{proof}
Formula \textup{(EF7)} is \textup{(EF3)} after splitting the nontrivial
characters.  The cycle-index coefficient bound gives
\(\abs{E_m(\chi)}\le\binom{\ceil\Lambda+m-1}{m}\), proving
\textup{(EF8)}.
\end{proof}

\begin{definition}[Pointwise minor-arc range]\label{def:prefix-flat-range}
A primitive weighted prefix chart satisfies the pointwise minor-arc range if the characteristic is larger than \(m\), every certified minor lift has a rational phase of total pole-degree at most \(\Delta_{\rm pole}\) and satisfies the nondegeneracy hypotheses of \cref{prop:weighted-weil-minor-arcs}, and, with
\[
        \Lambda=C_0(\Delta_{\rm pole}+1)\sqrt{\abs\B}+\abs P
\]
for the absolute Weil constant \(C_0\) and planted exceptional set \(P\), one has
\[
        \tag{PF}
        R\log\abs\B+
        \log\binom{\Lambda+m-1}{m}
        -\log\binom{\abs T}{m}\le o(\abs T).
\]
For circle twin-cosets the same definition is used with \(2C_0(\Delta_{\rm pole}+1)\sqrt{\abs\B}\) in place of \(C_0(\Delta_{\rm pole}+1)\sqrt{\abs\B}\), accounting for the two inverse-coset lifts on the torus before the involution quotient.
\end{definition}


\part{Primitive Q and the residual compiler}
\section{The primitive prefix leaf}\label{sec:primitive-leaf}

After first-match removal of paid cells, a residual prefix-boundary chart
has a fixed set of active coordinates \(T\), \(\abs T=N\), and a fixed
support size \(m\).  The full profile slice is
\[
        \Omega_{T,m}\defeq\{x\in\{0,1\}^{T}:\sum_{t\in T}x_t=m\},
\]
and the primitive residual is a subset \(\Omc\subseteq\Omega_{T,m}\).
The superscript circle records a first-match residual; no Zariski openness
is asserted.  The normalization is taken from the full profile slice, not
from the possibly much smaller residual mass.  It is nevertheless the
\emph{realized image}, rather than the formal codomain, that supplies the
default number of target fibers.

The three words in \emph{primitive first-match residual} have separate
content.  ``First match'' means that a slope is removed as soon as one of
its witnesses occurs in an earlier ordered cell; ``residual'' means that
only witnesses surviving those removals remain; and ``primitive'' means
that the row-specific quotient, planted, field-descent, rank, and ray-saturation
certificates named by the atlas have all been applied.  Primitivity does
not mean merely trivial setwise stabilizer, and it does not assume the
Fourier, Sidon, max-fiber, or ray estimates that will be imposed below.

The prefix syndrome map is a linear map \(\Phi:\Z^T\to\B^R\), restricted
first to the full slice and then to \(\Omc\).  In the unprofiled locator
chart, when \(R<\operatorname{char}\B\), it is equivalent through Newton's
triangular change of coordinates to
\begin{equation}
        \Phi(x)=\sum_{t\in T}x_t(t,t^2,\ldots,t^R).
        \label{eq:exact-power-sum-map}
\end{equation}
Equivalently, the augmented columns
\(\widetilde v_t=(1,t,\ldots,t^R)\) have constant first coordinate
\(\sum_tx_t=m\), and the other \(R\) coordinates are \(\Phi\).  A residual
quotient or rational chart is allowed to replace these columns by
\(v_t=\rho(t)(1,t,\ldots,t^{R-1})\) only when that genuine weighted
Vandermonde representation, with \(\rho(t)\ne0\), has been proved for the
chart.  It is not a consequence merely of constructibility or of deleting
a Jacobian locus.  The number \(R\) is the number of independent prefix
equations; in the unprofiled MCA boundary leaf \(R=w=a-K\).

Put \(M=\abs{\Omega_{T,m}}\), and write
\begin{equation}
 \Scal=\Phi(\Omega_{T,m}),\qquad L=\abs\Scal,
 \qquad A=\abs\B^R,
 \qquad \barN^{\rm img}=M/L,
 \qquad \barN^{\rm amb}=M/A,
 \label{eq:image-ambient-scales}
\end{equation}
and for \(s\in\Scal\) put
\(F_s=\Omc\cap\Phi^{-1}(s)\) and \(f_s=\abs{F_s}\).  Unless an
ambient full-image certificate has been proved, we set
\(\barN=\barN^{\rm img}\).  The certificate is
\[
        L\ge e^{-o(N)}A.                       \tag{FI}\label{eq:full-image-certificate}
\]
The set \(\Scal\) is the \emph{effective image}: it consists of the
prefix targets actually attained by the full profile slice.  The formal
ambient target space \(\B^R\) can be much larger.  Condition \textup{(FI)},
the \emph{full-image certificate}, says that these two target counts differ
by at most a subexponential factor.  An \emph{effective-image collapse} is
the failure of this comparison; it must be retained as an effective-image
rank-collapse profile, or handled throughout with image normalization.
Under \eqref{eq:full-image-certificate}, the two scales differ by only
\(e^{o(N)}\), so either may be used at exponential accuracy.  If the
certificate fails, effective-image collapse must be retained as an
effective-image rank-collapse profile, or all estimates on this leaf must stay
at image scale.  Deleting earlier cells can only decrease every fiber.

The image-scale frontier condition is
\(\log M-\log L=o(N)\).  The familiar ambient equation
\(\log\binom Nm-R\log\abs\B=o(N)\) is interchangeable with it only under
\eqref{eq:full-image-certificate}.  This distinction is immaterial for a
surjective prefix map but essential for a collapsed primitive image.

\begin{lemma}[Exact image--ambient moment conversion]
\label{lem:image-ambient-moment-conversion}
For \(q\ge1\), extend \(f_s\) by zero from \(\Scal\) to \(\B^R\) and
define
\[
 \Gamma_q^{\rm img}=\frac1L\sum_{s\in\Scal}
       \left(\frac{f_s}{\barN^{\rm img}}\right)^q,
 \qquad
 \Gamma_q^{\rm amb}=\frac1A\sum_{s\in\B^R}
       \left(\frac{f_s}{\barN^{\rm amb}}\right)^q.
\]
Then
\begin{equation}
 \Gamma_q^{\rm amb}
   =\left(\frac{A}{L}\right)^{q-1}\Gamma_q^{\rm img}.
 \label{eq:image-ambient-moment-identity}
\end{equation}
Thus an ambient-normalized moment bound implies the corresponding
image-normalized bound.  The converse is valid with subexponential loss at
logarithmic order only under \eqref{eq:full-image-certificate}.
\end{lemma}

\begin{proof}
Since \(\barN^{\rm amb}=M/A\) and \(\barN^{\rm img}=M/L\), zero extension
and one rearrangement give
\[
 \Gamma_q^{\rm amb}
 =\frac1A\sum_{s\in\Scal}\left(\frac{Af_s}{M}\right)^q
 =\left(\frac AL\right)^{q-1}
   \frac1L\sum_{s\in\Scal}\left(\frac{Lf_s}{M}\right)^q.
\]
Because \(L\le A\), the asserted one-way implication follows.  Under
\eqref{eq:full-image-certificate},
\((q-1)\log(A/L)=o(Nq)\), which proves the reverse transfer at the scale
used here.
\end{proof}

\begin{remark}[Full-slice flatness certifies the image size]
\label{rem:flatness-certifies-image}
If a Fourier argument proves
\(\max_s\abs{\Omega_{T,m}\cap\Phi^{-1}(s)}
 \le e^{o(N)}\barN^{\rm amb}\), then averaging over the nonempty image
fibers gives \(A/L\le e^{o(N)}\).  Hence such an ambient flatness theorem
itself proves \eqref{eq:full-image-certificate}; image collapse cannot be
silently assumed away before that estimate has been established.
\end{remark}

\begin{definition}[Primitive Q]\label{def:primitive-q}
The \emph{Q branch} is the primitive max-fiber problem: it asks whether one
effective prefix target contains substantially more residual supports than
the image-normalized average.  A primitive prefix leaf satisfies Q with
loss \(e^{o(N)}\) if
\[
        \max_{s\in\Scal}f_s\le e^{o(N)}\barN^{\rm img}.
\]
A sequence of primitive leaves satisfies logarithmic-moment Q if, at every
logarithmic order \(q=q_N\to\infty\), \(q\le(\log N)^C\), used by the
argument,
\[
 \Gord_q\defeq\Gamma_q^{\rm img}
 =L^{-1}\sum_{s\in\Scal}
       \left(\frac{f_s}{\barN^{\rm img}}\right)^q
 \le e^{o(Nq)}.
\]
Here a \emph{logarithmic moment order} means
\(q=q_N\to\infty\) with \(q\le(\log N)^C\) for a fixed \(C\).  The
displayed normalized \(q\)-th moment is a R\'enyi-type probe of the fiber
distribution: letting \(q\) grow slowly makes it approximate the largest
normalized fiber without introducing an exponential moment-order cost.
An ambient formulation is permitted only when it is proved directly or
when \eqref{eq:full-image-certificate} has already been certified.
\end{definition}

The next lemma is the primitive logarithmic moment equivalence used in the earlier RS--MCA reductions.  It is included because it is the exact interface between moment estimates and max-fiber Q.

\begin{lemma}[Logarithmic moments and primitive Q]\label{lem:logmoment-q}
Assume \(q=q_N\to\infty\) and \(\log L/q=o(N)\).  Then
\(\Gord_q\le e^{o(Nq)}\) implies primitive Q.  Conversely, primitive Q
implies \(\Gord_q\le e^{o(Nq)}\).
\end{lemma}

\begin{proof}
Let \(M_*=\max_s f_s/\barN^{\rm img}\).  Since
\(M_*^q\le\sum_s(f_s/\barN^{\rm img})^q=L\Gord_q\), the moment bound gives
\(\log M_*\le(\log L+\log\Gord_q)/q=o(N)\).  Conversely,
\(\sum_sf_s\le\abs{\Omega_{T,m}}=L\barN^{\rm img}\), so
\(\Gord_q\le M_*^{q-1}\).  Primitive Q gives \(M_*=e^{o(N)}\), hence
\(\Gord_q=e^{o(Nq)}\).
\end{proof}

The genuine Vandermonde condition removes the ordinary rank-defect alternative.

\begin{lemma}[Augmented Vandermonde independence]\label{lem:vandermonde}
Let \(t_1,\ldots,t_r\in\B\) be distinct and \(r\le R+1\).  Then the
columns \(\widetilde v_{t_i}=(1,t_i,\ldots,t_i^R)\) are linearly
independent.  The same holds for \(\rho(t_i)(1,t_i,\ldots,t_i^{R-1})\)
when \(r\le R\) and every \(\rho(t_i)\ne0\).
\end{lemma}

\begin{proof}
In either case the leading \(r\times r\) minor, after removing the nonzero
column weights when present, is \((t_i^j)_{0\le j<r,1\le i\le r}\).  Its
determinant is \(\prod_{i<j}(t_j-t_i)\ne0\).
\end{proof}

In the high-energy argument below the Vandermonde lemma is not used:
Boolean-cube growth gives the contradiction directly.  The lemma certifies
only the exact locator chart, or a residual chart for which the displayed
weighted form has separately been verified; it does not classify arbitrary
rank defects as paid cells.


\section{Prefix coordinates and the Vandermonde map}\label{sec:prefix-coordinates}

This section explains why the primitive residual has the linear Vandermonde form used in \cref{sec:primitive-leaf}.  Let \(S\subseteq D\) have size \(m\), and write its monic locator as
\[
        Q_S(X)=\prod_{t\in S}(X-t)=X^m+q_1(S)X^{m-1}+\cdots+q_m(S).
\]
The first \(R\) boundary coordinates may be taken either as elementary symmetric coefficients \(q_1,\ldots,q_R\) or, when \(R<\operatorname{char}\B\), as power sums \(p_j(S)=\sum_{t\in S}t^j\), \(1\le j\le R\).  Newton identities give triangular polynomial changes of variables between these two coordinate systems; the diagonal entries are \(1,2,\ldots,R\), so the change is invertible in characteristic greater than \(R\).

For the unprofiled locator chart, fixing the support size makes the zeroth
power sum constant and Newton's identities identify the first \(R\)
locator coefficients with the power sums
\(\sum_tx_tt^j\), \(1\le j\le R\).  Thus
\eqref{eq:exact-power-sum-map} is exact.  For a general residual chart one
first fixes the planted roots, quotient data, common factors, and all
coordinates charged to earlier cells.  The fixed part contributes a
constant syndrome \(s_0\).  To use the primitive theorem one must then
exhibit the remaining map explicitly, either as the same power-sum map, as
a genuine common-weight Vandermonde map, or as a map for which the required
Sidon estimate has been proved directly.  Coordinate-dependent rational
weights do not become a Vandermonde system merely because they are
nonzero.  Here ``common-weight'' means that one scalar \(\rho(t)\)
multiplies every monomial coordinate of the column at \(t\), rather than
using a different weight for each coordinate.  This verification is part of the primitive-map requirement in
\cref{def:admissible-sequence}.

The fixed-density condition is also intrinsic.  In a prefix leaf the total
support size is fixed by the agreement threshold, and all paid planted
blocks have fixed size.  Thus the number of remaining choices is fixed.  If
a profile leaves several colors of coordinates, one obtains a product of
fixed-density slices; the proof applies to each color after encoding the
colors in a bounded alphabet.  For the main statement we present the
Boolean case because it is the MCA support case and because the
Boolean-cube difference bound applies directly.

\begin{lemma}[Newton-coordinate fiber equivalence]\label{lem:newton-equivalence}
Assume \(R<\operatorname{char}\B\).  For supports of fixed size, the fibers of the first \(R\) elementary locator coefficients are exactly the fibers of the first \(R\) power sums.  Consequently the Q max-fiber problem may be stated using either coordinate system.
\end{lemma}

\begin{proof}
Newton identities give, for \(1\le j\le R\),
\[
        p_j+q_1p_{j-1}+\cdots+q_{j-1}p_1+jq_j=0.
\]
Since \(j\) is invertible in \(\B\), \(q_j\) is determined by \(p_1,\ldots,p_j\), and conversely \(p_j\) is determined by \(q_1,\ldots,q_j\).  The transformations are triangular inverse polynomial maps on the first \(R\) coordinates.
\end{proof}

The \emph{description entropy} of a profile family is the logarithm of the
number of allowed auxiliary/profile descriptions.  It measures the census
of cells and is distinct from the algebraic description complexity of one
cell, which measures the number and degrees of its defining equations.

\begin{lemma}[Primitive profiles have subexponential multiplicity]\label{lem:profile-multiplicity}
If the cell ledger fixes only bounded-complexity quotient, planted, tangent,
extension, and split-pencil profiles, and the total description entropy of
all data outside the moving support is \(o(n)\) bits, then the number of
primitive profiles is \(e^{o(n)}\).
\end{lemma}

\begin{proof}
There are at most \(2^{o(n)}=e^{o(n)}\) descriptions by hypothesis.  In
particular, a planted or common block of size \(o(n)\) has
\(\sum_{j=o(n)}\binom nj=e^{o(n)}\) possible supports, but recording
\(s=o(n)\) freely chosen field values costs \(s\log_2\abs\B\) bits and is
subexponential only when that product is \(o(n)\).  Positive-density data
requires its own profile census and entropy payment; it cannot be discarded
as a bounded-complexity label.
\end{proof}

\begin{remark}
The subexponential profile lemma is the asymptotic counterpart of the
finite ledger census.  It is the reason a row proof must distinguish
between a genuine cell payment and a mere change of variables.  A change
of variables with exponentially many charts would consume the whole
frontier budget.
\end{remark}

\section{The Sidon split}\label{sec:sidon-split}

The Q moment can be large for two opposite reasons.  A fiber may contain
many repeated additive differences, which is the high-energy situation
seen by inverse additive combinatorics, or it may be large while its
differences almost never repeat, which is the Sidon-like situation.  The
split below separates these mechanisms before either one is estimated.

Every support is identified with its incidence vector in the torsion-free
group \(\Z^T\).  In particular, all sums and differences in this section
are integer operations, even when the Reed--Solomon coefficient field has
characteristic two.  For a finite set \(F\subseteq\{0,1\}^T\), define its
additive energy
\[
        E(F)=\abs{\{(a,b,c,d)\in F^4:a-b=c-d\}}.
\]
Let \(X,X'\) be independent uniform points of \(F\).  Then \(E(F)=\abs F^4\sum_z\Prob(X-X'=z)^2\).  It is convenient to normalize by
\[
        \Delta(F)=\frac{E(F)}{\abs F^3}.
\]
The quantity \(\Delta(F)\) is an additive closure probability:
\[
        \Delta(F)=\Prob_{a,b,c\in F}(a-b+c\in F).
\]
Indeed, once \(a,b,c\) are chosen, the fourth point in an energy quadruple is forced to be \(d=a-b+c\).

Thus additive energy counts repeated differences, and \(\Delta(F)\) is
their normalized density.  Values \(\Delta(F)=e^{-o(N)}\) indicate
substantial additive closure at exponential scale, whereas
\(\Delta(F)\le e^{-\sigma N}\) is the low-energy, Sidon-like regime.
The logarithmic moments below are the slowly growing normalized moments
from \cref{def:primitive-q}; they measure how much of the Q obstruction is
carried by fibers of either type.
Throughout these sections, \emph{positive rate} means a fixed positive
exponential rate along a subsequence: for a fiber it means an excess of
the form \(e^{cN-o(N)}\), and for a logarithmic moment it means an excess
of the form \(e^{cNq-o(Nq)}\), for some constant \(c>0\).

For the fiber \(F_s\), write \(\Delta_s=E(F_s)/f_s^3\), with \(\Delta_s=0\) if \(f_s=0\).

\begin{definition}[Sidon-heavy logarithmic moment]\label{def:sidon-heavy}
For \(\sigma>0\), the Sidon-heavy part of the normalized moment is
\[
        \Gsid_{q,\sigma}=L^{-1}\sum_{\Delta_s\le e^{-\sigma N}}
        \left(\frac{f_s}{\barN}\right)^q.
\]
A sequence has no positive-rate Sidon-heavy obstruction if \(\Gsid_{q,\sigma}\le e^{o(Nq)}\) for every fixed \(\sigma>0\) and every logarithmic \(q\).
Here ``Sidon'' refers to the exponentially small normalized energy
\(\Delta_s\), while ``heavy'' refers to the positive-exponential
contribution of those fibers to the normalized logarithmic moment; it does
not assert that every low-energy fiber is individually large.
\end{definition}

The following dichotomy is the correct replacement for the naive assertion that collision excess directly creates small doubling.

\begin{proposition}[Ordinary moment split]\label{prop:ordinary-moment-split}
Fix \(\eta>0\) and \(\sigma>0\).  If \(\Gord_q\ge e^{\eta Nq}\) and \(\Gsid_{q,\sigma}\le \frac12 e^{\eta Nq}\), then there is a syndrome \(s\) such that
\[
        f_s\ge e^{\eta N-o(N)}\barN,
        \qquad
        \Delta_s>e^{-\sigma N}.
\]
If no positive-rate Sidon-heavy obstruction is present, then any positive-rate moment failure gives, after taking \(\sigma\to0\) slowly, a fiber with \(f_s\ge e^{\eta N-o(N)}\barN\) and \(E(F_s)\ge f_s^3e^{-o(N)}\).
\end{proposition}

\begin{proof}
The high-energy part of the moment is at least \(\frac12e^{\eta Nq}\).  Since there are \(L\) syndromes, some high-energy syndrome satisfies
\[
        \left(\frac{f_s}{\barN}\right)^q
        \ge \frac{L}{2}\,e^{\eta Nq}\cdot L^{-1}
        =\frac12 e^{\eta Nq}.
\]
Thus \(f_s\ge e^{\eta N-o(N)}\barN\), and by construction \(\Delta_s>e^{-\sigma N}\).  If \(\Gsid_{q,\sigma}\le e^{o(Nq)}\) for every fixed \(\sigma\), apply the first part along a sequence \(\sigma_j\downarrow0\) and diagonalize; the normalization \(\Delta_s=E(F_s)/f_s^3\) gives the energy conclusion.
\end{proof}

The proof also explains the no-go point.  Suppose a fiber is heavy but \(\Delta_s\le e^{-\sigma N}\).  A closure-rich diagram using tests \(a-b+c\in F_s\) pays a factor \(\Delta_s\) for each nonredundant closure.  Such diagrams cannot account for the ordinary contribution \(f_s^q\) of \(q\) independent choices in \(F_s\).  Therefore Sidon-heavy fibers must be removed by a separate cell; they cannot be forced into the high-energy inverse branch.

\begin{definition}[Sidon moment payment]\label{def:sidon-paid-cell}
A primitive prefix leaf has a Sidon moment payment if
\(\Gsid_{q,\sigma}=e^{o(Nq)}\) for every fixed \(\sigma>0\) and every
logarithmic moment order used by the primitive-Q argument, uniformly over
profiles.  This is an analytic support-fiber statement.  It is not
equivalent to a first-match distinct-slope payment; the latter still
requires \textup{(RC)} or a direct ray bound.
\end{definition}

The equivalence in the definition follows from \cref{lem:logmoment-q} restricted to the low-energy set of syndromes.  Operationally, one proves payment either directly by bounding these fibers or indirectly by proving Fourier flatness on the primitive complement of algebraic major arcs.


\section{Why the Sidon cell is necessary}\label{sec:sidon-necessity}

It is tempting to try to prove primitive Q by expanding the logarithmic moment into diagrams and then showing that every primitive diagram contains many additive closure tests.  That strategy is correct only for a closure-rich submoment.  It cannot capture the ordinary moment on a heavy low-energy fiber.  The obstruction is simple enough to record as a lemma.

Let \(F=F_s\) be a fiber of size \(f\).  A closure test is an equation of the form \(a-b+c\in F\), with \(a,b,c\in F\) already chosen.  Its success probability is \(\Delta(F)=E(F)/f^3\).  A closure-rich diagram with \(\ell\) nonredundant closure tests and \(r\) free choices contributes, up to a subexponential diagram factor,
\[
        f^r\Delta(F)^\ell .
\]
After the free coordinates have been chosen, in the image normalization of a primitive prefix leaf, the remaining \(q-r\) coordinates are supplied only at the random scale \(\barN\).  Thus its contribution is at most
\[
        e^{o(Nq)}\barN^{q-r}f^r\Delta(F)^\ell .
\]

\begin{lemma}[No-go for ordinary moment capture]\label{lem:no-go}
Assume that \(f\ge e^{\eta N}\barN\), \(\Delta(F)\le e^{-\sigma N}\), and that a family of diagrams has \(r=o(q)\) free fiber choices and \(\ell\ge c q\) nonredundant closure tests.  Then the total contribution of these diagrams is smaller than the ordinary fiber contribution \(f^q\) by a factor
\[
        \exp\bigl(-(\eta+c\sigma)Nq+o(Nq)\bigr)
\]
up to changing \(\eta\) by \(o(1)\).
\end{lemma}

\begin{proof}
For one diagram the ratio to \(f^q\) is at most
\[
        e^{o(Nq)}\left(\frac{\barN}{f}\right)^{q-r}\Delta(F)^\ell
        \le e^{o(Nq)}\exp(-\eta N(q-r)-c\sigma Nq).
\]
Since \(r=o(q)\), this is \(\exp(-(\eta+c\sigma)Nq+o(Nq))\).  The number of bounded-complexity logarithmic diagrams is \(e^{O(q\log q)}=e^{o(Nq)}\), so summing over them does not change the exponential rate.
\end{proof}

The lemma has an important conceptual consequence.  A large Sidon-like fiber is not a hidden approximate group.  It is a different phenomenon: many independent choices land in the same syndrome, but their pairwise differences almost never repeat.  Additive-combinatorics inverse tools are designed for the opposite situation, where repeated differences are abundant.  Therefore the first-match ledger must contain a Sidon/Fourier cell before the primitive inverse argument begins.

The valid implication is exactly \cref{prop:ordinary-moment-split}.  Ordinary
moment mass splits into a low-energy part, which needs a separately proved
Sidon moment estimate, and a high-energy part, which is dispatched by
\cref{prop:high-energy-impossible}.

This mechanism does not replace a prefix-flatness or Sidon-payment theorem;
it identifies exactly where one is needed.  The first-match order is:
algebraic major arcs first, then a separately certified Sidon/Fourier cell,
and only then the high-energy primitive inverse step.  Naming a large
low-energy fiber a cell does not pay it.

\section{Fourier flatness as a Sidon payment}\label{sec:fourier}\label{sec:sidon-closure}

This section records the general weighted form of the Fourier/Sidon payment.  It is phrased for an arbitrary finite field \(\B\), because the primitive residual charts that come from the moduli ledger need not have unweighted power-sum coordinates.  Let \(T\) be a finite set, \(\abs T=N\), let \(g:T\to\B^R\) be any function, and set
\[
        \Omega_{T,m}=\{x\in\{0,1\}^T: \sum_{t\in T}x_t=m\},
        \qquad
        \Psi(x)=\sum_{t\in T}x_tg(t).
\]
In applications \(g(t)=(\rho_0(t),\rho_1(t)t,\ldots,\rho_{R-1}(t)t^{R-1})\) with nonzero rational weights \(\rho_i\) on the primitive chart.

Fourier inversion has three pieces.  The zero character produces the
average-fiber main term.  On the effective dual, the chart-specific
partition of \cref{def:effective-major-minor} designates certified minor
characters and the complementary major characters.  The ambient algebraic
exceptional locus of \cref{def:major-arc} helps construct that partition
but does not canonically determine it, because an effective character has
many ambient lifts.  The pointwise condition \textup{(PF)} controls every
certified minor lift, while the aggregate condition \textup{(MA)} controls
the sum of all designated major characters.  Neither estimate substitutes
for the other.

The condition \textup{(PF')} below is the raw power-sum flatness
inequality when one has a uniform bound for every nonzero character.
Condition \textup{(PF)} is its row-specific Weil specialization for minor
characters after substituting the pole-degree bound; the omitted major
characters are then handled by \textup{(MA)}.

\begin{theorem}[Prefix flatness from power-sum control]\label{thm:prefix-flatness-power-sum}
Fix a nontrivial additive character \(\psi\) of \(\B\).  For \(\alpha\in\B^R\setminus\{0\}\) and \(1\le j\le m\), put
\[
        P_j(\alpha)=\sum_{t\in T}\psi\bigl(j\alpha\cdot g(t)\bigr).
\]
Assume \(\abs{P_j(\alpha)}\le \Lambda\) for every \(\alpha\ne0\) and every \(1\le j\le m\).  Then, for every \(z\in\B^R\),
\[
        \abs{\Psi^{-1}(z)}
        \le \abs\B^{-R}\binom Nm+\binom{\Lambda+m-1}{m}.
\]
Consequently, if
\[
        \tag{PF'}
        R\log\abs\B+\log\binom{\Lambda+m-1}{m}-\log\binom Nm\le o(N),
\]
then \(\max_z\abs{\Psi^{-1}(z)}\le e^{o(N)}\abs\B^{-R}\binom Nm\).
\end{theorem}

\begin{proof}
By orthogonality,
\[
        \abs{\Psi^{-1}(z)}=\abs\B^{-R}
        \sum_{\alpha\in\B^R}\psi(-\alpha\cdot z)
        e_m\bigl(\psi(\alpha\cdot g(t)):t\in T\bigr),
\]
where \(e_m\) denotes the \(m\)-th elementary symmetric coefficient.  The term \(\alpha=0\) is the main term \(\abs\B^{-R}\binom Nm\).  For \(\alpha\ne0\), write \(a_t=\psi(\alpha\cdot g(t))\).  The generating identity
\(\sum_{r\ge0}e_r(a_t)u^r=\exp(\sum_{j\ge1}(-1)^{j-1}(\sum_ta_t^j)u^j/j)\) and the hypothesis \(\abs{\sum_ta_t^j}\le\Lambda\) for \(j\le m\) give
\(\abs{e_m(a_t:t\in T)}\le[u^m](1-u)^{-\Lambda}=\binom{\Lambda+m-1}{m}\).  Summing the nontrivial characters and using the outside factor \(\abs\B^{-R}\) gives the first bound.  The displayed condition \textup{(PF')} makes the error term subexponential relative to the random-fiber main term.
\end{proof}

\begin{remark}[Small characteristic cycles]\label{rem:small-characteristic-cycles}
If some integers \(j\le m\) vanish in the characteristic, the formal
Li--Wan cycle index \cite{LiWanSieve} separates the cycles divisible by
\(p=\operatorname{char}\B\); the corresponding coefficient majorant is
\([u^m](1-u)^{-\Lambda}(1-u^p)^{-(N-\Lambda)/p}\).  This bookkeeping
identity does not supply the missing character-sum bounds for those
cycles, exclude Artin--Schreier phases, or prove a uniform Sidon payment.
The pointwise theorem above is therefore deliberately stated in the
large-characteristic range.  A small-characteristic leaf needs a direct
cycle-by-cycle certificate or a separate image-normalized Q/Sidon theorem.
\end{remark}

\begin{proposition}[Weighted Weil minor arcs]\label{prop:weighted-weil-minor-arcs}
Let \(T\) be either a multiplicative coset in \(\B^\times\) or the \(x\)-coordinate of a torus twin coset.  Suppose that every certified minor lift \(\alpha\in\B^R\) has phase \(R_\alpha(t)=\alpha\cdot g(t)\) which is a nonconstant rational function on the corresponding genus-zero curve, is not of Artin--Schreier form, and has total pole-degree at most \(\Delta_{\rm pole}\).  If \(m<\operatorname{char}\B\), then the stated power-sum bound holds for every certified minor lift, with
\[
        \Lambda=C_0(\Delta_{\rm pole}+1)\sqrt{\abs\B}+\abs P
\]
for multiplicative cosets, and with \(2C_0(\Delta_{\rm pole}+1)\sqrt{\abs\B}+\abs P\) for circle twin-cosets.  Here \(P\) is the planted exceptional set and \(C_0\) is an absolute Weil constant.
\end{proposition}

\begin{proof}
For a multiplicative coset \(\theta H\subseteq\B^\times\), write the coset indicator as the average of the multiplicative characters of \(\B^\times/H\).  Each nontrivial power sum becomes an average of mixed multiplicative-additive character sums \(\sum_x\chi(x)\psi(jR_\alpha(\theta x))\).  Since \(1\le j<m<\operatorname{char}\B\), multiplication by \(j\) does not make the rational function constant or Artin--Schreier.  Weil's bound for one-variable mixed character sums \cite{Weil} gives \(C_0(\Delta_{\rm pole}+1)\sqrt{\abs\B}\).  Removing planted exceptional points changes the sum by at most \(\abs P\).  The circle case is the same after pulling back by \(x=(u+u^{-1})/2\) to the norm-one torus; the two torus branches give the factor two.
\end{proof}

\begin{theorem}[Unconditional shallow-prefix Fourier flatness]
\label{thm:unconditional-shallow-mi-ma}
Let \(p\to\infty\) through odd primes.  For each \(p\), let \(T_p\) be
either a multiplicative coset in \(\F_p^\times\) or a Chebyshev
twin-coset \(x\)-domain over \(\F_p\), in the latter case with
\(p\equiv3\pmod4\), and put \(N_p=\abs{T_p}\).
Fix \(0<\alpha<1/2\), choose integers \(m_p,R_p\) with
\[
 1\le R_p,\qquad
 \alpha\le \frac{m_p}{N_p}\le1-\alpha,
 \qquad g_p(t)=(t,t^2,\ldots,t^{R_p}),
 \qquad R_p\sqrt p=o(N_p),                         \tag{SFM1}
\]
and let \(\Psi_p(S)=\sum_{t\in S}g_p(t)\) on
\(\binom{T_p}{m_p}\).  Then \(V_{g_p}=\F_p^{R_p}\), and the certified effective partition may take
every nontrivial effective character to be minor and no character to be
major.  For some \(c_\alpha>0\),
\[
 \sum_{1\ne\chi\in\widehat{V_{g_p}}}
 \left|e_{m_p}\bigl(\chi(g_p(t)-g_p(t_0)):t\in T_p\bigr)\right|
 \le e^{-c_\alpha N_p}\binom{N_p}{m_p}.            \tag{SFM2}
\]
Consequently effective \textup{(MI)} holds, \textup{(MA)} is vacuous,
and
\[
 \max_z\abs{\Psi_p^{-1}(z)}
 \le\bigl(1+e^{-c_\alpha N_p}\bigr)
       p^{-R_p}\binom{N_p}{m_p}.                   \tag{SFM3}
\]
Indeed every \(z\in\F_p^{R_p}\) is attained for all sufficiently large
rows, and uniformly in \(z\),
\[
 \abs{\Psi_p^{-1}(z)}
 =p^{-R_p}\binom{N_p}{m_p}
  \left(1+O\bigl(e^{-c_\alpha N_p}\bigr)\right).   \tag{SFM4}
\]
Thus these smooth and circle prefix charts have unconditional effective
Fourier payment and image coverage in the shallow range \textup{(SFM1)}.
\end{theorem}

\begin{proof}
Condition \textup{(SFM1)} implies \(R_p<p\), \(R_p<N_p\), and
\(R_p\log p=o(N_p)\).  Moreover \(N_p\le p+1\), so the fixed upper
density bound gives \(m_p<p\) for every sufficiently large \(p\).
For a nonzero ambient parameter, let
\(d=\max\{j:a_j\ne0\}\).  Then \(1\le d\le R_p<p\), and
\(P(X)=\sum_{j=1}^{R_p}a_jX^j\) has a pole of order \(d\) at infinity.
Every pole of a nonconstant Artin--Schreier function \(G^p-G+c\) has
order divisible by \(p\), so \(P\) is non-Artin--Schreier.  In the circle
case \(P((u+u^{-1})/2)\) has poles of the same order \(d<p\) at the two
ends of the torus compactification and is likewise non-Artin--Schreier.

For a multiplicative coset, the character expansion of its indicator and
the mixed Weil bound give, uniformly for \(1\le j\le m_p<p\),
\[
 \left|\sum_{t\in T_p}\psi(jP(t))\right|=O(R_p\sqrt p)=o(N_p).
\]
For a circle domain, pullback by
\(x=(u+u^{-1})/2\) gives the same conclusion with an inessential factor
two.  Put \(\Lambda_p=O(R_p\sqrt p)=o(N_p)\).  The cycle-index estimate
therefore bounds every nontrivial fixed-weight Fourier coefficient by
\[
 \binom{\ceil{\Lambda_p}+m_p-1}{m_p}=e^{o(N_p)}.
\]
If a nonzero ambient character annihilated \(V_{g_p}\), its character
value would be constant on \(T_p\), making the power sum have modulus
\(N_p\), contrary to the preceding \(o(N_p)\) bound.  Thus the
annihilator is zero and \(V_{g_p}=\F_p^{R_p}\).  There are
\(p^{R_p}=e^{o(N_p)}\) effective characters, whereas
Stirling's formula and the density interval give
\(\binom{N_p}{m_p}\ge
e^{(h(\alpha)+o(1))N_p}\).  Summing the coefficient bounds proves
\textup{(SFM2)}, after decreasing the positive constant
\(c_\alpha\).  All nontrivial effective characters have just received a
certified minor lift, so the major set is empty.  Finally
Fourier inversion shows that the absolute nonzero-character error in each
fiber is \(e^{o(N_p)}\), whereas its main term is
\(p^{-R_p}\binom{N_p}{m_p}=e^{(h(m_p/N_p)+o(1))N_p}\).
This proves \textup{(SFM3)}--\textup{(SFM4)} and eventual surjectivity.
\end{proof}

\begin{definition}[Ambient algebraic exceptional locus]\label{def:major-arc}
An ambient phase parameter is \emph{algebraically exceptional} if its
weighted phase is constant on a routed quotient fiber, is Artin--Schreier
degenerate, has a pole or zero supported on a positive-density moving
divisor, or factors through a proper quotient, Chebyshev map,
field-descent locus, tangent rank drop, differential-locator defect, or
ray-saturation collapse.  On an effective chart this locus is used only
to construct the certified partition of
\cref{def:effective-major-minor}; it is not itself a numerical estimate.
In particular, an Artin--Schreier phase defined on the whole active set
restricts to the trivial effective character by
\cref{lem:constant-modes-annihilator}.
\end{definition}

\begin{proposition}[Major-arc algebraic interface]\label{prop:major-arcs-are-cells}
Each condition in \cref{def:major-arc} is a constructible condition on the
dual phase parameters and points to a quotient, Chebyshev, field-descent,
planted-divisor, differential, or rank-loss profile.  This classification
does not imply that the character vanishes after primal first-match
deletion and does not prove \textup{(MA)}.  A flatness argument must also
bound \eqref{eq:major-arc-aggregate}, recursively or directly.
\end{proposition}

\begin{proof}
Constancy on a quotient fiber, Chebyshev factorization,
Artin--Schreier degeneracy, a positive-density pole divisor, and a rank
drop are respectively coefficient, Frobenius, resultant, or determinantal
conditions.  They therefore identify constructible dual loci on which a
recursive estimate can be attempted.  Fourier inversion sums characters,
not primal witnesses, so no support-level payment follows from this fact.
\end{proof}

\begin{proposition}[Frontier Weil separation]\label{prop:frontier-weil-separation}
Let \(N=\abs T\), let \(m=\theta N+o(N)\) with \(0<\theta<1\), and suppose a primitive smooth or circle chart has minor-arc power-sum parameter \(\Lambda=o(N)\).  If the ambient random-fiber scale \(\barN=\abs\B^{-R}\binom Nm\) satisfies \(\log\barN=o(N)\), or more generally \(\log\barN\ge -o(N)\), then the prefix-flat inequality \textup{(PF')} holds.  In particular, minor arcs alone cannot create a positive-rate max-fiber or Sidon-heavy moment at this near-zero ambient entropy scale.
\end{proposition}

\begin{proof}
The elementary estimate \(\binom{\Lambda+m-1}{m}=\binom{\Lambda+m-1}{\Lambda-1}\le (e(m+\Lambda)/\Lambda)^{\Lambda}\) gives \(\log\binom{\Lambda+m-1}{m}=o(N)\), since \(\Lambda=o(N)\).  The relative minor-arc error exponent is
\[
        \log\binom{\Lambda+m-1}{m}-\log\barN
        =R\log\abs\B+\log\binom{\Lambda+m-1}{m}-\log\binom Nm.
\]
The assumed frontier inequality makes this at most \(o(N)\); it may be
negative by a linear amount, which is only stronger.  Thus the minor-arc
contribution to every full-profile fiber is at most
\(e^{o(N)}\barN\).  This statement concerns only minor characters; a
full flatness conclusion also requires \textup{(MA)}.
\end{proof}

\begin{theorem}[Sidon payment in the pointwise flat range]\label{thm:sidon-resolved-payment}
Let \(\Omc\subseteq\Omega_{T,m}\) be a primitive first-match residual of a
smooth or circle chart, with weighted prefix map \(\Psi\) and ambient
scale \(\barN^{\rm amb}=\abs\B^{-R}\binom Nm\).  Put
\(A_{\rm amb}=\abs\B^R\) and
\(L=\abs{\Psi(\Omega_{T,m})}\).  Suppose the pointwise minor-arc
condition \textup{(PF)} and the ambient instance of the aggregate
condition \textup{(MA)} hold.
Then, for every fixed \(\sigma>0\) and every
logarithmic \(q\le(\log N)^C\), for a fixed \(C\),
\[
        \Gsid_{q,\sigma}(\Omc)\le e^{o(Nq)},
\]
where \(\Gsid\) uses the image normalization of
\cref{def:sidon-heavy}.
Equivalently, no such pointwise-flat residual leaf supports positive-rate
low-energy heavy fibers.
\end{theorem}

\begin{proof}
It is enough to bound every residual fiber, and a residual is contained in
the full slice.  Fourier inversion on that slice splits into the zero,
minor, and major characters.  The zero character contributes
\(\barN^{\rm amb}\).
The cycle-index estimate and \cref{prop:weighted-weil-minor-arcs}, together
with \textup{(PF)}, bound the complete minor contribution by
\(e^{o(N)}\barN^{\rm amb}\).  Condition \textup{(MA)} bounds the complete major
contribution by the same quantity.  Thus every full-slice, and hence every
residual, fiber is \(e^{o(N)}\barN^{\rm amb}\).  This proves the
full-image certificate by \cref{rem:flatness-certifies-image}, and
\cref{lem:image-ambient-moment-conversion} transfers the ambient moment
bound to image normalization.
\end{proof}

\begin{remark}[Role of the Sidon-heavy cell]
The theorem implements ``pay structure, flatten Sidon, inverse high energy''
only in the range where both \textup{(PF)} and \textup{(MA)} are verified.
At entropy depth a phase
can have degree up to \(R\), and the raw Weil parameter is of order
\(R\sqrt{\abs\B}\); this is not automatically \(o(N)\) when
\(R\asymp N/\log\abs\B\).  Outside the pointwise-flat range a different
Sidon payment remains necessary.
\end{remark}

\section{External additive combinatorics}\label{sec:additive-tools}

Only two external additive-combinatorics inputs are used in the primitive high-energy proof.

\begin{theorem}[Balog--Szemeredi--Gowers, energy form]\label{thm:bsg}
There is an absolute constant \(C\) such that if \(A\) is a finite subset of an abelian group and \(E(A)\ge \abs A^3/K\), then there is \(A'\subseteq A\) with \(\abs{A'}\ge K^{-C}\abs A\) and \(\abs{A'-A'}\le K^C\abs{A'}\).
\end{theorem}

This is the usual energy form of the Balog--Szemeredi--Gowers theorem; polynomial dependence on \(K\) follows from Gowers's refinement of the Balog--Szemeredi theorem \cite{BalogSzemeredi,GowersSzemeredi}.  The difference-set form follows from the sumset form by replacing \(A\) by \(-A\) and using standard Ruzsa calculus \cite{TaoVu}, or directly by applying the graph form to differences.

\begin{theorem}[Boolean-cube difference growth]\label{thm:quasicube}
If \(U\subseteq\{0,1\}^d\), then
\[
                  \abs{U-U}\ge \abs U^{3/2}.
\]
\end{theorem}

This is the Boolean-cube specialization of a broader sumset inequality
of Green--Matolcsi--Ruzsa--Shakan--Zhelezov
\cite{GreenMatolcsiRuzsaShakanZhelezov}.  It also follows from the
induced-doubling identity of Matolcsi--Ruzsa--Shakan--Zhelezov
\cite{MatolcsiRuzsaShakanZhelezov}.  Only the displayed Boolean statement
is used below.

\begin{remark}
Entropy inverse theorems of Tao and the entropy-doubling theory of Green--Manners--Tao are compatible with this proof and are often useful after one has produced small-doubling trades \cite{TaoEntropy,GreenMannersTao}.  They are not needed as hypotheses here.  The Boolean-cube growth theorem gives a direct contradiction to a large small-doubling subset of a primitive Boolean support fiber.
\end{remark}


\section{Entropy inverse theory and its role}\label{sec:entropy-role}

The terminology ``Tao--Gowers method'' can refer to two related but
distinct steps.  The first is BSG, used directly in
\cref{prop:high-energy-impossible}.  The second is Freiman-type structural
theory, meaning inverse theorems that model a set with small sumset or
difference set by a generalized arithmetic progression or a coset
progression.  It is not needed for the Boolean contradiction, but it can suggest
candidate geometric strata in more general bounded-alphabet residuals;
those strata still require direct payment proofs.

A \emph{bounded integer trade} is a vector \(Y\in\Z^T\) whose
coordinates are bounded independently of \(N\), with \(\Phi(Y)=0\) and,
on a fixed-weight slice, \(\sum_tY_t=0\).  If \(Y\) is random, \(Y'\) is
an independent copy, and
\(\Ent(Y-Y')\le \Ent(Y)+o(N)\), then entropy BSG and entropy Freiman
theory produce, after conditioning and losing \(o(N)\) entropy, a set
model with doubling \(e^{o(N)}\).  Tao's entropy inverse theorem gives
this in \emph{coset-progression} language---a subgroup coset plus a
generalized arithmetic progression---for Shannon entropy \cite{TaoEntropy};
Green--Manners--Tao recast the theory in terms of entropic doubling and
Ruzsa distance \cite{GreenMannersTao}; Goh formulates an entropic analogue
of additive energy and the entropic BSG connection \cite{GohEnergy}.  In a
torsion model one may also use polynomial Freiman--Ruzsa technology after
reducing bounded integer trades modulo a large prime with no wraparound.

In the present paper the Boolean-cube difference theorem makes this
structural compression unnecessary for the primitive Q step.  Once BSG
finds \(A'\subseteq F_s\subseteq\{0,1\}^T\) with
\(\abs{A'-A'}\le e^{o(N)}\abs{A'}\), Boolean-cube difference growth
already forces \(\abs{A'}=e^{o(N)}\).  This contradicts the exponential
size supplied by moment excess.  Therefore there is no separate
entropy-Freiman hypothesis in the proof.

For non-Boolean residual trades, entropy inverse theory can suggest
coset-progression incidence strata or rank-defect tests.  This is a useful
heuristic for constructing a row-specific atlas, not an exhaustive
dichotomy: each suggested stratum still needs the explicit first-match census and
slope-projection payment required by \cref{def:admissible-sequence}, and arbitrary weighted charts
are not covered by \cref{lem:vandermonde}.  No such heuristic is used in
the proof of the Boolean primitive theorem.

\section{Primitive Q after the Sidon cut}\label{sec:primitive-q-proof}

The key primitive theorem is now short and self-contained modulo \cref{thm:bsg,thm:quasicube}.  It also addresses the main obstruction: ordinary \Renyi{} mass can be Sidon-heavy, but after that cell is removed it must be high-energy, and high-energy is impossible in a large Boolean fiber.

\begin{proposition}[High-energy Boolean fibers are small]\label{prop:high-energy-impossible}
Let \(F\subseteq\{0,1\}^T\), \(\abs T=N\).  If
\(E(F)\ge \abs F^3/K\), then \(\abs F\le K^{O(1)}\).  Consequently an
exponential set \(\abs F\ge e^{cN-o(N)}\) cannot have
\(E(F)\ge\abs F^3/e^{o(N)}\).
\end{proposition}

\begin{proof}
Apply \cref{thm:bsg}.  There is \(F'\subseteq F\) with \(\abs{F'}\ge K^{-C}\abs F\) and \(\abs{F'-F'}\le K^C\abs{F'}\).  Since \(F'\subseteq\{0,1\}^T\), \cref{thm:quasicube} gives \(\abs{F'-F'}\ge \abs{F'}^{3/2}\).  Hence \(\abs{F'}^{1/2}\le K^C\), so \(\abs F\le K^{3C}\) after increasing \(C\).  Taking \(K=e^{o(N)}\) rules out \(\abs F\ge e^{cN-o(N)}\).
\end{proof}

\begin{theorem}[Primitive Q after a Sidon moment payment]\label{thm:primitive-q}
Let \(\Omega_N^0\subseteq\{0,1\}^{T_N}\) be fixed-density full profile
slices, with \(\abs{T_N}=N\) and
\(m_N/N\in[\alpha,1-\alpha]\), and let
\(\Omc_N\subseteq\Omega_N^0\) be primitive first-match residuals.  Suppose
there is a logarithmic moment
order \(q_N\to\infty\) with
\(\log L_N/q_N=o(N)\), where
\(L_N=\abs{\Phi_N(\Omega_N^0)}\) and
\(\barN_N=\abs{\Omega_N^0}/L_N\), for which
\(\Gsid_{q_N,\sigma}\le e^{o(Nq_N)}\) for every fixed \(\sigma>0\).
Then the leaves satisfy primitive Q:
\[
        \max_s\abs{\Omc_N\cap\Phi_N^{-1}(s)}
        \le e^{o(N)}\barN_N .
\]
\end{theorem}

\begin{proof}
Assume primitive Q fails at positive exponential rate.  The lower half of
the moment sandwich gives
\(\Gord_{q_N}\ge e^{\eta Nq_N-o(Nq_N)}\) along a subsequence.  The Sidon
moment hypothesis and \cref{prop:ordinary-moment-split} then give a fiber
\(F_s\) with \(f_s\ge e^{\eta N-o(N)}\barN_N\) and
\(E(F_s)\ge f_s^3e^{-o(N)}\).  Since
\(\barN_N=\abs{\Omega_N^0}/L_N\ge1\), this fiber has size
\(e^{\eta N-o(N)}\), contradicting
\cref{prop:high-energy-impossible} with \(K=e^{o(N)}\).  Thus no
positive-rate max-fiber failure occurs.
\end{proof}

\section{Q, SP, and the MCA compiler}\label{sec:compiler}
This section uses the prefix rigidity, exact second moment, and slope-elimination results of \cite[Secs.~19--21 and Apps.~E--F]{CAP25v132} as imported inputs.  The new content is the occupancy/ray compiler and the precise hypotheses under which Q controls MCA slopes.

The \emph{Q branch} is the maximum-prefix-fiber problem.  The \emph{SP
branch} (support-pair, or shift-pair, branch) is its second-moment problem:
it counts ordered pairs of supports in one prefix fiber.  These names label
two counting interfaces and carry no assertion that either bound has
already been proved.  Neither count is automatically the MCA numerator: a
bad slope begins with one support, while converting support pairs to
projective slope directions requires a proved multiplicity or incidence
bound.  We first record the exact moment identities and then state that
separate ray compiler.

\begin{definition}[Q and SP ledgers]\label{def:q-sp}
For a first-match residual profile \(\lambda\), let \(\Omega^0_\lambda\)
be its full profile slice, let
\(\Omc_\lambda\subseteq\Omega^0_\lambda\) be the residual, and put
\[
 \Scal_\lambda=\Phi_\lambda(\Omega^0_\lambda),\qquad
 L_\lambda=\abs{\Scal_\lambda},\qquad
 \barN_\lambda=\abs{\Omega^0_\lambda}/L_\lambda,
 \qquad
 Q_\lambda(s)=\abs{\Omc_\lambda\cap\Phi_\lambda^{-1}(s)}.
\]
The Q ledger is discharged if
\(\max_sQ_\lambda(s)\le e^{o(n)}\barN_\lambda\) for every primitive
profile.  The support-pair SP statistic is
\(\sum_sQ_\lambda(s)^2\).  A distinct-ray ledger is discharged only by a
direct slope bound or by \textup{(RC)} below.
If the ambient target count \(\abs{\B_\lambda}^{R_\lambda}\) is used in
place of \(L_\lambda\), the ledger must also record the full-image
certificate \eqref{eq:full-image-certificate} or a direct ambient theorem.
\end{definition}


The compiler uses two elementary inequalities repeatedly.  They are included to make explicit how the logarithmic moment, max-fiber Q, and shift-pair second moment interact.

\paragraph{Imported moment inequality.}
For fiber sizes \(N(s)\), mean \(\bar N\), ratios \(R(s)=N(s)/\bar N\),
and \(\Gamma_r=L^{-1}\sum_sR(s)^r\), CAP25 v13.2
\cite[Sec.~19 and Apps.~E--F]{CAP25v132} gives the elementary bounds
\[
        \max_sR(s)\le(L\Gamma_r)^{1/r},
        \qquad
        \Gamma_r\le(\max_sR(s))^{r-1}.
        \tag{M}\label{eq:imported-moment-interface}
\]


\begin{corollary}[Finite moment floor]\label{cor:finite-moment-floor}
Suppose a finite row has remaining Q bit margin \(\Delta\), meaning that one needs \(\max_sR(s)\le2^\Delta\).  A moment proof of order \(r\) can certify this only if
\[
        \log_2\Gamma_r+\log_2 L\le r\Delta,
\]
where \(L\) is the number of realized targets in the selected
normalization.  In an ambient prefix proof this specializes to
\(\log_2\Gamma_r^{\rm amb}+R\log_2\abs\B\le r\Delta\); transferring an
image-normalized moment to that statement additionally costs
\((r-1)\log_2(\abs\B^R/L)\).
\end{corollary}

\begin{proof}
The moment sandwich gives \(\log_2\max_sR(s)\le(\log_2L+\log_2\Gamma_r)/r\).  To make this at most \(\Delta\) one needs the displayed inequality.
\end{proof}

The finite corollary explains why a small adjacent margin cannot be closed
by a fixed-order moment when \(R\log\abs\B\) is large.

\begin{definition}[Explanation image and retained-support occupancy]
\label{def:explanation-occupancy}
Fix \(a\ge k+1\), a received pair \(r=(r_0,r_1)\), and a cell
\(\Ccal\subseteq\Wcal_a(r)\).  Its \emph{explanation image} and
\emph{slope image} are
\[
 \Rcal(\Ccal)=\{(\gamma,h):\exists S\ (\gamma,S,h)\in\Ccal\},
 \qquad Z(\Ccal)=\{\gamma:\exists h\ (\gamma,h)\in\Rcal(\Ccal)\}.
\]
For \(\rho=(\gamma,h)\in\Rcal(\Ccal)\), its
\emph{retained-support occupancy} is
\[
 \nu_{\Ccal}(\rho)
   =\abs{\{S\in\tbinom Da:(\gamma,S,h)\in\Ccal\}}.
\]
Thus the witness projection factors canonically as
\[
 \Ccal\longrightarrow\Rcal(\Ccal)\longrightarrow Z(\Ccal),
 \qquad (\gamma,S,h)\longmapsto(\gamma,h)\longmapsto\gamma.
\]
The first map forgets an exact-agreement support; the second forgets the
explaining polynomial.  Distinct explanation states may have the same
slope, so neither map is silently treated as a bijection.  A
\emph{ray compiler} means a proved estimate for the final slope image,
obtained from these actual fibers or from a direct incidence bound.
\end{definition}

\begin{lemma}[Exact occupancy compiler]
\label{lem:exact-occupancy-compiler}
With the notation above,
\[
 \abs{\Ccal}=\sum_{\rho\in\Rcal(\Ccal)}\nu_{\Ccal}(\rho),
 \qquad
 \abs{\Rcal(\Ccal)}
   =\sum_{w\in\Ccal}
       \frac1{\nu_{\Ccal}(\pi_{\rm exp}(w))},
 \qquad
 \abs{Z(\Ccal)}\le\abs{\Rcal(\Ccal)}.             \tag{RC$_{\rm occ}$}
\]
Here \(\pi_{\rm exp}(\gamma,S,h)=(\gamma,h)\).  In particular, if every
retained explanation state has occupancy at least \(H\ge1\), then
\[
        \abs{Z(\Ccal)}\le
        \floor{\frac{\abs{\Ccal}}H}.                \tag{RC1}
\]
Also, because one noncommon exact-\(a\) support carries at most one slope
and the explaining polynomial on \(a\ge k+1\) points is unique,
\[
 \abs{Z(\Ccal)}\le
 \abs{\{S:\exists\gamma,h\ (\gamma,S,h)\in\Ccal\}}. \tag{RC2}
\]
All these statements are exact finite-row identities or inequalities.
\end{lemma}

\begin{proof}
Partition \(\Ccal\) by the fibers of \(\pi_{\rm exp}\).  This gives the
first identity; summing the reciprocal of the fiber size over each fiber
gives the second.  Projection \((\gamma,h)\mapsto\gamma\) can only
decrease cardinality.  If every first fiber has size at least \(H\),
\textup{(RC1)} follows.  Finally, if the same noncommon support carried two
distinct slopes, slope elimination would simultaneously explain the
received pair on that support.  For fixed support and slope, uniqueness of
interpolation gives at most one \(h\).  This proves \textup{(RC2)}.
\end{proof}

\begin{lemma}[Max-occupancy add-back]
\label{lem:max-occupancy-addback}
Let \(\Ccal\subseteq\Wcal_a(r)\) be partitioned into profile cells
\(\Ccal=\coprod_{\lambda\in\Lambda}\Ccal_\lambda\), and put
\(P=\abs\Lambda\).  For every explanation state
\(\rho=(\gamma,h)\in\Rcal(\Ccal)\), let
\[
 M(\rho)=\abs{\{S:(\gamma,S,h)\in\Ccal\}}.
\]
Assign \(\rho\) to a profile \(\lambda(\rho)\) on which
\(\nu_{\Ccal_\lambda}(\rho)\) is maximal, and let
\(\Rcal_\lambda^\star\) be the assigned states.  Then
\[
 \nu_{\Ccal_\lambda}(\rho)\ge\ceil{M(\rho)/P}
 \qquad(\rho\in\Rcal_\lambda^\star).               \tag{RC$_{\rm max}$1}
\]
Consequently, if \(M(\rho)\ge H\) for every retained state, then
\[
 \abs{Z(\Ccal)}
 \le\sum_{\lambda\in\Lambda}\abs{\Rcal_\lambda^\star}
 \le\sum_{\lambda\in\Lambda}
   \floor{\frac{\abs{\Ccal_\lambda^\star}}
                   {\ceil{H/P}}},                  \tag{RC$_{\rm max}$2}
\]
where \(\Ccal_\lambda^\star\) consists of the witnesses in
\(\Ccal_\lambda\) lying above assigned states.  Call \(\Ccal\)
\emph{explanation-state complete} if, whenever
\((\gamma,h)\in\Rcal(\Ccal)\), every exact-\(a\) noncommon witness
\((\gamma,S,h)\in\Wcal_a(r)\) also belongs to \(\Ccal\).  If \(\Ccal\)
is explanation-state complete, every retained state has exact agreement
\(b\ge a\), and the received pair is not simultaneously explained on any
\(a\)-subset of that agreement set, then one may take \(H=\binom ba\).
\end{lemma}

\begin{proof}
The \(P\) profile occupancies of a fixed state sum to \(M(\rho)\), so
their maximum is at least \(\ceil{M(\rho)/P}\).  Apply
\cref{lem:exact-occupancy-compiler} on each assigned cell and sum.  Under
the final hypotheses, explanation-state completeness retains every
\(a\)-subset of the \(b\)-point agreement set, and every such subset is
noncommon.  Hence \(M(\rho)=\binom ba\).
\end{proof}

\begin{definition}[Support interpolation functionals]
\label{def:pair-to-ray-map}
Let \(T\subseteq D\), \(\abs T=m\ge k\), put \(w=m-k\), and let
\(Q_T(X)=\prod_{x\in T}(X-x)\).  For a word \(u\), define
\begin{equation}
 \mathcal A_T(u)=
 \left(
   \sum_{x\in T}\frac{u(x)x^r}{Q_T'(x)}
 \right)_{0\le r<w}\in\F^w.
 \label{eq:interpolation-functional}
\end{equation}
\end{definition}

\paragraph{Imported slope interface.}
CAP25 v13.2 \cite[Sec.~19 and Apps.~E--F]{CAP25v132} proves that a word
\(u\) is explained by \(\RS_\F(D,k)\) on \(T\) exactly when
\(\mathcal A_T(u)=0\).  Hence
\[
 \mathcal A_T(u_0)+\gamma\mathcal A_T(u_1)=0,
 \tag{SE}\label{eq:imported-slope-elimination}
\]
and every noncommon support carries at most one finite slope.  We use this only as an imported incidence input to the occupancy compiler above.


\paragraph{Imported support-pair identity.}
For every residual prefix profile \(\lambda\), the foundational paper
\cite[Sec.~19 and Apps.~E--F]{CAP25v132} identifies the ordered
same-prefix support-pair count as
\[
        \sum_sQ_\lambda(s)^2
        \le
        \bigl(\max_sQ_\lambda(s)\bigr)\sum_sQ_\lambda(s).
        \tag{SP$_0$}\label{eq:imported-support-pair}
\]


Q therefore controls a support-pair statistic.  It does not justify dividing
that statistic by \(\abs{\Omega^0_\lambda}\): a ray can have a single
representative at exact agreement.

\begin{proposition}[Q and SP do not determine rays]
\label{prop:q-sp-no-ray}
Let \(\Phi:\Omega\to\Sigma\) be any support-profile map with
\(\Omega\ne\varnothing\), put
\(Q(s)=\abs{\Phi^{-1}(s)}\), and
\({\rm SP}=\sum_sQ(s)^2\).  Regard \(\Omega\) as an abstract set of
candidate noncommon supports, and suppose the only retained
slope-incidence axiom is that each support carries at most one slope.  For
every nonempty finite slope set \(\Gamma\) and every
\(1\le M\le\min\{\abs\Omega,\abs\Gamma\}\), within the class of abstract
incidence structures obeying these retained data there is a partial
support-to-slope map having exactly \(M\) distinct values.  There is also
a one-value map.  Hence no ray bound can be deduced from Q, SP, and that
axiom alone; an RS-specific bound must use additional algebraic incidence
information.
\end{proposition}

\begin{proof}
Choose \(M\) distinct supports and \(M\) distinct slopes and map them
bijectively, leaving all other supports unlabeled.  This changes neither
\(\Phi\), its fibers, nor SP, and it respects one-slope-per-support.
Mapping the same chosen supports to one slope gives identical Q and SP
data with a one-ray image.  The missing datum is the image incidence, not
another moment of the prefix fibers.
\end{proof}

\begin{proposition}[Exact pair-to-ray multiplicity requirement]
\label{prop:pair-ray-multiplicity}
Let
\(\mathcal P=\{(A,B)\in\Omega^2:\Phi(A)=\Phi(B)\}\), so
\(\abs{\mathcal P}={\rm SP}\).  Let \(Z\) be a bad-slope set and
\(I\subseteq Z\times\mathcal P\) an incidence relation, and let
\(H,J\ge1\).  If every
\(\gamma\in Z\) is incident with at least \(H\) pairs and every pair is
incident with at most \(J\) slopes, then
\begin{equation}
 \abs Z\le\frac{J\,{\rm SP}}H
       \le\frac{J(\max_sQ(s))\abs\Omega}{H}.
 \label{eq:pair-ray-multiplicity}
\end{equation}
Consequently this pair-count argument yields a ray estimate at the same
profile scale provided \(J\abs\Omega/H=e^{o(n)}\); alternatively one may
prove a direct transverse-secant estimate.  Merely proving that every ray
has one representing pair is insufficient.
\end{proposition}

\begin{proof}
Double counting gives
\(H\abs Z\le\abs I\le J\abs{\mathcal P}=J\,{\rm SP}\).  The second
inequality follows from
\({\rm SP}\le(\max_sQ(s))\sum_sQ(s)=(\max_sQ(s))\abs\Omega\).
\end{proof}

\begin{corollary}[Exact finite pair-to-ray constant]
\label{cor:finite-pair-ray-compiler}
For a residual profile \(\lambda\), put
\(m_\lambda=\sum_sQ_\lambda(s)\),
\(L_\lambda=\abs{\Phi_\lambda(\Omega^0_\lambda)}\), and
\(\barN_\lambda=\abs{\Omega^0_\lambda}/L_\lambda\).  For an integer
\(q\ge2\), define
\[
 \Gamma_{q,\lambda}=L_\lambda^{-1}\sum_s
 \left(\frac{Q_\lambda(s)}{\barN_\lambda}\right)^q.
\]
If the pair-to-ray incidence has lower ray degree \(H_\lambda\) and upper
pair degree \(J_\lambda\), then
\[
 \abs{Z_\lambda^\circ}\le
 \floor{\frac{J_\lambda m_\lambda}{H_\lambda}\,
  \barN_\lambda
  \bigl(L_\lambda\Gamma_{q,\lambda}\bigr)^{1/q}}.   \tag{RC$_{\rm pair}$}
\]
Thus the finite compiler uses the actual residual mass and literal
incidence degrees; it contains no unnamed polynomial or asymptotic loss.
\end{corollary}

\begin{proof}
The moment sandwich gives
\(\max_sQ_\lambda(s)\le\barN_\lambda
(L_\lambda\Gamma_{q,\lambda})^{1/q}\).  Hence
\(\sum_sQ_\lambda(s)^2\le m_\lambda\max_sQ_\lambda(s)\).
Apply \cref{prop:pair-ray-multiplicity} and take the integer floor.
\end{proof}

\begin{proposition}[Curve-degree ray compiler]
\label{prop:curve-degree-ray-compiler}
Let \(V\) be a finite-dimensional space of locator polynomials and, for
\(x\in D\), let
\(H_x=\{[L]\in\Pj(V):L(x)=0\}\) be its \emph{evaluation hyperplane}.
Suppose a residual slope set \(Z\) admits an injective assignment into a
disjoint union of projective integral curves
\[
              Z\hookrightarrow\coprod_{i=1}^sX_i(\F),
\]
where ``integral curve'' means an irreducible reduced one-dimensional
projective variety, together with locator morphisms
\(\psi_i:X_i\to\Pj(V)\).  Put
\[
 \delta_i=\deg\psi_i^*\mathcal O_{\Pj(V)}(1),
\]
the degree on \(X_i\) of the pullback of a projective hyperplane.  For
every \(\gamma\in Z\), if its assigned point is \(y\in X_i(\F)\), require
\(\psi_i(y)=[L_{\gamma,y}]\), where \(L_{\gamma,y}\) is a locator from an
actual residual witness to \(\gamma\).  For each \(i\), put
\[
 G_i=\{x\in D:\psi_i(X_i)\subseteq H_x\},
 \qquad D_i^{\rm mov}=D\setminus G_i.
\]
Assume the locator attached to every chosen representative on \(X_i\)
has at least \(h_i\ge1\) roots in \(D_i^{\rm mov}\).  Then
\[
 \abs Z\le
 \floor{\sum_{i=1}^s
       \frac{\abs{D_i^{\rm mov}}\delta_i}{h_i}}
 \le\floor{n\sum_{i=1}^s\frac{\delta_i}{h_i}}.
 \tag{RC$_{\rm curve}$}
\]
In particular, a cover of subexponential total locator degree gives a
subexponential ray budget when the \(h_i\) have no exponential loss.  The
standard degree-one pencil \([s:t]\mapsto[sA+tB]\) is the special case
\(X=\Pj^1\) and \(\delta=1\).
\end{proposition}

\begin{proof}
Choose one representative point for each slope.  For fixed \(i\) and
\(x\in D_i^{\rm mov}\), the pullback of \(H_x\) is a nonzero effective
divisor of degree \(\delta_i\), and hence contains at most \(\delta_i\)
distinct rational points.  Each chosen point on \(X_i\) supplies at least
\(h_i\) moving-root incidences.  Thus the number assigned to \(X_i\) is
at most \(\abs{D_i^{\rm mov}}\delta_i/h_i\).  Sum over \(i\) and take
the integer floor.
\end{proof}

\begin{corollary}[Automatic exact-support locator-curve compiler]
\label{cor:automatic-locator-curve-ray}
Fix a received line and exact agreement \(a\ge k+1\).  For each slope in
a residual set \(Z\), choose one noncommon witness support
\(S_\gamma\in\binom Da\) and its locator \(Q_{S_\gamma}\).  Suppose the
locator points are covered by
\(\psi_i(X_i(\F))\), where
\(\psi_i:X_i\to\Pj(V)\) are nonconstant morphisms from projective
integral curves.  Put
\[
 \delta_i=\deg\psi_i^*\mathcal O(1),\qquad
 G_i=\{x\in D:\psi_i(X_i)\subseteq H_x\},
 \qquad g_i=\abs{G_i}.
\]
Then
\[
 \abs Z\le
 \#\{i:g_i=a\}+
 \floor{\sum_{i:g_i<a}\frac{(n-g_i)\delta_i}{a-g_i}}. \tag{RC$_{\rm loc}$}
\]
No separate slope-to-curve injectivity hypothesis is required.  A
component with \(g_i=a\) contains at most one selected degree-\(a\)
locator, because its \(a\) common roots determine the monic support
locator uniquely; this accounts for the first term.  Components with
\(g_i>a\) contain no selected degree-\(a\) locator and are discarded.
\end{corollary}

\begin{proof}
Two distinct slopes cannot use the same chosen noncommon support.  Since a
monic squarefree locator determines its root set, their projective locator
points are distinct as well.  Assign each locator to the first covering
component and choose one rational preimage; this is the injective
assignment required by \cref{prop:curve-degree-ray-compiler}.  On
component \(i\), every selected degree-\(a\) locator has the \(g_i\)
common roots and at least \(a-g_i\) roots outside them.  If \(g_i=a\),
there is only one such monic locator.  On the other components apply
\textup{(RC$_{\rm curve}$)} with \(h_i=a-g_i\).
\end{proof}

\begin{corollary}[Automatic exact-support one-pencil compiler]
\label{cor:automatic-one-pencil-ray}
In the setting above, suppose all selected locators lie in the projective
pencil spanned by \(A,B\), and let \(g<a\) be the number of common roots
of \(A,B\) in \(D\).  Then
\[
                         \abs Z\le\floor{(n-g)/(a-g)}. \tag{RC$_{\rm pen}$}
\]
The same argument applies to residual locators of degree \(e\) whose roots
lie in a fixed active domain \(T\subseteq D\), provided the fixed profile
data together with the residual locator determine the exact support.  If
\(N=\abs T\) and \(g_T\) is the number of common roots of \(A,B\) in
\(T\), then
\[
                         \abs Z\le\floor{(N-g_T)/(e-g_T)}.
\]
\end{corollary}

\begin{proof}
The exact-support locator assignment is injective by the preceding proof.
Apply \cref{lem:pencil-payment}, or the curve corollary with
\(X=\Pj^1\) and \(\delta=1\).
\end{proof}

By \cref{thm:syndrome-secant-exact}, the genuinely missing invariant can
be taken to be \(\Theta_t(y_0,y_1)\).  Equivalently one may construct a
higher-dimensional split-pencil \emph{eliminant}, meaning a polynomial in
the slope parameter obtained after eliminating locator and support
variables, whose degree bounds that transverse secant incidence.  By
\cref{lem:independent-union-rays}, only dependent support unions can
support more than \(t+1\) rays.  Those unions are no longer untreated:
\cref{thm:fixed-union-ray,thm:directional-johnson-ray} bound every fixed
union, and \cref{prop:active-fixed-union-payments} gives the exact active
low-nullity ranges.  What remains is an uncontrolled family of many such
unions, a high-nullity chart, or a direction whose rank defect exceeds the
quantitative threshold of \cref{cor:quantitative-direction-defect}; a
higher-dimensional balanced core must still be routed into one of those
certified cells or paid by its own eliminant.

Here an \emph{MDS-circuit stratum} is a chart on which the relevant union
of generalized Vandermonde parity-check columns has a minimal linear
dependence.  Equivalently, deleting any one column restores independence.
The name identifies the only dependence pattern left by the MDS property;
it does not by itself place all witnesses in one fixed circuit or provide
a count for an unrestricted union of such strata.

The next hypothesis packages exactly this missing conversion.  Its number
\(H_\lambda\) is a lower bound on how many certified support pairs represent
one bad ray, while \(J_\lambda\) is an upper bound on how many bad rays one
pair can represent.  The ratio in \textup{(RC)} is what makes the resulting
double count stay at the profile scale.

\begin{hypothesis}[Ray compiler]\label{hyp:ray-compiler}
For every received line and primitive residual profile \(\lambda\), let
\(Z_\lambda^\circ\) be its actual first-match set of unpaid bad slopes and
put
\[
\Pcal_\lambda=\{(A,B)\in(\Omc_\lambda)^2:
                       \Phi_\lambda(A)=\Phi_\lambda(B)\}.
\]
Put \(m_\lambda=\abs{\Omc_\lambda}=\sum_sQ_\lambda(s)\).
The row satisfies \textup{(RC)} on this profile if either it has the direct
bound \(\abs{Z_\lambda^\circ}\le e^{o(n)}(1+\barN_\lambda)\), or there are
an incidence
\(I_\lambda\subseteq Z_\lambda^\circ\times\Pcal_\lambda\) and numbers
\(H_\lambda,J_\lambda\ge1\) such that
\[
 \deg_{I_\lambda}(\gamma)\ge H_\lambda,\qquad
 \deg_{I_\lambda}(A,B)\le J_\lambda,\qquad
 \frac{J_\lambda m_\lambda}{H_\lambda}=e^{o(n)}.
 \tag{RC}\label{eq:ray-compiler}
\]
All bounds are uniform in the received line and realized profile.  The
incidence must arise from the RS witness geometry; its existence is not a
consequence of Q or SP.  In particular, one representing pair per ray does
not supply the required lower degree.
\end{hypothesis}

\begin{proposition}[Q plus RC implies rays]\label{prop:q-implies-sp}
If primitive Q is discharged and \textup{(RC)} holds on every residual
profile, then all primitive ray ledgers are discharged
at total cost \(e^{o(n)}\mathfrak E_n\).
\end{proposition}

\begin{proof}
The boundary prefix fibers are bounded by Q.  For every remaining unpaid
slope choose one noncommon support, as permitted by
the imported slope interface \eqref{eq:imported-slope-elimination}; \textup{(RC)} bounds their distinct slope set by
\(e^{o(n)}\barN_\lambda\).  Sum over the subexponential profile set and use
\eqref{eq:profile-envelope}.
\end{proof}

The proof of \cref{thm:main-smooth-circle} is now complete: the Sidon payment and \cref{thm:primitive-q} pay primitive Q, while \cref{prop:q-implies-sp} and \textup{(RC)} convert the remaining support bounds into distinct-ray bounds.


\part{Finite deployment: Q, one-parameter BC, and the exact ledger}
\section{Finite max-fiber calibration}\label{sec:finite-calibration}
We import the four unsafe endpoints and challenge budgets from CAP25 v13.2 \cite[Cor.~14.3 and Def.~21.1]{CAP25v132}.  Only the adjacent-row quantities consumed by the new upper compiler are printed here.

\begin{table}[H]
\centering
\caption{Imported active frontier rows and the adjacent safe-side calibration.}
\label{tab:active-frontier-rows}
\small
\begin{tabular}{@{}lrrrr@{}}
\toprule
row & $a_0$ & $a_+=a_0+1$ & $w=a_+-K$ & $B^*$\\
\midrule
KoalaBear MCA & 1116047 & 1116048 & 67471 & 274980728111395087\\
KoalaBear list & 1116046 & 1116047 & 67471 & 274980728111395087\\
Mersenne-31 MCA & 1116023 & 1116024 & 67447 & 16777215\\
Mersenne-31 list & 1116022 & 1116023 & 67447 & 16777215\\
\bottomrule
\end{tabular}
\end{table}
Here $n=2^{21}$, $K=2^{20}+1$ on the MCA route, and $K=2^{20}$ on the list route.  Put
\[
 \overline F=\binom n{a_+}|\B|^{-w}.
\]
The exact ceilings of this average are, in table order,
\begin{equation}
57198030366,\quad 65065153468,\quad 1752700,\quad 1993678.\label{eq:finite-average-ceilings}
\end{equation}
Hence the full-budget Q overhead ceilings are respectively
\begin{equation}
4807520.9295,\quad 4226236.5253,\quad 9.5722,\quad 8.4152.\label{eq:finite-q-ratios}
\end{equation}
Any payment made to another cell lowers these values.

The exact moment interface imported from the foundation is
\begin{equation}
 \max_z R(z)\le (|\B|^w\Gamma_r)^{1/r},
 \qquad R(z)=\frac{|\Fib_w(z)|}{\binom n{a_+}|\B|^{-w}}.\label{eq:imported-prefix-moment-sandwich}
\end{equation}
The exact second-moment decomposition is written
\begin{equation}
 \sum_zN_w(z)^2=\binom n{a_+}+\sum_eP_e.\label{eq:imported-second-moment}
\end{equation}

\begin{theorem}[Finite moment criterion for Q]\label{thm:moment-q}
If $\Gamma_r\le e^A$, then the normalized maximum fiber satisfies
\[
 R_Q^{\max}\le\exp\!\left(\frac{A+w\log|\B|}{r}\right).
\]
Thus a finite row with remaining bit margin $\Delta$ can be proved by this route only if
\begin{equation}
 \log_2\Gamma_r+w\log_2|\B|\le r\Delta.\label{eq:finite-moment-criterion}
\end{equation}
\end{theorem}
\begin{proof}
Take logarithms in \eqref{eq:imported-prefix-moment-sandwich}.
\end{proof}

\begin{lemma}[Pencil payment]\label{lem:pencil-payment}
Let $L_{[s:t]}=sA+tB$ be a projective polynomial pencil and let $T$ be a finite set.  If every counted member has at least $h$ roots in $T$ that are not common roots of $A$ and $B$, then at most $\lfloor |T|/h\rfloor$ projective parameters are counted.
\end{lemma}
\begin{proof}
A point $x\in T$ that is not a common root solves the homogeneous linear equation $sA(x)+tB(x)=0$ for exactly one projective parameter.  Count moving-root incidences.
\end{proof}

\begin{definition}[projective locator pencil and its common \(D\)-part]\label{def:projective-locator-pencil}
Let \(D\subseteq\F\) be finite, put \(\Lambda_D=\prod_{x\in D}(X-x)\), and let \(A,B\in\F[X]\) be not both zero.  The projective locator pencil generated by \(A,B\) is
\[
        L_{[s:t]}(X)=sA(X)+tB(X),\qquad [s:t]\in\mathbb P^1(\F).
\]
Its fixed \(D\)-part is
\[
        G_D(A,B)=\gcd(A,B,\Lambda_D),
        \qquad g_D(A,B)=\deg G_D(A,B).
\]
A root of \(G_D(A,B)\) is a common root of every member of the pencil; these are precisely the roots assigned to the common-GCD branch in the first-match ledger.
\end{definition}

\begin{theorem}[moving-root bound for one-parameter split pencils]\label{thm:bc-moving-root}
Let \(D\subseteq\F\) have size \(n\), and let \(L_{[s:t]}=sA+tB\) be a projective locator pencil as in \cref{def:projective-locator-pencil}.  Put \(G=G_D(A,B)\) and \(g=\deg G\).  Let \(\mathcal Z\subseteq\mathbb P^1(\F)\), and suppose that for every \(\lambda=[s:t]\in\mathcal Z\), the polynomial \(L_\lambda/G\) has at least \(h\ge1\) distinct roots in \(D\setminus Z(G)\).  Then
\[
        |\mathcal Z|\le \left\lfloor\frac{n-g}{h}\right\rfloor .
\]
In particular, if every counted member has degree \(j\), has fixed \(D\)-part exactly \(G\), and is \(D\)-split, then
\[
        |\mathcal Z|\le
        \left\lfloor\frac{n-g}{j-g}\right\rfloor,
        \qquad j>g.
\]
The case \(j=g\) is not a moving split-pencil cell: all \(D\)-roots are fixed and the member belongs to the common-GCD branch.
\end{theorem}

\begin{proof}
Count incidences
\[
        I=\{(\lambda,x):\lambda\in\mathcal Z,
        \ x\in D\setminus Z(G),\ L_\lambda(x)=0\}.
\]
For a fixed moving root \(x\in D\setminus Z(G)\), the pair \((A(x),B(x))\) is not \((0,0)\).  Hence the homogeneous linear equation
\[
        sA(x)+tB(x)=0
\]
has exactly one solution \([s:t]\in\mathbb P^1(\F)\).  Thus each moving domain point contributes to at most one incidence, and \(|I|\le n-g\).  On the other hand, every \(\lambda\in\mathcal Z\) contributes at least \(h\) incidences by hypothesis, so \(|I|\ge h|\mathcal Z|\).  This proves the first bound.

If a counted member is \(D\)-split of degree \(j\) and has fixed \(D\)-part exactly \(G\), then exactly \(j-g\) of its \(D\)-roots are moving roots in \(D\setminus Z(G)\).  Applying the first bound with \(h=j-g\) gives the displayed inequality.  If \(j=g\), no moving root remains; the split condition has already been paid by the common-GCD branch rather than by a primitive moving pencil.
\end{proof}

\begin{corollary}[BC is settled on primitive one-parameter locator pencils]\label{cor:bc-one-pencil}
Consider an MCA split-pencil chart at agreement \(m\), and write \(\omega=n-m\).  Suppose that after the first-match tangent, common-support, quotient, extension, degree-drop, and common-GCD branches have been removed, the residual candidate error locators in this chart are represented by a projective locator pencil \(L_\lambda=sA+tB\), with the slope parameter injecting into \(\lambda\), and that every residual bad slope in the chart has at least one degree-\(\omega\) \(D\)-split locator in the pencil.  Then the number of residual bad finite slopes in this chart is at most
\[
        \left\lfloor\frac{n-g}{\omega-g}\right\rfloor,
        \qquad g=g_D(A,B)<\omega .
\]
In the primitive case \(g=0\), this is \(\lfloor n/(n-m)\rfloor\).  For the two active MCA adjacent rows in \cref{tab:active-frontier-rows},
\[
\begin{array}{c|c|c|c}
\text{row} & m=a_+ & \omega=n-m & \lfloor n/\omega\rfloor\\ \hline
\text{KoalaBear MCA} & 1116048 & 981104 & 2\\
\text{Mersenne-31 MCA} & 1116024 & 981128 & 2
\end{array}
\]
so every primitive one-parameter BC pencil contributes at most two finite bad slopes.
\end{corollary}

\begin{proof}
The first-match removals ensure that the chart is counted only through moving roots of the displayed pencil.  A residual bad slope supplies at least one degree-\(\omega\) split locator, and the slope-to-pencil parameter is injective by hypothesis; hence the slope count is bounded by the number of split parameters.  Apply \cref{thm:bc-moving-root} with \(j=\omega\).  The displayed row values use \(n=2^{21}\), \(a_+=1116048\) for KoalaBear MCA, and \(a_+=1116024\) for Mersenne-31 MCA.
\end{proof}


\begin{definition}[saturated codeword rays and support census]\label{def:saturated-rays}
Let \(C=\RS[\F,D,K]\), let \(U:D\to\F\), and put
\[
        S_c(U)=\{x\in D:U(x)=c(x)\},\qquad s_c(U)=|S_c(U)|
\]
for \(c\in C\).  The saturated ray set at agreement \(m\) is
\[
        \operatorname{Ray}(U;m)=\{c\in C:s_c(U)\ge m\}.
\]
Let \(\omega=n-m\), and define the support-locator census
\[
\begin{aligned}
\Cen(U;m)=\#\{(W,N)\in \F[X]^2:\;& W\text{ monic},\ \deg W=\omega,\ W\mid \ell_D,\\
        & WU=N\text{ on }D,\quad W\mid N,\quad \deg(N/W)<K\}.
\end{aligned}
\]
Equivalently, \(W=\ell_{D\setminus T}\) for an agreement support \(T\subseteq D\) of size \(m\).
\end{definition}

\begin{theorem}[exact saturation identity]\label{thm:saturation}
With \(C=\RS[\F,D,K]\) and \(\Cen(U;m)\) as in \cref{def:saturated-rays}, for every word \(U:D\to\F\),
\[
        \Cen(U;m)=\sum_{c\in C}\binom{s_c(U)}m .
\]
Moreover, the support locators lying above a fixed codeword ray \(c\) are exactly
\[
        (W,N)=H\,(G_c,G_cc),
        \qquad
        G_c=\ell_{D\setminus S_c(U)},
        \qquad
        H\mid\ell_{S_c(U)},
        \qquad
        \deg H=s_c(U)-m .
\]
Consequently the fiber size of the forgetful map from support locators to saturated codeword rays is \(\binom{s_c(U)}m\) above \(c\).
\end{theorem}

\begin{proof}
Let \((W,N)\) be counted by \(\Cen(U;m)\).  Since \(W\) is monic, divides \(\ell_D\), and has degree \(n-m\), there is a unique \(m\)-set \(T\subseteq D\) such that \(W=\ell_{D\setminus T}\).  Since \(W\mid N\) and \(\deg(N/W)<K\), write \(N=Wc\) for a unique codeword \(c\in C\).  On every \(x\in T\), the value \(W(x)\) is nonzero; the identity \(WU=N=Wc\) on \(D\) therefore gives \(U(x)=c(x)\).  Thus \(T\subseteq S_c(U)\).

Conversely, if \(c\in C\) and \(T\subseteq S_c(U)\) has \(|T|=m\), then \(W=\ell_{D\setminus T}\) and \(N=Wc\) satisfy all defining conditions of \(\Cen(U;m)\).  For fixed \(c\), the number of such supports is \(\binom{s_c(U)}m\), and summing over \(c\) gives the first identity.

For the fiber statement, write \(G_c=\ell_{D\setminus S_c(U)}\).  If \(T\subseteq S_c(U)\), then
\[
        \ell_{D\setminus T}
        =\ell_{D\setminus S_c(U)}\ell_{S_c(U)\setminus T}
        =G_cH,
\]
where \(H=\ell_{S_c(U)\setminus T}\), hence \(H\mid\ell_{S_c(U)}\) and \(\deg H=s_c(U)-m\).  The converse is the same construction reversed, because every monic divisor \(H\) of \(\ell_{S_c(U)}\) of degree \(s_c(U)-m\) is the locator of \(S_c(U)\setminus T\) for a unique \(m\)-set \(T\subseteq S_c(U)\).
\end{proof}

\begin{corollary}[raw support BC is not the MCA object]\label{cor:raw-bc-fails}
In the setting of \cref{thm:saturation}, if \(U\) agrees with a single codeword \(c\) on \(n-d\) positions and with no other codeword on \(m\) or more positions, then
\[
        |\operatorname{Ray}(U;m)|=1,
        \qquad
        \Cen(U;m)=\binom{n-d}{m} .
\]
Thus an exponentially large raw support-locator family may represent one MCA ray.  A split-pencil proof for MCA must therefore count saturated primitive line-rays after quotient, prefix, tangent, and common-support branches have been paid; a raw support census is a list/moment object, not the final MCA numerator.
\end{corollary}

\begin{proof}
The ray statement is the hypothesis.  The support-census identity is \cref{thm:saturation} with one nonzero summand \(\binom{s_c(U)}m=\binom{n-d}m\).  The final sentence is just the same equality interpreted in MCA terms: MCA counts a bad slope once, whereas \(\Cen(U;m)\) counts all size-\(m\) supports below the same saturated agreement ray.
\end{proof}

\begin{definition}[line rays]\label{def:line-rays}
In the setting of \cref{def:saturated-rays}, for an affine line \(U_Z=u+Zv\) and a set of finite slopes \(E\subseteq\F\), define
\[
        \LineRay_E(u,v;m)
        =
        \{(z,c)\in E\times C:\ |\{x\in D:u(x)+zv(x)=c(x)\}|\ge m\}.
\]
Write \(s_{z,c}=|\{x\in D:u(x)+zv(x)=c(x)\}|\).
\end{definition}

\begin{proposition}[line-ray saturation identity]\label{prop:line-ray-saturation}
With notation as in \cref{def:line-rays}, for every \(E\subseteq\F\),
\[
        \sum_{z\in E}\Cen(U_z;m)
        =
        \sum_{(z,c)\in\LineRay_E(u,v;m)}\binom{s_{z,c}}m .
\]
Consequently
\[
        |\{z\in E:\exists c\ (z,c)\in\LineRay_E(u,v;m)\}|
        \le
        |\LineRay_E(u,v;m)|
        \le
        \sum_{z\in E}\Cen(U_z;m).
\]
The two inequalities are the exact deduplication losses between raw support locators, saturated codeword rays, and slope numerators.
\end{proposition}

\begin{proof}
Apply \cref{thm:saturation} separately to the word \(U_z=u+zv\) for each \(z\in E\), and then sum over \(z\).  The first inequality forgets the codeword coordinate of a line ray, and the second follows because each line ray has \(s_{z,c}\ge m\), hence contributes at least one support to the right-hand side of the identity.  \Cref{cor:raw-bc-fails} shows that the second inequality can be exponentially loose for a single slope and a single codeword ray, so an MCA upper ledger must either count slopes directly or control this saturation factor.
\end{proof}

\begin{theorem}[Q discharges the shift-pair ledger]\label{thm:q-implies-sp}
Let \(N_w(z)=|\Fib_w(z)|\), let
\[
        \overline F=\binom nm |\B|^{-w},
\]
and let \(P_e\) denote the full off-diagonal shift-pair stratum in the imported decomposition \eqref{eq:imported-second-moment}, namely
\[
        P_e=\sum_{\substack{R\subseteq D\\ |R|=m-e}}\operatorname{sp}_w(e;D\setminus R).
\]
If Q holds in max-fiber form with constant \(\kappa\),
\[
        \max_z N_w(z)\le \kappa\overline F,
\]
then necessarily \(\kappa\overline F\ge1\) whenever \(\binom Dm\) is nonempty, and
\[
        \sum_{e=w+1}^{\min(m,n-m)}P_e
        \le
        \left(\kappa-\frac{1}{\overline F}\right)\binom nm\,\overline F .
\]
Every quotient-removed or primitive shift-pair subledger satisfies the same upper bound.  Hence SP is not an independent residual input in any closing theorem that already proves Q as a max-fiber theorem.
\end{theorem}

\begin{proof}
The imported exact second-moment identity \eqref{eq:imported-second-moment} says
\[
        \sum_z N_w(z)^2
        =\binom nm+
        \sum_{e=w+1}^{\min(m,n-m)}P_e .
\]
On the other hand,
\[
        \sum_zN_w(z)^2
        \le (\max_zN_w(z))\sum_zN_w(z)
        \le \kappa\overline F\binom nm,
\]
because \(\sum_zN_w(z)=\binom nm\).  Since at least one fiber is nonempty when \(\binom Dm\ne\varnothing\), the hypothesis also implies \(\kappa\overline F\ge1\), so the displayed right-hand side is nonnegative in the nonvacuous case.  Subtracting the diagonal term \(\binom nm\) gives the displayed inequality.  Any primitive or quotient-removed ledger is a sub-sum of the full off-diagonal ledger, so it is bounded a fortiori.
\end{proof}


\begin{theorem}[SP: unconditional primitive shift-pair bound]\label{thm:sp-proper}
Use the notation of the imported exact second-moment ledger.  For \(w+1\le e\le\min(m,n-m)\), put
\[
        T_e(n,m)=\binom n{m-e}\binom{n-m+e}{e}\binom{n-m}{e}.
\]
Then the total off-diagonal contribution at distance \(e\) satisfies
\[
        P_e^{\rm quot}+P_e^{\rm prim}\le T_e(n,m).
\]
If \(D\subseteq\B\), then the top stratum \(e=w+1\) also satisfies the sharper constant-shift bound
\[
        P_{w+1}^{\rm quot}+P_{w+1}^{\rm prim}
        \le
        (|\B|-1)\binom n{m-w-1}\binom{n-m+w+1}{w+1}.
\]
Consequently
\[
        \Gamma_2
        \le
        \frac{1}{\overline F}
        +\frac{\sum_{e=w+1}^{\min(m,n-m)}T_e(n,m)}{\binom{n}{m}\overline F},
\]
with the option of replacing the \(e=w+1\) term by the sharper displayed top-stratum bound.
\end{theorem}

\begin{proof}
Fix \(e\).  In the imported exact second-moment decomposition \eqref{eq:imported-second-moment}, an off-diagonal pair is encoded by a common part \(R\subseteq D\) of size \(m-e\), then by two disjoint degree-\(e\) root sets inside \(D\setminus R\).  There are \(\binom n{m-e}\) choices for \(R\).  Once \(R\) is fixed, the ambient set \(D\setminus R\) has size \(n-m+e\); the first root set has at most \(\binom{n-m+e}{e}\) choices and the second, disjoint from it, has at most \(\binom{n-m}{e}\) choices.  This ignores the depth equation and the quotient/primitive first-match assignment, so it is an upper bound for \(P_e^{\rm quot}+P_e^{\rm prim}\).

When \(e=w+1\), the imported decomposition \eqref{eq:imported-second-moment} shows that every top-stratum shift pair has the form \(A-B=c\in\F^\times\).  If both polynomials split over \(D\subseteq\B\), then both have coefficients in \(\B\), hence \(c\in\B^\times\).  For each fixed \(R\), choose \(A\) by choosing its \(e\)-element root set in \(D\setminus R\), and choose \(c\in\B^\times\); the polynomial \(B=A-c\) is then determined.  Requiring \(B\) to split over \(D\setminus R\), to be disjoint from \(A\), and then assigning the pair to either the quotient or primitive ledger can only reduce the count.  This gives the top-stratum bound.  The displayed \(\Gamma_2\) inequality is the imported exact second-moment ledger with the total quotient-plus-primitive off-diagonal contribution in every stratum replaced by the just-proved upper bound.
\end{proof}


\begin{proposition}[size of the proper Q bound at the active adjacent rows]\label{prop:proper-q-gap}
At the four active adjacent agreements, the imported Q packing estimate \cite[Secs.~19--21]{CAP25v132} gives the following one-term upper bounds for the remaining normalized prefix overhead:
\[
\begin{array}{c|ccc}
\text{row} & w & \log_2 R_Q^{\rm pack}\text{ allowed by the bound} & \text{spare margin}\\
\hline
\text{KoalaBear MCA} & 67471 & 1660789.024 & 22.1969\\
\text{KoalaBear list} & 67471 & 1660789.017 & 22.0109\\
\text{Mersenne-31 MCA} & 67447 & 1660926.120 & 3.2589\\
\text{Mersenne-31 list} & 67447 & 1660926.114 & 3.0730 .
\end{array}
\]
Thus the unconditional packing proof is a real theorem but is far too weak to supply the adjacent safe ledger.
\end{proposition}

\begin{proof}
For each row, \(n=2097152\), \(K=k+1=1048577\) on the MCA route, \(K=k=1048576\) on the list route, and \(w=a_+-K\).  The base-field orders are \(2^{31}-2^{24}+1\) for KoalaBear and \(2^{31}-1\) for Mersenne-31.  The imported Q packing inequality \cite[Secs.~19--21]{CAP25v132} gives
\[
        \log_2 R_Q^{\rm pack}
        \le
        w\log_2|\B|-\log_2\binom{a_+}{\lfloor w/2\rfloor}
             -\log_2\binom{n-a_+}{\lfloor w/2\rfloor}.
\]
Substituting the exact field orders and
\[
        a_+\in\{1116048,1116047,1116024,1116023\}
\]
gives the displayed values.  For these four rows the Johnson-ball summand
\[
        J_i=\binom{a_+}{i}\binom{n-a_+}{i}
\]
is increasing on \(0\le i\le t\).  Indeed
\[
        \frac{J_i}{J_{i-1}}
        =
        \frac{(a_+-i+1)(n-a_+-i+1)}{i^2},
\]
and at \(i=t\) this ratio is already \(>900\) in all four rows, while the ratio is larger for smaller \(i\).  Hence \(V_t(n,a_+)\le(t+1)J_t\), so replacing the one-term denominator by the full ball can lower the displayed logarithmic upper bound by less than \(\log_2(t+1)<16\) bits.  This is negligible compared with the gap between the displayed million-bit overhead and the row margins.
\end{proof}


\begin{definition}[row-sharp Q atom bound]\label{def:q-row-atom}
Fix a deployed adjacent row, let \(a_+\) be its adjacent agreement, let \(K\) be the list dimension used on that route, and put \(w=a_+-K\).  For a first-match residual prefix-boundary family \(\mathcal P_Q(z)\subseteq\Fib_w(z)\), define
\[
        R_Q^{\max}
        =
        |\B|^w\max_z\frac{|\mathcal P_Q(z)|}{\binom n{a_+}}.
\]
The row-sharp Q atom bound with bit margin \(\Delta_Q\) is
\[
        R_Q^{\max}\le 2^{\Delta_Q}.
\]
Equivalently, if the entire row budget is hypothetically assigned to Q, the sufficient integer form is
\[
        \max_z|\mathcal P_Q(z)|\le B^* .
\]
Any non-Q cell paid in the same first-match ledger only decreases the available \(\Delta_Q\).
\end{definition}

\begin{proposition}[exact finite Q atom target at the four adjacent rows]\label{prop:q-exact-target}
At the active adjacent agreements, the full-budget Q atom target is as follows:
\[
\begin{array}{c|r|r|r|r}
\text{row} & w & \left\lceil \binom n{a_+}|\B|^{-w}\right\rceil & B^* & B^*/\left\lceil \binom n{a_+}|\B|^{-w}\right\rceil\\
\hline
\text{KoalaBear MCA} & 67471 & 57198030366 & 274980728111395087 & 4807520.9295\\
\text{KoalaBear list} & 67471 & 65065153468 & 274980728111395087 & 4226236.5253\\
\text{Mersenne-31 MCA} & 67447 & 1752700 & 16777215 & 9.5722\\
\text{Mersenne-31 list} & 67447 & 1993678 & 16777215 & 8.4152
\end{array}
\]
In bits, these are exactly the spare margins already printed in the row table:
\[
        22.1969,
        \quad 22.0109,
        \quad 3.2589,
        \quad 3.0730 .
\]
Thus the binding Q problem is the Mersenne-31 list row: after all first-match payments, the remaining primitive prefix-boundary atom must be at most about \(8.42\) times its average size, and less if any other cell consumes budget.
\end{proposition}

\begin{proof}
For each row, substitute \(n=2^{21}\), \(k=2^{20}\), the displayed adjacent agreement \(a_+\), and \(K=k+1\) on the MCA route and \(K=k\) on the list route.  The average prefix fiber is \(\binom n{a_+}|\B|^{-w}\), and the integer lower-route replay uses its ceiling.  The budgets are
\[
        B^*_{\rm KB}=\left\lfloor\frac{(2^{31}-2^{24}+1)^6}{2^{128}}\right\rfloor,
        \qquad
        B^*_{\rm M31}=\left\lfloor\frac{(2^{31}-1)^4}{2^{100}}\right\rfloor .
\]
The displayed ratios are the exact integer quotients evaluated as decimals.  Taking base-two logarithms of \(B^*/(\binom n{a_+}|\B|^{-w})\) gives the four printed bit margins.
\end{proof}


\begin{proposition}[Exact fixed-union payments at the active rows]
\label{prop:active-fixed-union-payments}
Let \(t=n-a_+\).

\textup{(a) Fixed-word Q and list charts.}
Let \(K=k+1\) on an MCA route and \(K=k\) on a list route, put
\(R_Q=n-K\), and let \(\mathcal A\) be a subfamily of one boundary-Q
prefix fiber, or of one arbitrary-word list, whose error supports are all
contained in a fixed union \(U\) of size \(R_Q+\nu\).  Then
\cref{thm:fixed-union-list-johnson} gives a full-budget payment for every
integer nullity in the ranges below:
\[
\begin{array}{c|r|r|r|r}
\text{row} & R_Q & R_Q-t & 0\le\nu\le &
 \max\limits_{\nu\text{ in range}}|\mathcal A|\\ \hline
\text{KoalaBear MCA}  &1048575&67471&4983&94008\\
\text{KoalaBear list} &1048576&67471&4983&94632\\
\text{Mersenne-31 MCA}&1048575&67447&4980&3555853\\
\text{Mersenne-31 list}&1048576&67447&4980&4735771
\end{array}
\tag{FU-Q/list}\label{eq:active-fixed-union-list}
\]
Every number in the last column is below the corresponding challenge
budget \(B^*\) of \cref{prop:q-exact-target}.  In particular, a global Q
counterexample at the binding Mersenne-31 list row cannot be contained in
one support union of nullity at most \(4980\).

\textup{(b) Fixed-line MCA charts.}
For the actual MCA code, \(R=n-k=1048576\).  The unconditional
multiplicity compiler \cref{thm:fixed-union-ray} pays the following fixed
unions within the full row budget:
\[
\begin{array}{c|r|r|r}
\text{row}&0<\nu\le&
 \max\limits_{\nu\text{ in range}}|Z|&B^*\\ \hline
\text{KoalaBear MCA}&2&2847909263951&274980728111395087\\
\text{Mersenne-31 MCA}&1&8150817&16777215
\end{array}
\tag{FU-MCA}\label{eq:active-fixed-union-mca}
\]
If the direction is rank-regular on its union, so that
\(d_U(y_1)=R\), the directional compiler
\cref{cor:rank-regular-fixed-union-ray} pays the much larger ranges
\[
\begin{array}{c|r|r}
\text{row}&0\le\nu\le&
 \max\limits_{\nu\text{ in range}}|Z|\\ \hline
\text{KoalaBear MCA}&4982&94008\\
\text{Mersenne-31 MCA}&4979&3555853
\end{array}
\tag{FU-MCA-reg}\label{eq:active-rank-regular-mca}
\]
The direction-defect threshold of
\cref{cor:quantitative-direction-defect} pays more than the rank-regular
case.  With the full row budget, selected exact thresholds are
\[
\begin{array}{c|rrrrrrr}
\text{KoalaBear }\nu&0&1000&4000&4500&4979&4980&4982\\ \hline
J_{B^*}(\nu)&4341&3466&853&418&3&2&0
\end{array}
\tag{FU-KB-def}\label{eq:active-kb-direction-defect}
\]
and
\[
\begin{array}{c|rrrrr}
\text{Mersenne-31 }\nu&0&1000&4000&4500&4979\\ \hline
J_{B^*}(\nu)&4338&3463&849&415&0
\end{array}
\tag{FU-M31-def}\label{eq:active-m31-direction-defect}
\]
Thus an unpaid fixed-union MCA chart is either above the displayed
nullity range or has defect \(j>J_{B^*}(\nu)\); it need not be declared
exceptional merely because \(j>0\).  At the Mersenne row, two disjoint
one-circuit charts cost at most
\(2\cdot8150817=16301634<16777215\), leaving \(475581\) units of the
full budget.
\end{proposition}

\begin{proof}
For a boundary-Q fiber, the imported exact witness-list dictionary
\cite[Secs.~18--21]{CAP25v132} associates to every support a distinct
codeword of \(\RS[\F,D,K]\) agreeing with one received word on that
support.  Hence a subfamily whose error supports lie in \(U\) is a subset
of the affine syndrome fiber \(\mathcal L_U(y,t)\) in
\cref{thm:fixed-union-list-johnson}.  The same statement is tautological
for an arbitrary-word list.  Substituting \(N=R_Q+\nu\) and
\(h=N-t\) into \eqref{eq:fixed-union-list-johnson}, and evaluating every
integer in the displayed ranges, gives \eqref{eq:active-fixed-union-list}.
At the next nullity the Johnson denominator is nonpositive in every row:
\(\nu=4984\) for KoalaBear and \(\nu=4981\) for Mersenne-31.

For MCA, substitute \(R=1048576\) and the two deployed values of \(t\)
into \eqref{eq:fixed-union-ray}.  The largest full-budget nullities are
\(2\) and \(1\), giving \eqref{eq:active-fixed-union-mca}.  Under rank
regularity, substitute the same row data into
\eqref{eq:rank-regular-fixed-union-ray}; its denominator is positive
through \(\nu=4982\) and \(4979\), respectively, and the displayed maxima
occur at the final integer in each range.  Finally substitute the row
budgets into \eqref{eq:direction-defect-threshold} to obtain
\cref{eq:active-kb-direction-defect,eq:active-m31-direction-defect}.
All comparisons are exact integer comparisons and are reproduced by the
release verifier.
\end{proof}

\begin{proposition}[Exact recursive affine-span payments at the active rows]
\label{prop:active-affine-span-payments}
In the boundary-Q witness list, or in an arbitrary-word list for the same
route, suppose the associated codewords lie in one affine subspace of
\(\RS[\F,D,K]\) of dimension \(s\).  The recursive compiler
\cref{thm:affine-span-list} gives the following full-budget payments:
\[
\begin{array}{c|r|r|r}
\text{row}&0\le s\le&
 \max\limits_{s\text{ in range}}|\mathcal L_{\mathcal A}|&
 \text{compiler value at the next }s\\ \hline
\text{KoalaBear MCA}&14&47876303026096432&743896698428332665\\
\text{KoalaBear list}&14&47876942243704279&743907339955962922\\
\text{Mersenne-31 MCA}&6&14115447&219426634\\
\text{Mersenne-31 list}&6&14115528&219428099
\end{array}
\tag{AF-Q/list}\label{eq:active-affine-span-list}
\]
The middle column is below the corresponding full challenge budget in
every row.  The final column only records that this compiler no longer
fits at dimension \(15\) or \(7\); it is not a lower bound on an actual
list.  Consequently a Q counterexample surviving the full-budget payments
must have affine codeword-span dimension at least \(15\) on a KoalaBear
row and at least \(7\) on a Mersenne-31 row.
\end{proposition}

\begin{proof}
Apply \cref{thm:affine-span-list} with \(m=a_+\), with \(K=k+1\) on an
MCA boundary route and \(K=k\) on a list route.  Evaluate the single
rational expression in \eqref{eq:affine-span-list} by exact integer
products.  The value is increasing over each displayed range, so the
maximum occurs at its last dimension.  Comparison with the exact budgets
in \cref{prop:q-exact-target} gives the claim; the next-dimension values
mark the limit of the recursive compiler.
\end{proof}

\begin{proposition}[Exact affine-span MCA payments at the active rows]
\label{prop:active-affine-span-mca}
Assume \eqref{eq:direction-list-separated}.  If the codeword explanations
of an MCA chart lie in one affine subspace of the actual
\(\RS[\F,D,k]\) code of dimension \(s\), then
\cref{thm:affine-span-mca} gives
\[
\begin{array}{c|r|r|r}
\text{row}&1\le s\le&
 \max\limits_{s\text{ in range}}|Z|&
 \text{compiler value at the next }s\\ \hline
\text{KoalaBear MCA}&11&49107626893329409&1526096478566110535\\
\text{Mersenne-31 MCA}&4&1756139&54600050
\end{array}
\tag{AF-MCA}\label{eq:active-affine-span-mca}
\]
Both in-range maxima fit the full challenge budget.  Thus a surviving
separated-direction MCA chart has codeword affine-span dimension at least
\(12\) on KoalaBear and at least \(5\) on Mersenne-31, unless it has
already been paid by another cell.  If separation fails, the residual is
the explicit direction-list cell of \eqref{eq:direction-list-separated}.
\end{proposition}

\begin{proof}
Substitute \(K=k\), \(m=a_+\), and the exact row budgets into
\eqref{eq:affine-span-mca}.  Exact falling- and rising-product arithmetic
gives the displayed values.  At the next dimensions this compiler exceeds
the full budget, which records only the limit of the estimate.
\end{proof}


\begin{proposition}[Exact rank-flat and common-zero reductions at the active rows]
\label{prop:active-rank-flat-common-zero}
Consider the first affine dimensions not paid by
\cref{prop:active-affine-span-payments}: \(s=15\) on KoalaBear and
\(s=7\) on Mersenne-31.  If such an affine Q/list chart exceeds the full
row budget, \cref{cor:rank-flat-concentration} forces a proper direction
subcode with the following coarse support ceiling:
\[
\begin{array}{c|r|r|r|r}
\text{row}&s&\Theta^{\rm coarse}_{s,B^*}&d_j\le&d_j-(n-K)\le\\ \hline
\text{KoalaBear MCA}&15&152252&1133356&84781\\
\text{KoalaBear list}&15&152252&1133357&84781\\
\text{Mersenne-31 MCA}&7&232423&1213551&164976\\
\text{Mersenne-31 list}&7&232423&1213552&164976
\end{array}
\tag{RF-active}\label{eq:active-rank-flat}
\]
Thus an over-budget first-unpaid affine chart is not generalized-weight
uniform: it contains a proper direction subcode supported on a union much
smaller than the full domain.

There is also an exact common-zero refinement beyond the former
fixed-union boundary.  Write the common-zero set of the affine direction
space as \(z=K-\nu\), and let \(b\) be the number of those coordinates on
which the common affine value disagrees with the received word.  At the
first nullity not paid by \cref{prop:active-fixed-union-payments}, the
common-zero Johnson compiler gives
\[
\begin{array}{c|r|r|r|c}
\text{row}&\nu&\min b&\text{bound}&\text{residual }b\\ \hline
\text{KoalaBear MCA}&4984&2&537111&b\le1\\
\text{KoalaBear list}&4984&2&558125&b\le1\\
\text{Mersenne-31 MCA}&4981&7&590532&b\le6\\
\text{Mersenne-31 list}&4981&7&616024&b\le6
\end{array}
\tag{CZ-active}\label{eq:active-common-zero}
\]
At nullity \(5000\), the corresponding paid mismatch thresholds are
\(b\ge102\) on the two KoalaBear rows and \(b\ge126\) on the two
Mersenne-31 rows.
\end{proposition}

\begin{proof}
For \eqref{eq:active-rank-flat}, use the coarse form of
\cref{cor:rank-flat-concentration}.  The integer roots are
\[
 \left\lfloor
 \left(
 \frac{n^{\underline{15}}}{(B^*_{\rm KB}+1)(67471+15)}
 \right)^{1/14}
 \right\rfloor=152252
\]
and
\[
 \left\lfloor
 \left(
 \frac{n^{\underline 7}}{(B^*_{\rm M31}+1)(67447+7)}
 \right)^{1/6}
 \right\rfloor=232423.
\]
Adding the exact radii \(t=n-a_+\) gives the support and nullity ceilings
in the table.

For \eqref{eq:active-common-zero}, substitute the row data into
\eqref{eq:common-zero-nu} and choose the least nonnegative integer \(b\)
for which the denominator is positive and the integer floor is at most the
row budget.  All displayed comparisons, including the nullity-
\(5000\) thresholds, are exact and are reproduced by the verifier.
\end{proof}

\begin{proposition}[Exact codimension-one recursion at the active rows]
\label{prop:active-codim-one}
Consider a first-unpaid affine Q/list chart: dimension \(15\) on a
KoalaBear route and dimension \(7\) on a Mersenne-31 route.  Suppose the
low-support direction subcode forced by
\cref{prop:active-rank-flat-common-zero} has support closure of codimension
one in the chart direction space.  Write \(j=14\) or \(j=6\) for the
dimension of that support-saturated hyperplane, \(d\) for its support
size, \(e\) for the support increment to the whole chart, and \(b_0\) for
the common mismatch count outside the whole support.  Then the exact
full-budget payments are
\[
\begin{array}{c|r|r|r|r|r}
\text{row}&j&d-(n-K)\le&e\text{ paid from}&b_0\text{ paid from}
 &\text{largest residual nullity}\\ \hline
\text{KoalaBear MCA}&14&84781&8565&9813&93345\\
\text{KoalaBear list}&14&84781&8565&9813&93345\\
\text{Mersenne-31 MCA}&6&164976&73266&40074&238241\\
\text{Mersenne-31 list}&6&164976&73267&40074&238242
\end{array}
\tag{CR-active}\label{eq:active-codim-one-ranges}
\]
Here ``\(e\) paid from'' means that every chart with at least that support
increment is below the full row budget, and similarly for \(b_0\).  The
largest residual nullity is \(d+e-(n-K)\) after both payments have failed.
More explicitly, every surviving codimension-one branch lies in
\begin{align}
 e&\le8564, & b_0&\le9812
 &&\text{on either KoalaBear route},
 \tag{CR-KB}\label{eq:active-codim-one-kb}\\
 e&\le73265, & b_0&\le40073
 &&\text{on the Mersenne-31 MCA route},
 \tag{CR-MCA}\label{eq:active-codim-one-mca}\\
 e&\le73266, & b_0&\le40073
 &&\text{on the Mersenne-31 list route}.
 \tag{CR-list}\label{eq:active-codim-one-list}
\end{align}
The corresponding certified maxima at the first paid integers are
\begingroup\scriptsize
\[
\begin{array}{c|r|r|r}
\text{row}&C_e&C_{b_0}&B^*\\ \hline
\text{KoalaBear MCA}&274959863953460332&274954310643125130&274980728111395087\\
\text{KoalaBear list}&274963447501329540&274957707108580869&274980728111395087\\
\text{Mersenne-31 MCA}&16777189&16776155&16777215\\
\text{Mersenne-31 list}&16777174&16776251&16777215
\end{array}
\tag{CR-budget}\label{eq:active-codim-one-budgets}
\]
\endgroup
where $C_e$ is the closed bound at the first paid support increment and
$C_{b_0}$ is the all-extender bound at the first paid mismatch count.
The immediately preceding integer fails for the displayed MDS-soft
certificate in every row; this records the sharp integer transition of
this compiler, not a lower bound on an actual list.
\end{proposition}

\begin{proof}
The support closure has the same support as the direction subcode supplied
by \cref{prop:active-rank-flat-common-zero}; hence its support size is in
the exact ranges
\[
\begin{array}{c|c}
\text{row}&d\text{ range}\\ \hline
\text{KoalaBear MCA}&1048589\le d\le1133356\\
\text{KoalaBear list}&1048590\le d\le1133357\\
\text{Mersenne-31 MCA}&1048581\le d\le1213551\\
\text{Mersenne-31 list}&1048582\le d\le1213552.
\end{array}
\]
For the MDS-soft profile \(\Pi\) of
\cref{cor:codim-one-mds-soft}, the largest initial factor is
\(A=d-t+b_0\) and \(Q=w+1+b_0\).  Uniformly over the displayed ranges,
\[
 (j-1)Q-A\ge
 \begin{cases}
 13\cdot67472-152252=724884,&\text{KoalaBear},\\
 5\cdot67448-232423=104817,&\text{Mersenne-31}.
 \end{cases}
\]
The final term grows by \((j-2)b_0\), so
\cref{lem:codim-one-profile-interpolation} proves profile interpolation
for every \(e\) and \(b_0\) in the active ranges.

The closed bound \eqref{eq:codim-one-closed} decreases with \(e\) and
with \(b_0\), while the all-extender bound
\eqref{eq:codim-one-all-extenders-mds} decreases with \(b_0\).  It
therefore suffices to use \(b_0=0\) for the support-increment payment and
to test the displayed mismatch threshold for the all-extender payment.
Exact rational comparison over every integer \(d\) in the four finite
ranges gives the maxima in \eqref{eq:active-codim-one-budgets}.  At the
preceding support increments the maxima are respectively
\[
274997419229066860,
\quad275001003273987385,
\quad16777303,
\quad16777288,
\]
and at the preceding mismatch counts they are
\[
275005816112956831,
\quad275009213214651183,
\quad16777247,
\quad16777343.
\]
Each exceeds its row budget.  Finally combine the support ceiling with
\(e\le e_{\rm paid}-1\) to obtain the residual nullities in
\eqref{eq:active-codim-one-ranges}.  The release verifier performs all
comparisons with exact integers.
\end{proof}




\begin{proposition}[Active higher-codimension flag payment]
\label{prop:active-support-flag}
Consider a first-unpaid affine Q/list chart: dimension $15$ on a
KoalaBear route and dimension $7$ on a Mersenne-31 route.  If the chart is
over the full row budget, choose a generalized-weight minimizer supplied
by \cref{cor:rank-flat-concentration}.  By
\cref{lem:weight-minimizer-saturated,lem:support-saturated-flag}, its
support closure admits the exact coset-free flag certificate of
\cref{thm:support-flag-recursion} in every codimension.

For support-closure codimension at least two, the coarse all-extender
certificate already pays every chart with
\begin{equation}
 b_0\ge70230
 \quad\text{on either KoalaBear route},
 \qquad
 b_0\ge108962
 \quad\text{on either Mersenne-31 route}.
 \label{eq:active-flag-mismatch}
\end{equation}
At the first paid integers, the worst exact bounds are
\[
\begin{array}{c|r|r|r}
\text{row}&b_0&\text{certified maximum}&B^*\\ \hline
\text{KoalaBear MCA}&70230&274974976450914526&274980728111395087\\
\text{KoalaBear list}&70230&274975238687487221&274980728111395087\\
\text{Mersenne-31 MCA}&108962&16776934&16777215\\
\text{Mersenne-31 list}&108962&16776950&16777215
\end{array}
\tag{HF-active}\label{eq:active-flag-budgets}
\]
The preceding mismatch integer fails the same uniform certificate, with
values respectively
\[
 275004931457252515,
 \quad275005193722392530,
 \quad16777600,
 \quad16777616.
\]
These are transitions of the all-extender flag certificate, not lower
bounds on actual lists.  Below \eqref{eq:active-flag-mismatch}, the exact
binary-pattern linear program \eqref{eq:flag-dual-bound} and the closed
tensor certificate \eqref{eq:flag-tensor-bound} remain available for the
actual support-layer profile.
\end{proposition}

\begin{proof}
The rank-flat conclusion supplies a generalized-weight minimizer of some
dimension $j<s$.  It is support-saturated by
\cref{lem:weight-minimizer-saturated}, and therefore has a
support-saturated flag to the whole chart by
\cref{lem:support-saturated-flag}.  For codimension at least two, use
\eqref{eq:flag-all-extender}, replace the flag-support product by
$(n-j)^{\underline{s-j}}$, and use the exact support ceilings in
\eqref{eq:active-rank-flat}.  The resulting bound is
\[
 \frac{d^{\underline j}(n-j)^{\underline{s-j}}}
 {(d-t+b_0)
  \prod_{i=1}^{j-1}(w+i+b_0)
  (w+1+b_0)^{s-j}}.
\]
For fixed $j$ its maximum over the allowed support interval occurs at an
endpoint: the ratio of the $d$-dependent factor at $d+1$ and $d$ changes
sign at most once, since the numerator of the comparison is
\[
 (j-1)d-j(t-b_0)+j-1.
\]
Checking the two endpoints for $1\le j\le13$ on KoalaBear and
$1\le j\le5$ on Mersenne-31 gives the exact transitions displayed above.
The independent verifier performs these integer comparisons without
floating point.
\end{proof}


\begin{proposition}[Exact paving-basis MCA payments at the active rows]
\label{prop:active-paving-payments}
Let \(j=R-d_U(y_1)\) be the direction defect of a separated fixed-union
MCA chart.  With the full row budget, the paving threshold of
\cref{cor:paving-threshold} is
\[
\begin{array}{c|rrrrr}
\text{KoalaBear }\nu&0\text{--}9&10&11&12&13\\ \hline
J_{B^*}^{\rm pav}(\nu)&67471&67468&67423&66715&55724
\end{array}
\tag{PAV-KB}\label{eq:active-paving-kb}
\]
and
\[
\begin{array}{c|rrrrr}
\text{Mersenne-31 }\nu&0\text{--}1&2&3&4&5\\ \hline
J_{B^*}^{\rm pav}(\nu)&67447&67432&67213&63797&10700.
\end{array}
\tag{PAV-M31}\label{eq:active-paving-m31}
\]
Consequently every separated KoalaBear direction defect is paid through
nullity \(9\).  At Mersenne nullity \(2\), only the top fifteen possible
defects \(67433\le j\le67447\) remain outside this compiler.  At every
nullity the certified range is the maximum of the paving threshold and the
directional-Johnson threshold in
\cref{eq:active-kb-direction-defect,eq:active-m31-direction-defect}.
\end{proposition}

\begin{proof}
Substitute \(R=1048576\), the deployed radii, and the exact row budgets
into \eqref{eq:paving-threshold}.  At the last paid defects in the nontrivial
columns, the paving bounds are respectively
\[
\begin{array}{c|r|r}
\nu&J_{B^*}^{\rm pav}(\nu)&\text{bound at }J_{B^*}^{\rm pav}(\nu)\\ \hline
10&67468&215264294199835875\\
11&67423&273052400452931367\\
12&66715&274631447525088415\\
13&55724&274966795861149003
\end{array}
\]
and
\[
\begin{array}{c|r|r}
\nu&J_{B^*}^{\rm pav}(\nu)&\text{bound at }J_{B^*}^{\rm pav}(\nu)\\ \hline
2&67432&15838845\\
3&67213&16764415\\
4&63797&16774561\\
5&10700&16776956
\end{array}
\]
The next defect exceeds the budget in every displayed nonterminal column.
All calculations use exact binomial integers.
\end{proof}

\begin{proposition}[moment-order floor for a finite Q proof]\label{prop:q-moment-order-floor}
Let
\[
        \tau=\frac{\sum_z|\mathcal P_Q(z)|}{\binom nm}\in(0,1]
\]
be the mass of the pruned residual relative to the full support slice.  A proof based only on the moment criterion of \cref{thm:moment-q} must satisfy the necessary condition
\[
        r\bigl(\Delta_Q-\log_2\tau\bigr)
        \ge w\log_2|\B| .
\]
In the full-mass case \(\tau=1\), this reduces to
\[
        r\ge\left\lceil\frac{w\log_2|\B|}{\Delta_Q}\right\rceil .
\]
For the active rows the corresponding full-mass floors are
\[
\begin{array}{c|r|r|r}
\text{row} & w & \Delta_Q\text{ bits} & \text{minimum }r\\
\hline
\text{KoalaBear MCA} & 67471 & 22.1969 & 94196\\
\text{KoalaBear list} & 67471 & 22.0109 & 94991\\
\text{Mersenne-31 MCA} & 67447 & 3.2589 & 641593\\
\text{Mersenne-31 list} & 67447 & 3.0730 & 680397
\end{array}
\]
Thus fixed moments cannot prove the finite adjacent rows in the full-mass model.  After first-match pruning, the displayed row floors remain applicable only when \(\tau=1\); otherwise the residual mass must be carried explicitly, or one must use an off-diagonal or falling-factorial moment or isolate sparse-heavy fibers as a separate cell.
\end{proposition}

\begin{proof}
Normalize the residual masses by the full slice and put
\(\mu(z)=|\mathcal P_Q(z)|/\binom nm\), so \(\sum_z\mu(z)=\tau\).  Convexity over at most \(|\B|^w\) prefix values gives
\[
        |\B|^{w(r-1)}\sum_z\mu(z)^r\ge\tau^r.
\]
In the notation of \cref{thm:moment-q}, this is \(\Gamma_r\ge\tau^r\).  The finite criterion requires
\[
        \log_2\Gamma_r+w\log_2|\B|\le r\Delta_Q .
\]
Substituting the lower bound and rearranging gives the stated necessary condition.  Setting \(\tau=1\) yields the table.  The numerical entries use the exact row prime in \(\log_2|\B|\).
\end{proof}

\begin{proposition}[the BC moving-root theorem does not pay boundary Q]\label{prop:bc-not-q}
In the boundary-Q profile of the imported boundary-Q dictionary \cite[Secs.~18--21]{CAP25v132}, the unknown divisor is
\[
        Q_z+A,
        \qquad
        \deg A\le \omega-w-1,
        \qquad
        \omega=n-a_+ .
\]
Thus the coefficient parameter space has dimension \(\omega-w\).  At the active rows this dimension is
\[
\begin{array}{c|r|r|r}
\text{row} & \omega=n-a_+ & w & \omega-w\\
\hline
\text{KoalaBear MCA} & 981104 & 67471 & 913633\\
\text{KoalaBear list} & 981105 & 67471 & 913634\\
\text{Mersenne-31 MCA} & 981128 & 67447 & 913681\\
\text{Mersenne-31 list} & 981129 & 67447 & 913682
\end{array}
\]
Therefore \cref{thm:bc-moving-root,cor:bc-one-pencil} cannot be applied directly to boundary Q: those theorems count split parameters on a projective one-parameter locator pencil, while Q is a high-dimensional affine divisor slice.  To route Q through BC one would need an additional theorem decomposing this affine slice into paid one-parameter pencils with a first-match bound on the number of relevant pencils.  No such theorem is present in this manuscript.
\end{proposition}

\begin{proof}
The imported boundary-Q dictionary \cite[Secs.~18--21]{CAP25v132} states exactly that a prefix fiber is counted by the divisibility condition \(Q_z+A\mid X^n-\beta\) with \(\deg A\le\omega-w-1\).  A polynomial of degree at most \(\omega-w-1\) has \(\omega-w\) free coefficients.  Substituting the four values of \(a_+\), \(K\), and \(w=a_+-K\) gives the table.  Since \(\omega-w\) is larger than nine hundred thousand in all four cases, the family is not a one-parameter pencil.  The moving-root theorem is still valid for every line inside this affine space, but a line-by-line decomposition without a bound on the number of lines gives no row budget.
\end{proof}



\part{Order-\texorpdfstring{$32$}{32} line rank and rational-atom classification}
\label{part:rank-atoms}
The rest of the paper changes the MCA completion mechanism.  Instead of adding many local cell budgets, it seeks a maximum-type classification: every large bad-slope set is either one global affine codeword line, one coherent rational atom, or one primitive spread family.  This part proves the exact rank dictionary, the dyadic quotient branch, low-degree and low-complexity atom extraction, and atom coherence.

\section{Rank-theoretic setup}
Let $D\subseteq\F$ consist of $n$ distinct evaluation points and let
\[
 C=\RS[\F,D,k]
 =\{(h(x))_{x\in D}:h\in\F[X],\ \deg h<k\}.
\]
Fix distinct finite slopes $\gamma_1,\ldots,\gamma_L$ and a received line $r_\gamma=r_0+\gamma r_1$.  Suppose $h_i\in\F[X]_{<k}$ agrees with $r_{\gamma_i}$ on a support $S_i$ of size $m$; shrinking supports to exact size $m$ does not affect the rank calculation.  Put
\[
 I_x=\{i:x\in S_i\}.
\]
The tuple is globally affine if $h_i=A+\gamma_iB$ for some $A,B\in\F[X]_{<k}$.

\section{The rank-two reduced intersection matrix}

\subsection{Local relation spaces}

For $I\subseteq[L]$, define
\[
 \cK_\gamma(I)
 :=\left\{c\in\F^L:
 \supp(c)\subseteq I,\quad
 \sum_{i=1}^Lc_i=0,\quad
 \sum_{i=1}^Lc_i\gamma_i=0
 \right\}.
\]
Since the slopes are distinct,
\[
 \dim\cK_\gamma(I)=(|I|-2)_+.
\]
Let $v_k(x)=\vander{x}{k}\in\F^k$.

\begin{definition}[rank-two reduced intersection matrix]\label{def:r2rim}
Choose any basis $\mathcal B_x$ of $\cK_\gamma(I_x)$ for every $x\in D$.  The matrix
\[
 \cM^{(2)}(D,\mathcal S,\gamma)
\]
has $Lk$ columns, grouped into $L$ blocks of length $k$, and one row
\[
 c\otimes v_k(x)
\]
for every $x\in D$ and $c\in\mathcal B_x$.
\end{definition}

Changing the local bases left-multiplies the corresponding row blocks by invertible matrices, so the kernel and rank are intrinsic.

\begin{theorem}[exact kernel dictionary]\label{thm:kernel-dictionary}
For $h_i\in\F[X]_{<k}$, let $\mathbf h$ be the concatenated coefficient vector.  Then
\[
 \mathbf h\in\ker\cM^{(2)}(D,\mathcal S,\gamma)
\]
if and only if, for every $x\in D$, there exist scalars $a_x,b_x\in\F$ such that
\[
 h_i(x)=a_x+\gamma_i b_x
 \qquad(i\in I_x).
\]
In particular, every family of codeword explanations of one received line belongs to the kernel.
\end{theorem}

\begin{proof}
For fixed $x$, the local equations are
\[
 \sum_{i\in I_x}c_i h_i(x)=0
 \qquad(c\in\cK_\gamma(I_x)).
\]
The orthogonal complement of $\cK_\gamma(I_x)$ in $\F^{I_x}$ is exactly
\[
 \Span\{\one_{I_x},(\gamma_i)_{i\in I_x}\}.
\]
Thus the local value vector is affine in the slope exactly when all local rows annihilate it.  Applying this independently at each coordinate proves the claim.  For a received line, take $a_x=r_0(x)$ and $b_x=r_1(x)$.
\end{proof}

\begin{proposition}[row count and trivial kernel]\label{prop:row-count}
The matrix has
\[
 \sum_{x\in D}(r_x-2)_+
 \ge Lm-2n
\]
rows.  It always contains the $2k$-dimensional kernel
\[
 h_i=A+\gamma_iB,
 \qquad A,B\in\F[X]_{<k}.
\]
Consequently its maximum useful rank is $(L-2)k$, and the equation surplus over the nontrivial unknown dimension is
\[
 \boxed{\ L(m-k)-2(n-k).\ }
\]
\end{proposition}

\begin{proof}
Since $(r-2)_+\ge r-2$,
\[
 \sum_x(r_x-2)_+
 \ge\sum_xr_x-2n
 =\sum_i|S_i|-2n
 =Lm-2n.
\]
A globally affine tuple satisfies every local relation.  Distinct slopes make the map $(A,B)\mapsto(A+\gamma_iB)_i$ injective, so this kernel has dimension $2k$.  Subtracting $(L-2)k$ from the row lower bound gives the displayed surplus.
\end{proof}

\section{Why the deployed critical order is exactly 32}

The actual Reed--Solomon dimension on both active MCA rows is
\[
 n=2^{21}=2097152,
 \qquad k=2^{20}=1048576.
\]
The adjacent safe agreements are
\[
 m_{\rm KB}=1116048,
 \qquad
 m_{\rm M31}=1116024.
\]

\begin{proposition}[critical order]\label{prop:critical-32}
For either deployed row,
\[
 L_*:=\left\lfloor\frac{2(n-k)}{m-k}\right\rfloor+1=32.
\]
More precisely,
\[
\begin{array}{c|r|r|r}
\toprule
\text{row}&m-k&31(m-k)-2(n-k)&32(m-k)-2(n-k)\\
\midrule
\text{KoalaBear MCA}&67472&-5520&61952\\
\text{Mersenne-31 MCA}&67448&-6264&61184\\
\bottomrule
\end{array}
\]
Thus order $31$ can remain underdetermined for dimension reasons, whereas order $32$ has a positive row surplus.
\end{proposition}

\begin{proof}
Direct substitution into \cref{prop:row-count}.
\end{proof}

\section{What full relative rank would buy}

\begin{theorem}[one global code-line block]\label{thm:global-block}
Let $Z$ be a set of bad slopes whose explaining codewords lie on one global codeword line,
\[
 h_\gamma=A+\gamma B.
\]
Assume the received line is support-wise MCA-bad at agreement $m$.  Then
\[
 \boxed{|Z|\le n-m+1.}
\]
\end{theorem}

\begin{proof}
Let
\[
 C_0:=\{x\in D:r_0(x)=A(x),\ r_1(x)=B(x)\},
 \qquad c:=|C_0|.
\]
MCA-badness gives $c<m$.  Outside $C_0$, the equation
\[
 r_0(x)-A(x)+\gamma(r_1(x)-B(x))=0
\]
has at most one finite solution $\gamma$.  Counting agreements over all $\gamma\in Z$ therefore yields
\[
 |Z|m\le |Z|c+(n-c).
\]
Hence
\[
 |Z|\le\frac{n-c}{m-c}\le n-m+1,
\]
where the last expression is the maximum over integers $0\le c\le m-1$.
\end{proof}

\begin{corollary}[conditional generic closure]\label{cor:generic-closure}
Suppose every $32$-subfamily of a set of bad explanations has full relative rank, meaning that the kernel of its rank-two matrix is exactly the global affine kernel.  Then all explanations lie on one global codeword line and
\[
 |Z|\le n-m+1.
\]
At the deployed rows the bounds are
\[
 981105
 \qquad\text{and}\qquad
 981129,
\]
respectively.
\end{corollary}

\begin{proof}
Any $32$ explanations are globally affine.  If there are more than $32$, fix two slopes and place any third slope in a $32$-subset containing the fixed pair; the unique codeword line through the fixed pair contains the third.  Apply \cref{thm:global-block}.
\end{proof}

The Mersenne-31 challenge numerator is $16777215$, so the generic order-$32$ branch would fit with more than fifteen million units of margin.  The difficult issue is therefore not the generic branch.  It is classification and exclusive payment of specialized rank defects.

\section{A necessary partition inequality}

The following obstruction identifies the correct rank-two analogue of the partition conditions in higher-order MDS theory.

For a partition $\cP$ of $[L]$, put
\[
 c(\cP):=\sum_{P\in\cP}\min\{2,|P|\},
\]
and for $I\subseteq[L]$ define
\[
 w_\cP(I)
 :=\sum_{P\in\cP}\min\{2,|I\cap P|\}-\min\{2,|I|\}.
\]

\begin{proposition}[partition obstruction]\label{prop:partition-obstruction}
If
\[
 \sum_{x\in D}w_\cP(I_x)<k\bigl(c(\cP)-2\bigr)
\]
for some partition $\cP$, then the rank-two matrix has kernel dimension strictly larger than $2k$.
Consequently full relative rank requires
\[
 \boxed{
 \sum_{x\in D}w_\cP(I_x)
 \ge k\bigl(c(\cP)-2\bigr)
 \quad\text{for every partition }\cP.
 }
\]
\end{proposition}

\begin{proof}
Consider tuples that are independently affine on each block of $\cP$: a singleton block contributes one free degree-$<k$ polynomial, and a block of size at least two contributes two.  This space has dimension $kc(\cP)$.  At coordinate $x$, forcing the blockwise-affine local values on $I_x$ to lie on one affine slope line imposes at most $w_\cP(I_x)$ scalar conditions.  Hence the intersection with the rank-two kernel has dimension at least
\[
 kc(\cP)-\sum_xw_\cP(I_x).
\]
Under the strict inequality this exceeds $2k$.
\end{proof}

For generic evaluation points, higher-order MDS and row-span constrained local-property machinery make closely related partition inequalities sufficient for the expected rank and for curve-decoding phenomena \cite{BGM23,GGSW26}.  The deployed domains are not generic.  The point of the next sections is to identify what specializations must be removed before a sufficiency theorem can be true.  Recent work explicitly notes that identifying deterministic Reed--Solomon evaluation sets with the random-evaluation curve-decoding behavior remains open \cite{GGSW26}.

\section{Exact dyadic quotient descent}

\begin{theorem}[pair descent on a multiplicative dyadic domain]\label{thm:pair-descent}
Assume $\operatorname{char}\F\ne2$ and
\[
 D=D_+\sqcup(-D_+).
\]
Suppose the incidence pattern is pair-invariant:
\[
 I_x=I_{-x}\qquad(x\in D_+).
\]
Write uniquely
\[
 h_i(X)=u_i(X^2)+Xv_i(X^2),
\]
where
\[
 \deg u_i<\left\lceil\frac{k}{2}\right\rceil,
 \qquad
 \deg v_i<\left\lfloor\frac{k}{2}\right\rfloor.
\]
Then the rank-two kernel on $D$ is naturally the direct sum of two rank-two kernels on the squared domain
\[
 D^{(2)}:=\{x^2:x\in D_+\},
\]
with the common incidence sets $I_x=I_{-x}$ and degree bounds $\lceil k/2\rceil$ and $\lfloor k/2\rfloor$.
In particular, every nontrivial pair-invariant defect descends to a nontrivial defect on the half-size quotient in at least one parity component.
\end{theorem}

\begin{proof}
Fix $x\in D_+$ and $c\in\cK_\gamma(I_x)=\cK_\gamma(I_{-x})$.  The two local equations are
\[
 \sum_i c_i\bigl(u_i(x^2)+xv_i(x^2)\bigr)=0,
 \qquad
 \sum_i c_i\bigl(u_i(x^2)-xv_i(x^2)\bigr)=0.
\]
Because $2x\ne0$, adding and subtracting gives
\[
 \sum_i c_i u_i(x^2)=0,
 \qquad
 \sum_i c_i v_i(x^2)=0.
\]
The converse follows by reversing the calculation.  The even/odd polynomial decomposition is a vector-space isomorphism, so the full kernel is the direct sum claimed.  The global affine kernels descend componentwise; hence any excess kernel dimension appears in at least one component.
\end{proof}

Iterating \cref{thm:pair-descent} proves exact descent for every fully periodic dyadic incidence atom.  This is the rigorous quotient branch of the proposed specialization theorem.  What fails is the assertion that every non-descending atom must be a simple pole.

\section{Rational atoms and profile depth}

Let
\[
 \Lambda_i(X):=\prod_{x\in S_i}(X-x)
\]
be the monic support locator of degree $m$.

\begin{definition}[scalar-locator rational atom]\label{def:rational-atom}
A family is a scalar-locator rational atom if there exist
\[
 Q,A,B\in\F[X],
 \qquad c_i=c_0+c_1\gamma_i,
\]
with $Q(x)\ne0$ for all $x\in D$, such that
\[
 \boxed{
 Qh_i+c_i\Lambda_i=A+\gamma_iB
 \qquad(i\in[L]).
 }
\]
\end{definition}

\begin{proposition}[rational atoms are MCA explanations]\label{prop:rational-to-mca}
Every atom of \cref{def:rational-atom} is explained by the rational received line
\[
 r_\gamma(x)=\frac{A(x)+\gamma B(x)}{Q(x)}.
\]
The codeword $h_i$ agrees with $r_{\gamma_i}$ on all roots of $\Lambda_i$.
\end{proposition}

\begin{proof}
At $x\in S_i$, the locator term vanishes and division by $Q(x)$ is valid.
\end{proof}

\begin{proposition}[converse under the scalar degree profile]\label{prop:mca-to-rational}
Put $m=k+d$.  Suppose
\[
 r_\gamma(x)=\frac{A(x)+\gamma B(x)}{Q(x)}
\]
on $D$, where $Q$ has no root in $D$, $\deg Q=s\le d$, and $\deg A,\deg B\le m$.  If $h_i\in\F[X]_{<k}$ agrees with $r_{\gamma_i}$ on the $m$ roots of $\Lambda_i$, then
\[
 A+\gamma_iB-Qh_i=c_i\Lambda_i
\]
for a scalar $c_i$, and $c_i$ is affine in $\gamma_i$.
\end{proposition}

\begin{proof}
The left side has degree at most $m$ and vanishes at the $m$ distinct roots of $\Lambda_i$, so it is a scalar multiple of $\Lambda_i$.  Since $\deg(Qh_i)\le k+s-1\le m-1$, its degree-$m$ coefficient is zero.  Comparing degree-$m$ coefficients gives
\[
 c_i=[X^m]A+\gamma_i[X^m]B.
\]
\end{proof}

\begin{corollary}[scaled-locator prefix depth]\label{cor:profile-depth}
Under the hypotheses of \cref{prop:mca-to-rational}, the coefficients of
\[
 c_i\Lambda_i
\]
in degrees
\[
 k+s,k+s+1,\ldots,m
\]
are affine functions of $\gamma_i$.  Apart from the leading scaling coefficient, this is a depth-$(d-s)$ affine prefix constraint.
\end{corollary}

\begin{proof}
The product $Qh_i$ has degree at most $k+s-1$, so the displayed high coefficients of $c_i\Lambda_i$ equal those of $A+\gamma_iB$.
\end{proof}

Thus a simple pole, $s=1$, is only one endpoint of a profile continuum.  At the opposite endpoint $s=d$, only the leading scaling is forced, while the locator residues modulo $Q$ must lie on a projective affine line.  Any correct rank-defect classification must account for the entire continuum or prove that the already-declared first-match cells remove all but selected endpoints.

\section{An exact degree-two rank defect over \texorpdfstring{$\F_{17}$}{F17}}

We now give a completely explicit obstruction to an unqualified ``quotient or simple pole'' theorem.

\begin{theorem}[degree-two support-wise MCA atom]\label{thm:f17-atom}
Let
\[
 \F=\F_{17},\qquad
 D=\mu_8=\{1,9,13,15,16,8,4,2\},
 \qquad k=4,\quad m=6.
\]
Take slopes
\[
 (\gamma_0,\gamma_1,\gamma_2,\gamma_3,\gamma_4)=(0,1,4,7,2)
\]
and supports
\[
\begin{array}{c|l}
 i&S_i\\
\midrule
0&\{1,15,16,8,4,2\}\\
1&\{1,9,13,15,16,8\}\\
2&\{1,13,15,16,4,2\}\\
3&\{1,9,15,16,4,2\}\\
4&\{1,9,13,15,8,4\}.
\end{array}
\]
Let
\[
\begin{aligned}
 h_0&=h_1=0,\\
 h_2&=9+13X+8X^2+4X^3,\\
 h_3&=3+10X+14X^2+7X^3,\\
 h_4&=11+8X+9X^2+6X^3.
\end{aligned}
\]
Define a received line by the following values, in the displayed order of $D$:
\[
\begin{array}{c|rrrrrrrr}
 x&1&9&13&15&16&8&4&2\\
\midrule
r_0(x)&0&16&6&0&0&0&0&0\\
 r_1(x)&0&1&11&0&0&0&5&12.
\end{array}
\]
Then:
\begin{enumerate}[label=\textup{(\roman*)}]
\item $h_i$ agrees with $r_0+\gamma_i r_1$ on $S_i$ for every $i$;
\item the received line is support-wise MCA-bad at agreement $m=6$;
\item the rank-two matrix has rank $11$, whereas full relative rank is $12$;
\item the defect is not first-level quotient-periodic;
\item it has no scalar-locator rational representation with $\deg Q\le1$, but it has one with $\deg Q=2$.
\end{enumerate}
\end{theorem}

\begin{proof}
Direct substitution proves (i).  For (ii), observe that $r_0$ is zero at exactly the six points $S_0$.  On any other six-point set, a degree-$<4$ polynomial agreeing with $r_0$ would have at least four zero roots and also take a prescribed nonzero value, which is impossible; with five zero roots the same conclusion is immediate.  Hence the only possible six-point common explanation set for the first coefficient is $S_0$.  On $S_0$, the word $r_1$ is zero at $1,15,16,8$ and nonzero at $4,2$, so no degree-$<4$ polynomial can agree with it there.  Thus no pair of codeword polynomials simultaneously explains the received line on six coordinates.

Part (i) and \cref{thm:kernel-dictionary} give a nontrivial kernel vector.  It is not globally affine because $h_0=h_1=0$ at slopes $0$ and $1$, while $h_2\ne0$.  Exact row reduction gives rank $11$; one $11\times11$ pivot minor has determinant $9\in\F_{17}^\times$.  This proves (iii).

For (iv), the incidence sets at $1$ and $-1=16$ are different: the former contains all five slopes, while the latter omits slope $\gamma_4$.  Thus the hypothesis of \cref{thm:pair-descent} fails already at the first dyadic level.

For (v), let
\[
\begin{aligned}
 Q&=12+3X+5X^2,\\
 A&=13+10X+7X^2+13X^3+5X^4+11X^5+9X^6,\\
 B&=7+5X+6X^2+14X^3+3X^4+15X^5+X^6,
\end{aligned}
\]
and $c_i=9+\gamma_i$.  The polynomial $Q$ is nonzero on every point of $D$, and exact multiplication gives
\[
 Qh_i+c_i\Lambda_i=A+\gamma_iB
 \qquad(i=0,\ldots,4).
\]
For a denominator bound $s$, the identities of \cref{def:rational-atom} form a homogeneous coefficient system in $Q,A,B,c_0,c_1$.  At $s=0$ and $s=1$ the matrices have full column ranks $17$ and $18$, respectively.  At $s=2$ the $35\times19$ system has rank $18$ and its one-dimensional kernel is generated by the displayed certificate.  Hence degree two is minimal within this atom model.
\end{proof}

\begin{remark}[the common-support qualifier is essential]\label{rem:common-factor}
The example has the common support factor
\[
 H=(X-1)(X-15)=X^2+X+15.
\]
It divides every locator and also $A,B,h_0,\ldots,h_4$.  Therefore \cref{thm:f17-atom} refutes an \emph{unqualified} quotient-or-pole theorem, but it does not refute a theorem stated only after the common-support first-match branch has been removed.  Instead, it proves that the qualifier cannot be omitted and that rational denominator profiles can be hidden inside common-support reductions.
\end{remark}

The incidence pattern also satisfies every partition inequality of \cref{prop:partition-obstruction}, with minimum slack $1$.  Thus the defect is a genuine specialization phenomenon rather than a failure of the obvious partition count.  This finite claim is included in the verifier.

\section{Maximal supports and the slope-degree barrier}

For each explanation, take its \emph{maximal} agreement support
\[
 \widehat S_i
 :=\{x\in D:h_i(x)=r_0(x)+\gamma_i r_1(x)\},
 \qquad |\widehat S_i|\ge m.
\]
Put
\[
 \widehat I_x:=\{i:x\in\widehat S_i\},
 \qquad
 C_\cap:=\bigcap_{i=1}^{L}\widehat S_i,
 \qquad c:=|C_\cap|.
\]

Let $R_0,R_1\in\F[X]_{<n}$ be the interpolation polynomials of $r_0,r_1$ on $D$.  Interpolating the codeword polynomials coefficientwise in the slope gives the unique polynomial
\[
 H(X,Z)\in\F[X,Z],
 \qquad
 \deg_X H<k,
 \qquad
 \deg_Z H<L,
\]
with
\[
 H(X,\gamma_i)=h_i(X)
 \qquad(i\in[L]).
\]
Define the slope-error polynomial
\[
 E(X,Z):=H(X,Z)-R_0(X)-ZR_1(X).
\]

\begin{lemma}[zero slope fibers are exactly common agreements]\label{lem:zero-fibers}
For $x\in D$,
\[
 E(x,Z)\equiv0
 \quad\Longleftrightarrow\quad
 x\in C_\cap.
\]
\end{lemma}

\begin{proof}
If $x\in C_\cap$, then $E(x,\gamma_i)=0$ for all $L$ distinct slopes.  Since $\deg_ZE(x,Z)<L$, the polynomial is zero.  Conversely, if $E(x,Z)$ is zero, then evaluating at every $\gamma_i$ gives
\[
 h_i(x)=R_0(x)+\gamma_iR_1(x)=r_0(x)+\gamma_i r_1(x),
\]
so $x$ belongs to every maximal support.
\end{proof}

\begin{theorem}[maximal-support slope-degree barrier]\label{thm:slope-degree}
Assume the explanations are not globally affine: there do not exist $A,B\in\F[X]_{<k}$ with
\[
 h_i=A+\gamma_iB
 \qquad(i\in[L]).
\]
Then $E\ne0$.  Writing
\[
 r:=\deg_ZE,
\]
one has $c<k$ and
\[
 \boxed{
 Lm\le Lc+r(n-c).
 }
\]
Equivalently,
\[
 \boxed{
 r\ge
 \ceil{\frac{L(m-c)}{n-c}}.
 }
\]
In particular, after the common-support branch is removed ($c=0$),
\[
 r\ge\ceil{\frac{Lm}{n}}.
\]
\end{theorem}

\begin{proof}
If $c\ge k$, choose two slopes and let $A,B\in\F[X]_{<k}$ be the unique codeword line through their polynomials.  For every $i$, the polynomial $h_i-A-\gamma_iB$ has degree $<k$ and vanishes on $C_\cap$, hence is zero.  This contradicts non-affinity, so $c<k$.

For $x\notin C_\cap$, \cref{lem:zero-fibers} says $E(x,Z)$ is nonzero.  It has the $|\widehat I_x|$ distinct roots $\gamma_i$ indexed by agreements at $x$, whence
\[
 |\widehat I_x|\le r.
\]
Counting maximal-support incidences gives
\[
 Lm
 \le\sum_i|\widehat S_i|
 =\sum_{x\in C_\cap}L+\sum_{x\notin C_\cap}|\widehat I_x|
 \le Lc+r(n-c).
\]
It remains only to justify that $E\ne0$.  If it were zero, then $H$ would be affine in $Z$ and all $h_i=H(X,\gamma_i)$ would lie on one global codeword line.
\end{proof}

\begin{corollary}[the active primitive degree is at least eighteen]\label{cor:degree-18}
For $L=32$ and either deployed adjacent row, a non-affine explanation with no common agreement coordinate satisfies
\[
 \boxed{18\le r\le31.}
\]
Indeed,
\[
 \ceil{\frac{32m_{\rm KB}}{n}}
 =
 \ceil{\frac{32m_{\rm M31}}{n}}
 =18.
\]
\end{corollary}

Thus every slope-degree-$\le17$ explanation is already global-affine or common-support.  This removes the entire low-degree branch before any determinant specialization argument begins.

\section{Local incidence complexity}

For the rational extraction theorem, choose exact $m$-subsupports
\[
 S_i\subseteq\widehat S_i,
 \qquad |S_i|=m,
\]
and set
\[
 I_x:=\{i:x\in S_i\},
 \qquad r_x:=|I_x|.
\]
Let $N_a$ count coordinates of incidence multiplicity $a$, let
\[
 N_{\ge2}:=|\{x:r_x\ge2\}|,
 \qquad
 U:=\bigcup_iS_i,
 \qquad u:=|U|.
\]

\begin{definition}[two-cover incidence complexity]\label{def:chi}
Define
\[
 \chi(\cS)
 :=\sum_{x\in D}\min\{2,r_x\}
 =N_1+2N_{\ge2}.
\]
Equivalently,
\[
 \boxed{
 \chi(\cS)=2u-N_1=2n-2N_0-N_1.
 }
\]
\end{definition}

\begin{proposition}[exact relation to the rank-two row count]\label{prop:chi-rows}
For exact $m$-supports,
\[
 \sum_{x\in D}(r_x-2)_+
 =Lm-\chi(\cS).
\]
\end{proposition}

\begin{proof}
At multiplicity zero or one, both sides contribute zero after subtracting $\min\{2,r_x\}$.  At multiplicity at least two, the difference is $r_x-2$.  Sum over $x$ and use $\sum_xr_x=Lm$.
\end{proof}

The quantity $\chi$ is the number of scalar conditions needed to force one common rational received line on the occupied coordinates: two conditions at a multiply occupied coordinate and one at a singleton.

\section{Support-collapsed rational interpolation}

Let
\[
 \Lambda_i(X):=\prod_{x\in S_i}(X-x)
\]
be the monic locator of $S_i$.

\begin{definition}[scalar-locator certificate]\label{def:certificate}
A scalar-locator certificate of denominator degree at most $s$ is a tuple
\[
 (Q,A,B,c_0,c_1)
\]
with
\[
 \deg Q\le s,
 \qquad
 \deg A,\deg B\le m,
\]
not all zero, such that, with $c_i=c_0+c_1\gamma_i$,
\[
 \boxed{
 Qh_i+c_i\Lambda_i=A+\gamma_iB
 \qquad(i\in[L]).
 }
\]
It is a rational atom when $Q\ne0$ and $(c_0,c_1)\ne(0,0)$, a pure locator pencil when $Q=0$, and globally affine when $(c_0,c_1)=(0,0)$.
\end{definition}

When $Q$ has no root on $D$, a rational atom is explained by the received line $(A+\gamma B)/Q$.  A root of $Q$ on $D$ is retained as a separate denominator-root first-match branch rather than being silently divided away.

\begin{theorem}[low-complexity atom extraction]\label{thm:atom-extraction}
Assume $L\ge2$.  Let
\[
 d=m-k
\]
and fix an integer $0\le s\le d$.  If
\[
 \boxed{
 \chi(\cS)<2m+s+3,
 }
\]
then the explanations admit a scalar-locator certificate of denominator degree at most $s$.

More precisely, one of the following holds:
\begin{enumerate}[label=\textup{(\roman*)}]
\item the codeword explanations are globally affine;
\item they lie in a pure locator pencil;
\item they form a rational atom, possibly with a denominator-root degeneracy on $D$.
\end{enumerate}
\end{theorem}

\begin{proof}
Use as unknowns the coefficients of
\[
 Q\in\F[X]_{\le s},
 \qquad
 A,B\in\F[X]_{\le m}.
\]
There are
\[
 (s+1)+2(m+1)=2m+s+3
\]
unknowns.

At a coordinate $x$ with $r_x\ge2$, impose the two homogeneous linear equations
\[
 A(x)=Q(x)r_0(x),
 \qquad
 B(x)=Q(x)r_1(x).
\]
At a singleton coordinate, with $I_x=\{i\}$, impose
\[
 A(x)+\gamma_iB(x)=Q(x)h_i(x).
\]
No equation is needed at an unoccupied coordinate.  The total number of equations is at most $\chi(\cS)$.  Under the strict inequality, the homogeneous system has a nonzero solution $(Q,A,B)$.

For every $i$ and every $x\in S_i$, the imposed equations give
\[
 A(x)+\gamma_iB(x)=Q(x)h_i(x).
\]
The polynomial
\[
 P_i:=A+\gamma_iB-Qh_i
\]
has degree at most $m$ because
\[
 \deg(Qh_i)\le s+k-1\le m-1.
\]
It vanishes on the $m$ distinct roots of $\Lambda_i$, so
\[
 P_i=c_i\Lambda_i
\]
for a scalar $c_i$.  Comparing coefficients of $X^m$ gives
\[
 c_i=[X^m]A+\gamma_i[X^m]B,
\]
which is affine in $\gamma_i$.  This is the required certificate.

If $Q=0$, nontriviality and two distinct slopes rule out $c_0=c_1=0$, so the certificate is a pure locator pencil.  If $Q\ne0$ but $c_0=c_1=0$, then
\[
 Qh_i=A+\gamma_iB.
\]
Using two slopes shows $Q$ divides both $A$ and $B$, and cancellation gives a global affine codeword line.  The remaining case is a rational atom.
\end{proof}

\begin{remark}[relation to rational-function interpolation]
The proof is a support-collapsed Berlekamp--Welch argument: it interpolates only the two received-line coefficients on multiply occupied coordinates, rather than imposing a separate condition for every support incidence.  This is compatible with the rational-function and curve-decoding viewpoint in recent proximity-gap work \cite{BSCHKS25,GG26}, but the theorem above is elementary and finite; no random-evaluation or asymptotic result is imported.
\end{remark}

\begin{corollary}[full denominator profile]\label{cor:full-profile}
Taking $s=d=m-k$, every explanation with
\[
 \boxed{
 \chi(\cS)<3m-k+3
 }
\]
is globally affine, a pure locator pencil, or a scalar-locator rational atom of denominator degree at most $m-k$.
\end{corollary}

\begin{corollary}[support-union form]\label{cor:union-form}
If
\[
 2u-N_1<3m-k+3,
\]
then the same alternatives hold.  In particular, it suffices that
\[
 u\le\floor{\frac{3m-k+2}{2}}.
\]
\end{corollary}

\begin{corollary}[exact deployed extraction thresholds]\label{cor:active-extraction}
For the active $32$-tuples, put
\[
 \Xi:=3m-k+3.
\]
Then
\[
\begin{array}{c|r|r|r|r}
\toprule
\text{row}&\Xi&2n-\Xi&\text{automatic union ceiling}&\text{union nullity ceiling}\\
\midrule
\text{KoalaBear MCA}&2299571&1894733&1149785&101209\\
\text{Mersenne-31 MCA}&2299499&1894805&1149749&101173\\
\bottomrule
\end{array}
\]
where the last column subtracts $n-k=1048576$ from the union ceiling.

Equivalently, extraction is automatic if
\[
 2N_0+N_1\ge1894734
\]
on KoalaBear, or if
\[
 2N_0+N_1\ge1894806
\]
on Mersenne-31.
\end{corollary}

These are classification thresholds, not challenge-numerator payments.  Their use is to show that a large low-complexity support family belongs to one atom instead of being charged as many unrelated cells.

\section{The degree-two counterexample lies at the extraction threshold}

The degree-two $\F_{17}$ example of \cref{thm:f17-atom} has
\[
 n=8,
 \qquad k=4,
 \qquad m=6,
 \qquad L=5.
\]
Its five listed supports are maximal.  Their incidence multiplicities are
\[
 (5,3,3,5,4,3,4,3),
\]
so
\[
 \chi=16
 \quad\text{while}\quad
 3m-k+3=17.
\]
Thus \cref{thm:atom-extraction} forces a denominator of degree at most
\[
 d=m-k=2,
\]
which is exactly the minimal degree established by \cref{thm:f17-atom}.

The common support has size $c=2$.  The coefficientwise slope interpolation of the five codewords has degree $r=4$, and
\[
 \ceil{\frac{5(6-2)}{8-2}}=4.
\]
Hence the example also attains equality in \cref{thm:slope-degree}.  The counterexample is therefore not an unexplained accident: it sits simultaneously on the common-support slope-degree boundary and the low-complexity rational-extraction boundary.

\section{Collision pencils for two atom certificates}

Suppose the same indexed explanations
\[
 (\gamma_i,h_i,\Lambda_i),
 \qquad i\in I,
\]
satisfy two nontrivial scalar-locator certificates
\[
 Qh_i+(c_0+c_1\gamma_i)\Lambda_i=A+\gamma_iB,
\]
\[
 Q'h_i+(c'_0+c'_1\gamma_i)\Lambda_i=A'+\gamma_iB'.
\]
Assume $|I|\ge2$, $Q,Q'\ne0$, and both scalar pairs are nonzero.  Define
\[
\begin{aligned}
 P_0&:=Q'c_0-Qc'_0,
 &P_1&:=Q'c_1-Qc'_1,\\
 R_0&:=Q'A-QA',
 &R_1&:=Q'B-QB'.
\end{aligned}
\]
Eliminating $h_i$ gives the collision identity
\[
 \boxed{
 (P_0+\gamma_iP_1)\Lambda_i
 =R_0+\gamma_iR_1.
 }
\]

Let
\[
 G:=\{x\in D:R_0(x)=R_1(x)=0\},
 \qquad g:=|G|,
\]
and
\[
 H:=\{x\in G:P_0(x)=P_1(x)=0\},
 \qquad h:=|H|.
\]

\begin{theorem}[atom collision rigidity]\label{thm:collision-rigidity}
If $R_0=R_1=0$ and the certificates share at least two distinct slopes, then the certificates are projectively identical.

Otherwise, if $g<m$, then
\[
 \boxed{
 |I|\le\floor{\frac{n-g}{m-g}}.
 }
\]
Moreover, every coordinate in $G\setminus H$ belongs to at least $|I|-1$ of the supports $S_i$.

If both denominators have degree at most $d$, then two distinct certificates satisfy
\[
 h\le d.
\]
\end{theorem}

\begin{proof}
First suppose $R_0=R_1=0$.  Then
\[
 (P_0+\gamma_iP_1)\Lambda_i=0
\]
as a polynomial.  Since $\Lambda_i\ne0$, two distinct slopes imply $P_0=P_1=0$.  Thus
\[
 Q'(c_0,c_1)=Q(c'_0,c'_1).
\]
Choose a nonzero component of $(c_0,c_1)$.  Because $Q,Q'\ne0$, this identity gives a scalar $\lambda\in\F^\times$ with
\[
 Q'=\lambda Q,
 \qquad
 (c'_0,c'_1)=\lambda(c_0,c_1).
\]
The equations $R_0=R_1=0$ then give
\[
 A'=\lambda A,
 \qquad B'=\lambda B.
\]
So the certificates are projectively identical.

Now assume $(R_0,R_1)\ne(0,0)$.  At every root of $\Lambda_i$,
\[
 R_0(x)+\gamma_iR_1(x)=0.
\]
After removing the at most $g$ roots in $G$, each $S_i$ contributes at least $m-g$ incidences.  At a coordinate outside $G$, the affine equation
\[
 R_0(x)+\gamma R_1(x)=0
\]
has at most one slope solution.  Hence
\[
 |I|(m-g)\le n-g,
\]
which proves the bound.

For $x\in G\setminus H$, the polynomial
\[
 P_0(x)+\gamma P_1(x)
\]
is a nonzero affine function of $\gamma$ and therefore vanishes at at most one of the shared slopes.  The collision identity then forces $\Lambda_i(x)=0$ for all other $i$, proving the near-sunflower assertion.

Finally, if the certificates are distinct, then $(P_0,P_1)\ne(0,0)$ by the first part.  Both have degree at most $d$, so their common root set in $D$ has size at most $d$.
\end{proof}

\begin{corollary}[primitive atom uniqueness]\label{cor:primitive-unique}
If $G=\varnothing$, two distinct atom certificates share at most
\[
 \floor{\frac nm}=1
\]
explanation at either deployed row.  Thus two primitive certificates sharing two slopes are projectively identical.
\end{corollary}

\section{Affine lines versus rational atoms}

A similar argument prevents a primitive rational atom from masquerading as a global affine codeword line.

\begin{theorem}[affine--atom collision]\label{thm:affine-atom}
Suppose $h_i=A_0+\gamma_iB_0$ for $i\in I$, and the same explanations satisfy a nontrivial atom certificate
\[
 Qh_i+(c_0+c_1\gamma_i)\Lambda_i=A+\gamma_iB,
 \qquad (c_0,c_1)\ne(0,0).
\]
Put
\[
 E_0:=A-QA_0,
 \qquad
 E_1:=B-QB_0,
\]
and let
\[
 G_{\rm aff}:=\{x\in D:E_0(x)=E_1(x)=0\},
 \qquad g_{\rm aff}:=|G_{\rm aff}|.
\]
If $|I|\ge2$, then $(E_0,E_1)\ne(0,0)$, and if $g_{\rm aff}<m$,
\[
 \boxed{
 |I|\le\floor{\frac{n-g_{\rm aff}}{m-g_{\rm aff}}}.
 }
\]
Every point of $G_{\rm aff}$ belongs to at least $|I|-1$ supports.
In particular, a primitive atom and a global affine line share at most one explanation.
\end{theorem}

\begin{proof}
Substitution gives
\[
 (c_0+c_1\gamma_i)\Lambda_i=E_0+\gamma_iE_1.
\]
If $E_0=E_1=0$, then $c_0+c_1\gamma_i=0$ for every $i$, since $\Lambda_i\ne0$.  A nonzero affine function of the slope has at most one root, contradicting $|I|\ge2$.

The root-incidence count for the pencil $E_0+\gamma E_1$ is identical to the proof of \cref{thm:collision-rigidity}.  At a common fixed root, all supports except possibly the unique slope with $c_0+c_1\gamma=0$ contain the coordinate.
\end{proof}

\section{Coherence or a quantified near-sunflower}

The graph whose vertices are the $32$-subsets of a fixed slope set and whose edges join subsets with $31$ common slopes is connected.  Collision rigidity can therefore propagate a local classification globally.

\begin{theorem}[order-$32$ coherence]\label{thm:coherence}
Let $Z$ be a set of at least $32$ bad slopes.  Suppose every $32$-subset of the corresponding explanations is classified as either
\begin{enumerate}[label=\textup{(\alph*)}]
\item one global affine codeword line, or
\item one nontrivial scalar-locator rational atom of denominator degree at most $d=m-k$.
\end{enumerate}
Assume all cross-fixed sets arising between distinct local classifications have already been removed by the first-match rule.  Then the entire set $Z$ lies on one global affine codeword line or in one projective rational atom certificate.
\end{theorem}

\begin{proof}
Adjacent $32$-subsets share $31$ explanations.  Two affine codeword lines sharing two distinct slopes are identical.  By \cref{cor:primitive-unique}, two primitive atom certificates sharing two explanations are identical.  By \cref{thm:affine-atom}, a primitive atom and an affine line cannot share two explanations.  Therefore adjacent vertices of the $32$-subset graph receive the same type and the same structure.  Connectedness propagates that structure to every $32$-subset and hence to every explanation in $Z$.
\end{proof}

Without the primitive hypothesis, failure of coherence is not unstructured.

\begin{corollary}[exact near-sunflower alternative on a $31$-overlap]\label{cor:near-sunflower}
Suppose two distinct local classifications share $q=31$ explanations.  Then at least one classification is an atom, and their cross-fixed set has size at least
\[
 g_{31}:=\ceil{\frac{31m-n}{30}}.
\]
For two rational atoms, at least $g_{31}-d$ of those coordinates belong to at least $30$ of the $31$ supports.  For an affine-line/atom collision, all $g_{31}$ fixed coordinates have that property.

At the deployed rows,
\[
\begin{array}{c|r|r|r}
\toprule
\text{row}&g_{31}&d=m-k&g_{31}-d\\
\midrule
\text{KoalaBear MCA}&1083345&67472&1015873\\
\text{Mersenne-31 MCA}&1083320&67448&1015872\\
\bottomrule
\end{array}
\]
Thus every failure of local atom coherence produces a $30$-of-$31$ near-sunflower on more than one million domain coordinates.
\end{corollary}

\begin{proof}
Rearrange the collision inequality
\[
 31(m-g)\le n-g
\]
to obtain
\[
 g\ge\ceil{\frac{31m-n}{30}}.
\]
For two atoms, \cref{thm:collision-rigidity} gives a collision core $H$ of size at most $d$; every point outside it lies in at least thirty supports.  The affine--atom statement follows from \cref{thm:affine-atom}.
\end{proof}

For reference, if two classifications share all $32$ explanations, the corresponding fixed-root thresholds are
\[
\begin{array}{c|r|r}
\toprule
\text{row}&g_{32}=\ceil{(32m-n)/31}&g_{32}-d\\
\midrule
\text{KoalaBear MCA}&1084400&1016928\\
\text{Mersenne-31 MCA}&1084375&1016927\\
\bottomrule
\end{array}
\]

\section{The proved part of the relative order-\texorpdfstring{$32$}{32} theorem}

The results can now be stated as one relative classification theorem for the actual explanation vector, which is weaker than classifying every vector in the rank-two kernel but is sufficient for MCA.

\begin{theorem}[partial relative order-\texorpdfstring{$32$}{32} explanation theorem]\label{thm:partial-relative}
Fix either deployed adjacent MCA row and $32$ distinct bad slopes.  After maximalizing supports, removing their common-support branch, and selecting exact $m$-subsupports, any non-global-affine explanation outside the pure-locator, denominator-root, and scalar-locator rational-profile cells must satisfy both
\[
 \boxed{18\le\deg_ZE\le31}
\]
and
\[
 \boxed{\chi(\cS)\ge3m-k+3.}
\]
Numerically, the second inequality is
\[
 \chi(\cS)\ge2299571
 \quad\text{on KoalaBear},
\]
and
\[
 \chi(\cS)\ge2299499
 \quad\text{on Mersenne-31}.
\]

Moreover, if every residual $32$-subset is classified as affine or rational, then either all bad slopes belong to one coherent structure or a $31$-overlap enters the quantified near-sunflower branch of \cref{cor:near-sunflower}.
\end{theorem}

\begin{proof}
The slope-degree statement is \cref{cor:degree-18}.  The incidence-complexity statement is the contrapositive of \cref{cor:full-profile}.  The coherence alternative follows from \cref{thm:coherence,cor:near-sunflower}.
\end{proof}

This proves the relative theorem in two substantial regimes:
\begin{itemize}[leftmargin=2em]
\item low slope degree ($r\le17$) is impossible outside global-affine/common-support structure;
\item low two-cover complexity ($\chi<3m-k+3$) automatically produces a rational or pure-locator atom.
\end{itemize}
It also discharges the separate atom-coherence obligation once the near-sunflower first-match cell is applied.


\part{Primitive spread abundance and the exact MCA endgame}
\label{part:spread-endgame}
The rank and atom theorems reduce a large bad-slope set to one coherent global structure, except for a quantified exceptional set.  This part proves that universal spread exclusion is false, identifies the correct spread-abundance target, localizes rational atoms to a canonical owner, and bounds broad classes of spread-core corrections.

\section{A critical spread core exists}

A universal theorem excluding primitive spread critical tuples on dyadic domains would be stronger than the deployed abundance statement.  The following exact example shows that such a universal prohibition is false.

\begin{proposition}[exact dyadic critical spread core]\label{prop:f17-spread}
Let
\[
 \F=\F_{17},
 \qquad
 D=\F_{17}^{\times}=\langle3\rangle,
 \qquad
 n=16,
 \quad k=8,
 \quad m=10.
\]
The critical order is
\[
 L_*=\floor{\frac{2(n-k)}{m-k}}+1=9.
\]
There exist nine distinct slopes, nine codeword explanations, and exact size-$10$ witness supports with all of the following properties.
\begin{enumerate}[label=\textup{(\roman*)}]
\item The received pair is support-wise MCA-bad at agreement $10$.
\item The maximal agreement supports have empty common intersection.
\item The rank-two reduced intersection matrix has rank $55$, whereas full relative rank is $(9-2)8=56$.
\item The two-cover complexity is $32$, above the extraction threshold of \cref{cor:full-profile} $3m-k+3=25$.
\item The incidence pattern is not periodic at any nontrivial level of the dyadic tower.
\item There is no scalar-locator certificate with denominator degree $0$, $1$, or $2=m-k$.
\item The coefficientwise slope interpolation has degree $8$, above the common-support-free lower barrier $\ceil{9m/n}=6$.
\item The direction code contains a word of weight $9=n-k+1$, so the minimum-support excess is exactly one.
\end{enumerate}
Moreover, for this same received line every slope in $\F_{17}$ has a degree-$<8$ codeword agreeing on at least ten coordinates.
\end{proposition}

\begin{proof}[Exact certificate]
Order the domain as
\[
 (1,3,9,10,13,5,15,11,16,14,8,7,4,12,2,6).
\]
Use slopes $\gamma_i=i$ for $0\le i\le8$ and the following exact size-$10$ supports, written by domain indices:
\[
\begin{array}{c|l}
\toprule
 i&S_i\\
\midrule
0&0,3,4,5,7,9,10,11,12,13\\
1&1,3,5,6,7,10,11,12,13,14\\
2&1,4,6,7,9,10,11,12,13,15\\
3&0,1,2,4,5,6,7,9,14,15\\
4&0,2,3,4,5,6,7,9,12,13\\
5&0,3,4,5,6,7,8,9,10,14\\
6&1,2,3,5,6,8,9,11,13,15\\
7&0,3,4,5,6,7,11,12,14,15\\
8&2,3,4,5,6,7,8,9,10,14\\
\bottomrule
\end{array}
\]
The codeword coefficient vectors, constant coefficient first, are
\[
\begin{array}{c|rrrrrrrr}
\toprule
 i&1&X&X^2&X^3&X^4&X^5&X^6&X^7\\
\midrule
0&1&13&16&16&9&16&7&12\\
1&13&9&14&12&6&4&2&13\\
2&2&2&2&4&2&12&0&1\\
3&13&3&3&4&0&13&16&5\\
4&1&4&11&4&2&16&9&16\\
5&16&13&15&13&2&15&5&7\\
6&3&3&0&13&0&8&12&4\\
7&3&2&6&8&10&13&10&12\\
8&1&12&2&14&9&10&9&4\\
\bottomrule
\end{array}
\]
and the received coefficient words on the ordered domain are
\[
\begin{aligned}
 r_0&=(5,16,0,0,0,0,0,0,5,7,8,0,8,10,0,6),\\
 r_1&=(6,14,15,0,0,0,2,13,14,12,6,3,15,13,6,15).
\end{aligned}
\]
Direct substitution verifies every claimed support.  Maximalizing the nine supports gives sizes $10$ or $11$ and empty total intersection.

For the rank statement, form the rank-two matrix of \cref{def:r2rim}.  It has $58$ rows and $72$ columns.  The displayed explanation vector supplies one kernel direction independent of the $16$-dimensional global-affine kernel, so its rank is at most $55$; exact Gaussian elimination over $\F_{17}$ gives rank $55$.  The scalar-locator systems at denominator degrees $0,1,2$ have column counts and ranks
\[
 (25,25),\qquad(26,26),\qquad(27,27),
\]
respectively.  Exact interpolation gives slope degree $8$, and direct evaluation of all pairwise codeword differences gives minimum weight $9$.

Finally, exhaustive interpolation over the $\binom{16}{10}$ candidate common supports finds no ten-coordinate support on which both $r_0$ and $r_1$ are degree-$<8$ evaluations.  Enumerating the $\binom{16}{8}$ interpolation bases at each of the seventeen slopes finds at least one agreement-$10$ codeword for every slope.  The accompanying verifier repeats all calculations in exact arithmetic.
\end{proof}

\begin{remark}[what the example does and does not refute]\label{rem:counter-scope}
The example refutes the \emph{universal} prohibition of primitive spread critical tuples.  It does not refute a row-sharp theorem for the two deployed length-$2^{21}$ domains.  It also shows why the minimum-distance refinement is relevant but not by itself decisive: the hard spread core lies exactly in the support-excess-$1$ branch, the same branch in which the boundary top seam survives by \cref{cor:top-seam-localization}.
\end{remark}

\section{The deployed spread-abundance target}

\begin{definition}[first-match primitive spread core]\label{def:spread-core}
A set of $32$ explanations is a \emph{first-match primitive spread core} if it satisfies the residual conditions of \cref{thm:partial-relative}: no global affine codeword line, common-support factor, exact dyadic quotient descent, scalar-locator certificate of denominator degree at most $m-k$, denominator-root, extension, tangent, field-drop, or quantified near-sunflower atom; slope degree lies between $18$ and $31$; and two-cover complexity is at least $3m-k+3$.
\end{definition}

A universal nonexistence theorem is false by \cref{prop:f17-spread}.  The finite MCA theorem requires the weaker and more natural abundance statement.

\begin{problem}[deployed spread-abundance theorem]\label{prob:spread-abundance}
For either deployed domain, prove that if a support-wise MCA-bad received line contains one first-match primitive spread core, then its total number of bad challenge slopes is at most the row budget $B^*$.

A stronger useful form would bound the number of slopes extending a fixed core by a quantity below $B^*-32$, with every failure routed to one canonical quotient, extension, rational-owner, clone, or near-sunflower certificate.
\end{problem}

\begin{remark}
The distinction is essential.  The finite theorem does not need local higher-order-MDS rank at every critical tuple.  It needs a global statement that a line carrying one genuine spread defect cannot carry too many further slopes.  The exact example in \cref{prop:f17-spread} shows that any proof must use the deployed domain and field geometry, not only the abstract critical-order dimension count.
\end{remark}

\section{Rational atoms have a canonical owner}

Consider one coherent rational atom certificate
\begin{equation}\label{eq:atom}
 Qh_i+(c_0+c_1\gamma_i)\Lambda_i=A+\gamma_iB,
 \qquad i\in I,
\end{equation}
where $\Lambda_i$ is the locator of a witness support $S_i$, $|S_i|\ge m$, and $Q$ has no root on $D$.  Put
\[
 \widetilde r_0(x)=\frac{A(x)}{Q(x)},
 \qquad
 \widetilde r_1(x)=\frac{B(x)}{Q(x)}.
\]
The line
\[
 \widetilde r_\gamma=\widetilde r_0+\gamma\widetilde r_1
\]
is the \emph{owner line} of the atom.

\begin{definition}[fixed owner set]\label{def:owner-set}
Define
\[
 G=\{x\in D:r_0(x)=\widetilde r_0(x),\ r_1(x)=\widetilde r_1(x)\},
 \qquad g=|G|.
\]
\end{definition}

\begin{theorem}[exclusive rational-owner localization]\label{thm:owner-localization}
Retain \eqref{eq:atom} and assume every scalar $c_0+c_1\gamma_i$ is nonzero; zero-scalar slopes are a separate global-affine degeneracy and contribute at most one slope.  Then:
\begin{enumerate}[label=\textup{(\alph*)}]
\item for every $x\in D\setminus G$, at most one support $S_i$ contains $x$;
\item if $g<m$, then
\[
 \boxed{
 |I|\le\floor{\frac{n-g}{m-g}}\le n-m+1;
 }
\]
\item if $g\ge m$, at most $n-g$ supports meet $D\setminus G$, while the supports contained in $G$ form a support-wise MCA-bad instance for the punctured code
\[
 C|_G\cong\RS[\F,G,k].
\]
Consequently
\[
 \boxed{
 |I|\le n-g+\Bbad(\RS[\F,G,k],m).
 }
\]
\end{enumerate}
\end{theorem}

\begin{proof}
On $S_i$, the locator vanishes, and \eqref{eq:atom} gives
\[
 h_i(x)=\widetilde r_0(x)+\gamma_i\widetilde r_1(x).
\]
Since $S_i$ is also an agreement support for the original received line,
\[
 (r_0-\widetilde r_0)(x)
 +\gamma_i(r_1-\widetilde r_1)(x)=0.
\]
For $x\notin G$ this is a nonzero affine equation in $\gamma_i$, hence has at most one solution.  This proves (a).

If $g<m$, every support uses at least $m-g$ coordinates outside $G$.  By (a), those outside incidences are disjoint across slopes, so
\[
 |I|(m-g)\le n-g.
\]
The quotient $(n-g)/(m-g)$ is increasing for $g<m$, and at $g=m-1$ equals $n-m+1$.  This proves (b).

Now assume $g\ge m$.  Distinct supports meeting $D\setminus G$ use disjoint nonempty outside-coordinate sets, so there are at most $n-g$ of them.  Every remaining support lies in $G$ and witnesses the punctured owner line there.  Since $g\ge m>k$, evaluation on $G$ is injective and the punctured code is Reed--Solomon of dimension $k$.  If the punctured pair admitted a common size-$m$ explaining support, the same support would explain the original pair on $D$, contradicting support-wise MCA-badness.  The contained slopes are therefore bounded by the punctured MCA numerator.
\end{proof}

\begin{corollary}[all small-owner atoms are paid]\label{cor:small-owner}
For either deployed row, every coherent rational atom with
\[
 g\le2m-k
\]
has at most $n$ bad slopes.  Explicitly, the paid owner ranges are
\[
\begin{array}{c|r|r}
\toprule
\text{row}&2m-k&\text{atom bound}\\
\midrule
\text{KoalaBear MCA}&1183520&2097152\\
\text{Mersenne-31 MCA}&1183472&2097152\\
\bottomrule
\end{array}
\]
Both fit their challenge budgets; on Mersenne-31 the exact residual margin is
\[
 16777215-2097152=14680063.
\]
\end{corollary}

\begin{proof}
The case $g<m$ is \cref{thm:owner-localization}(b).  For $m\le g\le2m-k$, the punctured error count is $g-m$ and
\[
 2(g-m)\le g-k.
\]
CAP25 v13.2 proves, by its half-distance pincer and unique-decoding correlated-agreement input, that the punctured MCA numerator is at most $g$ in this range \cite{CAP25v132}.  Apply \cref{thm:owner-localization}(c):
\[
 |I|\le(n-g)+g=n.
\]
\end{proof}

\section{A self-contained minimum-distance owner payment}

The corollary uses the half-distance proximity theorem of CAP25 v13.2.  The next statement is elementary and retains the actual minimum support of the punctured direction code.

\begin{theorem}[triple-collapse from direction minimum support]\label{thm:triple-collapse}
Assume $g\ge m$ and restrict to the atom slopes whose supports lie in $G$.  Let
\[
 C'_G=\Span\{h_i-h_j:i,j\in I\}\subseteq\RS[\F,G,k]
\]
be their direction code.  If it is nonzero, write
\[
 d_1(C'_G)=g-k+a,
 \qquad a\ge1.
\]
If
\[
 \boxed{
 3m-2g\ge k-a+1,
 }
\]
then all contained codeword explanations lie on one global codeword line.  Hence the full atom, including supports meeting $D\setminus G$, satisfies
\[
 \boxed{|I|\le n-m+1.}
\]
Equivalently, this payment applies whenever
\[
 g\le\floor{\frac{3m-k+a-1}{2}}.
\]
\end{theorem}

\begin{proof}
For three distinct slopes define the affine deviation
\[
 p_{ijk}
 =(
 \gamma_j-\gamma_k)h_i
 +(\gamma_k-\gamma_i)h_j
 +(\gamma_i-\gamma_j)h_k.
\]
It belongs to $C'_G$.  On $S_i\cap S_j\cap S_k$, all three codewords equal the owner line at their slopes, so $p_{ijk}$ vanishes.  Inclusion--exclusion gives
\[
 |S_i\cap S_j\cap S_k|\ge3m-2g.
\]
A nonzero word of $C'_G$ has at most
\[
 g-d_1(C'_G)=k-a
\]
zeros.  Under the displayed hypothesis, $p_{ijk}$ must therefore be zero for every triple.

Fix two slopes.  The vanishing of every triple deviation shows that every $h_i$ lies on the same global codeword line $H_0+\gamma_iH_1$.  Let $C_0\subseteq G$ be the coordinate set on which this codeword line equals the owner line coefficientwise.  Support-wise MCA-badness gives $|C_0|<m$.  Outside $C_0$, equality of the two affine lines determines at most one slope.  Thus the contained slopes satisfy
\[
 |I_{\rm in}|(m-|C_0|)\le g-|C_0|,
 \qquad
 |I_{\rm in}|\le g-m+1.
\]
There are at most $n-g$ crossing supports by \cref{thm:owner-localization}, and hence
\[
 |I|\le(n-g)+(g-m+1)=n-m+1.
\]
\end{proof}

\begin{corollary}[exact support-excess-one thresholds]\label{cor:triple-active}
At $a=1$, \cref{thm:triple-collapse} pays owners through
\[
\begin{array}{c|r}
\toprule
\text{row}&\floor{(3m-k)/2}\\
\midrule
\text{KoalaBear MCA}&1149784\\
\text{Mersenne-31 MCA}&1149748\\
\bottomrule
\end{array}
\]
Larger direction support excess increases the threshold by one owner coordinate for every two units of excess.
\end{corollary}

\begin{remark}[connection with the minimum-distance sharpening of \cref{sec:min-distance-sharpening}]
For the boundary prefix dictionary, \cref{prop:exchange-defect} proves that a shift pair of exchange defect $r$ can occur only when $r\ge a$, where $a$ is the direction-code support excess; the top seam $r=1$ is therefore confined to $a=1$ .  The counterexample in \cref{prop:f17-spread} also has $a=1$.  Thus the difficult seam is now consistently localized: large $a$ is paid by the sharpened flag and owner bounds, while the exact-minimum-distance branch remains the genuine image-counting problem.
\end{remark}

\section{Owner pencils and a seven-point rich-incidence bound}

The exclusive atom theorem also requires control of competing owner certificates.  \Cref{thm:collision-rigidity} gives uniqueness once two slopes are shared.  The following theorem gives a complementary geometric bound when owners vary in a projective pencil.

Let
\[
 (Q_\tau,A_\tau,B_\tau)
 =(Q_0,A_0,B_0)+\tau(Q_1,A_1,B_1),
 \qquad \tau\in\mathbb P^1(\F),
\]
be a projective pencil of owner triples.  At a coordinate $x\in D$, set
\[
 F_x(\gamma,\tau)
 =A_\tau(x)+\gamma B_\tau(x)
 -Q_\tau(x)(r_0(x)+\gamma r_1(x)).
\]
This has bidegree at most $(1,1)$ on $\mathbb P^1_\gamma\times\mathbb P^1_\tau$.

\begin{theorem}[component-free owner-pencil rich points]\label{thm:owner-pencil}
Assume no $F_x$ is identically zero and no two coordinate curves $F_x=0$ share an irreducible component.  Then the number of parameter pairs $(\gamma,\tau)$ for which at least $m$ coordinate equations vanish is at most
\[
 \boxed{
 \floor{\frac{2\binom n2}{\binom m2}}
 =\floor{\frac{2n(n-1)}{m(m-1)}}.
 }
\]
For both deployed MCA rows this number is exactly $7$.
\end{theorem}

\begin{proof}
Two bidegree-$(1,1)$ curves with no common component have intersection number at most
\[
 (1,1)\cdot(1,1)=2
\]
on $\mathbb P^1\times\mathbb P^1$.  A parameter pair lying on at least $m$ coordinate curves contributes at least $\binom m2$ incidences with unordered coordinate-curve pairs.  Summing first over parameter pairs and then over the $\binom n2$ curve pairs gives
\[
 N_{\rm rich}\binom m2\le2\binom n2.
\]
The deployed integer evaluations are direct.
\end{proof}

\begin{remark}[the shared-component branches are explicit]
A nonzero bidegree-$(1,1)$ polynomial is either irreducible or factors into one vertical and one horizontal linear factor.  Hence a shared component is one of:
\begin{enumerate}[label=\textup{(\roman*)}]
\item a fixed-slope vertical component;
\item a fixed-owner horizontal component;
\item a common irreducible $(1,1)$ component, in which case the two coordinate equations are proportional and form a coordinate-clone cell.
\end{enumerate}
Identically zero $F_x$ are fixed owner coordinates.  Thus every failure of \cref{thm:owner-pencil} is already a named structural branch rather than an unpriced multiplicity.
\end{remark}

\section{The exact large-owner atom target}

After \cref{cor:small-owner}, only
\[
 g\ge2m-k+1
\]
remains for a coherent rational atom.  If at most $31$ exceptional slopes are reserved for the local-to-global first-match transition, \cref{thm:owner-localization} shows that the required bound for the owner-contained slopes is
\begin{equation}\label{eq:owner-target}
 \boxed{
 B_{\rm owner}(g)
 \le B^*-31-(n-g).
 }
\end{equation}

At the first unproved owner size and at $g=n$, the targets are
\[
\begin{array}{c|r|r|r}
\toprule
\text{row}&g_{\min}=2m-k+1&\text{target at }g_{\min}&\text{target at }g=n\\
\midrule
\text{KoalaBear MCA}&1183521&274980728110481425&274980728111395056\\
\text{Mersenne-31 MCA}&1183473&15863505&16777184\\
\bottomrule
\end{array}
\]
The Mersenne-31 row is binding.

For the full-owner boundary-prefix atom, use the CAP25 convention $K=k+1$ and $w=m-K$.  The average prefix-fiber sizes are
\[
 \overline F=\binom nm|\mathbb B|^{-w}.
\]
Their high-precision values and the full-owner multiplicative targets are
\[
\begin{array}{c|r|r|r}
\toprule
\text{row}&w&\log_2\overline F&(B^*-31)/\overline F\\
\midrule
\text{KoalaBear MCA}&67471&35.7352464170&4807520.929566\\
\text{Mersenne-31 MCA}&67447&20.7411470346&9.57219783037\\
\bottomrule
\end{array}
\]
Thus the exact remaining Mersenne theorem is a factor-$9.5722$ maximum-image or maximum-fiber statement before any additional cell consumes budget.  Owner localization has removed every smaller owner and all multi-owner component-free pencils, but it does not prove this full-owner prefix bound.

\begin{problem}[exclusive large-owner atom image bound]\label{prob:large-owner}
For every first-match coherent rational atom on either deployed domain with $g>2m-k$, prove \eqref{eq:owner-target}.  In the full-owner simple-pole branch it suffices to prove the row-sharp challenge-slope image bound
\[
 |\{U_z(\alpha)-\Lambda_M(\alpha):M\in\operatorname{Fib}_w(z)\}\cap\Gamma|
 \le B^*-31.
\]
For Mersenne-31, the stronger support-fiber estimate need only lose a factor below $9.57219783037$ from the exact average.
\end{problem}

\section{A conditional exact adjacent-row theorem}

We can now state the final certificate without reverting to a sum of many unrelated local budgets.

\begin{definition}[exception routing input]\label{def:exception-routing}
Say that exception routing holds if, for every bad received line with more than $31$ slopes, there is a set $E$ of at most $31$ slopes such that every remaining local order-$32$ classification is primitive and \cref{thm:coherence} applies; every denominator-root, extension, coordinate-clone, imperfect-quotient, and quantified near-sunflower failure is either included in $E$ or assigned to the spread-abundance or large-owner input with the same received-line owner retained.
\end{definition}

\begin{theorem}[exact conditional adjacent-row closure]\label{thm:conditional-final}
Fix one of the two deployed MCA rows.  Assume the following three inputs.
\begin{description}[leftmargin=3.4em,labelwidth=2.6em,style=nextline]
\item[\textup{(S)}] The deployed spread-abundance theorem, \cref{prob:spread-abundance}.
\item[\textup{(A)}] The exclusive large-owner atom image bound, \cref{prob:large-owner}.
\item[\textup{(E)}] Exception routing in the sense of \cref{def:exception-routing}.
\end{description}
Then
\[
 \boxed{\Bbad(C,m)\le B^*.}
\]
Together with the unconditional CAP25 v13.2 witness at agreement $m-1$, this proves that the row's exact adjacent MCA threshold is $m$.
\end{theorem}

\begin{proof}
Let $Z$ be the set of bad challenge slopes.  If $|Z|\le31$, the claim is immediate.  If $Z$ contains a primitive spread core, assumption (S) pays the whole line.

Otherwise remove the exceptional set $E$ supplied by exception routing.  Every $32$-subset of $Z\setminus E$ is classified by \cref{thm:partial-relative} as a global affine codeword line or one primitive rational atom.  The overlap graph of $32$-subsets is connected, and \cref{thm:collision-rigidity} forces one coherent global structure.

If that structure is a global affine codeword line, the standard coordinate-injection argument gives at most $n-m+1$ slopes.  Adding $|E|\le31$ remains far below either budget.

Suppose instead that it is one rational atom with owner-set size $g$.  For $g<m$, \cref{thm:owner-localization} gives at most $n-m+1$ atom slopes.  For $m\le g\le2m-k$, \cref{cor:small-owner} gives at most $n$.  Again the additional $31$ slopes fit both budgets.  Finally, for $g>2m-k$, there are at most $n-g$ crossing slopes and assumption (A), namely \eqref{eq:owner-target}, pays the contained slopes; adding the reserved $31$ gives exactly at most $B^*$.

CAP25 v13.2 already proves an unsafe witness at $m-1$, so safety at $m$ identifies the adjacent threshold.
\end{proof}

\section{Core interpolant and correction setup}

Let
\[
 C=\RS[\F,D,k],\qquad |D|=n,
\]
and let
\[
 r_\gamma=r_0+\gamma r_1\in\F^D
\]
be support-wise MCA-bad at agreement $m>k$.  Put
\[
 d=m-k,\qquad R=n-k,\qquad t=n-m.
\]
Fix one first-match primitive spread core in the sense of \cref{prob:spread-abundance}
\[
 (\gamma_i,h_i,S_i)_{i=1}^{32},
\]
where the slopes are distinct, $h_i\in\F[X]_{<k}$, and $S_i$ is the \emph{maximal} agreement support of $h_i$ with $r_{\gamma_i}$.  The common-support branch has already been removed, so
\begin{equation}\label{eq:no-common}
 \bigcap_{i=1}^{32}S_i=\varnothing.
\end{equation}

There is a unique coefficientwise interpolant
\begin{equation}\label{eq:H}
 H(X,Z)=\sum_{j=0}^{31}H_j(X)Z^j,
 \qquad H(X,\gamma_i)=h_i(X),
 \qquad \deg H_j<k.
\end{equation}
For $x\in D$ define
\begin{equation}\label{eq:Ex}
 E_x(Z)=H(x,Z)-r_0(x)-Zr_1(x)
\end{equation}
and
\[
 q_x=|\{i:x\in S_i\}|.
\]
Every core agreement contributes a root of $E_x$, so
\begin{equation}\label{eq:qsum}
 \sum_{x\in D}q_x=\sum_{i=1}^{32}|S_i|\ge32m.
\end{equation}
Moreover, \eqref{eq:no-common} and maximality imply
\begin{equation}\label{eq:nonzero-E}
 E_x\ne0\quad\text{for every }x\in D.
\end{equation}
Indeed, $E_x\equiv0$ would put $x$ in every maximal core support.

The deployed values are
\[
\begin{array}{c|r|r|r|r}
\toprule
\text{row}&m&d&n-m&B^*\\
\midrule
\text{KoalaBear MCA}&1116048&67472&981104&274980728111395087\\
\text{Mersenne-31 MCA}&1116024&67448&981128&16777215\\
\bottomrule
\end{array}
\]
with $n=2^{21}$ and $k=2^{20}$.

\section{Only fifty-eight slopes can use the core interpolant}

\begin{theorem}[core-compatible abundance bound]\label{thm:core-compatible}
Let $Z_0$ be the set of slopes $\gamma\in\F$ for which the codeword $H(X,\gamma)$ agrees with $r_\gamma$ on at least $m$ coordinates.  Then
\begin{equation}\label{eq:58}
 \boxed{
 |Z_0|\le\floor{\frac{31n}{m}}=58.
 }
\end{equation}
More precisely, outside the $32$ core slopes there are at most
\begin{equation}\label{eq:26}
 \boxed{
 \floor{\frac{31n-32m}{m}}=26
 }
\end{equation}
additional core-compatible slopes on either deployed row.
\end{theorem}

\begin{proof}
By \eqref{eq:nonzero-E}, every $E_x$ has at most $31$ roots.  A slope in $Z_0$ contributes at least $m$ coordinate roots, hence
\[
 |Z_0|m\le\sum_{x\in D}\deg E_x\le31n,
\]
which proves \eqref{eq:58}.

For a non-core slope, every agreement coordinate consumes a root distinct from the $q_x$ core roots already present at $x$.  The remaining root capacity is at most
\[
 \sum_x(31-q_x)\le31n-32m
\]
by \eqref{eq:qsum}.  Dividing by $m$ gives \eqref{eq:26}.
\end{proof}

\begin{remark}
The theorem uses maximal supports only to exclude identically zero coordinate error polynomials.  It is independent of quotient, rational-owner, or minimum-distance estimates.  Thus any over-budget spread line must obtain essentially all of its extra slopes from nonzero codeword corrections to $H$.
\end{remark}

\section{An unconditional theorem for one complete correction ray}

Fix a nonzero $P\in\F[X]_{<k}$.  Consider all parameter pairs $(\gamma,c)$ for which
\begin{equation}\label{eq:rayword}
 h_{\gamma,c}(X)=H(X,\gamma)+cP(X)
\end{equation}
agrees with $r_\gamma$ on at least $m$ coordinates.  At $x\in D$ the agreement equation is
\begin{equation}\label{eq:raycurve}
 E_x(\gamma)+cP(x)=0.
\end{equation}
No component-freeness assumption will be imposed.

For $P(x)\ne0$, put
\[
 f_x(Z)=\frac{E_x(Z)}{P(x)}\in\F[Z]_{\le31}.
\]
Coordinates with the same $f_x$ form a \emph{clone class}.  Coordinates with $P(x)=0$ form the vertical class.

\begin{lemma}[clone-class dichotomy]\label{lem:clone}
Let $C_f=\{x:P(x)\ne0,\ f_x=f\}$.  Then exactly one of the following holds.
\begin{enumerate}[label=\textup{(\roman*)}]
\item $|C_f|\le k-1$;
\item the codeword curve
\[
 G_f(X,Z)=H(X,Z)-f(Z)P(X)
\]
has slope degree at most one.  In this case the graph $c=-f(\gamma)$ is a global affine codeword line.
\end{enumerate}
At most two clone classes of type \textup{(ii)} can have size at least $k$.
\end{lemma}

\begin{proof}
For every $x\in C_f$,
\[
 G_f(x,Z)=r_0(x)+Zr_1(x)
\]
as a polynomial identity in $Z$.  If $G_f$ has a nonzero coefficient of $Z^j$ for some $j\ge2$, that coefficient is a nonzero degree-$<k$ polynomial vanishing on $C_f$, so $|C_f|\le k-1$.  Otherwise $G_f=A_f+ZB_f$ is a global affine codeword line.

Clone classes are disjoint subsets of $D$.  A class of type (ii) not covered by (i) has at least $k$ coordinates.  Since $n=2k$, there can be at most two.
\end{proof}

\begin{lemma}[global affine-line block]\label{lem:affine-block}
For any fixed global codeword line $A+\gamma B$, the number of slopes for which it agrees with $r_\gamma$ on at least $m$ coordinates is at most
\begin{equation}\label{eq:affinecost}
 n-m+1.
\end{equation}
\end{lemma}

\begin{proof}
Let $C_0$ be the coordinate set on which $A=r_0$ and $B=r_1$.  Support-wise MCA-badness gives $|C_0|<m$.  Outside $C_0$, agreement of the two affine lines determines at most one slope.  Hence
\[
 N(m-|C_0|)\le n-|C_0|,
\]
and the right quotient is maximized at $|C_0|=m-1$.
\end{proof}

\begin{theorem}[complete correction-ray bound]\label{thm:ray}
For either deployed row, the number of rich parameter pairs $(\gamma,c)$ satisfying \eqref{eq:rayword} is at most
\begin{equation}\label{eq:raybound}
 \boxed{
 2(n-m+1)
 +\floor{\frac{31\binom n2}{(k-1)(m-k+1)}}.
 }
\end{equation}
The final fraction equals $963$ on both rows.  Thus one full correction ray contributes at most
\[
\begin{array}{c|r|r}
\toprule
\text{row}&\text{ray bound}&B^*-\text{ray bound}\\
\midrule
\text{KoalaBear MCA}&1963173&274980728109431914\\
\text{Mersenne-31 MCA}&1963221&14813994\\
\bottomrule
\end{array}
\]
In particular, a single correction ray can never be the residual spread-abundance obstruction.
\end{theorem}

\begin{proof}
Remove all rich points lying on a type-(ii) clone graph whose class has at least $k$ coordinates.  By \cref{lem:clone,lem:affine-block}, there are at most two such graphs and each contributes at most $n-m+1$ slopes.

Consider a remaining rich point and choose exactly $m$ of its agreement coordinates.  Partition them into the vertical class and the clone classes meeting the point.  The vertical class has size at most $k-1$, because a nonzero degree-$<k$ polynomial has at most $k-1$ zeros.  Every clone class present at the point has size at most $k-1$: type-(i) classes have this bound, while every larger type-(ii) graph was removed.

Since $m<2(k-1)$ on both rows, a partition of $m$ elements into parts of size at most $k-1$ has at least
\begin{equation}\label{eq:crosspairs}
 (k-1)(m-k+1)
\end{equation}
heterogeneous unordered pairs.  This is the minimum obtained from the two-part partition $(k-1,m-k+1)$.

A heterogeneous pair contributes to at most $31$ rich parameter points.  For two graph coordinates from different clone classes, the condition is
\[
 f_x(\gamma)=f_y(\gamma),
\]
a nonzero polynomial equation of degree at most $31$, after which $c$ is determined.  For one vertical and one graph coordinate, $E_x(\gamma)=0$ has at most $31$ roots and again the graph equation determines $c$.  We never count vertical--vertical pairs or pairs inside one clone class.

Double counting rich-point/heterogeneous-pair incidences gives
\[
 N_{\rm res}(k-1)(m-k+1)\le31\binom n2.
\]
Adding the at most two affine-line blocks proves \eqref{eq:raybound}.  Counting parameter pairs only overestimates the number of distinct slopes.
\end{proof}

\begin{remark}[minimum-support refinement]\label{rem:a-refine}
Suppose every nonzero codeword in the span of $P$ and the high slope coefficients $H_2,\ldots,H_{31}$ has support at least $R+a$.  Then $k-1$ in the proof can be replaced by $k-a$.  Writing $q=k-a$, the exact cross-pair denominator is
\[
 \Xi(m,q)=\binom m2-u\binom q2-\binom r2,
 \qquad m=uq+r,\quad0\le r<q,
\]
and there are at most $\floor{n/(q+1)}$ large affine clone classes.  In the active residual wedge $m\le2q$, so $\Xi(m,q)=q(m-q)$.  The exact-minimum-distance case $a=1$ is the worst case in the range left by the minimum-distance sharpening of \cref{sec:min-distance-sharpening}; the same section also proves that the boundary top seam occurs only at $a=1$.
\end{remark}

\section{Higher-dimensional correction spaces}

Let $W\le C$ have dimension $s$, and consider all rich points
\[
 (\gamma,P)\in\F\times W
\]
for which $H(X,\gamma)+P(X)$ agrees with $r_\gamma$ on at least $m$ coordinates.  Choose a basis $P_1,\ldots,P_s$ of $W$ and write $P=\sum c_jP_j$.  The coordinate equation
\begin{equation}\label{eq:hypersurface}
 F_x(Z,\mathbf c)=E_x(Z)+\sum_{j=1}^s c_jP_j(x)=0
\end{equation}
has bidegree at most $(31,1)$ on $\mathbb P^1_Z\times\mathbb P^s_{\mathbf c}$.

\subsection{The proper-intersection compiler}

\begin{definition}[proper correction space]
The correction space $W$ is \emph{proper for the core} if every $s+1$ coordinate hypersurfaces from \eqref{eq:hypersurface} have empty or zero-dimensional common intersection in $\mathbb P^1\times\mathbb P^s$.
\end{definition}

\begin{theorem}[proper-intersection correction compiler]\label{thm:proper}
If $W$ is proper for the core, then the number $N_W$ of rich parameter points satisfies
\begin{equation}\label{eq:proper}
 \boxed{
 N_W\le
 \floor{
 31(s+1)\frac{\binom n{s+1}}{\binom m{s+1}}
 }.
 }
\end{equation}
At the deployed rows this pays every proper correction space through
\[
\begin{array}{c|r|r|r}
\toprule
\text{row}&s\le&\text{bound at final }s&\text{bound at }s+1\\
\midrule
\text{KoalaBear MCA}&50&148068539552473273&283695391248936790\\
\text{Mersenne-31 MCA}&15&11989622&23938324\\
\bottomrule
\end{array}
\]
The next values only mark the limit of this compiler.
\end{theorem}

\begin{proof}
The divisor class of each projective hypersurface is at most
\[
 31H_Z+H_W.
\]
In the Chow ring of $\mathbb P^1\times\mathbb P^s$,
\[
 (31H_Z+H_W)^{s+1}=31(s+1)H_ZH_W^s,
\]
because $H_Z^2=0$ and $H_W^{s+1}=0$.  Hence every proper intersection of $s+1$ coordinate hypersurfaces has degree at most $31(s+1)$.

A rich point lies on at least $m$ hypersurfaces and therefore contributes at least $\binom m{s+1}$ incidences with coordinate $(s+1)$-subsets.  Summing first over rich points and then over the $\binom n{s+1}$ coordinate subsets proves \eqref{eq:proper}.
\end{proof}

\begin{lemma}[what a nonproper tuple means]\label{lem:nonproper}
Let $T$ be a set of $s+1$ coordinates.
\begin{enumerate}[label=\textup{(\roman*)}]
\item If the evaluation functionals of $T$ on $W$ have rank below $s$, then a nonzero word of $W$ vanishes on a subset spanning the same evaluation flat.
\item If their rank is $s$ and the common intersection is positive-dimensional, choose any evaluation basis $B\subset T$.  There is a unique polynomial curve $P_B(Z)\in W\otimes\F[Z]_{\le31}$ solving the equations on $B$, and every equation in $T$ vanishes identically on that curve.
\end{enumerate}
Thus every failure of properness is either an evaluation rank-flat or an exact polynomial clone component.
\end{lemma}

\begin{proof}
Part (i) is the annihilator statement for the column matroid of the evaluation map.  For (ii), the constant evaluation matrix on $B$ is invertible, so solving its equations gives $P_B(Z)$ coefficientwise and with degree at most $31$.  Substitution into the remaining equation gives a univariate polynomial.  A positive-dimensional intersection forces that polynomial to vanish identically.
\end{proof}

\subsection{A clone-tolerant basis-curve compiler}

Let
\[
 V=\Span(W,H_2,\ldots,H_{31})\le C
\]
and write
\begin{equation}\label{eq:a}
 d_1(V)=R+a,
 \qquad a\ge1.
\end{equation}
We say that $W$ \emph{absorbs the high core} if $H_j\in W$ for every $j\ge2$.

\begin{theorem}[clone-tolerant basis-curve bound]\label{thm:clone-tolerant}
Assume $s\ge1$ and that $W$ does not absorb the high core.  Put
\begin{equation}\label{eq:Ma}
 M_a=\floor{\frac{31(R+a)}{d+a}}.
\end{equation}
Then
\begin{equation}\label{eq:clone-tolerant}
 \boxed{
 N_W\le
 \floor{
 M_a\frac{\fall ns}{\rise{(d+a)}s}
 }.
 }
\end{equation}
No component-freeness assumption is required.
\end{theorem}

\begin{proof}
Fix a rich point and an exact size-$m$ agreement support $S$.  For every $j$-dimensional subcode $U\le W$, strict increase of generalized Hamming weights and \eqref{eq:a} give
\[
 |\supp_D(U)|\ge R+a+j-1.
\]
At most $t=n-m$ of these support coordinates lie outside $S$, so the restricted code $W|_S$ has
\[
 d_j(W|_S)\ge d+a+j-1.
\]
Greedily choosing independent evaluation columns therefore gives at least
\begin{equation}\label{eq:bases}
 \frac{\rise{(d+a)}s}{s!}
\end{equation}
unordered evaluation bases $B\subset S$.

For each such $B$, solve the basis equations to obtain a unique polynomial correction curve
\[
 P_B(Z)\in W\otimes\F[Z]_{\le31}.
\]
Let $C_B$ be the coordinates whose equations vanish identically after this substitution, and put $c_B=|C_B|$.  Since $W$ does not absorb all high core coefficients, the codeword curve $H+P_B$ has a nonzero coefficient of $Z^j$ for some $j\ge2$.  That coefficient lies in $V$, so it has at most $k-a$ zeros.  Hence
\begin{equation}\label{eq:clone-size}
 c_B\le k-a.
\end{equation}

Every rich point on the curve $P=P_B(\gamma)$ agrees automatically on $C_B$ and must obtain at least $m-c_B$ further agreements outside $C_B$.  Each outside coordinate supplies a nonzero polynomial equation of degree at most $31$.  Root-capacity counting on this one curve gives
\[
 N(B)(m-c_B)\le31(n-c_B).
\]
The quotient $(n-c)/(m-c)$ is increasing for $c<m$, and \eqref{eq:clone-size} yields
\[
 N(B)\le
 \floor{\frac{31(R+a)}{d+a}}=M_a.
\]

Each rich point is incident to at least \eqref{eq:bases} basis curves.  Globally there are at most $\binom ns$ evaluation bases, and each basis curve contains at most $M_a$ rich points.  Therefore
\[
 N_W\frac{\rise{(d+a)}s}{s!}
 \le M_a\binom ns
 =M_a\frac{\fall ns}{s!},
\]
which is \eqref{eq:clone-tolerant}.
\end{proof}

\begin{corollary}[exact deployed transitions]\label{cor:transitions}
At exact minimum support $a=1$, \cref{thm:clone-tolerant} pays through
\[
\begin{array}{c|r|r|r}
\toprule
\text{row}&s\le&\text{bound at final }s&\text{bound at }s+1\\
\midrule
\text{KoalaBear MCA}&9&13013823503882165&404431535289439486\\
\text{Mersenne-31 MCA}&3&14457337&449492838\\
\bottomrule
\end{array}
\]
The actual minimum-support excess enlarges the range.  The first exact paid transitions beyond those dimensions are
\[
\begin{array}{c|r|r|r|r}
\toprule
\text{row}&s&a_{\rm paid}&\text{bound at }a_{\rm paid}&\text{bound at }a_{\rm paid}-1\\
\midrule
\text{KoalaBear MCA}&10&2434&274948660791683460&274987992550612247\\
&11&25508&274953206296382843&274985734988552690\\
&12&50875&274977972290567960&275005854396152321\\
\text{Mersenne-31 MCA}&4&64258&16777099&16777608\\
\bottomrule
\end{array}
\]
All comparisons are exact integer comparisons with the row budgets.
\end{corollary}

\begin{remark}[relation to the minimum-distance wedge]
\Cref{prop:min-support-transitions} proves that the first-unpaid charts already satisfy $a\le70831$ on KoalaBear and $a\le111528$ on Mersenne-31 at zero outside mismatch, with positive mismatch shrinking the residual further.  It also confines the boundary top seam to $a=1$.  Thus \cref{cor:transitions} is not merely an abstract monotonicity statement: it removes correction dimensions $10$--$12$ on substantial parts of the KoalaBear wedge and dimension $4$ on a substantial part of the Mersenne wedge, while the genuine top-seam endpoint remains the exact-minimum-distance case.
\end{remark}

\section{The new spread residual}

\begin{theorem}[spread residual after core-relative incidence]\label{thm:residual}
Assume a deployed support-wise MCA-bad line contains a first-match primitive spread core and has more bad slopes than its row budget.  Then all of the following must hold.
\begin{enumerate}[label=\textup{(R\arabic*)}]
\item At most $58$ bad slopes use the core interpolant itself.
\item The remaining corrections are not contained in one projective correction ray.
\item If their linear correction span $W$ has dimension at most $50$ on KoalaBear or $15$ on Mersenne-31, then some $s+1$ coordinate equations have a positive-dimensional common component.
\item If $W$ does not absorb the high core, then its dimension and support excess lie beyond every transition in \cref{cor:transitions}.
\item Every low-dimensional surviving component is therefore an evaluation rank-flat or an exact polynomial clone component in the sense of \cref{lem:nonproper}; it is not an unstructured failure of Bezout counting.
\end{enumerate}
\end{theorem}

\begin{proof}
Items (R1)--(R4) are the contrapositives of \cref{thm:core-compatible,thm:ray,thm:proper,thm:clone-tolerant}.  Item (R5) is \cref{lem:nonproper}.
\end{proof}

The theorem changes the spread-abundance target.  It is no longer necessary to control arbitrary extensions of a core.  The only remaining spread mechanism is
\[
 \boxed{
 \begin{array}{c}
 \text{many projectively independent correction directions, together with}\\
 \text{a high-dimensional correction span or a positive-dimensional}\\
 \text{rank-flat/clone atlas surviving all first-match routes.}
 \end{array}
 }
\]

\begin{problem}[next spread theorem]\label{prob:next}
Prove that every positive-dimensional correction component from \cref{thm:residual} either
\begin{enumerate}[label=\textup{(\alph*)}]
\item yields a rational-owner, quotient, extension, field-drop, or quantified near-sunflower atom declared in \cref{thm:partial-relative,thm:owner-localization,cor:near-sunflower};
\item has correction directions contained in a bounded union of projective rays, so \cref{thm:ray} pays it; or
\item admits a proper quotient correction space to which \cref{thm:proper} or \cref{thm:clone-tolerant} applies.
\end{enumerate}
For Mersenne-31 it is enough that the total surviving spread contribution be at most $16{,}777{,}215$; for KoalaBear the available budget is much larger.
\end{problem}


\part{Completion certificates and remaining row-sharp inputs}
\label{part:completion}

\section{Integrated theorem status}
\label{sec:status-and-obligations}
\begin{theorem}[Audited theorem status]\label{thm:audited-status}
All statements explicitly presented as theorems, propositions, lemmas, or corollaries in Parts~I--VI are unconditional under their displayed hypotheses.  In particular, the paper proves the complete support and profile compiler, the minimum-distance flag sharpening, the primitive-Q/Sidon implication and its shallow unconditional range, saturation, one-pencil moving-root BC, Q $\Rightarrow$ SP, the order-$32$ rank dictionary, dyadic descent, rational-atom extraction and coherence, owner localization, the seven-point component-free owner-pencil bound, the $58$-slope core-compatible bound, the complete correction-ray bound, and the displayed proper and clone-tolerant correction-space payments.

No theorem in this paper proves either deployed adjacent MCA-safe row or either deployed adjacent list-safe row.  The open statements are exactly the problems recorded in \cref{prob:next,prob:large-owner,prob:mca-exception-routing,prob:list-completion}.
\end{theorem}

\section{The final MCA certificate}
\label{sec:mca-final-certificate}
The order-$32$ method replaces the old sum over many independently budgeted MCA cells by a maximum-type endgame.

\begin{problem}[Complete spread-component routing]\label{prob:mca-spread-routing}
Prove that every positive-dimensional correction component surviving \cref{thm:residual} is routed, with the same received-line owner retained, into one of the following disjoint outcomes:
\begin{enumerate}[label=\textup{(\alph*)}]
\item a rational-owner, quotient, extension, field-drop, or quantified near-sunflower atom;
\item a bounded union of complete projective correction rays paid by \cref{thm:ray};
\item a proper quotient correction space paid by \cref{thm:proper} or \cref{thm:clone-tolerant};
\item an explicitly named residual component with a literal row-sharp slope bound.
\end{enumerate}
The total spread contribution must fit the row budget.
\end{problem}

\begin{problem}[Complete MCA exception routing]\label{prob:mca-exception-routing}
Verify the exception-routing input of \cref{def:exception-routing}: denominator-root, extension, coordinate-clone, imperfect-quotient, and quantified near-sunflower failures must either be absorbed into the spread or large-owner bounds with a common owner retained, or occupy a set of at most $31$ slopes.
\end{problem}

\begin{theorem}[Exact MCA completion certificate]\label{thm:mca-completion-certificate}
Fix either deployed MCA row.  If \cref{prob:mca-spread-routing,prob:large-owner,prob:mca-exception-routing} are proved with the literal row constants in Parts~V--VI, then
\[
 B_{\rm MCA}(m)\le B^*.
\]
Together with the unsafe witness at agreement $m-1$ from CAP25 v13.2, the exact adjacent MCA threshold is $m$.
\end{theorem}

\begin{proof}
The hypotheses supply the spread-abundance and exception-routing inputs of \cref{thm:conditional-final}; \cref{prob:large-owner} supplies its atom input.  Apply that theorem and then the imported unsafe witness.
\end{proof}

\section{The final list certificate}
\label{sec:list-final-certificate}
For a list row retain the disjoint summed ledger
\begin{equation}
 U_{\rm list}
 =U_{\rm paid}+U_Q+U_{\rm list-int}+U_{\rm ext}+U_{\rm new}.
 \label{eq:list-final-ledger}
\end{equation}
Here $U_{\rm paid}$ is the exact first-match sum of all tangent, common-support, quotient, planted, field-drop, fixed-union, affine-span, common-zero, rank-flat, codimension-one, support-flag, minimum-distance, puncturing, and other certified cells; $U_Q$ is the row-sharp pruned boundary-prefix maximum; $U_{\rm list-int}$ is the high-nullity arbitrary-word interior codeword-ray term; $U_{\rm ext}$ is the exact extension projection payment; and $U_{\rm new}$ is zero unless an explicitly named residual cell survives.

\begin{problem}[Row-sharp list completion]\label{prob:list-completion}
For each deployed list row, prove exact integer bounds for the remaining high-nullity prefix fiber, arbitrary-word interior, and extension projection terms so that
\[
 U_{\rm list}\le B^*.
\]
The prefix estimate must use the actual residual mass and the exact budget left after the certified compiler cells are charged.
\end{problem}

\begin{theorem}[Exact summed completion certificate]\label{thm:exact-completion-certificate}
Fix one deployed list row.  If an exhaustive first-match compiler proves, with no unresolved cell,
\[
 U_{\rm list}\le B^*,
\]
then the first safe integer agreement is the adjacent row $a_0+1$.
\end{theorem}

\begin{proof}
CAP25 v13.2 proves the unsafe inequality at $a_0$.  Exhaustive first-match coverage and the displayed upper bound give safety at $a_0+1$.  Monotonicity identifies the first safe integer agreement.
\end{proof}

\section{Conclusion}\label{sec:conclusion}
This paper gives one unified Grande Finale manuscript.  It contains the exact threshold refinements, profile and Fourier compiler, primitive Q, support and minimum-distance recursions, saturation and moving-root geometry, the order-$32$ rank pivot, rational-atom extraction and coherence, owner localization, and the current spread-core incidence theory.

The remaining MCA problem has been compressed to three row-sharp inputs: route the positive-dimensional correction components isolated by \cref{thm:residual}, prove the large-owner image bound of \cref{prob:large-owner}, and complete the finite exception routing of \cref{prob:mca-exception-routing}.  The binding numerical atom target is the Mersenne-31 full-owner factor $9.57219783037$.  The remaining list problem is the exact high-nullity prefix/interior/extension sum of \cref{prob:list-completion}.  Until those inputs are proved, no adjacent safe row is claimed.

\begin{thebibliography}{99}
\bibitem[Cho26]{CAP25v132}
P. Chojecki,
\newblock Universal field-size caps and a two-sided sandwich for mutual correlated agreement on smooth Reed--Solomon domains,
\newblock Version 13.2, manuscript, July 2026.

\bibitem[BS94]{BalogSzemeredi}
A. Balog and E. Szemer\'edi,
\newblock A statistical theorem of set addition,
\newblock \emph{Combinatorica} 14 (1994), 263--268.

\bibitem[BGM23]{BGM23}
J. Brakensiek, S. Gopi, and V. Makam,
\newblock Generic Reed--Solomon codes achieve list-decoding capacity,
\newblock \emph{Proceedings of STOC 2023}; arXiv:2206.05256.

\bibitem[BCHKS25]{BSCHKS25}
E. Ben-Sasson, D. Carmon, U. Hab\"ock, S. Kopparty, and S. Saraf,
\newblock On proximity gaps for Reed--Solomon codes,
\newblock ECCC TR25-169, 2025.

\bibitem[GG25]{GG26}
R. Goyal and V. Guruswami,
\newblock Optimal proximity gaps for subspace-design codes and (random) Reed--Solomon codes,
\newblock ECCC TR25-166, 2025.

\bibitem[GGSW26]{GGSW26}
R. Goyal, V. Guruswami, Y. Sun, and M. Wootters,
\newblock Locality of curve-decoding and improved proximity gaps,
\newblock arXiv:2607.08516, 2026.

\bibitem[GMR+22]{GreenMatolcsiRuzsaShakanZhelezov}
B. Green, D. Matolcsi, I. Z. Ruzsa, G. Shakan, and D. Zhelezov,
\newblock A weighted Pr\'ekopa--Leindler inequality and sumsets with quasicubes,
\newblock in \emph{Analysis at Large}, Springer, 2022, 125--129.

\bibitem[LW10]{LiWanSieve}
J. Li and D. Wan,
\newblock A new sieve for distinct coordinate counting,
\newblock \emph{Sci. China Math.} 53 (2010), 2351--2362.

\bibitem[Tao10]{TaoEntropy}
T. Tao,
\newblock Sumset and inverse sumset theorems for Shannon entropy,
\newblock \emph{Combin. Probab. Comput.} 19 (2010), 603--639.

\bibitem[TV06]{TaoVu}
T. Tao and V. Vu,
\newblock \emph{Additive Combinatorics},
\newblock Cambridge University Press, 2006.

\bibitem[Gow98]{GowersSzemeredi}
W. T. Gowers,
\newblock A new proof of Szemer\'edi's theorem for arithmetic progressions of length four,
\newblock \emph{Geom. Funct. Anal.} 8 (1998), 529--551.

\bibitem[GMT23]{GreenMannersTao}
B. Green, F. Manners, and T. Tao,
\newblock Sumsets and entropy revisited,
\newblock arXiv:2306.13403, 2023.

\bibitem[Goh24]{GohEnergy}
M. K. Goh,
\newblock On an entropic analogue of additive energy,
\newblock arXiv:2406.18798, 2024.

\bibitem[MRSZ22]{MatolcsiRuzsaShakanZhelezov}
D. Matolcsi, I. Z. Ruzsa, G. Shakan, and D. Zhelezov,
\newblock An analytic approach to cardinalities of sumsets,
\newblock \emph{Combinatorica} 42 (2022), 203--236.

\bibitem[Wei48]{Weil}
A. Weil,
\newblock On some exponential sums,
\newblock \emph{Proc. Natl. Acad. Sci. USA} 34 (1948), 204--207.
\end{thebibliography}
\end{document}
